### 2016-03-12 Chapters/chap2/manuscript.tex
Initialize

% \documentclass[journal=jpcbfk,manuscript=article]{achemso}
% \usepackage[version=3]{mhchem} % Formula subscripts using \ce{}

% \usepackage{tikz}
% \usetikzlibrary{arrows}
% \usepackage{natbib}
% \usepackage{graphicx}% Include figure files
% \usepackage{animate}
% \usepackage{dcolumn}% Align table columns on decimal point
% \usepackage{bm}% bold math

% \usepackage{animate}
% \usepackage{subfloat}
% \usepackage{amsmath} % AMS Math Package
% \usepackage{amsthm} % Theorem Formatting
% \usepackage{amssymb}	% Math symbols such as \mathbb
% %\nofiles

% \renewcommand{\labelenumi}{(\alph{enumi})} % Use letters for enumerate
% % \DeclareMathOperator{\Sample}{Sample}
% \let\vaccent=\v % rename builtin command \v{} to \vaccent{}
% \renewcommand{\v}[1]{\ensuremath{\mathbf{#1}}} % for vectors
% \newcommand{\gv}[1]{\ensuremath{\mbox{\boldmath$ #1 $}}}
% % for vectors of Greek letters
% \newcommand{\uv}[1]{\ensuremath{\mathbf{\hat{#1}}}} % for unit vector
% \newcommand{\abs}[1]{\left| #1 \right|} % for absolute value
% \newcommand{\avg}[1]{\left< #1 \right>} % for average
% \let\underdot=\d % rename builtin command \d{} to \underdot{}
% \renewcommand{\d}[2]{\frac{d #1}{d #2}} % for derivatives
% \newcommand{\dd}[2]{\frac{d^2 #1}{d #2^2}} % for double derivatives
% \newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}}
% % for partial derivatives
% \newcommand{\pdd}[2]{\frac{\partial^2 #1}{\partial #2^2}}
% % for double partial derivatives
% \newcommand{\pdc}[3]{\left( \frac{\partial #1}{\partial #2}
%  \right)_{#3}} % for thermodynamic partial derivatives
% \newcommand{\ket}[1]{\left| #1 \right>} % for Dirac bras
% \newcommand{\bra}[1]{\left< #1 \right|} % for Dirac kets
% \newcommand{\braket}[2]{\left< #1 \vphantom{#2} \right|
%  \left. #2 \vphantom{#1} \right>} % for Dirac brackets
% \newcommand{\matrixel}[3]{\left< #1 \vphantom{#2#3} \right|
%  #2 \left| #3 \vphantom{#1#2} \right>} % for Dirac matrix elements
% \newcommand{\grad}[1]{\gv{\nabla} #1} % for gradient
% \let\divsymb=\div % rename builtin command \div to \divsymb
% \renewcommand{\div}[1]{\gv{\nabla} \cdot #1} % for divergence
% \newcommand{\curl}[1]{\gv{\nabla} \times #1} % for curl
% \let\baraccent=\= % rename builtin command \= to \baraccent
% \renewcommand{\=}[1]{\stackrel{#1}{=}} % for putting numbers above =

% %====commands for fermion operators =====
% %\newcommand{\cdup}[1]{c^\dagger_{#1\uparrow}}
% %\newcommand{\cdsig}[1]{c^\dagger_{#1\sigma}}
% %\newcommand{\cddown}[1]{c^\dagger_{#1\downarrow}}
% %\newcommand{\cup}[1]{c_{#1\uparrow}}
% %\newcommand{\csig}[1]{c_{#1\sigma}}
% %\newcommand{\cdown}[1]{c_{#1\downarrow}}
% %
% %
% %

% %%\listfiles

% \title{
% Intramolecular Charge and Energy Transfer Rates with Reduced Modes: Comparison to Marcus Theory for Donor-Bridge-Acceptor Systems
% }

% \author{Xunmo Yang}
% \affiliation{Department of Chemistry, University of Houston, Houston, TX 77204}

% \author{Eric R Bittner}
% \affiliation{Department of Chemistry, University of Houston, Houston, TX 77204}
% \phone{832-842-8849}
% \fax{713-743-2709}
% \email{bittner@uh.edu}

% \begin{document}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{abstract}
%  We present a new, fully {\em ab initio} approach for computing intramolecular charge and
% energy transfer rates.  Using a time-convolutionless master equation approach and parameterized
% using couplings obtained using an accurate quantum chemical approach, we  benchmark the approach
% against  experimental results and Marcus theory rates for triplet energy transfer for a
% series of donor-bridge-acceptor systems.
% An important component of our analysis is the use of a projection operator scheme
% that parses out specific internal nuclear motions that accompany
% the electronic transition.
% Using an iterative Lanczos approach, we  concentrate the coupling between the electronic and nuclear
% degrees of freedom into a small number of reduced harmonic modes.
% We find that  using only a single reduced mode--termed the ``primary mode'',
%  one obtains an accurate evaluation of the golden-rule rate constant and
% insight into the nuclear motions responsible for coupling the initial and final electronic states.
% In particular, the primary mode reflects the irreducible representation of the
% donor and acceptor excited states.
% \end{abstract}

% {\bf Keywords:} Quantum master equation, energy transfer rates, diabatic states,  triplet energy transfer

% \newpage
\chapter{Chapter 2}
\section{Introduction}
\label{sec:intro}

Energy and electronic transport plays a central role in a
wide range of  chemical  and biological systems.
It is the fundamental mechanism for transporting the  energy  of a
absorbed photon to a reaction center in light harvesting systems
and for initiating a wide range of photo-induced  chemical processes,
including vision, DNA mutation, and pigmentation.
The seminal model for calculating electron transfer rates was developed by
Marcus in the 1950's\cite{marcus1956theory,marcus1965theory,marcus1993electron}.
\begin{equation}
k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta\epsilon)^{2}/4\text{\ensuremath{\lambda}}k_{B}T}.\label{eq:marcus}
\end{equation}
where $\lambda$ is  energy required to reorganize the environment
following the transfer of an electron from donor to acceptor.
and $\Delta \epsilon$ is the driving force for the reaction.

\begin{figure}[b]
\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure1}
\caption{Sketch of Marcus parabolas for a model energy or charge transfer system.
Labeled are the key parameters used to compute the Marcus rate constant (Eq. 1).
Energies are given in eV and the collective nuclear displacement  is dimensionless.
}
\label{marcus}
\end{figure}

If we assume that the nuclear motions about the equilibrium configurations of the
donor and acceptor species is harmonic,  the chemical reactions resulting from
energy or charge transfer events can be understood in terms of intersecting
diabatic potentials as sketched in Fig.~\ref{marcus}.    The upper and lower
curves are the adiabatic potential energy surfaces describing the nuclear dynamics
resulting from an energy or charge transfer event, taking the geometry of the donor
state as the origin.
%For reactions carried out in open systems,  the Marcus parabolas represent
%free energy surfaces with driving force $\Delta G$.
As the transfer occurs by crossing an energy barrier,
the transfer rate can be expected to be in the Arrhenius form
\begin{eqnarray}
k\propto e^{-E_{A}/k_{B}T},
\end{eqnarray}
with $E_{A}$ as the activation energy.
 Using $E_{A}={(\lambda+\Delta \epsilon)^{2}}/{4\lambda}$
 we can relate the activation energy to both the reorganization energy and driving force, $-\Delta \epsilon$.
One of the most profound predictions of the theory is that  as the driving force increases,
the transfer rate reaches a maximum and further increases in the driving force
lead to lower reaction rates, termed the inverted regime.

We focus here on the rates of triplet exchange between a naphthalene donor and a benzaldehyde acceptor linked by a variety of bridging units.
\begin{center}
\includegraphics[width=0.50\columnwidth]{Chapters/chap2/Scheme1}
\end{center}
Triplet energy exchange in these systems occurs via the through-space Dexter mechanism\cite{Dexter:1952}.
This is a short-ranged interaction involving the simultaneous exchange of two electrons between the
donor and acceptor moieties.
Systems such as these formed the basis of a series of experiments by  Closs and Miller\cite{miller1984intramolecular}
in which they verified the existence of the Marcus inverted regime
and serve as crucial benchmarks for testing new theoretical models for computing
energy and charge transfer rates\cite{subotnik2008constructing,subotnik2009initial,Subotnik:2010}.

A number of years ago,  we developed a time-convolutionless  master equation approach for computing
state-to-state rates in which the coupling between  states depends upon the
nuclear coordinates\cite{pereverzev:104906}. This approach incorporates a fully quantum
mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
vibrational normal mode frequencies, and the electronic energies and energy derivatives
at a reference configuration.  The approach has been used by our group to compute state-to-state
transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
\cite{Tamura08,tamura:021103,Bittner:2014ab,Jaykrishna-Singh:2009ly}.
This paper represents the first time we have used this approach within the context of a fully {\em ab initio} quantum
chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
using state-of-the-art quantum chemical methods
and results compared to both theoretical and experimental
rates.

Central to the work presented here is the use of a diabatization scheme for determining
donor and acceptor states in a molecular unit.  We benchmark the approach
by computing the  triplet energy transfer rates for a series of donor-bridge-acceptor molecules
originally studied by Closs\cite{miller1984intramolecular}.  The triplet energy transfer rates computed using our approach
compare well against both the experimental rates and with
more recent theoretical rates presented by Subotnik {\em et al.}
\cite{subotnik2008constructing,subotnik2009initial,Subotnik:2010}.
An important component of our analysis is the use of a projection operator scheme
that parses out specific internal nuclear motions that accompany
the electronic transition.
Similar decomposition schemes have been presented by Burghardt
 \cite{Cederbaum:2005,gindensperger:144103,gindensperger:144104,PhysRevLett.94.113003}
 and the approach used here builds upon the method given in Ref.~\cite{pereverzev:034104}.
 By analyzing the electron-phonon couplings, we can
discern a reduced set of motions that are responsible for coupling between the donor and
acceptor states.

\section{Theoretical Approach}

\subsection{Model Hamiltonian}
We consider a generic model for $n$ electronic states coupled linearly
to a phonon bath.  Taking the electronic ground state of the system as a reference
and assuming that the electronic states are coupled linearly to a common set of
 modes, we arrive a generic form for the Hamiltonian:
 \begin{eqnarray}
H=\left(\begin{array}{cc}
\epsilon_{1} & 0\\
0 & \epsilon_{2}
\end{array}\right)+\left(\begin{array}{cc}
{\mathbf g}_{11}&{\mathbf g}_{12} \\
{\mathbf g}_{21} &{\mathbf g}_{22}
\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
\nonumber \\
\label{ham1}
\end{eqnarray}
Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
reference geometry--typically that of the donor or acceptor state.   The second term represents the
linearized coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
normal coordinates $\mathbf q$.   The diagonal terms
give the adiabatic displacement forces between the reference geometry and the two states.  If we choose one of the
states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish.
The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.

\begin{table*}[t]
\begin{centering}
\begin{tabular}{llccc|ccc}
\hline \hline
 & & \multicolumn{3}{c}{Rates (s$^{-1}$) }& \\
                &                                                                &   Expt.                 &        Marcus Theory   & This work      & \multicolumn{3}{c}{Marcus theory parameters} \\
 Bridge   &  Structure                                                &        Ref.~\cite{closs1988determination,closs1989connection} &              Ref. \cite{Subotnik:2010}  &                  &      $\lambda$ (eV)  &  $\Delta \epsilon$ (eV)  &  $V_{ab}$ ($\mu$eV) \\
\hline
 c-1,3ea  &  \includegraphics[height=.60cm]{Chapters/chap2/Table1-c13ea.pdf}  &                     3.3E9  &                     3.9E9  &          2.2E9  &           0.823  &           -0.612  &      470.1  \\
\hline
 c-1,3ee  &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-c13ee.pdf}  &                     7.7E9  &                    2.1E10  &         2.8E10  &           0.810  &           -0.580  &     1687.3  \\
\hline
 c-1,4ea  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-c14ea.pdf}  &                     4.0E7  &                     1.3E7  &          1.8E7  &           0.817  &           -0.604  &      43.20 \\
\hline
 c-1,4ee  &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-c14ee.pdf}  &                     1.3E9  &                     3.9E9  &          3.6E9  &           0.826  &           -0.642  &      605.8  \\
\hline
 d-2,6ae  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-d26ae.pdf}  &                     1.3E5  &                     1.0E4  &          4.7E4  &           0.836  &           -0.577  &    2.239  \\
\hline
d-2,6ea  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-d26ea.pdf}  &                     7.0E5  &                     3.9E4  &          5.8E4  &            0.821  &            -0.609  &    2.414  \\
\hline
 d-2,6ee  &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-d26ee.pdf}  &                     3.1E6  &                     5.0E6  &          4.8E6  &           0.810  &           -0.581  &     22.12  \\
\hline
 d-2,7ae  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-d27ae.pdf}  &                     1.1E7  &                     2.8E7  &          3.0E7  &           0.826  &           -0.605  &     55.16   \\
\hline
 d-2,7ea  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-d27ea.pdf}  &                     1.5E7  &                     1.8E7  &          4.3E7  &           0.817  &           -0.605  &     65.85  \\
\hline
 d-2,7ee  &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-d27ee.pdf}  &                     9.1E7  &                     3.5E8  &          3.4E8  &           0.831  &           -0.648  &     185.1  \\
\hline
 M        &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-M.pdf}      &                    5.0E10  &                      n.r.  &          1.2E9  &       	   0.896  &		 -0.636  &      357.0 \\
\hline
\end{tabular}

\par\end{centering}
\caption{Comparison of triplet-triplet energy transfer rates obtained from our  approach,  Marcus rates are
from Ref.\cite{Subotnik:2010}
and experimental rates from Refs.\cite{closs1988determination,closs1989connection}.   The experimental error is estimated to be 20\% in each
case studied here.
The $V_{ab}$ are the diabatic couplings obtained using  Edmiston-Ruedenberg diabatization.
In each case, D =4-benzophenonyl and A = 2-napthyl.  n.r. = Not Reported.
}
\label{summarytable}
\end{table*}

We now separate Eq.~\ref{ham1} into diagonal and
off-diagonal terms
\begin{eqnarray}
\hat  H = \hat H_{o} + \hat V
\end{eqnarray}
and perform a polaron transform
using the unitary transformation~\cite{grover:2099,rice:2504,pereverzev:104906}.
\begin{eqnarray}
U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
n|(a^{\dagger}_i-a_i)}
 \nonumber \\
&=&
\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
\label{unitary}
\end{eqnarray}
under which the transformed Hamiltonian is written in terms of the
diagonal elements
\begin{eqnarray} \tilde H_0=U^{-1}H_0U
=\sum_n\tilde\epsilon_n |n\rangle \langle
n|+\sum_i\omega_ia^{\dagger}_ia_i,
 \end{eqnarray}
with  the renormalized electronic energies,
\begin{eqnarray}
\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
\end{eqnarray}
and off-diagonal terms,
\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
\label{opm}
\end{eqnarray}
In the transformed (or dressed) picture the electronic transition from state
$|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
normal phonon modes.  Transforming to the interaction representation
and performing a trace over the phonons gives the spectral density in
terms of the autocorrelation of the electron-phonon coupling
operators.
\begin{eqnarray}
S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{spec-dens}
\end{eqnarray}
Here, $\hat V_{nm}(t)$ is the electron-phonon coupling term in the Heisenberg representation and
$\langle \cdots \rangle$ denotes a thermal average over the
vibrational degrees of freedom.
The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
Ref.~\cite{pereverzev:104906}.

\subsection{Non-Markovian Master Equation and Golden-Rule rates}

In Ref.~\cite{pereverzev:104906}, Pereverzev and Bittner derived
a non-Markovian, time-convolutionless form of the Pauli master
equation (TCLME)  for general system described by Eq.~\ref{ham1}.
\begin{eqnarray}
\frac{dP_{n}}{dt} = \sum_{m} W_{nm}(t)P_{m}(t) - \left(\sum_{m} W_{mn}(t)\right)P_{n}(t)
\end{eqnarray}
where the time-dependent rates are given by
\begin{eqnarray}
W_{nm}(\tau)=2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
\label{rate-expression}
\end{eqnarray}
In the limit that $\tau\to\infty$, Eq.~\ref{rate-expression} gives the Fermi's Golden Rule expression for the
transition rate,
\begin{eqnarray}
k_{nm}=2{\rm Re}\int_{0}^{\infty}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
\label{gr-expression}
\end{eqnarray}

At this point it is useful to connect the various terms in the phonon-dressed Hamiltonian
with specific physical parameters.
First, the reorganization energy is given by
%The terms involving $$
%are related to the reorganized energy difference between the two states.
%$$
%\lambda_{nm} =\sum_{j}((g_{nnj}-g_{mmj})/\omega_j)^{2} = \sum_{j}\hbar \omega_{j}S_{j}
%$$
\[
\lambda_{nm}=\sum_{j}\frac{\left(g_{nnj}-g_{mmj}\right)^{2}}{\omega_{j}} = \sum_{j}\hbar \omega_{j}S_{j}
\]
where  the $\{S_{j}\}$  are  the Huang-Rhys factors for each phonon mode.
These are related to the Franck-Condon factor
describing the overlap between the $v_j=1$ vibronic state in one electronic state
with the $v_j=0$ vibronic state in the other.
Likewise, the energy difference between the renormalized energy gaps is related to the
driving force of the state-to-state transition,
\begin{eqnarray}
\Delta E_{nm} = \tilde \epsilon_n-\tilde \epsilon_m.
\end{eqnarray}

The difficulty in using this approach is that
it requires both diagonal (${\mathbf g}_{nn}$) and off-diagonal  (${\mathbf g}_{nm}$) derivative couplings between
adiabatic states.    In the following section, we discuss how we have used the Edmiston-Ruedenberg localization scheme
to estimate the couplings\cite{RevModPhys.35.457}.   We also
present how one can construct a reduced set of harmonic modes that
fully capture the electron/nuclear coupling.
\subsection{Parameterization from quantum chemistry}

 In order to obtain the final form of our target Hamiltonian, we assume the diabatic  potentials
are a good approximation to the actual adiabatic potentials.

When the adiabatic (and diabatic) energy minima
are far enough away from the crossing points and the mixing angles between the diabatic  and adiabatic
states is small, we can
use the gradients of the adiabatic potentials to approximate the diabatic potentials.
Thus, if we perform calculations at the
optimized geometry of the final acceptor state  ({\em i.~e.} about $Q_{2}$  in Fig.~\ref{marcus}),
we can write the Hamiltonian as
\begin{eqnarray}
H_{dia,e}=\left(\begin{array}{cc}
\epsilon_{1} & V_{12}\\
V_{21} & \epsilon_{2}
\end{array}\right)+\left(\begin{array}{cc}
0 & 0\\
0 & 1
\end{array}\right) {\mathbf g}_{22}\cdot{\mathbf q}+H_{osc},
\end{eqnarray}
where $H_{osc}$ is the harmonic oscillator Hamiltonian for the vibrational normal modes.
The linear assumption amounts  to performing a series expansion of the
full, multi-dimensional coupling term and keeping only the lowest order terms.
Systematic improvement can be made by including higher-order (e.g.  quadratic) off-diagonal couplings.
However, this would involve a substantial increase in the complexity of the theory.
The linear assumption is reasonable so long as  the mixing angle is small,
as verified by the benchmark calculations presented below.

We obtain the diabatic couplings $V_{12}$
and the mixing angle $\theta$  via ER localization and transform the electronic Hamiltonian
from the adiabatic basis to the diabatic basis {\em viz.}
\begin{equation}
H_{dia}=\left(\begin{array}{cc}
\cos\theta & -\sin\theta\\
\sin\theta & \cos\theta
\end{array}\right)\left(\begin{array}{cc}
\epsilon_{1}  & 0 \\
0  & \epsilon_{2}
\end{array}\right)\left(\begin{array}{cc}
\cos\theta & \sin\theta\\
-\sin\theta & \cos\theta
\end{array}\right).\label{eq:boys}
\end{equation}
The diabatic coupling is then given by
\begin{eqnarray}
V_{ab}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
\end{eqnarray}

We then diagonalize the electronic part and transform the electron/nuclear coupling
back into the adiabatic basis.  In doing so,  we obtain the Hamiltonian in the
form given in Eq. \ref{ham1}
\begin{eqnarray}
H&=&U^{T}H_{dia}U\nonumber  \\
&=&\left(\begin{array}{cc}
E_{1}  & 0 \\
0 & E_{2}
\end{array}\right)+\left(\begin{array}{cc}
\sin^{2}\theta & \frac{1}{2}\sin2\theta\\
\frac{1}{2}\sin2\theta & \cos^{2}\theta
\end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
&+& H_{osc}.\label{eq:locaiHam}
\end{eqnarray}

In Fig.~\ref{parabs} we show the adiabatic potential curves and off-diagonal couplings along an interpolation coordinate
connecting the equilibrium geometries of the donor and acceptor states for the donor-[d-2,6ae]-acceptor case.
The dashed curve gives the parabolic approximation to the
lower potential curves.  Along this coordinate, the off-diagonal coupling is small and essentially linear and the parabolic
approximation provides a good approximation to the actual potential.  This indicates that the assumptions in our model Hamiltonian
are generally robust for the systems we consider herein.

\begin{figure}[t]
\subfloat[c-1,4ee]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure2a}}
\subfloat[d-2,6ae]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure2b}}
\caption{Adiabatic energy curves and off-diagonal couplings computed along an interpolation coordinate between the
$D^{*}-B-A$ and $D-B-A^{*}$ equilibrium geometries.  $V_{ab}$ is the off-diagonal coupling at each point along this coordinate.} \label{parabs}
\end{figure}

\section{Energy transfer rates in  Donor-Bridge-Acceptor systems}

Using the ER localization approach, all parameters needed for our model can be  obtained from
standard  quantum chemical packages.   The vertical energies, $\epsilon_{a}$
and $\epsilon_{b}$ are obtained from single point CI(S) calculations at a given
reference geometry.   We then project the energy gradients onto the vibrational normal
coordinates to obtain the electron-phonon coupling constants.  Either the Boys or ER
localization scheme can be use to compute the mixing
angles for constructing diabatic states. For all calculations shown here we
used the qChem 4.0 code and employed the 6-31G(d){*}{*} basis set
in order to compare our results  with  Ref. \cite{Subotnik:2010}.

 We  benchmark our approach against a series of donor-bridge-acceptor
molecules studied by Closs\cite{closs1988determination,closs1988intramolecular,closs1989connection}.
These cases are significant in that they provided a crucial verification of the Marcus inverted regime.
Table~\ref{summarytable} and Fig.~\ref{compare}  summarize our results.
In addition, we give the diabatic coupling $V_{ab}$, reorganization energy $\lambda$, and driving force $\Delta \epsilon$
computed using the Edmiston-Reudenberg (ER) localization method.

\begin{figure}[t]
\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure3}
\caption{Comparison between predicted (TCLME) rate constants and the experimental rates from Ref.\cite{miller1984intramolecular}.  With exception of
the methyl and D-2,6-ea bridged cases, the TCLME results are in good agreement with the experimental results.  }\label{compare}
\end{figure}

In general, our results and those in Ref.\cite{Subotnik:2010} agree with each other well and both are
comparable to the experimental results which report an estimated error of 10-20\% in the
rate for each case presented here.  Furthermore,  all theoretical values were computed
in the absence of solvent environment, whereas the experiments were all performed in benzene solvent at a standard temperature.
However,  there is considerable disagreement between the experimental and theoretical results for
the d-2,6ea and methyl (M) bridged cases.   For the d-2,6ea bridge,  our results are similar to the
Marcus theory rates given in Ref. \cite{Subotnik:2010}.  In this case, the
 the ER localization gives a  small diabatic coupling
 % $V_{ab} = 4.4\times 10^{-6}$eV
 and it was  difficult to obtain converged localized states.
In the case of the methyl-bridge,  there is a significant change in the geometry between donor and acceptor states.
As a result,  the potential surfaces are no longer parabolic
and the Condon approximation breaks down.\cite{Subotnik:2010}

\section{Determining the Optimal Electron-Phonon Coupling Components}

While the Marcus expression is elegant in its simplicity in requiring three parameters that
can be obtained experimentally, it masks a wealth of detail that underlie the quantum transition.
Central to the theory is that there exists a collective nuclear displacement coordinate
that connects the initial geometry of the donor to the final geometry of the acceptor.

Generally speaking, this collective coordinate involves all nuclear degrees of freedom.
However, the form of the electronic Hamiltonian in Eq.~\ref{ham1} suggests that
there exists a subset of motions that are specific modes  that capture the majority of the
electronic/nuclear coupling and give the dominant contribution to the collective
reaction coordinate.  Within the linearized approximation for the electronic/nuclear coupling,
we can write a force tensor
\begin{eqnarray}
{\mathbf F} =
\left(\begin{array}{cc}
{\mathbf g}_{11}&{\mathbf g}_{12} \\
{\mathbf g}_{21} &{\mathbf g}_{22}
\end{array}\right)
\end{eqnarray}
where ${\mathbf F}\cdot \mathbf q$ is the electronic/nuclear coupling term in Eq.~\ref{ham1}.
If we consider each unique element $\{ \mathbf g_{11}, \mathbf g_{12} , \mathbf g_{22}\}$ to be
linearly independent, but non-orthogonal force vectors,  one can develop a  projection operator scheme to
to parse the $N$-dimensional linear vector space spanned by the mass-weighted normal mode vectors into two subspaces:
one spanned by three vectors describing the coupling between the electronic states
and the other spanned by the remaining $N-3$ dimensional space spanned by motions that
do not couple the electronic states.
This  subspace  can be generated by defining a projection operator
\begin{eqnarray}
\mathbf{P}=\sum_{\alpha\beta}'\left(\mathbf{S^{-1}}\right)_{\alpha\beta}\mathbf{g_{\alpha}}\otimes\mathbf{g_{\beta}}
\end{eqnarray}
in which the summation is limited to linearly independent vectors.
   Here $\mathbf{S}_{\alpha\beta}=\mathbf{g_{\alpha}}\cdot\mathbf{g_{\beta}}$,
$\otimes$ is outer product,  and $\mathbf{I}$ is unitary operator.
This $N\times N$ matrix projects out all normal modes that are directly coupled to the
electronic degrees of freedom and
 its complement $\mathbf{Q}=\mathbf{I}-\mathbf{P}$ projects out all modes not directly coupled.
By diagonalizing the matrix
\begin{eqnarray}
\mathbf{K}=\mathbf{P}\cdot\mathbf\Omega\cdot \mathbf{P}+\mathbf{Q}\cdot\mathbf\Omega\cdot\mathbf{Q}
\end{eqnarray}
we obtain a  transformation, ${\mathbf M}$,  between the normal coordinates and a new set of orthogonal
coordinates.  Both $\mathbf{P}\cdot\mathbf\Omega\cdot \mathbf{P}$ and $\mathbf{Q}\cdot\mathbf\Omega\cdot\mathbf{Q}$ are $N\times N$ matrices.
However, for a two-state system, the former will have exactly $3$ non-trivial eigenvalues, $\{\alpha_{p}\}$, with corresponding
eigenvectors, $\{ M_{p}\}$, whereas the latter will have exactly $N_{r} = N-3$ non-trivial eigenvalues, $\{\alpha_{q}\}$,  and corresponding
eigenvectors, $\{M_q\}$.   This the full $N\times N$ transformation is formed by joining the non-trivial vectors from the
two respective subspaces ${\mathbf M} = \{M_{p}, M_{q}\}$.
The transformed electron-phonon coupling constants are given by projecting the  couplings   in the normal mode basis on to the new
basis.
\begin{eqnarray}
\mathbf{g}_{ab}'=\mathbf{M}_{p}\cdot\mathbf{g}_{ab}.
\end{eqnarray}
By examining the types of molecular motions that compose the ${\mathbf M_{p}}$ subspace, we can
gain a deeper understanding of the specific classes of internal motion that are directly involved with the
electron transfer process.  In addition,  we can gain a computational advantage since presumably this
 reduced set of modes give the dominant contribution to the electron-phonon coupling and  autocorrelation
 function given as the kernel in Eq. ~\ref{gr-expression}.

\subsection{Lanczos Method}
It is crucial to notice that the vectors  given in Eq.~\ref{eq:locaiHam} are {\em not linearly independent}.
 Consequently, special care
must be taken to generate the reduced sub-space.  To do so, we use an iterative Lanczos approach
taking the normalized vector ${\mathbf v}_{1} = {\mathbf g}_{22}$ as a starting point.

As above, we initialize each step indexed by $k$,  by defining a projection operator
\begin{eqnarray}
{\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
\end{eqnarray}
and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
%${\mathbf P}_{k}$ is the projection operator for the
$k$-th mode.
%We also construct
%\begin{eqnarray}
%\mathbf p = \sum_{k} \mathbf P_{k}
%\end{eqnarray}
%as  the total projection operator for all ${k} \le N$ modes.
We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
\begin{eqnarray}
\mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
\end{eqnarray}
and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
respectively.
As above, $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
The first set will have a single
non-trivial eigenvalue and the second set
will have $N-k$ non-trivial eigenvalues.  As above we collect the non-trivial eigenvectors associated with each
to form the orthogonal transformation matrix
\begin{eqnarray}
{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
\end{eqnarray}
and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
 At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
$k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
a diagonal submatrix in the lower-right.  For example, after $k=3$ iterations, one has
a Hessian matrix of the form:
\begin{eqnarray}
{\mathbf\Omega}' =
\begin{pmatrix}
\alpha_{1}   & b_{1}    & 0                    &               &             &            & 0 \\
b_{1}     & \alpha_{2}  & b_{2}                         \\
0            &   b_{2}         & \alpha_{3}    &   c_{k+1}   & c_{k+2}  & \cdots & c_{N}     \\
               &                     &           c_{k+1}           &     \alpha_{k+ 1} & &             & 0                 \\
               &                     &           c_{k+2}           &                 & \alpha_{k+2}  \\
               &                     &          \vdots           &                 &                    &  \ddots \\
   0           &                     &           c_{N}           &     0   &&& \alpha_{N}\\
\end{pmatrix}.
\label{omega-prime}
\end{eqnarray}
We note that only the $k$-th mode is coupled the $N-k$ remaining modes.
Since all of the transformations are orthogonal, diagonalizing $\mathbf\Omega'$ at any point
returns the original Hessian matrix.

To continue iterating, we  take the $k$-th row of $\mathbf\Omega'$ and zero the first $k$ elements
$$
{\mathbf e} = \{0,\cdots 0,c_{k+1},c_{k+2},\cdots ,c_{N}\}.
$$
This is the coupling between the upper tridiagonal block and the lower diagonal block.
We thus obtain a new vector
$$
{\mathbf v}_{k+1} = {\mathbf e} \cdot {\mathbf M}
$$
which is then reintroduced into the iteration scheme.

At any point along the way, we can terminate the iteration and obtain a reduced set of
couplings.  Since the  Lanczos approach uses the power method for finding the largest eigenvector of a matrix,
it converges first upon the vector with the largest electron/nuclear coupling--which
 we refer to as the ``primary mode''.  Subsequent iterations produce reduced modes with
 weaker electron/nuclear couplings and the entire  process can be terminated after a few iterations.
After $k$-steps, the final electron-phonon couplings are then obtained by
projecting the original set of couplings (in the normal mode basis) into the final vector space.

For the first iteration, ${\mathbf v}_{1}$ is parallel to the bare electron-phonon coupling vector $g_{22}$
and the associated frequency is ${\mathbf v}_{1}\cdot\Omega\cdot{\mathbf v}_{1}$.   The subsequent iterations introduce
corrections to this via phonon-phonon coupling.  For example, for the $k=3$ iteration,
we would determine the active vector space in terms of the upper-left 3$\times 3$ block of the matrix in
Eq.~\ref{omega-prime}.
\begin{eqnarray}
{\mathbf \Omega}_{3}' =
\begin{pmatrix}
\alpha_{1}   & b_{1}    & 0      \\
b_{1}     & \alpha_{2}  & b_{2}                         \\
0            &   b_{2}         & \alpha_{3}
\end{pmatrix}
\end{eqnarray}
Diagonalizing  ${\mathbf \Omega}_{3}'$ returns a set of frequencies and  associated eigenvectors
which are then used to compute the electron-phonon couplings in this reduced active space.
After $N-1$ iterations, $\mathbf\Omega'$ is a fully tridiagonal matrix and diagonalizing this returns the original
normal mode basis.

%{\bf XUNMO---how are frequencies and couplings determined at this point??---  }

\begin{figure}[b]
\subfloat[c-1,4ee]{\includegraphics[width=0.75\columnwidth]{Chapters/chap2/Figure4a}}\\
\subfloat[d-2,6ae]{\includegraphics[width=0.75\columnwidth]{Chapters/chap2/Figure4b}}
\caption{
Primary coupling modes for (a) c-1,4ee and (b) d-2,6ae projected onto the atomic displacement coordinates.
}\label{LanczosModes}
\end{figure}

As an illustrative example of our approach, we consider the
first few collective modes for the c-1,4ee and d-2,5ae cases.
 In Fig.~\ref{LanczosModes}
we show the projection of the primary coupling mode onto the
coordinate frame of each molecule.  The vectors indicate the direction
of the electron-phonon coupling vectors projected onto the Cartesian displacement
vectors of the individual atoms.   In each case, the primary
coupling mode involves the  $b_{2u}$ in plane C=C stretching motions of the naphthalene donor and the
 in-plane $\nu_{8}$ (in the Mulliken numbering scheme) ring-squeezing motions of the benzaldehyde acceptor\cite{doi:10.1021/jp961282l}.
It is interesting to note
that $^{3}B_{2u}$ is also the symmetry of the first triplet $\pi-\pi^{*}$ excited state in naphthalene \cite{doi:10.1021/j100066a007},
Moreover, if we were to approximate benzaldehyde as a $C_{2v}$ molecule, taking the aldehyde as local site,
the resulting first triplet $\pi-\pi^{*}$ is the product of a $b_{1}$ HOMO and a $b_{1}$ LUMO giving a state in the
  $a_{1}$ irreducible representation. This is the same irreducible representation one obtains for the $\nu_{8}$
  mode, approximating it as a symmetric stretching mode.
This suggests the existence of underlying symmetry selection or propensity rule in determining the coupling modes.

In order to substantiate our claim that the reduced modes generated by the iterative
procedure capture the most important electron-phonon couplings, we consider the
convergence of the electron-phonon autocorrelation function used
to compute the golden-rule rate constants
\begin{eqnarray}
C(t) = \langle \hat V_{nm}(t) \hat V_{nm}(0)\rangle \label{c-of-t}
\end{eqnarray}
with respect to the number of reduced modes.  We
can  this term exactly using all $N$ vibrational modes of the molecule and
compare to the results obtained using a subset of modes.

\begin{figure*}[t]
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5a}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5b}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5c}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5d}}
\caption{Convergence of the electronic coupling autocorrelation function (Eq. ~\ref{c-of-t})
with respect to number of reduced modes.\label{firstmodecorr}}
\end{figure*}

In Fig.~\ref{firstmodecorr}  we examine the convergence of $C(t)$ with respect to number of reduced modes for the c-1,4ee and d-2,6ae cases.
In both cases,  only a handful of reduced modes (4 for c-1,4ee and 15 for d-2,6ae)  is needed to  accurately track the
correlation function for the first 10 fs.   For comparison, d-2,6ae has 162 normal modes and c-1,4ee has 132 normal modes.
For the primary mode approximation, the recursions appear every 23 fs
and are suppressed by the addition of more reduced modes to the calculation.
The 23 fs recursion time corresponds to the period of the single reduced mode: $\omega_{1} = 0.18{\rm eV}$ (1450 cm$^{-1}$).
For the d-2,6ae case, including 15 modes is sufficient to fully suppress the recursion time to  beyond 100 fs.
 For purposes of computing golden rule rate constants,  the Markov limit is reached when
 $C(t)\to 0$.   For the cases at hand, this is well before the first recursion seen in Fig.~\ref{firstmodecorr}.

While it is surprising that only a few reduced modes are needed to converge the coupling correlation function, only
a single mode is necessary to accurately compute the golden-rule rate constant.
In Fig.~\ref{fig-1mode} we compare the exact rate constant (using all modes) and rate constants computed using
only the first mode generated by the Lanczos iterations.   In the first case represented by the blue points,
we approximate the reorganization energy as
$$
\lambda_{nm} \approx \frac{g_{1}^{2}}{\omega_1}
$$
where $g_{1}$ and $\omega_{1}$ are the coupling and frequency of the first  reduced mode.  This simple approximation
does a superb job compared to the numerically exact rate obtained using all modes and all couplings.
On average, the error between the exact and approximate rate is 2\%
over the entire series of model donor-bridge-acceptor systems considered.
The red points represent rates computed using the first reduced mode, but use the exact reorganization energy.
Here, the agreement is almost perfect for the two fastest rates corresponding to d-2,6ae and d-2,6ea.   However,  on average
this approximation is off by a factor of 3 compared to the exact rate.  For the methyl-bridged case, the rate is off by a factor of 8..
This implies that the first reduced mode indeed captures the majority of the electron-phonon coupling
 and provides a unique description of the Marcus reaction coordinate.

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Chapters/chap2/Figure6}
\caption{Comparison between exact rate constant and its primary mode approximation.  The blue points correspond to rates computed using
only the primary mode and the reorganization energy for only that mode.  The red points use the primary mode and the exact
renormalized energies. }\label{fig-1mode}
\end{figure}

In Table~\ref{table2} we tabulate the frequencies and electron-phonon coupling constant for the first reduced mode for each
test case.  Uniformly, these modes correspond to ring breathing motions on the donor and acceptor as illustrated in Fig.~\ref{LanczosModes}.
As seen in this figure, coupling mode does not involve normal modes localized on the bridge species.
Moreover, the magnitude of the electronic coupling carried by this mode is uniformly around 0.37 eV  and independent of the bridge.
No single normal mode captures all of the electronic coupling.  This is evidenced by the fact that the magnitude of the electronic coupling
carried by the first reduced mode is over twice that of the largest coupling along a single normal mode.

\begin{table}[t]
\begin{centering}
\begin{tabular}{lrrr}
 bridge   &  $\omega_1$(eV)  & $|g_{1}|$ (eV)  &  $|g_{max}|$ (eV)  \\
\hline
\hline
 c-1,3ea  &           0.184  &         0.367  &           0.159  \\
 c-1,3ee  &           0.185  &         0.365  &           0.162  \\
 c-1,4ea  &           0.185  &         0.367  &           0.166  \\
 c-1,4ee  &           0.185  &         0.370  &           0.171  \\
 d-2,6ae  &           0.185  &         0.367  &           0.159  \\
 d-2,6ea  &           0.185  &         0.367  &           0.142  \\
 d-2,6ee  &           0.185  &         0.365  &           0.143  \\
 d-2,7ae  &           0.184  &         0.366  &           0.165  \\
 d-2,7ea  &           0.185  &         0.367  &           0.142  \\
 d-2,7ee  &           0.185  &         0.370  &           0.149  \\
 M           &           0.184  &         0.366  &           0.160  \\
 \hline
\end{tabular}
\end{centering}
\caption{Frequencies and dimensionless electron-phonon couplings for
the first reduced mode for each model system. The last column gives the
absolute value of the largest coupling constant within the normal mode basis.
}\label{table2}

\end{table}

\section{Discussion}

We present here a new approach for computing intramolecular energy and charge transfer rates
by combining a time-convolutionless master equation approach for state to state population transfer as parameterized
by  a rigorous quantum chemical approach.   The approach is robust over a wide range of model systems and
generally gives good agreement compared to experimental rates and Marcus theory rates.
Only in cases where the parabolic approximation to the diabatic potentials breaks down or when the ER localization method
fails to converge is the agreement with the experimental rates less than satisfactory.

A crucial part of our analysis is the identification of a subset of collective modes that contain
the electron-phonon couplings.  Moreover, we show that there exists a unique mode--the ``primary mode'',
determined via an iterative
approach, along which  the off-diagonal electron-phonon coupling is maximized.   Using only the primary mode
mode as input to our golden-rule rate expression, we obtain excellent
agreement (to within 2\% on average over   all of the donor-bridge-acceptor systems studied here)
when compared to an exact evaluation using all normal modes.   One can visualize the primary mode by projecting it on to the
nuclear displacement vectors and gain insight into the coupled electronic/nuclear motions that underlie an electronic
transition.   Our analysis also suggests that the primary  mode reflects the irreducible representations of the
donor and acceptor excited states.

% \begin{acknowledgement}

% ERB acknowledges support from
% the National Science Foundation (CHE-1362006), and the Robert A. Welch Foundation (E-1337).
% We specifically thank Prof. Joseph Subotnik and his group for  discussions pertaining to the
% use of the ER localization methods and their implementation in qChem.
% XY thanks Nadia El-Hamdi for inspiration.

% \end{acknowledgement}

% \bibliography{../References-local}
% \bibliographystyle{plainnat}
% \chapterbib
\providecommand*\mcitethebibliography{\thebibliography}
\csname @ifundefined\endcsname{endmcitethebibliography}
  {\let\endmcitethebibliography\endthebibliography}{}
\begin{mcitethebibliography}{27}
\providecommand*\natexlab[1]{#1}
\providecommand*\mciteSetBstSublistMode[1]{}
\providecommand*\mciteSetBstMaxWidthForm[2]{}
\providecommand*\mciteBstWouldAddEndPuncttrue
  {\def\EndOfBibitem{\unskip.}}
\providecommand*\mciteBstWouldAddEndPunctfalse
  {\let\EndOfBibitem\relax}
\providecommand*\mciteSetBstMidEndSepPunct[3]{}
\providecommand*\mciteSetBstSublistLabelBeginEnd[3]{}
\providecommand*\EndOfBibitem{}
\mciteSetBstSublistMode{f}
\mciteSetBstMaxWidthForm{subitem}{(\alph{mcitesubitemcount})}
\mciteSetBstSublistLabelBeginEnd
  {\mcitemaxwidthsubitemform\space}
  {\relax}
  {\relax}

% \begin{thebibliography}{27}
\bibitem[Marcus(1956)]{marcus1956theory}
Marcus,~R.~A. On the Theory of Oxidation-Reduction Reactions Involving Electron
  Transfer. I. \emph{J. Chem. Phys.} \textbf{1956}, \emph{24},
  966--978\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Marcus(1965)]{marcus1965theory}
Marcus,~R.~A. On the Theory of Electron-Transfer Reactions. VI. Unified
  Treatment for Homogeneous and Electrode Reactions. \emph{J. Chem. Phys} \textbf{1965}, \emph{43}, 679\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Marcus(1993)]{marcus1993electron}
Marcus,~R.~A. Electron transfer reactions in chemistry. Theory and experiment.
  \emph{Rev. Mod.  Phys.} \textbf{1993}, \emph{65}, 599--610\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Dexter(1953)]{Dexter:1952}
Dexter,~D.~L. A Theory of Sensitized Luminescence in Solids. \emph{J. Chem. Phys.} \textbf{1953}, \emph{21}, 836--850\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Miller et~al.(1984)Miller, Calcaterra, and
  Closs]{miller1984intramolecular}
Miller,~J.; Calcaterra,~L.; Closs,~G. Intramolecular long-distance electron
  transfer in radical anions. The effects of free energy and solvent on the
  reaction rates. \emph{J.  Am.  Chem.  Soc.}
  \textbf{1984}, \emph{106}, 3047--3049\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Subotnik et~al.(2008)Subotnik, Yeganeh, Cave, and
  Ratner]{subotnik2008constructing}
Subotnik,~J.~E.; Yeganeh,~S.; Cave,~R.~J.; Ratner,~M.~A. Constructing diabatic
  states from adiabatic states: Extending generalized Mulliken--Hush to
  multiple charge centers with Boys localization. \emph{J. Chem. Phys.} \textbf{2008}, \emph{129}, 244101\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Subotnik et~al.(2009)Subotnik, Cave, Steele, and
  Shenvi]{subotnik2009initial}
Subotnik,~J.~E.; Cave,~R.~J.; Steele,~R.~P.; Shenvi,~N. The initial and final
  states of electron and energy transfer processes: Diabatization as motivated
  by system-solvent interactions. \emph{J. Chem. Phys.}
  \textbf{2009}, \emph{130}, 234102--234102\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Subotnik et~al.(2010)Subotnik, Vura-Weis, Sodt, and
  Ratner]{Subotnik:2010}
Subotnik,~J.~E.; Vura-Weis,~J.; Sodt,~A.~J.; Ratner,~M.~A. Predicting accurate
  electronic energy transfer rates via Marcus theory and Edminston-Ruedeberg
  localized diabatization. \emph{J. Phys. Chem. A} \textbf{2010},
  \emph{114}\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Pereverzev and Bittner(2006)Pereverzev, and
  Bittner]{pereverzev:104906}
Pereverzev,~A.; Bittner,~E.~R. Time-convolutionless master equation for
  mesoscopic electron-phonon systems. \emph{J. Chem. Phys.}
  \textbf{2006}, \emph{125}, 104906\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Tamura et~al.(2008)Tamura, Ramon, Bittner, and Burghardt]{Tamura08}
Tamura,~H.; Ramon,~J. G.~S.; Bittner,~E.~R.; Burghardt,~I. Phonon-Driven
  Ultrafast Exciton Dissociation at Donor-Acceptor Polymer Heterojunctions.
  \emph{Physical Review Letters} \textbf{2008}, \emph{100}, APS\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Tamura et~al.(2007)Tamura, Bittner, and Burghardt]{tamura:021103}
Tamura,~H.; Bittner,~E.~R.; Burghardt,~I. Exciton dissociation at
  donor-acceptor polymer heterojunctions: Quantum nonadiabatic dynamics and
  effective-mode analysis. \emph{J. Chem. Phys.}
  \textbf{2007}, \emph{126}, 021103\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Bittner and Silva(2014)Bittner, and Silva]{Bittner:2014ab}
Bittner,~E.~R.; Silva,~C. Noise-induced quantum coherence drives photo-carrier
  generation dynamics at polymeric semiconductor heterojunctions. \emph{Nat.   Comm.} \textbf{2014}, \emph{5}, 3119\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Singh et~al.(2009)Singh, Bittner, Beljonne, and
  Scholes]{Jaykrishna-Singh:2009ly}
Singh,~J.; Bittner,~E.~R.; Beljonne,~D.; Scholes,~G.~D. Fluorescence Depolarization in MEH-PPV:
Sites vs. Eigenstates Hopping. \emph{J. Chem.
  Phys.} \textbf{2009}, \emph{131}, 194905\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Cederbaum et~al.(2005)Cederbaum, Gildensperger, and
  Burghardt]{Cederbaum:2005}
Cederbaum,~L.; Gildensperger,~E.; Burghardt,~I. Short-Time Dynamics Through
  Conical Intersections in Macrosystems. \emph{Phys. Rev. Lett.} \textbf{2005},
  \emph{94}, 113003\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Gindensperger et~al.(2006)Gindensperger, Burghardt, and
  Cederbaum]{gindensperger:144103}
Gindensperger,~E.; Burghardt,~I.; Cederbaum,~L.~S. Short-time dynamics through
  conical intersections in macrosystems. I. Theory: Effective-mode formulation.
  \emph{J. Chem. Phys.} \textbf{2006}, \emph{124},
  144103\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Gindensperger et~al.(2006)Gindensperger, Burghardt, and
  Cederbaum]{gindensperger:144104}
Gindensperger,~E.; Burghardt,~I.; Cederbaum,~L.~S. Short-time dynamics through
  conical intersections in macrosystems. II. Applications. \emph{J. Chem. Phys.} \textbf{2006}, \emph{124}, 144104\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Cederbaum et~al.(2005)Cederbaum, Gindensperger, and
  Burghardt]{PhysRevLett.94.113003}
Cederbaum,~L.~S.; Gindensperger,~E.; Burghardt,~I. Short-Time Dynamics Through
  Conical Intersections in Macrosystems. \emph{Phys. Rev. Lett.} \textbf{2005},
  \emph{94}, 113003\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Pereverzev et~al.(2009)Pereverzev, Bittner, and  Burghardt]{pereverzev:034104}
Pereverzev,~A.; Bittner,~E.~R.; Burghardt,~I. Energy and charge-transfer
  dynamics using projected modes. \emph{J. Chem. Phys.}
  \textbf{2009}, \emph{131}, 034104\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Closs et~al.(1988)Closs, Piotrowiak, MacInnis, and
  Fleming]{closs1988determination}
Closs,~G.~L.; Piotrowiak,~P.; MacInnis,~J.~M.; Fleming,~G.~R. Determination of
  long-distance intramolecular triplet energy-transfer rates. Quantitative
  comparison with electron transfer. \emph{J.  Am.  Chem.  Soc.} \textbf{1988}, \emph{110}, 2652--2653\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Closs et~al.(1989)Closs, Johnson, Miller, and
  Piotrowiak]{closs1989connection}
Closs,~G.~L.; Johnson,~M.~D.; Miller,~J.~R.; Piotrowiak,~P. A connection
  between intramolecular long-range electron, hole, and triplet energy
  transfers. \emph{J.  Am.  Chem.  Soc.} \textbf{1989},
  \emph{111}, 3751--3753\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Grover and Silbey(1970)Grover, and Silbey]{grover:2099}
Grover,~M.~K.; Silbey,~R. Exciton--Phonon Interactions in Molecular Crystals.
  \emph{J. Chem. Phys.} \textbf{1970}, \emph{52},
  2099--2108\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Rice and Gartstein(1994)Rice, and Gartstein]{rice:2504}
Rice,~M.~J.; Gartstein,~Y.~N. Excitons and interband excitations in conducting
  polymers based on phenylene. \emph{Phys. Rev. Lett.} \textbf{1994},
  \emph{73}, 2504--2507\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Edmiston and Ruedenberg(1963)Edmiston, and
  Ruedenberg]{RevModPhys.35.457}
Edmiston,~C.; Ruedenberg,~K. Localized Atomic and Molecular Orbitals.
  \emph{Rev. Mod. Phys.} \textbf{1963}, \emph{35}, 457--464\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Closs and Miller(1988)Closs, and Miller]{closs1988intramolecular}
Closs,~G.~L.; Miller,~J.~R. Intramolecular long-distance electron transfer in
  organic molecules. \emph{Science} \textbf{1988}, \emph{240}, 440--447\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[Silva and Reilly(1996)Silva, and Reilly]{doi:10.1021/jp961282l}
Silva,~C.~R.; Reilly,~J.~P. Theoretical Calculations on Excited Electronic
  States of Benzaldehyde and Observation of the $S_2\leftarrow S_0$ Jet-Cooled
  Spectrum. \emph{J. Phys. Chem.} \textbf{1996}, \emph{100},
  17111--17123\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem
\bibitem[{\AA}gren et~al.(1994){\AA}gren, Minaev, and
  Knuts]{doi:10.1021/j100066a007}
{\AA}gren,~H.; Minaev,~B.~F.; Knuts,~S. Response Theory Studies of
  Triplet-State Spectra and Radiative Lifetimes of Naphthalene, Quinoxaline,
  and Phthalazine. \emph{J.  Phys.  Chem.} \textbf{1994},
  \emph{98}, 3943--3949\relax
\mciteBstWouldAddEndPuncttrue
\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
\EndOfBibitem

% \end{thebibliography}
\end{mcitethebibliography}

% \begin{tocentry}
% {\includegraphics[width=4.3cm]{Chapters/chap2/TOCFigure1}}
% {\includegraphics[width=4.3cm]{Chapters/chap2/TOCFigure2}}
% %Primary coupling modes for triplet energy transfer in model donor-bridge-acceptor systems.
% %These modes provide a unique representation of the electron/nuclear coupling for intramolecular charge and energy-transfer.
% \end{tocentry}

% \end{document}

### 2016-03-12 Chapters/chap3/Manuscript-FINAL.tex
Initialize

%% JCP Submission styles
%\documentclass[aip,jcp,citeautoscript,reprint]{revtex4-1}
% \documentclass[aip,jcp,citeautoscript,preprint,endfloats*]{revtex4-1}
% \usepackage{graphicx}
% %\usepackage{mathabx}
% %
% %\usepackage{listings}
% %\usepackage{newtxtext} % T1, lining figures in math, osf in text
% %\usepackage{amssymb,amsmath}
% %%\usepackage{epstopdf}
% \usepackage{tikz}
% \usepackage{chemfig}
% \usepackage{color}
% \usepackage{subfigure}
% %\usepackage{pinlabel}
% %
% %\usepackage{textcomp} % required for special glyphs
% %\usepackage{amsmath}

% \usepackage{listings}
% %\usepackage{amssymb,amsmath}
% %\usepackage[libertine]{newtxmath}
% %\usepackage{subfigure}
% %\usepackage{newtxtext} % T1, lining figures in math, osf in text
% \usepackage{textcomp} % required for special glyphs
% \usepackage{amsmath}
% %\usepackage[varg,cmintegrals]{newtxmath}
% \usepackage{bm} % load after all math to give access to bold math

% %\usepackage[varg,cmintegrals,bigdelims]{newtxmath}

% \usepackage{bm}

% \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

% \definecolor{mma1}{RGB}{63,60,153}
% \definecolor{mma2}{RGB}{135,60,121}
% \definecolor{mma4}{RGB}{61,134,99}
% \definecolor{mma3}{RGB}{135,123,79}

% \usetikzlibrary{arrows,snakes,backgrounds}

% %---notations--
% \newcommand{\bk}{\mathbf{k}}
% \newcommand{\bq}{\mathbf{q}}
% \newcommand{\bkp}{\mathbf{k^{\prime}}}
% \newcommand{\bkpp}{\mathbf{k^{\prime\prime}}}
% \newcommand{\psibkdag}{\hat\psi_\mathbf{k}^{\dagger}}
% \newcommand{\psibk}{\psi_\mathbf{k}}
% \newcommand{\psibkpdag}{\hat \psi_{\mathbf{k^{\prime}}}^{\dagger}}
% \newcommand{\psibkp}{\hat \psi_{\mathbf{k^{\prime}}}}
% \newcommand{\Bbk}{\hat B_\mathbf{k}}
% \newcommand{\Bbkdag}{\hat B_\mathbf{k}^{\dagger}}
% \newcommand{\betkk}{\beta_{-\mathbf{k}\mathbf{k^{\prime}}}}
% \newcommand{\betmkk}{\beta_{-\mathbf{k}-\mathbf{k^{\prime}}}}
% \newcommand{\betmkks}{\beta_{-\mathbf{k}-\mathbf{k^{\prime}}}^\ast}
% \newcommand{\betkks}{\beta_{-\mathbf{k}\mathbf{k^{\prime}}}^\ast}
% \newcommand{\betpkk}{\beta_{\mathbf{k}\mathbf{k^{\prime}}}}
% \newcommand{\betpkks}{\beta_{\mathbf{k}\mathbf{k^{\prime}}}^\ast}
% \newcommand{\Lambk}{\Lambda_\bk}
% \newcommand{\Lambkast}{\Lambda_\bk^\ast}
% \newcommand{\bn}{\mathbf{n}}
% \newcommand{\oo}{\omega_0}
% \newcommand{\Om}{\Omega}
% \newcommand{\eps}{\epsilon}
% \newcommand{\delkkp}{\delta_{\mathbf k,\mathbf{k^{\prime}}}}
% \newcommand{\ra}{\rangle}
% \newcommand{\la}{\langle}
% \newcommand{\rp}{\right)}
% \newcommand{\lp}{\left(}
% \newcommand{\rb}{\right]}
% \newcommand{\lb}{\left[}
% \newcommand{\Trk}[1]{\mathrm{Tr}_{_\bk}\lb{#1}\rb}

% \begin{document}

% % Use the \preprint command to place your local institutional report
% % number in the upper righthand corner of the title page in preprint mode.
% % Multiple \preprint commands are allowed.
% % Use the 'preprintnumbers' class option to override journal defaults
% % to display numbers if necessary
% %\preprint{}

% %Title of paper
% \title{Computing Intramolecular Charge and Energy Transfer Rates using Optimal  Modes.
% }

% % repeat the \author .. \affiliation  etc. as needed

% \author{Xunmo Yang}
% \affiliation{Department of Chemistry, University of Houston, Houston, TX 77204}
% \author{Eric R Bittner}
% \email{bittner@uh.edu}
% \affiliation{Department of Chemistry, University of Houston, Houston, TX 77204}

% \date{\today}

% \begin{abstract}
%   In our recent work (X. Yang and E. R Bittner, J. Phys. Chem. A \textbf{118} 5196 (2014)), we showed how to construct a reduced set of nuclear motions that capture the
% coupling between electronic and nuclear degrees of freedom over the course of an electronic transition.  We construct these modes, referred to as ``Lanczos modes'',
% by applying a search algorithm to find linear combinations of vibrational normal modes that optimize the electronic/nuclear coupling operator. Here we analyze the irreducible
% representations  of the dominant contributions of these modes and find that for the cases considered here, these belong to totally symmetric irreducible representations  of
% the donor and acceptor moieties. Upon investigating the molecular geometry changes following  the transition,   we propose that the electronic transition process can be
% broken into two steps, in the agreement of Born-Oppenheimer approximation:  a fast excitation transfer occurs, facilitated by the ``primary Lanczos mode'' (PLM),
% followed by slow nuclear relaxation on the final electronic diabatic surface.
% \end{abstract}

% % insert suggested PACS numbers in braces on next line \pacs{}
% % insert suggested keywords - APS authors don't need to do this
% %\keywords{}

% %\maketitle must follow title, authors, abstract, \pacs, and \keywords
% \maketitle

\chapter{Chapter 3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

One of the most important and fundamental processes in chemical  dynamics is
that of energy and charge transfer between molecular species.  The mechanism
itself is highly quantum mechanical in nature and involves strong coupling between nuclear and
electronic degrees of freedom.  The seminal model for the calculation of the transfer rate for this process
was developed by Marcus in the 1950's\cite{marcus1956theory,marcus1965theory,marcus1993electron}
\begin{equation}
k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T}\label{eq:marcus},
\end{equation}
which relates the Fermi golden-rule transition rate, $k_{Marcus}$
to the thermodynamic driving force $\Delta G^{o}$ and the reorganization energy $\lambda$.
One of the most striking predictions of this theory is that as the free energy difference between the final and initial state increases, the transition rate reaches its maximum,
and further increases in the energy off-set leads to slower transition rates.
This ``inverted regime''  was confirmed by Closs and Miller\cite{miller1984intramolecular,closs1988determination,closs1989connection}
nearly 30 yrs later.

Numerous improvements to the Marcus model have been presented over the years and
a detailed exploration of each is well beyond the scope of this work.
Aside from the electronic coupling, $V_{ab}$,  the other terms in the expression of rate constant arise from
a semi-classical approximation to the overlap between the initial vibrational states of the donor and the
the final  states of the acceptor state. It suffices to say that most of the
efforts focus upon incorporating more molecular-level detail into the couplings and vibrational modes
used in computing these terms.

A number of years ago,  we developed a time-convolutionless  master equation approach (TCLME) for computing
state-to-state rate in which the coupling between  states depends upon the
nuclear coordinates\cite{pereverzev:104906}. This approach incorporates a fully quantum
mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
the Marcus rate equation in the semiclassical limit.  The model itself is parameterized by the
vibrational normal mode frequencies, the electronic energies, and energy derivatives
at a reference configuration obtained from {\em ab initio} quantum  chemistry computations.
The approach has been intensively used and testified by our group to compute state-to-state
transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
\cite{tamura:107402,tamura:021103,singh:194905,Bittner:2014aa}.
Central to our work here is the use of a mode-projection scheme
 % which is similar to the Page-rank algorithm used by internet search engines such as
 % Google and Netflix\cite{brin1998anatomy, page2004method},
 which parses out a
reduced set of nuclear motions primarily coupled to the quantum transition.
We refer to the modes identified early in the iterative process as the ``primary Lanczos modes'' or PLMs.

Using the TCLME approach,  we recently investigated
triplet-triplet excitation energy transfer between a naphthalene donor and a
benzaldehyde acceptor linked by a variety of bridging units as shown in Fig.~\ref{struct}. \cite{xunmo2014}
\begin{figure}
%\includegraphics[width=\columnwidth]{Chapters/chap3/D-B-A-Numbered.pdf}
\includegraphics[width=\columnwidth]{Chapters/chap3/molecule1.pdf}
\caption{Molecular structure of naphthalene donor and a
benzaldehyde acceptor linked by various bridging units. }\label{struct}
\end{figure}
Such systems were the basis of a  classic series of experiments by
Closs and Miller\cite{miller1984intramolecular,closs1988determination,closs1989connection}
which verified the existence of the Marcus inverted regime.
In Ref. \cite{xunmo2014} we showed that both
the autocorrelation function of the electronic coupling operators
and the total transfer rate constant calculated using TCLME approach with only PLMs provide an
excellent approximation to the exact correlation functions and rate
constants computed using all normal modes, as well as to the experimental
and recent theoretical values for the transfer rates.\cite{subotnik2010predicting}

In this paper we analyze the symmetry of PLMs in model donor-bridge-acceptor systems as projected onto the local
 vibrational modes of the  donor (benzaldehyde)    and  acceptor (naphthalene) moieties.    By constructing the local modes
from the dominant normal modes in the projection,  one can deduce a relation between the PLMs,
fragment modes,  and normal modes for the entire molecule.
The structure of this paper is as follows.
We begin by reviewing the TCLME approach and how one generates the PLMs.  We then
discuss the symmetry  of PLMs and their relation to a linear coordinate linking the
initial/donor geometry to the final/acceptor geometry of the molecule.
%---NEED CONCLUDING STATEMENT----

\section{Theoretical Model}

% \subsection{Construction and parameterization}
Our method was detailed in Ref.\cite{xunmo2014} but to be self-contained, we briefly present it here.

% \subsection{Model Hamiltonian and transition rates}
% Our theory is initiated by considering a generic model for electronic transitions in the presence of
% nuclear degrees of freedom. Taking the electronic ground state of the system as a reference
% and assuming that the electronic states are coupled linearly to a common set of
%  modes, we arrive a generic form for the Hamiltonian:
%  \begin{eqnarray}
% H=\left(\begin{array}{cc}
% \epsilon_{1} & 0\\
% 0 & \epsilon_{2}
% \end{array}\right)+\left(\begin{array}{cc}
% {\mathbf g}_{11}&{\mathbf g}_{12} \\
% {\mathbf g}_{21} &{\mathbf g}_{22}
% \end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
% \nonumber \\
% % \label{ham1}
% \end{eqnarray}
% Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
% reference geometry--typically that of the donor or acceptor state.   The second term represents the
% linearized coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
% normal coordinates $\mathbf q$.   The diagonal terms
% give the adiabatic displacement forces between the reference geometry and the two states.  If we choose one of the
% states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish.
% The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
% In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.

% We now separate Eq. ~\ref{ham1} into diagonal and
% off-diagonal terms
% \begin{eqnarray}
% \hat  H = \hat H_{o} + \hat V
% \end{eqnarray}
% and perform a polaron transform
% using the unitary transformation~\cite{grover:2099,rice:2504,pereverzev:104906}.
% \begin{eqnarray}
% U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
% n|(a^{\dagger}_i-a_i)}
%  \nonumber \\
% &=&
% \sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
% \label{unitary}
% \end{eqnarray}
% under which the transformed Hamiltonian is written in terms of the
% diagonal elements
% \begin{eqnarray} \tilde H_0=U^{-1}H_0U
% =\sum_n\tilde\epsilon_n |n\rangle \langle
% n|+\sum_i\omega_ia^{\dagger}_ia_i,
%  \end{eqnarray}
% with  the renormalized electronic energies,
% \begin{eqnarray}
% \tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
% \end{eqnarray}
% and off-diagonal terms,
% \begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
% a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
% \label{opm}
% \end{eqnarray}
% In the transformed (or dressed) picture the electronic transition from state
% $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
% normal phonon modes.  Transforming to the interaction representation
% and performing a trace over the phonons gives the spectral density in
% terms of the autocorrelation of the electron/phonon coupling
% operators.
% \begin{eqnarray}
% S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
% \end{eqnarray}
% where
% $$
% %C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
% C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
% $$
% is the autocorrelation function of the
% polaron-transformed electron-phonon coupling operator in the Heisenberg representation and
% $\langle \cdots \rangle$ denotes a thermal average over the
% vibrational degrees of freedom.
% The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
% Ref.~\citenum{pereverzev:104906}.
% Using this approach , the golden-rule rates are given by
% \begin{eqnarray}
% k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
% \label{gr-expression}
% \end{eqnarray}
% In a practical sense, we take $\tau$ to be some finite time at which the
% autocorrelation function $C(t)$
% has relaxed to zero.

% Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
% the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
% For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
% In our previous work we showed that both $C(t)$
% and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
% excellent agreement with the exact quantities computed using  the full set of
% normal modes, as well as the experimental rates,
% when parameterized using accurate quantum chemical data.\cite{xunmo2014}

\subsection{Hamiltonian and Parameterization}

We start with the  generic form for the diabatic Hamiltonian, describing two electronic states coupled with $N$ normal modes:
\begin{eqnarray}
H_{dia}=\left(\begin{array}{cc}
\epsilon_{1} & V_{12}\\
V_{21} & \epsilon_{2}
\end{array}\right)
+\left(\begin{array}{cc}
{\mathbf g}_{11}&{\mathbf g}_{12} \\
{\mathbf g}_{21} &{\mathbf g}_{22}
\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
\nonumber \\
\end{eqnarray}
Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
reference geometry--typically that of the donor or acceptor state. $V_{ij}$ is the diabatic coupling between them.  The second term represents the
linear coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
normal coordinates $\mathbf q$.   The diagonal terms
give the diabatic displacement forces between the reference geometry and the two states.
The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.

If we choose one of the states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish. We further assume Condon approximation to neglect $\mathbf g_{12}$ and $\mathbf g_{21}$. Now the Hamiltonian is simplified to
\begin{eqnarray}
H_{dia}=\left(\begin{array}{cc}
\epsilon_{1} & V_{12}\\
V_{21} & \epsilon_{2}
\end{array}\right)+\left(\begin{array}{cc}
0 & 0\\
0 & 1
\end{array}\right) {\mathbf g}_{22}\cdot{\mathbf q}+H_{osc},
\end{eqnarray}
\label{eq:diaHam}
where $H_{osc}$ is the harmonic oscillator Hamiltonian for the vibrational normal modes.

To calculate transition rate, we transform to adiabatic representation. It is done via Edmiston-Ruendenberg (ER) localization\cite{subotnik2010predicting} implemented in Q-Chem and the electronic Hamiltonians
on adiabatic and diabatic basis are related by the mixing angle $\theta$.
\begin{equation}
H_{dia,e}=\left(\begin{array}{cc}
\cos\theta & -\sin\theta\\
\sin\theta & \cos\theta
\end{array}\right)\left(\begin{array}{cc}
\epsilon_{1}  & 0 \\
0  & \epsilon_{2}
\end{array}\right)\left(\begin{array}{cc}
\cos\theta & \sin\theta\\
-\sin\theta & \cos\theta
\end{array}\right).\label{eq:boys}
\end{equation}
The diabatic coupling is then given by
\begin{eqnarray}
V_{12}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
\end{eqnarray}
The full adiabatic Hamiltonian reads:
\begin{eqnarray}
H&=&U^{T}H_{dia}U\nonumber  \\
&=&\left(\begin{array}{cc}
E_{1}  & 0 \\
0 & E_{2}
\end{array}\right)+\left(\begin{array}{cc}
\sin^{2}\theta & \frac{1}{2}\sin2\theta\\
\frac{1}{2}\sin2\theta & \cos^{2}\theta
\end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
&+& H_{osc}.\label{eq:locaiHam}
\end{eqnarray}
where the electronic part is in the adiabatic basis with eigenenergies of $E_1$ and $E_2$ at certain reference geometry. The nuclear normal modes are described by $H_{osc}$ whereas $\theta$ is the mixing angle between two states.
%to describe the coupling between two electronic states, $|1\rangle$ and $|2\rangle$  by a set of nuclear vibrational motionsdescribed by $H_{osc}$.  The angle $\theta$ gives the mixing angle between diabatic states and $E_1$ and $E_{2}$ are electronic energies computed at the same reference configuration.

To parametrize our Hamiltonian, we assume the diabatic
are a good approximation to the actual adiabatic potentials.
This allows us to
use the gradients of the adiabatic potentials to approximate the diabatic potentials.
This approximation is  valid when the adiabatic (and diabatic) energy minima
are far enough away from the crossing points and the mixing angles between the diabatic  and adiabatic
states is small.
Thus, all parameters in Eq.~\ref{eq:locaiHam}  can be  obtained from
standard  quantum chemical computations.
As in our previous work, we use the Q-Chem 4.0 package  to obtain the vertical energies
 from single point CI(S) calculations with 6-31G** basis set at a given
reference geometry.   We then project the energy gradients onto the vibrational normal
coordinates

Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam} can be expressed in a time-convolutionless mater equation \cite{pereverzev:104906}. The derivation is lengthy so we present it briefly.

\subsection{Transition Rate and Autocorrelation}
We start from a more general Hamiltonian:
\begin{eqnarray}
H=\left(\begin{array}{cc}
\epsilon_{1} & 0\\
0 & \epsilon_{2}
\end{array}\right)+\left(\begin{array}{cc}
{\mathbf g}_{11}&{\mathbf g}_{12} \\
{\mathbf g}_{21} &{\mathbf g}_{22}
\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}
\nonumber \\
\label{ham1}
\end{eqnarray}
then perform a polaron transform
using the unitary transformation~\cite{grover:2099,rice:2504,pereverzev:104906}.
\begin{eqnarray}
U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
n|(a^{\dagger}_i-a_i)}
 \nonumber \\
&=&
\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
\label{unitary}
\end{eqnarray}
under which the transformed Hamiltonian is written in terms of the
diagonal elements
\begin{eqnarray} \tilde H_0=U^{-1}H_0U
=\sum_n\tilde\epsilon_n |n\rangle \langle
n|+\sum_i\omega_ia^{\dagger}_ia_i,
 \end{eqnarray}
with  the renormalized electronic energies,
\begin{eqnarray}
\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
\end{eqnarray}
and off-diagonal terms,
\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
\label{opm}
\end{eqnarray}
% In the transformed (or dressed) picture the electronic transition from state
% $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
% normal phonon modes.  Transforming to the interaction representation
% and performing a trace over the phonons gives the spectral density in
% terms of the autocorrelation of the electron/phonon coupling
% operators.
% \begin{eqnarray}
% S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
% \end{eqnarray}
% where
% $$
%C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
After lengthy derivation we get the autocorrelation function in the Heisenberg representation
$$
C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
$$
where $\langle \cdots \rangle$ denotes a thermal average over the
vibrational degrees of freedom.
% The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
% Ref.~\citenum{pereverzev:104906}.
Using this approach , the golden-rule rates are given by
\begin{eqnarray}
k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
\label{gr-expression}
\end{eqnarray}
In a practical sense, we take $\tau$ to be some finite time at which the
autocorrelation function $C(t)$
has relaxed to zero.

Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
In our previous work we showed that both $C(t)$
and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
excellent agreement with the exact quantities computed using  the full set of
normal modes, as well as the experimental rates,
when parameterized using accurate quantum chemical data.\cite{xunmo2014}

% Diagonalizing $H$ at a given nuclear configuration  provides the adiabatic potentials for our system, which can be used to approximate the diabatic potentials.

% The linear coupling parameter $ {\mathbf g}_{22}$ defines
% a force
% along a vector connecting the
% the initial and final equilibrium geometries of the molecule.
% This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
% using the ER localization
% scheme to approximate the donor and acceptor states.
% By analyzing this force we can gain the insight into the dynamics of the transition as well as
% open an avenue for developing improved approximations for transition rates.
% In our previous work \cite{xunmo2014},  we presented a Lanczos-base ranking algorithm that project
% out a series of nuclear displacements that are most important for
% the transition.   We refer to the highest-ranked mode identified by the algorithm
% as the ``primary Lanczos mode'' (PLM).

% \subsection{Computing spectral densities and transition rates}

% Once a suitable set of parameters and vibrational modes  have been determined,

\subsection{Constructing Primary Lanczos Modes}
The linear coupling parameter $ {\mathbf g}_{22}$ in Eq.~\ref{eq:locaiHam} defines
a force
along a vector connecting
the initial and final equilibrium geometries of the molecule.
This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
using the ER localization
scheme to approximate the donor and acceptor states.
By analyzing this force we can gain the insight into the dynamics of the transition as well as
open an avenue for developing improved approximations for transition rates.
In our previous work \cite{xunmo2014},  we presented a Lanczos-base ranking algorithm that project
out a series of nuclear displacements that are most important for
the transition.   We refer to the highest-ranked mode identified by the algorithm
as the ``primary Lanczos mode'' (PLM).
The process of finding the PLMs is initiated by defining the vector ${\mathbf v}_{1} = {\mathbf g}_{22}$.
At each step indexed by $k$,  we define a projection operator
\begin{eqnarray}
{\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
\end{eqnarray}
and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
We also construct
\begin{eqnarray}
\mathbf p = \sum_{k} \mathbf P_{k}
\end{eqnarray}
as  the total projection operator for all ${k} \le N$ modes.
We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
\begin{eqnarray}
\mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
\end{eqnarray}
and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
respectively.  $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
The first set of these  will have a single
non-trivial eigenvalue and the second set
will have $N-k$ non-trivial eigenvalues. We then collect the non-trivial eigenvectors associated with each
to form the orthogonal transformation matrix
\begin{eqnarray}
{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
\end{eqnarray}
and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
 At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
$k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
a diagonal submatrix in the lower-right.

\begin{figure*}[ht]
\subfloat[c-1,4ee]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure1a.pdf}}
\subfloat[d-2,6ae]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure1b.pdf}}
\caption{
Primary Lanczos modes for (a) c14ee and (b) d26ae projected onto the atomic displacement coordinates.  The frequencies
for both these are at 0.185 eV (1490 cm$^{-1}$), a typical $C=C$ stretching frequency for arene systems.
}\label{LanczosModes}
\end{figure*}

\begin{figure*}[ht]
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure2a.pdf}}
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure2b.pdf}} \\
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure2c.pdf}}
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure2d.pdf}}
\caption{Projection of PLMs onto (a) benzaldehyde in c14ee (b) symmetrized naphthalene in c14ee, (c) benzaldehyde in d26ae and (d) symmetrized naphthalene in d26ae.
The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are color-coded. The assigned IRs for naphthalene are exact
 whereas the IRs are only approximate for benzaldehyde. \label{fragProj}}
\end{figure*}

In Fig.~\ref{LanczosModes}  we show the PLMs for the
intramolecular triplet energy transfer within
two representative donor-bridge-acceptor molecules from our study, termed c14ee and d26ae.
In both cases, triplet energy is transferred from a benzaldehyde (BZ) donor group to a naphthyl- acceptor group.
Several observations can be made from Fig.~\ref{LanczosModes} concerning the primary Lanczos modes for these
donor-bridge-acceptor systems. First, there is negligible contribution from the bridging unit.
This is not surprising since the transitions involve  electronic energy
 transfer between $\pi$-orbitals localized on the donor and acceptor moieties.
 Since the bridges in these cases
are not conjugated, there is very weak electronic coupling between the D/A groups and the bridge itself.
Hence, to a good approximation, the electronic
contribution from the bridge can be effectively ignored, it simply serves to hold the donor and acceptor in fixed relative positions.
Secondly, the displacement vectors on donor and acceptor moieties are very much akin to  totally symmetric normal modes
of the corresponding moieties, and do not correspond any single normal vibrational  mode of the whole molecule.

In the next two Sections, we explore the role of symmetry in detail.
We first project the PLMs onto the normal modes of both the donor or acceptor moieties
and onto entire molecules (donor-bridge-acceptor).  Using these reduced PLMs we
 compute rate constants and compare to the numerically exact results obtained using the full
modes.  Then we do a similar set of projections using simply the geometric change from initial to final configurations
to explore  the relation between the PLMs and geometry.

\section{Symmetry of the Primary Lanczos Modes}

Fig.~\ref{fragProj} shows the projection of the PLMs  onto the local vibrational modes of
D/A moieties in molecules of c14ee and d26ae.
In each case, we label the dominant contributions by the
irreducible representation (IR) of the moiety. The normal mode basis is generated as follows:
first, we take the geometry of donor or acceptor moiety and add  the necessary hydrogens.
Then the $D_{2h}$ symmetry is applied to naphthalene using GaussView 5.
The benzaldehyde moiety is unchanged because it has very low  symmetry:  $C_{s}$ if planar and $C_{1}$  other wise.
If one treats the aldehyde group as a local site, one can classify the ring-motions of
benzaldehyde in terms of the $C_{2v}$ irreducible representations.
As a result, the assigned irreducible representations are exact for naphthalene but approximate for benzaldehyde.
We then assign a weight to each mode viz.
$$
w_i = \frac{\left\langle \overrightarrow{M_{i}}|\overrightarrow{PLM}\right\rangle ^{2}}{\sqrt{\sum_{i}\left\langle \overrightarrow{M_{i}}|\overrightarrow{PLM}\right\rangle ^{2}}}
$$
where $\overrightarrow{M_{i}}$ is the displacement vector of the $i$th normal mode.
The symmetrization of naphthalene introduces another problem
in that the projection depends on the orientation of the basis vectors.
Thus, we orient the original and symmetrized frames by first aligning the center of masses
and then minimize the RMS displacement between atoms.
Analyzing the projections it becomes clear that in all cases, the dominant components
belong to totally symmetric $A_{g}$ or $A_1$ irreducible representations,  in agreement
with the intuitive observations from Fig. ~\ref{LanczosModes}.

This behavior is not unique for the napthyl-bridge-benzaldehyde  system.
To see this, we repeated the analysis using various acceptor groups as shown in Fig.~\ref{benz}.
together with their PLMs and correlation functions for different numbers of projected modes.
% and d26ae and compute the
%coupling correlation functions in Eq.~\ref{cor-fun} and displacement vectors of their
%PLMs.  Fig.~\ref{benz} shows the correlation functions and PLMs for  two phenyl-[bridge]-BZ
For both molecules,  with 4 projected modes or more, the excellent agreement with exact (all modes) result out to 10 fs indicates that
the projection scheme provides an accurate description of the electronic coupling in  these cases as well.
%Moreover, the PLMs in each case are similar to the PLMs in the napthyl-[bridge]-BZ
Moreover, the PLMs are qualitatively similar to the PLM of unchanged c14ee.
The displacements on the benzaldehyde moiety are almost identical, while on the phenyl and anthracene moieties they belong to totally symmetric irreducible representations as well.

%Till now we have shown that in the donor and acceptor moieties, PLMs are collections of normal modes with totally symmetric representation. I
%
%In next section we'll show that several of these normal modes of donor and acceptor
%are enough to recover the PLM of the whole molecule, namely, the bridge is negligible.

%\begin{figure*}[tbh]
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/C14eeBenzaldehydeProj.pdf}}
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/C14eeNaphSymmProj.pdf}} \\
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/D26aeBenzaldehydeProj.pdf}}
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/D26aeNaphSymmProj.pdf}}
%\caption{Projection of PLMs onto (a) benzaldehyde in c14ee (b) symmetrized naphthalene in c14ee, (c) benzaldehyde in d26ae and (d) symmetrized naphthalene in d26ae.
%The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are colorcoded. The assigned IRs for naphthalene are exact
% whereas the  IRs are only approximate for benzaldehyde. \label{fragProj}}
%\end{figure*}

\begin{figure*}[th]
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure3a.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure3b.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure3c.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure3d.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/benzeneC14ee10fs.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/benzeneD26ae10fs.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/PrimeModeBenzeneC14ee.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/PrimeModeBenzeneD26ae.pdf}}
\caption{The correlation functions of projected modes for c14ee with the naphthalene moiety
replaced by (a) phenyl ring and (b) anthracene, with their PLMs shown in (c) and (d). \label{benz}}
%\caption{The correlation function of PLM compared to the exact one calculated with all normal modes for the (a) c14ee (b) d26ae, with naphthalene replaced by phenyl ring.Their PLMs are in (c) for c14ee and (d) for d26ae.\label{benz}}
\end{figure*}

\begin{figure*}[th]
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure4a.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure4b.pdf}}
\caption{The (a)  ($A_{u}$) HOMO and (b)  ($B_{2g}) $LUMO of naphthalene.\label{naphHOMOLUMO}}
\end{figure*}

%{\bf  Comment: this paragraph needs fleshing out since there's a lot going on here.}
It is not a coincidence that the PLMs belong to the totally symmetric irreducible representation of the isolated donor and acceptor moieties.
This connection can be understood by analyzing the corresponding  the changes in the electron density that accompany the transition.
For example, the PLM on the naphthalene part shown in  Fig. ~\ref{LanczosModes}
largely corresponds to a symmetric ring-stretching mode,  involving carbons
C1 - C2, C3 - C4, C5 - C6, and C7 - C8.
During the exciton transfer, an electron is promoted from the naphthalene HOMO to the naphthalene LUMO (shown in Fig. ~\ref{naphHOMOLUMO})
and one expects that changes in the bond lengths should reflect the changes in
electronic population.
For naphthalene, a HOMO$\to$ LUMO transition would
decrease the $\pi$-bond order between C1 - C2, C3 - C4, C5 - C6, and C7 - C8.
%As shown in
%electronic population in the  naphthalene HOMO contributes to the $\pi$ bond-order
%between these atoms while population in the naphthalene LUMO  would decrease
%$\pi$-bonding between C1 - C2, C3 - C4, C6-C7, and C8-C9.
% Since bond length does not depend on the sign of
%electron orbital density, naphthalene changes the geometry in a symmetric way, and
Similar statements can be made for the phenyl and anthracene systems.
In next section,  we examine the PLMs and bond-length changes that occur during an energy  transfer event.
We show that, in a more quantitative way,   while the  PLMs can be understood in terms of
geometric changes in the molecule,  the reverse is not true.
It is not at all straightforward to determine the PLMs by taking the difference between the initial
and final geometries of the molecule.
%{\bf Question:  if you examine the bond-lengths of the Naphthalene anion,  do you see a similar behavior?}

\begin{figure*}[th]
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure5a.pdf}}
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure5b.pdf}}
\caption{Projections of the PLM onto the normal modes of (a) c14ee and (b) d26ae.\label{LancProj}}
\end{figure*}

\section{Localized Property of the Primary Lanzcos Mode}

We have established  that the Primary Lanzcos Mode is more like the normal modes of the isolated
donor and acceptor moieties, rather than of the entire molecule. The relation between the
PLM and bond length change partially verifies our statement.
In this section, we explore  the localization in greater detail.
First, we project the PLM onto the normal modes of entire molecule,
which is shown in Fig. ~\ref{LancProj}, as a comparison to Fig. ~\ref{fragProj}, where the normal modes of the individual
moieties are used.    It is clear that on the basis of entire molecule, more modes are
significantly involved.   This is in contrast to the projection of the PLM onto only the local modes of the isolated moieties,
only a handful modes contribute.  Since the PLM  best captures the initial nuclear dynamics,
 its close relation with local sites reveals the fact that the exciton transfer here is more like a local excitation/de-excitation
coupled by exchange interaction,  in accordance with the Dexter mechanism \cite{dexter1953theory}.

\begin{figure*}[tbh]
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure6a.pdf}}
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure6b.pdf}}
\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c14ee and (b) d26ae.
They are almost same to Fig. ~\ref{fragProj}(b) and (d) except for a mode with $B_{2u}$ symmetry in c14ee.
Embedded are the most significant modes, namely, the 33rd modes \label{projNaph}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/C14eeNaphProj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/D26aeNaphProj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeNaph1stMode.png}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeNaph1stMode.png}}
%\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c14ee and (b) d26ae. They are almost same to Fig. ~\ref{fragProj}(b) and (d) except for a mode with $b_{2u}$ symmetry in (c). In the second row are the most dominant mode in projections above, namely, the 33rd normal mode of naphthalene in (c) c14ee and (d) d26ae. The mode in (d) belongs to  $A_g$ representation quite well while in (c), hydrogens move  in the  $B_{2u}$ way. \label{projNaph}}
\end{figure*}

%To construct coupling modes from the projections. We take the normal modes in  Fig. ~\ref{projNaph}, starting from the most significant ones, and sum their displacement vectors multiplied by their weights in projection. Results are summarized in Fig. ~\ref{backCorr}. Several conclusions can be made here. First, taking all modes in both sites, the ``NfBf'' in graph, gives same correlation function to the exact PLM. It verifies our observation that the bridge unit is negligible in PLM. Secondly, taking one mode in each fragment is not enough. 5 modes in each site is good enough and taking 10 gives indistinguishable correlation functions. Nevertheless, correlation function does not need to coincide perfectly to give a good rate constant so we calculate the rate constants for various combinations up to 10 modes in each fragment. The contour plots of the absolute values of their relative errors compared to the rate of PLM are shown in the second row in  Fig. ~\ref{backCorr}. We can see that, roughly, taking 3 modes in benzaldehyde and 2 modes in naphthalene suffices to give rate constants within 10\% error. The fact that more modes are needed in benzaldehyde is because more normal modes in it are involved in PLMs, as can be seen in Fig. ~\ref{fragProj}.

\begin{figure*}[tbh]
\subfloat[]{\includegraphics[width=\columnwidth]{Chapters/chap3/Figure7a.pdf}}
\subfloat[]{\includegraphics[width=\columnwidth]{Chapters/chap3/Figure7b.pdf}} \\
\subfloat[]{\includegraphics[width=\columnwidth]{Chapters/chap3/Figure7c.pdf}}
\subfloat[]{\includegraphics[width=\columnwidth]{Chapters/chap3/Figure7d.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateC14ee.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateD26ae.pdf}}
\caption{Correlation functions for different combinations of normal modes are shown for (a) c14ee and (b) d26ae.  The ``exact'' ones refer are for the PLMs.  ``NfBf"
is the mode made up from all normal modes of both the donor and acceptor sites.
The designation ``NxBy'' indicates that the correlation function was constructed using  $x$ most significant normal modes
on naphthalene and $y$ most significant ones on benzaldehyde.   Plots (c) and (d) show the
 relative error in rate constants calculated for various combinations of normal modes compared to the exact result
 or c14ee (c) and d26ae (d) respectively. \label{backCorr}}
\end{figure*}

One may argue that bridge is not included in our comparison.
As showed in Fig.~\ref{LanczosModes}, one can see that very few motions involving the bridge contribute to the PLM.
Thus, that we anticipate that we can construct the PLM using only local modes on the donor and acceptor units.
 In the next section, we  quantitatively verify this by using only
dominant modes on the  donor and acceptor to construct coupling modes.

%----- THIS PARAGRAPH IS A BIT CRYPTIC--------
However, before we can compare different ways to construct the Lanczos modes, we first need to
address a  subtle problem.   In the previous section, we symmetrized the geometry of naphthalene
for the convenience in assigning  irreducible representations to the vibrational modes.
However, for constructing the modes
for the entire unit one needs to use the optimized rather than symmetrized geometry.
In Fig. ~\ref{projNaph}  we show the project of the PLM onto the modes for optimized
naphthalene.  The irreducible representations have been roughly assigned to the dominant modes.
%Since we did not symmetrize benzaldehyde, its projection remains same.
The projections are
almost same to the ones on the symmetrized geometry, except a new $B_{2u}$ mode is involved
in c14ee. However, it does not exist in d26ae. The reason is that the most significant
mode of c14ee and d26ae are slightly different. The corresponding displacement vectors are
embedded in Fig. ~\ref{projNaph}. For c14ee, the dominant mode is not an exact $A_g$ mode, because
carbons move in the way of $A_g$ while
hydrogens behave like $B_{2u}$. On the contrary, d26ae has
a mode more similar to $A_g$.
As the result, in the projection of naphthalene in c14ee, a  $B_{2u}$
mode is needed to correct the hydrogen motions.

To construct coupling modes, we collect a small number of modes on both naphthalene
and benzaldehyde in the order of decreasing weights, then sum up the displacement vectors
multiplied by their weights.
We then bench-mark the quality of taking various different  combinations
of normal modes by computing the coupling auto-correlation function in  Eq. 3 and comparing to
the exact result obtained by including all modes.
We denote these as N$x$B$y$ where $x$ denotes the number of naphthalene  local modes and $y$ denotes
the number of benzaldehyde  local modes used in each case.
NfBf denotes that {\em all} local modes are
included.   The correlation functions and rate constants derived from various
combinations of normal modes are summarized in Fig. ~\ref{backCorr}.

 First, if we take all local modes from both moieties, (NfBf)
 the resulting approximated correlation function is indistinguishable from the exact correlation function.
This verifies our observation that the bridge unit is not needed in constructing the
PLM.
%Secondly, taking one mode in each moiety is not enough. 5 modes in each is good
%enough and taking 10 gives almost perfect correlation functions.
In order to achieve adequate agreement with the exact correlation function,
at least 10 of the strongest contributing local modes are needed from both the donor and acceptor units.
%Furthermore, as shown

However, as seen on our previous work \cite{xunmo2014},
the approximate correlation function does not need to give perfect agreement
with the exact correlation function to produce an accurate transition rate constant (Eq. 4).
To assess the accuracy of using different combinations of local modes,
we calculate the transition rate constants for various combinations up to 10 modes on
each moiety and compare to the exact rate.
This data is summarized in the form of contour plots in  Fig. ~\ref{backCorr}(c,d).
For the c14ee case, there is an optimal ``valley'' whereby taking 3 modes from benzaldehyde and 4-6 modes from
naphthalene produces an agreement with the exact result to within 5\%.
For the d26ae case,  fewer number of benzaldehyde modes than naphthalene modes are needed to
give agreement to within 5\% of the exact rate constant.   This is easily anticipated since
naphthalene is simply a larger molecule with more normal modes.

\section{Geometry Change and Relaxation Mode}

We showed that the PLMs agree with bond length changes on the moieties.   We next
consider the relation between the PLM and geometry change accompanying the transition.
First, we use the PLM to approximate geometry change by distorting the molecule
along the PLM.   The magnitude of the distortion
 is determined  by minimizing the average bond length difference of the four bonds on naphthalene
 which stretch significantly in PLM, between the optimized and approximate geometries. In Table 1 we list the differences between two geometries.
Comparing the maximum difference of bond
lengths and angles between the approximated and true final states, the differences are very small,
so PLMs seem to give fairly good approximations of geometry changes.

% We will then compare the projection of geometry change to that of the PLM.
% They seem to contradict each other. We conclude that the apparent contradiction
% reveals the mechanism of the transfer reaction, which is consist of two steps, agreeing with
% the Born-Oppenheimer principle.

\begin{table*}[t]
 \caption{Approximated geometry using the PLM and the relaxation modes (RM) compared to acceptor states}
 \label{aprroxGeom}
 \begin{tabular}{lllll}
   \hline
   Mode used & C14ee-PLM   & C14ee-DNM  & D26ae-PLM  & D26ae-DNM\\
   \hline
   Max. bond length difference (\AA)   & 0.034 & 0.160 &0.039 & 0.283   \\
     Max. bond angle difference (rad)   & 0.053 &0.075 & 0.057 &0.135   \\
   \hline
 \end{tabular}
\end{table*}

\begin{figure*}[th]
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8a.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8b.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8c.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8d.pdf}}
\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) benzaldehyde and (b) naphthalene sites in c14ee, and d26ae in (c) and (d). Except for some low frequency modes, they are similar to the projections of PLM. \label{geomDiffFragProj}}
\end{figure*}

%
%First we add PLM with a magnitude to initial donor state geometry,
%to get an approximate geometry of final state.
%In Table. ~\ref{aprroxGeom} we list the maximum difference of bond
%lengths and angles between the approximated and real final states. The differences are small,
%so PLMs seem to give fairly good approximations of geometry changes.
%In this part we discuss the mechanism why PLM is totally symmetric in donor and acceptor moieties. We show that it corresponds to geometry change of the moieties in the transfer. However, simply taking the difference of coordinates of initial and final states does not give PLM. By breaking down geometry change, we get the insight that the entire process consists of two steps, the fast excitation transfer facilitated by PLM and the relaxation after that.
%Looking at the symmetry of PLM in Fig. ~\ref{LanczosModes}, especially the naphthalene, it is basically the stretch of four bonds being symmetric to each other. Comparing the bonding and antibonding in the HOMO/LUMO of naphthalene in Fig. ~\ref{naphHOMOLUMO}, we noticed that these four bonds change lengths dramatically in deexcitation, so does PLM correspond to geometry change? Yes, and no. First, we prove the "yes".

%By adding  PLM with a magnitude to initial donor state, we can get an approximated geometry to final acceptor state. The magnitude is decided by minimizing the average bond length difference of the four bonds in naphthalene mentioned above, between real acceptor state and the approximated one. In Table. ~\ref{aprroxGeom} we list the maximum difference of bond lengths and angles between the derived and real final states. The differences are small. PLM seems to give fairly good approximation of final state geometry.

However, this is only one side of the story and we  need try to do this in reverse, {\em i.e.}, can we
determine the PLM from simply geometric changes accompanying the transition? To see if this is possible,
we can project the geometry change onto the normal modes of molecule and moieties respectively.  The
results for our two test cases are shown  in Fig. ~\ref{geomDiffFragProj} and \ref{geomDiffProj}.
When projected onto the whole molecule, we see that geometry change is mostly dominated
by one  very low frequency mode  corresponding to an internal  torsion of the entire donor-bridge-acceptor molecule.
Compared to the PLMs in the same basis in Fig. ~\ref{LancProj}
 we see that  PLMs  have many more modes involved.
However, if we compare the projections onto the  moieties in  Fig. ~\ref{fragProj}
and \ref{geomDiffFragProj}, the geometry changes resemble PLMs well, except in the low frequency region.
In essence, simply changing representation completely changes the implied dynamics.

% \begin{table*}[bh]
%   \caption{Miscellaneous single mode rate constants compared to exact ones}
%   \label{rates}
%   \begin{tabular}{lllll}
%     \hline
%     Mode(s) used &  All NM  & PLM  & Geometry change (GC) & GC without RM component\\
%     \hline
%     Rate constants in c14ee/$s^{-1}$   & 3.66E9 & 3.69E9 & 5.28E9 & 4.31E9   \\
%     Rate constants in d26ae/$s^{-1}$   & 4.66E4 &4.80E4 & 1.30E4 & 5.11E4 \\
%     \hline
%   \end{tabular}
% \end{table*}

%However, this is only one side of the story. In Fig. ~\ref{geomDiffProj} we project geometry change onto the normal modes of molecule. It does not look same to the projections of PLM in Fig. ~\ref{LancProj}. The geometry change of both c14ee and d26ae are dominated by single mode with very low frequency, shown in Fig. ~\ref{geomDiffProj}(c) and (d). We term them the dominant mode relaxation mode (RM) for the reason below. RM does not resemble PLM at all.

\begin{figure*}[th]
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure9a.pdf}}
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure9b.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeDADiffproj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeDADiffproj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeNM2.png}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeNM1.png}}
\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) c14ee and (b) d26ae. They are both dominated by single mode, the relaxation mode (RM), which is embedded.\label{geomDiffProj}}
\end{figure*}

\begin{figure*}[th]
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure10a.pdf}}
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure10b.pdf}}
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure10c.pdf}}
\caption{Correlation functions of relaxation mode (RM), PLM, geometry change (GC), and geometry change with the RM component eliminated for (a) c14ee and (b) d26ae.
(c) Relative comparison of the rate constants computed using different sets of reduced modes.  The exact rate is computed using the full set of normal modes:
blue = c14ee, gold =d26ae. }
\label{Corr}
\end{figure*}

The resolution to this inconsistency is to distinguish between the two types of geometric changes.
One is the internal changes within  the moieties.  These are well represented  by the PLM.
The other is the gross motion of the entire molecule, which we shall refer to as the ``relaxation mode'' (RM).  This latter motion
is not well represented by the PLM.
%Bond length change belongs to the first type while the relaxation modes
%correspond to the second, as suggested by the orientation of displacement vectors and the low frequency.
 These two kinds of motion  correspond to two different steps that accompany the electronic  transition. The
internal motion primarily affects C=C bond lengths,  and
hence is strongly coupled to the $\pi$-electronic degrees of freedom, while gross motion of moieties corresponds
to  relaxation after exciton transfer has occurred. This is verified in Table 1, where we use the relaxation mode to approximate the final geometry. The procedure is similar to that of PLM. Although RM is the dominant mode in the projection, it gives much worse approximated bond lengths and angles.
% In short, the PLM is a subvector within the relaxation mode.

%The procedure is same as before except the relaxation mode is used instead of the PLM.
Since the PLM explains the short-time dynamics and can approximate the local geometry changes within the individual
moieties very well, we anticipate that the PLMs facilitate the energy transfer step. To verify
our prediction, we computed correlation functions of the electron/phonon coupling operators
 (Eq. 4) using different  subsets of nuclear motions  to estimate the couplings:
 PLM,  RM,  geometry change (GC) , and
geometry change with the RM component eliminated (GC-RM).
The latter two correspond to taking the total geometric difference between the initial
and final states of the molecule and  projecting this onto normal modes, and to taking the geometric difference and
subtracting off the relaxation mode.
The various correlation functions and rate
constants are summarized in Fig. ~\ref{Corr}.
The exact results are obtained by  using all normal modes and couplings.
The PLM gives nearly perfect agreement to the exact calculation  for both the
time-correlation functions (Fig.~\ref{Corr}(a,b))  and the computed rates for both molecules considered  (Fig.~\ref{Corr}(c)).
The relaxation mode (RM) gives no contribution to the correlation function or the rate.
Finally, using just the over-all geometric change (GC) gives a poor estimate of both the correlation
function and the rate.   GC-RM gives the initial transient dynamics in the correlation function and
a reasonable approximation to  the overall rate.  However, the best agreement overall is
obtained by using the PLM identified using the Lanczos search algorithm.

%The results are consistent with our intuition.  The relaxation mode a gives negligible correlation
%function, so its contribution to the rate constant can be neglected.
%Using just the geometry change gives a reasonable rate and it gets even better when the RM component is removed, but
%neither of them beats the PLM.  GC-RM
%%The difference of bond lengths and angles are listed in Table. ~\ref{aprroxGeom}.
%

%Using the relaxation mode rather than the PLM we see that being the
%dominant mode in geometry change, relaxation mode gives much poorer approximation for
%both bond lengths and angles, which is reasonable due to the different nature of the internal and gross motions.
%%It is expected as we understand there are two types of motions here.
%
%

\section{Discussion}
%From the significance of relaxation mode in geometry change and its negligible role in rate
%constant we conclude that the entire transfer process consists of two steps, in the agreement
%of Born-Oppenheimer approximation. At first, the excited electron in donor moiety de-excites
%while one electron in acceptor moiety gets excited. This fast transfer is facilitated by PLM
%and changes bond lengths of donor and acceptor fragments in a totally symmetric way,
%agreeing with the form of HOMO/LUMO. After the exciton transfer, the entire molecule
%undergo es slow but relatively large relaxation under the new electron distribution.  The change
%is mainly the gross motions of fragments so mainly torsional normal modes with very low
%frequencies are involved. This works clarifies the role of shows the primary Lanczos mode.
%It participates the reaction mainly in the short-time fast transfer step, and is the collection
%of normal modes in a way that implicit knowledge of HOMO/LUMO is included.  We also
%show the power of our methodology in analyzing nuclear motions. We are able to discuss
%the contributions of certain directions in rate constants and their roles in transfer.   By
%investigating PLM and geometry change, we detail the picture of transfer in agreement with
%the Born-Oppenheimer approximation. In the future, we can apply our method to study
%dynamics of other systems. We are trying it for molecules involving bond breaking. If
%succeeded, our approach can be useful in the study of selective reaction.

We presented here a further exploration of the classes of nuclear motions that accompany
and electronic energy transition.
% Our approach  is similar to the way Google and Netflix ranks
% page-hits or movie preferences based upon similarity to a set of search criteria identifies
% a subset of nuclear motions that are most strongly coupled to the transition and ranks them according to the
% coupling strength.
We show that deeper insight can be gained by analyzing the primary  modes
and comparing them to both the geometric distortion of the molecule and to the electronic orbitals
involved in the transition.

Our results also suggest that the energy transfer process in these systems occurs in two distinct steps.
The initial transfer from the donor to acceptor occurs in a fixed nuclear frame--as per the Condon principle.
This fast transfer is facilitated by the PLM and  involves excitations  in the C=C bond lengths of
donor and acceptor fragments in accordance with changes in the HOMO/LUMO populations of each fragment.
 After the exciton transfer, the entire molecule
undergoes a slow but large geometric relaxation under the new electronic distribution.

Finally, we emphasize that the PLM approach and this analysis need not be limited to
the energy transfer cases studied here.  Combined with the time-convolutionless master equation
approach, this provides  a robust and efficient way for computing state-to-state  transitions rates
for a wide class of molecular systems.

% \begin{acknowledgments}
% This work was funded in part by grants from  the National Science
% Foundation (CHE-1362006) and the Robert A. Welch Foundation (E-1337).
% We thank Dr. Hao Li for useful comments and suggestions.
% \end{acknowledgments}

% \bibliography{fragmentanalysis}
%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{16}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Marcus}(1956)}]{marcus1956theory}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
  {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {24}},\ \bibinfo
  {pages} {966} (\bibinfo {year} {1956})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Marcus}(1965)}]{marcus1965theory}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
  {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {43}},\ \bibinfo
  {pages} {679} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Marcus}(1993)}]{marcus1993electron}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
  {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Reviews of Modern Physics}\ }\textbf {\bibinfo {volume} {65}},\ \bibinfo
  {pages} {599} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Miller}, \citenamefont {Calcaterra},\ and\
  \citenamefont {Closs}(1984)}]{miller1984intramolecular}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Miller}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Calcaterra}},
  \ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Closs}},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of the
  American Chemical Society}\ }\textbf {\bibinfo {volume} {106}},\ \bibinfo
  {pages} {3047} (\bibinfo {year} {1984})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Closs}\ \emph {et~al.}(1988)\citenamefont {Closs},
  \citenamefont {Piotrowiak}, \citenamefont {MacInnis},\ and\ \citenamefont
  {Fleming}}]{closs1988determination}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
  {Closs}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Piotrowiak}},
  \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont {MacInnis}}, \ and\
  \bibinfo {author} {\bibfnamefont {G.~R.}\ \bibnamefont {Fleming}},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of the
  American Chemical Society}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo
  {pages} {2652} (\bibinfo {year} {1988})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Closs}\ \emph {et~al.}(1989)\citenamefont {Closs},
  \citenamefont {Johnson}, \citenamefont {Miller},\ and\ \citenamefont
  {Piotrowiak}}]{closs1989connection}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
  {Closs}}, \bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Johnson}},
  \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Miller}}, \ and\
  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Piotrowiak}},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of the
  American Chemical Society}\ }\textbf {\bibinfo {volume} {111}},\ \bibinfo
  {pages} {3751} (\bibinfo {year} {1989})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Pereverzev}\ and\ \citenamefont
  {Bittner}(2006)}]{pereverzev:104906}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Pereverzev}}\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
  {Bittner}},\ }\href {\doibase 10.1063/1.2348869} {\bibfield  {journal}
  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
  {volume} {125}},\ \bibinfo {eid} {104906} (\bibinfo {year}
  {2006})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Tamura}\ \emph {et~al.}(2008)\citenamefont {Tamura},
  \citenamefont {Ramon}, \citenamefont {Bittner},\ and\ \citenamefont
  {Burghardt}}]{tamura:107402}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
  {Tamura}}, \bibinfo {author} {\bibfnamefont {J.~G.~S.}\ \bibnamefont
  {Ramon}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Bittner}},
  \ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Burghardt}},\
  }\href {\doibase 10.1103/PhysRevLett.100.107402} {\bibfield  {journal}
  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
  {100}},\ \bibinfo {eid} {107402} (\bibinfo {year} {2008})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Tamura}, \citenamefont {Bittner},\ and\ \citenamefont
  {Burghardt}(2007)}]{tamura:021103}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
  {Tamura}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Bittner}},
  \ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Burghardt}},\
  }\href {\doibase 10.1063/1.2431358} {\bibfield  {journal} {\bibinfo
  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
  {126}},\ \bibinfo {eid} {021103} (\bibinfo {year} {2007})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Singh}\ \emph {et~al.}(2009)\citenamefont {Singh},
  \citenamefont {Bittner}, \citenamefont {Beljonne},\ and\ \citenamefont
  {Scholes}}]{singh:194905}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Singh}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Bittner}},
  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Beljonne}}, \ and\
  \bibinfo {author} {\bibfnamefont {G.~D.}\ \bibnamefont {Scholes}},\ }\href
  {\doibase 10.1063/1.3259549} {\bibfield  {journal} {\bibinfo  {journal} {The
  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {131}},\ \bibinfo
  {eid} {194905} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bittner}\ and\ \citenamefont
  {Silva}(2014)}]{Bittner:2014aa}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
  {Bittner}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {Silva}},\ }\href {http://dx.doi.org/10.1038/ncomms4119} {\bibfield
  {journal} {\bibinfo  {journal} {Nat Commun}\ }\textbf {\bibinfo {volume}
  {5}},\ \bibinfo {pages} {3119} (\bibinfo {year} {2014})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Yang}\ and\ \citenamefont
  {Bittner}(2014)}]{xunmo2014}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
  {Yang}}\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
  {Bittner}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
  Journal of Physical Chemistry A}\ }\textbf {\bibinfo {volume} {118}},\
  \bibinfo {pages} {5196} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Subotnik}\ \emph {et~al.}(2010)\citenamefont
  {Subotnik}, \citenamefont {Vura-Weis}, \citenamefont {Sodt},\ and\
  \citenamefont {Ratner}}]{subotnik2010predicting}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
  {Subotnik}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Vura-Weis}},
  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Sodt}}, \ and\
  \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Ratner}},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The Journal of
  Physical Chemistry A}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo {pages}
  {8665} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Grover}\ and\ \citenamefont
  {Silbey}(1970)}]{grover:2099}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~K.}\ \bibnamefont
  {Grover}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Silbey}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {52}},\ \bibinfo
  {pages} {2099} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Rice}\ and\ \citenamefont
  {Gartstein}(1994)}]{rice:2504}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Rice}}\ and\ \bibinfo {author} {\bibfnamefont {Y.~N.}\ \bibnamefont
  {Gartstein}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Physical review letters}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo
  {pages} {2504} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Dexter}(1953)}]{dexter1953theory}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~L.}\ \bibnamefont
  {Dexter}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo
  {pages} {836} (\bibinfo {year} {1953})}\BibitemShut {NoStop}%
\end{thebibliography}%

% \end{document}
%
% ****** End of file template.aps ******

### 2016-03-12 FontTest/fonttest.tex
Initialize

\chapter*{Font test}

\emph{textrm:}
\textrm{On the other hand, we denounce with righteous indignation and
  dislike men who are so beguiled and demoralized by the charms of
  pleasure of the moment, so blinded by desire, that they cannot
  foresee the pain and trouble that are bound to ensue; and equal
  blame belongs to those who fail in their duty through weakness of
  will, which is the same as saying through shrinking from toil and
  pain. These cases are perfectly simple and easy to distinguish. In a
  free hour, when our power of choice is untrammelled and when nothing
  prevents our being able to do what we like best, every pleasure is
  to be welcomed and every pain avoided. But in certain circumstances
  and owing to the claims of duty or the obligations of business it
  will frequently occur that pleasures have to be repudiated and
  annoyances accepted. The wise man therefore always holds in these
  matters to this principle of selection: he rejects pleasures to
  secure other greater pleasures, or else he endures pains to avoid
  worse pains.}

\pagebreak

\input{FontTest/textfragment}

\pagebreak 
\emph{textsf:}
\textsf{On the other hand, we denounce with righteous indignation and
  dislike men who are so beguiled and demoralized by the charms of
  pleasure of the moment, so blinded by desire, that they cannot
  foresee the pain and trouble that are bound to ensue; and equal
  blame belongs to those who fail in their duty through weakness of
  will, which is the same as saying through shrinking from toil and
  pain. These cases are perfectly simple and easy to distinguish. In a
  free hour, when our power of choice is untrammelled and when nothing
  prevents our being able to do what we like best, every pleasure is
  to be welcomed and every pain avoided. But in certain circumstances
  and owing to the claims of duty or the obligations of business it
  will frequently occur that pleasures have to be repudiated and
  annoyances accepted. The wise man therefore always holds in these
  matters to this principle of selection: he rejects pleasures to
  secure other greater pleasures, or else he endures pains to avoid
  worse pains.}

\emph{texttt:}
\texttt{On the other hand, we denounce with righteous indignation and
  dislike men who are so beguiled and demoralized by the charms of
  pleasure of the moment, so blinded by desire, that they cannot
  foresee the pain and trouble that are bound to ensue; and equal
  blame belongs to those who fail in their duty through weakness of
  will, which is the same as saying through shrinking from toil and
  pain. These cases are perfectly simple and easy to distinguish. In a
  free hour, when our power of choice is untrammelled and when nothing
  prevents our being able to do what we like best, every pleasure is
  to be welcomed and every pain avoided. But in certain circumstances
  and owing to the claims of duty or the obligations of business it
  will frequently occur that pleasures have to be repudiated and
  annoyances accepted. The wise man therefore always holds in these
  matters to this principle of selection: he rejects pleasures to
  secure other greater pleasures, or else he endures pains to avoid
  worse pains.}

\emph{textit:}
\textit{On the other hand, we denounce with righteous indignation and
  dislike men who are so beguiled and demoralized by the charms of
  pleasure of the moment, so blinded by desire, that they cannot
  foresee the pain and trouble that are bound to ensue; and equal
  blame belongs to those who fail in their duty through weakness of
  will, which is the same as saying through shrinking from toil and
  pain. These cases are perfectly simple and easy to distinguish. In a
  free hour, when our power of choice is untrammelled and when nothing
  prevents our being able to do what we like best, every pleasure is
  to be welcomed and every pain avoided. But in certain circumstances
  and owing to the claims of duty or the obligations of business it
  will frequently occur that pleasures have to be repudiated and
  annoyances accepted. The wise man therefore always holds in these
  matters to this principle of selection: he rejects pleasures to
  secure other greater pleasures, or else he endures pains to avoid
  worse pains.}

\emph{textsf:}
\textsl{On the other hand, we denounce with righteous indignation and
  dislike men who are so beguiled and demoralized by the charms of
  pleasure of the moment, so blinded by desire, that they cannot
  foresee the pain and trouble that are bound to ensue; and equal
  blame belongs to those who fail in their duty through weakness of
  will, which is the same as saying through shrinking from toil and
  pain. These cases are perfectly simple and easy to distinguish. In a
  free hour, when our power of choice is untrammelled and when nothing
  prevents our being able to do what we like best, every pleasure is
  to be welcomed and every pain avoided. But in certain circumstances
  and owing to the claims of duty or the obligations of business it
  will frequently occur that pleasures have to be repudiated and
  annoyances accepted. The wise man therefore always holds in these
  matters to this principle of selection: he rejects pleasures to
  secure other greater pleasures, or else he endures pains to avoid
  worse pains.}

\emph{textsc:}
\textsc{On the other hand, we denounce with righteous indignation and
  dislike men who are so beguiled and demoralized by the charms of
  pleasure of the moment, so blinded by desire, that they cannot
  foresee the pain and trouble that are bound to ensue; and equal
  blame belongs to those who fail in their duty through weakness of
  will, which is the same as saying through shrinking from toil and
  pain. These cases are perfectly simple and easy to distinguish. In a
  free hour, when our power of choice is untrammelled and when nothing
  prevents our being able to do what we like best, every pleasure is
  to be welcomed and every pain avoided. But in certain circumstances
  and owing to the claims of duty or the obligations of business it
  will frequently occur that pleasures have to be repudiated and
  annoyances accepted. The wise man therefore always holds in these
  matters to this principle of selection: he rejects pleasures to
  secure other greater pleasures, or else he endures pains to avoid
  worse pains.}

\emph{textbf:}
\textbf{On the other hand, we denounce with righteous indignation and
  dislike men who are so beguiled and demoralized by the charms of
  pleasure of the moment, so blinded by desire, that they cannot
  foresee the pain and trouble that are bound to ensue; and equal
  blame belongs to those who fail in their duty through weakness of
  will, which is the same as saying through shrinking from toil and
  pain. These cases are perfectly simple and easy to distinguish. In a
  free hour, when our power of choice is untrammelled and when nothing
  prevents our being able to do what we like best, every pleasure is
  to be welcomed and every pain avoided. But in certain circumstances
  and owing to the claims of duty or the obligations of business it
  will frequently occur that pleasures have to be repudiated and
  annoyances accepted. The wise man therefore always holds in these
  matters to this principle of selection: he rejects pleasures to
  secure other greater pleasures, or else he endures pains to avoid
  worse pains.}

\emph{textmd:}
\textmd{On the other hand, we denounce with righteous indignation and
  dislike men who are so beguiled and demoralized by the charms of
  pleasure of the moment, so blinded by desire, that they cannot
  foresee the pain and trouble that are bound to ensue; and equal
  blame belongs to those who fail in their duty through weakness of
  will, which is the same as saying through shrinking from toil and
  pain. These cases are perfectly simple and easy to distinguish. In a
  free hour, when our power of choice is untrammelled and when nothing
  prevents our being able to do what we like best, every pleasure is
  to be welcomed and every pain avoided. But in certain circumstances
  and owing to the claims of duty or the obligations of business it
  will frequently occur that pleasures have to be repudiated and
  annoyances accepted. The wise man therefore always holds in these
  matters to this principle of selection: he rejects pleasures to
  secure other greater pleasures, or else he endures pains to avoid
  worse pains.}

\uppercase{On the other hand, we denounce with righteous indignation
  and dislike men who are so beguiled and demoralized by the charms of
  pleasure of the moment, so blinded by desire, that they cannot
  foresee the pain and trouble that are bound to ensue; and equal
  blame belongs to those who fail in their duty through weakness of
  will, which is the same as saying through shrinking from toil and
  pain. These cases are perfectly simple and easy to distinguish. In a
  free hour, when our power of choice is untrammelled and when nothing
  prevents our being able to do what we like best, every pleasure is
  to be welcomed and every pain avoided. But in certain circumstances
  and owing to the claims of duty or the obligations of business it
  will frequently occur that pleasures have to be repudiated and
  annoyances accepted. The wise man therefore always holds in these
  matters to this principle of selection: he rejects pleasures to
  secure other greater pleasures, or else he endures pains to avoid
  worse pains.}

### 2016-03-12 FrontBackmatter/Abstract.tex
Initialize

%*******************************************************
% Abstract ( 350 words max ! )
%*******************************************************
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Abstract}
Essential microscopic aspects of activated transport in liquids, which
precedes the glass transition, have evaded explanation for
decades. These poorly understood aspects include: the molecular
underpinning of the excess, configurational entropy; the transition
state configurations for the activated transport; the chemical origin
of the fragile vs. strong liquid behavior; and many others. This
dissertation puts forth a radically novel way to address these open
questions, in which liquids near their glass transition are viewed as
structurally degenerate assemblies of strongly interacting, local
sources of frozen-in stress. The thermodynamics and activated barriers
for rearrangement of this stress field have been mapped onto a
Heisenberg model with six-dimensional spins. A meanfield analysis of
the spin model has shown glasses can be viewed as frozen-in patterns
of shear stress and/or uniform compression/dilation, the two extremes
corresponding to the strong and fragile behaviors. A self-consistent
elasticity theory of aperiodic, metastable solids emerges in the
present analysis; it supersedes the traditional elasticity theory,
which fails to self-consistently account for the structural degeneracy
stemming from the inherent mismatch between cohesive forces and steric
repulsion.  The observable elastic constants self-consistently emerge
in the present theory similarly to how the dielectric susceptibility
is determined by the properties of molecular dipoles. First
simulations of the spin model have been carried out. In addition to
direct observations of transition states for the activated transport,
several key features of the glass transition are yielded by the spin
model, including a strongly non-exponential, non-Arrhenius character
of the relaxations and its correlation with the Poisson ratio of the
substance.
\endgroup			
\vfill

### 2016-03-12 FrontBackmatter/Acknowledgments.tex
Initialize

%*******************************************************
% Acknowledgments
%*******************************************************
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
I would like to express my sincere gratitude to Vas Lubchenko, whose
support often extended well beyond of what is normally required from
the graduate advisor. I am also thankful to him for very careful,
critical, and multiple reading of this manuscript which greatly
contributed to its quality.  This work would not be possible without
help of my family: my parents, my wife, and my son.  I am
deeply grateful to Eric R. Bittner who, by being such a wonderful
graduate advisor to my wife, made an inconspicuous, but very important,
influence on everything I did. I also would like to thank to Anne Goj,
Jon Golden, Pyotr Rabochiy, and other members of Bittner and
Lubchenko's groups who made this place such a nice professional
home. I am indebted to Elena and Phil Motuzko for helping me in the
time of need. Last but not least, I thank Sergei Lukyanets without
whom I would never became a scientist.

The numerical part of this work was completed using TLC2 HPC
facility of the University of Houston and Ares cluster of the Texas
Southern University. I am especially indebted to C. J. Tymczak for
providing the access to the latter.

I also gratefully acknowledge support by the Donors of the ACS Petroleum
Research Fund, the Arnold and Mabel Beckman Foundation, the Welch
Foundation Grant E-1765, and the NSF Grant CHE 0956127.
\endgroup

### 2016-03-12 FrontBackmatter/Bibliography.tex
Initialize

%********************************************************************
% Bibliography (can be broken due to biblatex usage)
%*******************************************************
% work-around to have small caps also here in the headline
\manualmark
\markboth{\spacedlowsmallcaps{\bibname}}{\spacedlowsmallcaps{\bibname}} % work-around to have small caps also
\addtocontents{toc}{\protect\vspace{\beforebibskip}} % to have the bib a bit from the rest in the toc
\addcontentsline{toc}{chapter}{\tocEntry{\bibname}}
\label{app:bibliography} 
\printbibliography

### 2016-03-12 FrontBackmatter/Preface.tex
Add preface

%*******************************************************
% Preface
%*******************************************************
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{}
Out yonder there was this huge world, which exists independently of us human beings and which stands before us like a great, eternal riddle, at least partially accessible to our inspection and thinking. The contemplation of this world beckoned as a liberation, and I soon noticed that many a man whom I had learned to esteem and to admire had found inner freedom and security in its pursuit. The mental grasp of this extra-personal world within the frame of our capabilities presented itself to my mind, half consciously, half unconsciously, as a supreme goal. Similarly motivated men of the present and of the past, as well as the insights they had achieved, were the friends who could not be lost.\\
\rightline{- Albert Einstein}
\endgroup

### 2016-03-29 Chapters/chap1/introduction.tex
Change "Fig. ~" to "Fig.~"

%!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex

### 2016-03-29 Chapters/chap2/manuscript.tex
Add footnotes for chapters
Change "Fig. ~" to "Fig.~"

@@
+%!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
+
 % \documentclass[journal=jpcbfk,manuscript=article]{achemso}
@@
 % \newpage
-\chapter{Chapter 2}
+
+\chapter{Chapter 2}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}
 \section{Introduction}
@@
 
-\begin{figure}[b]
+\begin{figure}[h]
 \includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure1}
@@
 In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.
-
-\begin{table*}[t]
-\begin{centering}
-\begin{tabular}{llccc|ccc}
-\hline \hline
- & & \multicolumn{3}{c}{Rates (s$^{-1}$) }& \\
-                &                                                                &   Expt.                 &        Marcus Theory   & This work      & \multicolumn{3}{c}{Marcus theory parameters} \\
- Bridge   &  Structure                                                &        Ref.~\cite{closs1988determination,closs1989connection} &              Ref.
-\cite{Subotnik:2010}  &                  &      $\lambda$ (eV)  &  $\Delta \epsilon$ (eV)  &  $V_{ab}$ ($\mu$eV) \\
-\hline
- c-1,3ea  &  \includegraphics[height=.60cm]{Chapters/chap2/Table1-c13ea.pdf}  &                     3.3E9  &                     3.9E9  &          2.2E9  &           0.823  &           -0.612  &      470.1  \\
-\hline
- c-1,3ee  &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-c13ee.pdf}  &                     7.7E9  &                    2.1E10  &         2.8E10  &           0.810  &           -0.580  &     1687.3  \\
-\hline
- c-1,4ea  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-c14ea.pdf}  &                     4.0E7  &                     1.3E7  &          1.8E7  &           0.817  &           -0.604  &      43.20 \\
-\hline
- c-1,4ee  &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-c14ee.pdf}  &                     1.3E9  &                     3.9E9  &          3.6E9  &           0.826  &           -0.642  &      605.8  \\
-\hline
- d-2,6ae  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-d26ae.pdf}  &                     1.3E5  &                     1.0E4  &          4.7E4  &           0.836  &           -0.577  &    2.239  \\
-\hline
-d-2,6ea  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-d26ea.pdf}  &                     7.0E5  &                     3.9E4  &          5.8E4  &            0.821  &            -0.609  &    2.414  \\
-\hline
- d-2,6ee  &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-d26ee.pdf}  &                     3.1E6  &                     5.0E6  &          4.8E6  &           0.810  &           -0.581  &     22.12  \\
-\hline
- d-2,7ae  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-d27ae.pdf}  &                     1.1E7  &                     2.8E7  &          3.0E7  &           0.826  &           -0.605  &     55.16   \\
-\hline
- d-2,7ea  &  \includegraphics[height=0.6cm]{Chapters/chap2/Table1-d27ea.pdf}  &                     1.5E7  &                     1.8E7  &          4.3E7  &           0.817  &           -0.605  &     65.85  \\
-\hline
- d-2,7ee  &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-d27ee.pdf}  &                     9.1E7  &                     3.5E8  &          3.4E8  &           0.831  &           -0.648  &     185.1  \\
-\hline
- M        &  \includegraphics[height=0.4cm]{Chapters/chap2/Table1-M.pdf}      &                    5.0E10  &                      n.r.  &          1.2E9  &       	   0.896  &		 -0.636  &      357.0 \\
-\hline
-\end{tabular}
-
-\par\end{centering}
-\caption{Comparison of triplet-triplet energy transfer rates obtained from our  approach,  Marcus rates are
-from Ref.\cite{Subotnik:2010}
-and experimental rates from Refs.\cite{closs1988determination,closs1989connection}.   The experimental error is estimated to be 20\% in each
-case studied here.
-The $V_{ab}$ are the diabatic couplings obtained using  Edmiston-Ruedenberg diabatization.
-In each case, D =4-benzophenonyl and A = 2-napthyl.  n.r. = Not Reported.
-}
-\label{summarytable}
-\end{table*}
 
@@
 fully capture the electron/nuclear coupling.
-\subsection{Parameterization from quantum chemistry}
+\subsection{Parameterization From Quantum Chemistry}
 
@@
 
+\begin{sidewaystable}
+% \begin{table*}[t]
+\begin{centering}
+\begin{tabular}{llccc|ccc}
+\hline \hline
+ & & \multicolumn{3}{c}{Rates (s$^{-1}$) }& \\
+                &                                                                &   Expt.                 &        Marcus Theory   & This work      & \multicolumn{3}{c}{Marcus theory parameters} \\
+ Bridge   &  Structure                                                &        Ref.~\cite{closs1988determination,closs1989connection} &              Ref.
+\cite{Subotnik:2010}  &                  &      $\lambda$ (eV)  &  $\Delta \epsilon$ (eV)  &  $V_{ab}$ ($\mu$eV) \\
+\hline
+ c-1,3ea  &  \includegraphics[height=.60cm,width=2cm]{Chapters/chap2/Table1-c13ea.pdf}  &                     3.3E9  &                     3.9E9  &          2.2E9  &           0.823  &           -0.612  &      470.1  \\
+\hline
+ c-1,3ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-c13ee.pdf}  &                     7.7E9  &                    2.1E10  &         2.8E10  &           0.810  &           -0.580  &     1687.3  \\
+\hline
+ c-1,4ea  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-c14ea.pdf}  &                     4.0E7  &                     1.3E7  &          1.8E7  &           0.817  &           -0.604  &      43.20 \\
+\hline
+ c-1,4ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-c14ee.pdf}  &                     1.3E9  &                     3.9E9  &          3.6E9  &           0.826  &           -0.642  &      605.8  \\
+\hline
+ d-2,6ae  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d26ae.pdf}  &                     1.3E5  &                     1.0E4  &          4.7E4  &           0.836  &           -0.577  &    2.239  \\
+\hline
+d-2,6ea  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d26ea.pdf}  &                     7.0E5  &                     3.9E4  &          5.8E4  &            0.821  &            -0.609  &    2.414  \\
+\hline
+ d-2,6ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-d26ee.pdf}  &                     3.1E6  &                     5.0E6  &          4.8E6  &           0.810  &           -0.581  &     22.12  \\
+\hline
+ d-2,7ae  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d27ae.pdf}  &                     1.1E7  &                     2.8E7  &          3.0E7  &           0.826  &           -0.605  &     55.16   \\
+\hline
+ d-2,7ea  &  \includegraphics[height=0.6cm,width=2cm]{Chapters/chap2/Table1-d27ea.pdf}  &                     1.5E7  &                     1.8E7  &          4.3E7  &           0.817  &           -0.605  &     65.85  \\
+\hline
+ d-2,7ee  &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-d27ee.pdf}  &                     9.1E7  &                     3.5E8  &          3.4E8  &           0.831  &           -0.648  &     185.1  \\
+\hline
+ M        &  \includegraphics[height=0.4cm,width=2cm]{Chapters/chap2/Table1-M.pdf}      &                    5.0E10  &                      n.r.
+&          1.2E9  &              0.896  &      -0.636  &      357.0 \\
+\hline
+\end{tabular}
+
+\par\end{centering}
+\caption{Comparison of triplet-triplet energy transfer rates obtained from our  approach,  Marcus rates are
+from Ref.\cite{Subotnik:2010}
+and experimental rates from Refs.\cite{closs1988determination,closs1989connection}.   The experimental error is estimated to be 20\% in each
+case studied here.
+The $V_{ab}$ are the diabatic couplings obtained using  Edmiston-Ruedenberg diabatization.
+In each case, D =4-benzophenonyl and A = 2-napthyl.  n.r. = Not Reported.
+}
+\label{summarytable}
+% \end{table*}
+\end{sidewaystable}
+
 \begin{figure}[t]
@@
 
-\begin{figure}[b]
+\begin{figure}[t]
 \subfloat[c-1,4ee]{\includegraphics[width=0.75\columnwidth]{Chapters/chap2/Figure4a}}\\
@@
 Primary coupling modes for (a) c-1,4ee and (b) d-2,6ae projected onto the atomic displacement coordinates.
-}\label{LanczosModes}
+}\label{LanczosModes_chap2}
 \end{figure}
@@
 first few collective modes for the c-1,4ee and d-2,5ae cases.
- In Fig.~\ref{LanczosModes}
+ In Fig.~\ref{LanczosModes_chap2}
 we show the projection of the primary coupling mode onto the
@@
 
-\begin{figure*}[t]
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5a}}
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5b}}\\
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5c}}
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5d}}
-\caption{Convergence of the electronic coupling autocorrelation function (Eq. ~\ref{c-of-t})
-with respect to number of reduced modes.\label{firstmodecorr}}
-\end{figure*}
-
 In Fig.~\ref{firstmodecorr}  we examine the convergence of $C(t)$ with respect to number of reduced modes for the c-1,4ee and d-2,6ae cases.
@@
  $C(t)\to 0$.   For the cases at hand, this is well before the first recursion seen in Fig.~\ref{firstmodecorr}.
+
+\begin{figure*}[t]
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5a}}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5b}}\\
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5c}}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure5d}}
+\caption{Convergence of the electronic coupling autocorrelation function (Eq. ~\ref{c-of-t})
+with respect to number of reduced modes.\label{firstmodecorr}}
+\end{figure*}
 
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{Chapters/chap2/Figure6}
+\includegraphics[width=0.6\columnwidth]{Chapters/chap2/Figure6}
 \caption{Comparison between exact rate constant and its primary mode approximation.  The blue points correspond to rates computed using
@@
 In Table~\ref{table2} we tabulate the frequencies and electron-phonon coupling constant for the first reduced mode for each
-test case.  Uniformly, these modes correspond to ring breathing motions on the donor and acceptor as illustrated in Fig.~\ref{LanczosModes}.
+test case.  Uniformly, these modes correspond to ring breathing motions on the donor and acceptor as illustrated in Fig.~\ref{LanczosModes_chap2}.
 As seen in this figure, coupling mode does not involve normal modes localized on the bridge species.
@@
 \begin{table}[t]
-\begin{centering}
+\centering
 \begin{tabular}{lrrr}
@@
 \end{tabular}
-\end{centering}
+% \end{centering}
 \caption{Frequencies and dimensionless electron-phonon couplings for

### 2016-03-29 Chapters/chap3/Manuscript-FINAL.tex
Add footnotes for chapters
Change "Fig. ~" to "Fig.~"

@@
+%!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
+
 %% JCP Submission styles
@@
 
-\chapter{Chapter 3}
+\chapter{Chapter 3}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Chemical Physics \textbf{142}, 244114 (2015)}
 
@@
 
-\begin{figure*}[ht]
-\subfloat[c-1,4ee]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure1a.pdf}}
-\subfloat[d-2,6ae]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure1b.pdf}}
+\begin{figure*}[t]
+\subfloat[c-1,4ee]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1a.pdf}}\\
+\subfloat[d-2,6ae]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1b.pdf}}
 \caption{
@@
 }\label{LanczosModes}
-\end{figure*}
-
-\begin{figure*}[ht]
-\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure2a.pdf}}
-\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure2b.pdf}} \\
-\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure2c.pdf}}
-\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap3/Figure2d.pdf}}
-\caption{Projection of PLMs onto (a) benzaldehyde in c14ee (b) symmetrized naphthalene in c14ee, (c) benzaldehyde in d26ae and (d) symmetrized naphthalene in d26ae.
-The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are color-coded. The assigned IRs for naphthalene are exact
- whereas the IRs are only approximate for benzaldehyde. \label{fragProj}}
 \end{figure*}
@@
 The benzaldehyde moiety is unchanged because it has very low  symmetry:  $C_{s}$ if planar and $C_{1}$  other wise.
+
+\begin{figure*}[ht]
+\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2a.pdf}}
+\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2b.pdf}} \\
+\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2c.pdf}}
+\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2d.pdf}}
+\caption{Projection of PLMs onto (a) benzaldehyde in c14ee (b) symmetrized naphthalene in c14ee, (c) benzaldehyde in d26ae and (d) symmetrized naphthalene in d26ae.
+The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are color-coded. The assigned IRs for naphthalene are exact
+ whereas the IRs are only approximate for benzaldehyde. \label{fragProj}}
+\end{figure*}
+
 If one treats the aldehyde group as a local site, one can classify the ring-motions of
@@
 belong to totally symmetric $A_{g}$ or $A_1$ irreducible representations,  in agreement
-with the intuitive observations from Fig. ~\ref{LanczosModes}.
+with the intuitive observations from Fig.~\ref{LanczosModes}.
 
@@
 
-\begin{figure*}[th]
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure3a.pdf}}
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure3b.pdf}}
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure3c.pdf}}
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure3d.pdf}}
+\begin{figure*}[t]
+\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3a.pdf}}
+\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3b.pdf}}\\
+\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3c.pdf}}
+\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3d.pdf}}
 %\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/benzeneC14ee10fs.pdf}}
@@
 This connection can be understood by analyzing the corresponding  the changes in the electron density that accompany the transition.
-For example, the PLM on the naphthalene part shown in  Fig. ~\ref{LanczosModes}
+For example, the PLM on the naphthalene part shown in  Fig.~\ref{LanczosModes}
 largely corresponds to a symmetric ring-stretching mode,  involving carbons
 C1 - C2, C3 - C4, C5 - C6, and C7 - C8.
-During the exciton transfer, an electron is promoted from the naphthalene HOMO to the naphthalene LUMO (shown in Fig. ~\ref{naphHOMOLUMO})
+During the exciton transfer, an electron is promoted from the naphthalene HOMO to the naphthalene LUMO (shown in Fig.~\ref{naphHOMOLUMO})
 and one expects that changes in the bond lengths should reflect the changes in
@@
 
-\begin{figure*}[th]
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure5a.pdf}}
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure5b.pdf}}
+\begin{figure*}[!h]
+\subfloat[]{\includegraphics[width=0.87\columnwidth]{Chapters/chap3/Figure5a.pdf}}\\
+\subfloat[]{\includegraphics[width=0.87\columnwidth]{Chapters/chap3/Figure5b.pdf}}
 \caption{Projections of the PLM onto the normal modes of (a) c14ee and (b) d26ae.\label{LancProj}}
@@
 First, we project the PLM onto the normal modes of entire molecule,
-which is shown in Fig. ~\ref{LancProj}, as a comparison to Fig. ~\ref{fragProj}, where the normal modes of the individual
-moieties are used.    It is clear that on the basis of entire molecule, more modes are
-significantly involved.   This is in contrast to the projection of the PLM onto only the local modes of the isolated moieties,
-only a handful modes contribute.  Since the PLM  best captures the initial nuclear dynamics,
+which is shown in Fig.~\ref{LancProj}, as a comparison to Fig.~\ref{fragProj}, where the normal modes of the individual moieties are used.
+It is clear that on the basis of entire molecule, more modes are significantly involved.
+This is in contrast to the projection of the PLM onto only the local modes of the isolated moieties, only a handful modes contribute.
+Since the PLM  best captures the initial nuclear dynamics,
  its close relation with local sites reveals the fact that the exciton transfer here is more like a local excitation/de-excitation
@@
 
-\begin{figure*}[tbh]
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure6a.pdf}}
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure6b.pdf}}
+\begin{figure*}[!h]
+\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure6a.pdf}}\\
+\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure6b.pdf}}
 \caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c14ee and (b) d26ae.
-They are almost same to Fig. ~\ref{fragProj}(b) and (d) except for a mode with $B_{2u}$ symmetry in c14ee.
+They are almost same to Fig.~\ref{fragProj}(b) and (d) except for a mode with $B_{2u}$ symmetry in c14ee.
 Embedded are the most significant modes, namely, the 33rd modes \label{projNaph}}
@@
 %\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c14ee and (b) d26ae.
-They are almost same to Fig.
-~\ref{fragProj}(b) and (d) except for a mode with $b_{2u}$ symmetry in (c).
+They are almost same to Fig.~\ref{fragProj}(b) and (d) except for a mode with $b_{2u}$ symmetry in (c).
 In the second row are the most dominant mode in projections above, namely, the 33rd normal mode of naphthalene in (c) c14ee and (d) d26ae.
@@
 %To construct coupling modes from the projections.
-We take the normal modes in  Fig.
-~\ref{projNaph}, starting from the most significant ones, and sum their displacement vectors multiplied by their weights in projection.
-Results are summarized in Fig.
-~\ref{backCorr}.
+We take the normal modes in  Fig.~\ref{projNaph}, starting from the most significant ones, and sum their displacement vectors multiplied by their weights in projection.
+Results are summarized in Fig.~\ref{backCorr}.
 Several conclusions can be made here.
@@
 Nevertheless, correlation function does not need to coincide perfectly to give a good rate constant so we calculate the rate constants for various combinations up to 10 modes in each fragment.
-The contour plots of the absolute values of their relative errors compared to the rate of PLM are shown in the second row in  Fig.
-~\ref{backCorr}.
+The contour plots of the absolute values of their relative errors compared to the rate of PLM are shown in the second row in  Fig.~\ref{backCorr}.
 We can see that, roughly, taking 3 modes in benzaldehyde and 2 modes in naphthalene suffices to give rate constants within 10\% error.
-The fact that more modes are needed in benzaldehyde is because more normal modes in it are involved in PLMs, as can be seen in Fig.
-~\ref{fragProj}.
-
-\begin{figure*}[tbh]
-\subfloat[]{\includegraphics[width=\columnwidth]{Chapters/chap3/Figure7a.pdf}}
-\subfloat[]{\includegraphics[width=\columnwidth]{Chapters/chap3/Figure7b.pdf}} \\
-\subfloat[]{\includegraphics[width=\columnwidth]{Chapters/chap3/Figure7c.pdf}}
-\subfloat[]{\includegraphics[width=\columnwidth]{Chapters/chap3/Figure7d.pdf}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateC14ee.pdf}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateD26ae.pdf}}
-\caption{Correlation functions for different combinations of normal modes are shown for (a) c14ee and (b) d26ae.  The ``exact'' ones refer are for the PLMs.  ``NfBf"
-is the mode made up from all normal modes of both the donor and acceptor sites.
-The designation ``NxBy'' indicates that the correlation function was constructed using  $x$ most significant normal modes
-on naphthalene and $y$ most significant ones on benzaldehyde.   Plots (c) and (d) show the
- relative error in rate constants calculated for various combinations of normal modes compared to the exact result
- or c14ee (c) and d26ae (d) respectively. \label{backCorr}}
-\end{figure*}
+The fact that more modes are needed in benzaldehyde is because more normal modes in it are involved in PLMs, as can be seen in Fig.~\ref{fragProj}.
 
@@
 for the entire unit one needs to use the optimized rather than symmetrized geometry.
-In Fig. ~\ref{projNaph}  we show the project of the PLM onto the modes for optimized
+In Fig.~\ref{projNaph}  we show the project of the PLM onto the modes for optimized
 naphthalene.  The irreducible representations have been roughly assigned to the dominant modes.
@@
 mode of c14ee and d26ae are slightly different. The corresponding displacement vectors are
-embedded in Fig. ~\ref{projNaph}. For c14ee, the dominant mode is not an exact $A_g$ mode, because
+embedded in Fig.~\ref{projNaph}. For c14ee, the dominant mode is not an exact $A_g$ mode, because
 carbons move in the way of $A_g$ while
@@
 included.   The correlation functions and rate constants derived from various
-combinations of normal modes are summarized in Fig. ~\ref{backCorr}.
+combinations of normal modes are summarized in Fig.~\ref{backCorr}.
+
+\begin{figure*}[!h]
+\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7a.pdf}}
+\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7b.pdf}} \\
+\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7c.pdf}}
+\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7d.pdf}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateC14ee.pdf}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateD26ae.pdf}}
+\caption{Correlation functions for different combinations of normal modes are shown for (a) c14ee and (b) d26ae.  The ``exact'' ones refer are for the PLMs.  ``NfBf"
+is the mode made up from all normal modes of both the donor and acceptor sites.
+The designation ``NxBy'' indicates that the correlation function was constructed using  $x$ most significant normal modes
+on naphthalene and $y$ most significant ones on benzaldehyde.   Plots (c) and (d) show the
+ relative error in rate constants calculated for various combinations of normal modes compared to the exact result
+ or c14ee (c) and d26ae (d) respectively. \label{backCorr}}
+\end{figure*}
 
@@
 each moiety and compare to the exact rate.
-This data is summarized in the form of contour plots in  Fig. ~\ref{backCorr}(c,d).
+This data is summarized in the form of contour plots in  Fig.~\ref{backCorr}(c,d).
 For the c14ee case, there is an optimal ``valley'' whereby taking 3 modes from benzaldehyde and 4-6 modes from
@@
 Comparing the maximum difference of bond
-lengths and angles between the approximated and true final states, the differences are very small,
+lengths and angles between the approximated and true final states (Table. ~\ref{aprroxGeom}), the differences are very small,
 so PLMs seem to give fairly good approximations of geometry changes.
@@
 
-\begin{figure*}[th]
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8a.pdf}}
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8b.pdf}}
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8c.pdf}}
-\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8d.pdf}}
-\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) benzaldehyde and (b) naphthalene sites in c14ee, and d26ae in (c) and (d).
-Except for some low frequency modes, they are similar to the projections of PLM.
-\label{geomDiffFragProj}}
-\end{figure*}
-
 %
@@
 By breaking down geometry change, we get the insight that the entire process consists of two steps, the fast excitation transfer facilitated by PLM and the relaxation after that.
-%Looking at the symmetry of PLM in Fig.
-~\ref{LanczosModes}, especially the naphthalene, it is basically the stretch of four bonds being symmetric to each other.
-Comparing the bonding and antibonding in the HOMO/LUMO of naphthalene in Fig.
-~\ref{naphHOMOLUMO}, we noticed that these four bonds change lengths dramatically in deexcitation, so does PLM correspond to geometry change?
+%Looking at the symmetry of PLM in Fig.~\ref{LanczosModes}, especially the naphthalene, it is basically the stretch of four bonds being symmetric to each other.
+Comparing the bonding and antibonding in the HOMO/LUMO of naphthalene in Fig.~\ref{naphHOMOLUMO}, we noticed that these four bonds change lengths dramatically in deexcitation, so does PLM correspond to geometry change?
 Yes, and no.
@@
 we can project the geometry change onto the normal modes of molecule and moieties respectively.  The
-results for our two test cases are shown  in Fig. ~\ref{geomDiffFragProj} and \ref{geomDiffProj}.
+results for our two test cases are shown  in Fig.~\ref{geomDiffFragProj} and \ref{geomDiffProj}.
+
+\begin{figure*}[!h]
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8a.pdf}}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8b.pdf}}\\
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8c.pdf}}
+\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8d.pdf}}
+\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) benzaldehyde and (b) naphthalene sites in c14ee, and d26ae in (c) and (d).
+Except for some low frequency modes, they are similar to the projections of PLM.
+\label{geomDiffFragProj}}
+\end{figure*}
+
+\begin{figure*}[!h]
+\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure9a.pdf}}\\
+\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure9b.pdf}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeDADiffproj.pdf}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeDADiffproj.pdf}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeNM2.png}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeNM1.png}}
+\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) c14ee and (b) d26ae.
+They are both dominated by single mode, the relaxation mode (RM), which is embedded.\label{geomDiffProj}}
+\end{figure*}
+
 When projected onto the whole molecule, we see that geometry change is mostly dominated
 by one  very low frequency mode  corresponding to an internal  torsion of the entire donor-bridge-acceptor molecule.
-Compared to the PLMs in the same basis in Fig. ~\ref{LancProj}
+Compared to the PLMs in the same basis in Fig.~\ref{LancProj}
  we see that  PLMs  have many more modes involved.
-However, if we compare the projections onto the  moieties in  Fig. ~\ref{fragProj}
+However, if we compare the projections onto the  moieties in  Fig.~\ref{fragProj}
 and \ref{geomDiffFragProj}, the geometry changes resemble PLMs well, except in the low frequency region.
@@
 %However, this is only one side of the story.
-In Fig.
-~\ref{geomDiffProj} we project geometry change onto the normal modes of molecule.
-It does not look same to the projections of PLM in Fig.
-~\ref{LancProj}.
-The geometry change of both c14ee and d26ae are dominated by single mode with very low frequency, shown in Fig.
-~\ref{geomDiffProj}(c) and (d).
+In Fig.~\ref{geomDiffProj} we project geometry change onto the normal modes of molecule.
+It does not look same to the projections of PLM in Fig.~\ref{LancProj}.
+The geometry change of both c14ee and d26ae are dominated by single mode with very low frequency, shown in Fig.~\ref{geomDiffProj}(c) and (d).
 We term them the dominant mode relaxation mode (RM) for the reason below.
 RM does not resemble PLM at all.
-
-\begin{figure*}[th]
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure9a.pdf}}
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure9b.pdf}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeDADiffproj.pdf}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeDADiffproj.pdf}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeNM2.png}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeNM1.png}}
-\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) c14ee and (b) d26ae.
-They are both dominated by single mode, the relaxation mode (RM), which is embedded.\label{geomDiffProj}}
-\end{figure*}
-
-\begin{figure*}[th]
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure10a.pdf}}
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure10b.pdf}}
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/Figure10c.pdf}}
-\caption{Correlation functions of relaxation mode (RM), PLM, geometry change (GC), and geometry change with the RM component eliminated for (a) c14ee and (b) d26ae.
-(c) Relative comparison of the rate constants computed using different sets of reduced modes.  The exact rate is computed using the full set of normal modes:
-blue = c14ee, gold =d26ae. }
-\label{Corr}
-\end{figure*}
 
@@
 The various correlation functions and rate
-constants are summarized in Fig. ~\ref{Corr}.
+constants are summarized in Fig.~\ref{Corr}.
 The exact results are obtained by  using all normal modes and couplings.
 The PLM gives nearly perfect agreement to the exact calculation  for both the
-time-correlation functions (Fig.~\ref{Corr}(a,b))  and the computed rates for both molecules considered  (Fig.~\ref{Corr}(c)).
+time-correlation functions (Fig.~\ref{Corr})  and the computed rates for both molecules considered  (Fig.~\ref{RateComp}.
 The relaxation mode (RM) gives no contribution to the correlation function or the rate.
@@
 obtained by using the PLM identified using the Lanczos search algorithm.
+
+\begin{figure*}[!h]
+\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10a.pdf}}\\
+\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10b.pdf}}\\
+% \subfloat[]{\includegraphics[width=0.53\columnwidth]{Chapters/chap3/Figure10c.pdf}}
+\caption{Correlation functions of relaxation mode (RM), PLM, geometry change (GC), and geometry change with the RM component eliminated for (a) c14ee and (b) d26ae.
+The exact rate is computed using the full set of normal modes.}
+\label{Corr}
+\end{figure*}
+
+\begin{figure*}[!h]
+\subfloat[]{\includegraphics[width=0.9\columnwidth]{Chapters/chap3/Figure10c.pdf}}
+\caption{Relative comparison of the rate constants computed using different sets of reduced modes. blue = c14ee, gold =d26ae. }
+\label{RateComp}
+\end{figure*}
 

### 2016-03-29 Chapters/chap2/manuscript.tex
Change to bib

@@
 \end{center}
-Triplet energy exchange in these systems occurs via the through-space Dexter mechanism\cite{Dexter:1952}.
+Triplet energy exchange in these systems occurs via the through-space Dexter mechanism\cite{dexter1953theory}.
 This is a short-ranged interaction involving the simultaneous exchange of two electrons between the
@@
 and serve as crucial benchmarks for testing new theoretical models for computing
-energy and charge transfer rates\cite{subotnik2008constructing,subotnik2009initial,Subotnik:2010}.
+energy and charge transfer rates\cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
 
@@
 state-to-state rates in which the coupling between  states depends upon the
-nuclear coordinates\cite{pereverzev:104906}. This approach incorporates a fully quantum
+nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
 mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
@@
 transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
-\cite{Tamura08,tamura:021103,Bittner:2014ab,Jaykrishna-Singh:2009ly}.
+\cite{tamura2008phonon,tamura2007exciton,bittner2014noise,singh2009fluorescence}.
 This paper represents the first time we have used this approach within the context of a fully {\em ab initio} quantum
@@
 more recent theoretical rates presented by Subotnik {\em et al.}
-\cite{subotnik2008constructing,subotnik2009initial,Subotnik:2010}.
+\cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
 An important component of our analysis is the use of a projection operator scheme
@@
 Similar decomposition schemes have been presented by Burghardt
- \cite{Cederbaum:2005,gindensperger:144103,gindensperger:144104,PhysRevLett.94.113003}
- and the approach used here builds upon the method given in Ref.~\cite{pereverzev:034104}.
+ \cite{cederbaum2005short,gindensperger2006shortI,gindensperger2006shortII,cederbaum2005short}
+ and the approach used here builds upon the method given in Ref.~\cite{pereverzev2009energy}.
  By analyzing the electron-phonon couplings, we can
@@
 and perform a polaron transform
-using the unitary transformation~\cite{grover:2099,rice:2504,pereverzev:104906}.
+using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
 \begin{eqnarray}
@@
 The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
-Ref.~\cite{pereverzev:104906}.
+Ref.~\cite{pereverzev2006time}.
 
@@
 
-In Ref.~\cite{pereverzev:104906}, Pereverzev and Bittner derived
+In Ref.~\cite{pereverzev2006time}, Pereverzev and Bittner derived
 a non-Markovian, time-convolutionless form of the Pauli master
@@
 adiabatic states.    In the following section, we discuss how we have used the Edmiston-Ruedenberg localization scheme
-to estimate the couplings\cite{RevModPhys.35.457}.   We also
+to estimate the couplings\cite{edmiston1963localized}.   We also
 present how one can construct a reduced set of harmonic modes that
@@
 used the qChem 4.0 code and employed the 6-31G(d){*}{*} basis set
-in order to compare our results  with  Ref. \cite{Subotnik:2010}.
+in order to compare our results  with  Ref. \cite{subotnik2010predicting}.
 
@@
  Bridge   &  Structure                                                &        Ref.~\cite{closs1988determination,closs1989connection} &              Ref.
-\cite{Subotnik:2010}  &                  &      $\lambda$ (eV)  &  $\Delta \epsilon$ (eV)  &  $V_{ab}$ ($\mu$eV) \\
+\cite{subotnik2010predicting}  &                  &      $\lambda$ (eV)  &  $\Delta \epsilon$ (eV)  &  $V_{ab}$ ($\mu$eV) \\
 \hline
@@
 \caption{Comparison of triplet-triplet energy transfer rates obtained from our  approach,  Marcus rates are
-from Ref.\cite{Subotnik:2010}
+from ~Ref. \cite{subotnik2010predicting}
 and experimental rates from Refs.\cite{closs1988determination,closs1989connection}.   The experimental error is estimated to be 20\% in each
@@
 \includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure3}
-\caption{Comparison between predicted (TCLME) rate constants and the experimental rates from Ref.\cite{miller1984intramolecular}.  With exception of
+\caption{Comparison between predicted (TCLME) rate constants and the experimental rates from ~Ref. \cite{miller1984intramolecular}.  With exception of
 the methyl and D-2,6-ea bridged cases, the TCLME results are in good agreement with the experimental results.  }\label{compare}
@@
 
-In general, our results and those in Ref.\cite{Subotnik:2010} agree with each other well and both are
+In general, our results and those in ~Ref. \cite{subotnik2010predicting} agree with each other well and both are
 comparable to the experimental results which report an estimated error of 10-20\% in the
@@
 the d-2,6ea and methyl (M) bridged cases.   For the d-2,6ea bridge,  our results are similar to the
-Marcus theory rates given in Ref. \cite{Subotnik:2010}.  In this case, the
+Marcus theory rates given in Ref. \cite{subotnik2010predicting}.  In this case, the
  the ER localization gives a  small diabatic coupling
@@
 As a result,  the potential surfaces are no longer parabolic
-and the Condon approximation breaks down.\cite{Subotnik:2010}
+and the Condon approximation breaks down.\cite{subotnik2010predicting}
 
@@
 coupling mode involves the  $b_{2u}$ in plane C=C stretching motions of the naphthalene donor and the
- in-plane $\nu_{8}$ (in the Mulliken numbering scheme) ring-squeezing motions of the benzaldehyde acceptor\cite{doi:10.1021/jp961282l}.
+ in-plane $\nu_{8}$ (in the Mulliken numbering scheme) ring-squeezing motions of the benzaldehyde acceptor\cite{silva1996theoretical}.
 It is interesting to note
-that $^{3}B_{2u}$ is also the symmetry of the first triplet $\pi-\pi^{*}$ excited state in naphthalene \cite{doi:10.1021/j100066a007},
+that $^{3}B_{2u}$ is also the symmetry of the first triplet $\pi-\pi^{*}$ excited state in naphthalene \cite{aagren1994response},
 Moreover, if we were to approximate benzaldehyde as a $C_{2v}$ molecule, taking the aldehyde as local site,
@@
 
+% \begin{}
+% \bibliographystyle{chicago}
+% \bibliography{Dbib}
+
 % \begin{acknowledgement}
@@
 % \chapterbib
-\providecommand*\mcitethebibliography{\thebibliography}
-\csname @ifundefined\endcsname{endmcitethebibliography}
-  {\let\endmcitethebibliography\endthebibliography}{}
-\begin{mcitethebibliography}{27}
-\providecommand*\natexlab[1]{#1}
-\providecommand*\mciteSetBstSublistMode[1]{}
-\providecommand*\mciteSetBstMaxWidthForm[2]{}
-\providecommand*\mciteBstWouldAddEndPuncttrue
-  {\def\EndOfBibitem{\unskip.}}
-\providecommand*\mciteBstWouldAddEndPunctfalse
-  {\let\EndOfBibitem\relax}
-\providecommand*\mciteSetBstMidEndSepPunct[3]{}
-\providecommand*\mciteSetBstSublistLabelBeginEnd[3]{}
-\providecommand*\EndOfBibitem{}
-\mciteSetBstSublistMode{f}
-\mciteSetBstMaxWidthForm{subitem}{(\alph{mcitesubitemcount})}
-\mciteSetBstSublistLabelBeginEnd
-  {\mcitemaxwidthsubitemform\space}
-  {\relax}
-  {\relax}
-
-% \begin{thebibliography}{27}
-\bibitem[Marcus(1956)]{marcus1956theory}
-Marcus,~R.~A. On the Theory of Oxidation-Reduction Reactions Involving Electron
-  Transfer. I. \emph{J. Chem. Phys.} \textbf{1956}, \emph{24},
-  966--978\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Marcus(1965)]{marcus1965theory}
-Marcus,~R.~A. On the Theory of Electron-Transfer Reactions. VI. Unified
-  Treatment for Homogeneous and Electrode Reactions. \emph{J. Chem. Phys} \textbf{1965}, \emph{43}, 679\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Marcus(1993)]{marcus1993electron}
-Marcus,~R.~A. Electron transfer reactions in chemistry. Theory and experiment.
-  \emph{Rev. Mod.  Phys.} \textbf{1993}, \emph{65}, 599--610\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Dexter(1953)]{Dexter:1952}
-Dexter,~D.~L. A Theory of Sensitized Luminescence in Solids. \emph{J. Chem. Phys.} \textbf{1953}, \emph{21}, 836--850\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Miller et~al.(1984)Miller, Calcaterra, and
-  Closs]{miller1984intramolecular}
-Miller,~J.; Calcaterra,~L.; Closs,~G. Intramolecular long-distance electron
-  transfer in radical anions. The effects of free energy and solvent on the
-  reaction rates. \emph{J.  Am.  Chem.  Soc.}
-  \textbf{1984}, \emph{106}, 3047--3049\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Subotnik et~al.(2008)Subotnik, Yeganeh, Cave, and
-  Ratner]{subotnik2008constructing}
-Subotnik,~J.~E.; Yeganeh,~S.; Cave,~R.~J.; Ratner,~M.~A. Constructing diabatic
-  states from adiabatic states: Extending generalized Mulliken--Hush to
-  multiple charge centers with Boys localization. \emph{J. Chem. Phys.} \textbf{2008}, \emph{129}, 244101\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Subotnik et~al.(2009)Subotnik, Cave, Steele, and
-  Shenvi]{subotnik2009initial}
-Subotnik,~J.~E.; Cave,~R.~J.; Steele,~R.~P.; Shenvi,~N. The initial and final
-  states of electron and energy transfer processes: Diabatization as motivated
-  by system-solvent interactions. \emph{J. Chem. Phys.}
-  \textbf{2009}, \emph{130}, 234102--234102\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Subotnik et~al.(2010)Subotnik, Vura-Weis, Sodt, and
-  Ratner]{Subotnik:2010}
-Subotnik,~J.~E.; Vura-Weis,~J.; Sodt,~A.~J.; Ratner,~M.~A. Predicting accurate
-  electronic energy transfer rates via Marcus theory and Edminston-Ruedeberg
-  localized diabatization. \emph{J. Phys. Chem. A} \textbf{2010},
-  \emph{114}\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Pereverzev and Bittner(2006)Pereverzev, and
-  Bittner]{pereverzev:104906}
-Pereverzev,~A.; Bittner,~E.~R. Time-convolutionless master equation for
-  mesoscopic electron-phonon systems. \emph{J. Chem. Phys.}
-  \textbf{2006}, \emph{125}, 104906\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Tamura et~al.(2008)Tamura, Ramon, Bittner, and Burghardt]{Tamura08}
-Tamura,~H.; Ramon,~J. G.~S.; Bittner,~E.~R.; Burghardt,~I. Phonon-Driven
-  Ultrafast Exciton Dissociation at Donor-Acceptor Polymer Heterojunctions.
-  \emph{Physical Review Letters} \textbf{2008}, \emph{100}, APS\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Tamura et~al.(2007)Tamura, Bittner, and Burghardt]{tamura:021103}
-Tamura,~H.; Bittner,~E.~R.; Burghardt,~I. Exciton dissociation at
-  donor-acceptor polymer heterojunctions: Quantum nonadiabatic dynamics and
-  effective-mode analysis. \emph{J. Chem. Phys.}
-  \textbf{2007}, \emph{126}, 021103\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Bittner and Silva(2014)Bittner, and Silva]{Bittner:2014ab}
-Bittner,~E.~R.; Silva,~C. Noise-induced quantum coherence drives photo-carrier
-  generation dynamics at polymeric semiconductor heterojunctions. \emph{Nat.   Comm.} \textbf{2014}, \emph{5}, 3119\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Singh et~al.(2009)Singh, Bittner, Beljonne, and
-  Scholes]{Jaykrishna-Singh:2009ly}
-Singh,~J.; Bittner,~E.~R.; Beljonne,~D.; Scholes,~G.~D. Fluorescence Depolarization in MEH-PPV:
-Sites vs. Eigenstates Hopping. \emph{J. Chem.
-  Phys.} \textbf{2009}, \emph{131}, 194905\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Cederbaum et~al.(2005)Cederbaum, Gildensperger, and
-  Burghardt]{Cederbaum:2005}
-Cederbaum,~L.; Gildensperger,~E.; Burghardt,~I. Short-Time Dynamics Through
-  Conical Intersections in Macrosystems. \emph{Phys. Rev. Lett.} \textbf{2005},
-  \emph{94}, 113003\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Gindensperger et~al.(2006)Gindensperger, Burghardt, and
-  Cederbaum]{gindensperger:144103}
-Gindensperger,~E.; Burghardt,~I.; Cederbaum,~L.~S. Short-time dynamics through
-  conical intersections in macrosystems. I. Theory: Effective-mode formulation.
-  \emph{J. Chem. Phys.} \textbf{2006}, \emph{124},
-  144103\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Gindensperger et~al.(2006)Gindensperger, Burghardt, and
-  Cederbaum]{gindensperger:144104}
-Gindensperger,~E.; Burghardt,~I.; Cederbaum,~L.~S. Short-time dynamics through
-  conical intersections in macrosystems. II. Applications. \emph{J. Chem. Phys.} \textbf{2006}, \emph{124}, 144104\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Cederbaum et~al.(2005)Cederbaum, Gindensperger, and
-  Burghardt]{PhysRevLett.94.113003}
-Cederbaum,~L.~S.; Gindensperger,~E.; Burghardt,~I. Short-Time Dynamics Through
-  Conical Intersections in Macrosystems. \emph{Phys. Rev. Lett.} \textbf{2005},
-  \emph{94}, 113003\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Pereverzev et~al.(2009)Pereverzev, Bittner, and  Burghardt]{pereverzev:034104}
-Pereverzev,~A.; Bittner,~E.~R.; Burghardt,~I. Energy and charge-transfer
-  dynamics using projected modes. \emph{J. Chem. Phys.}
-  \textbf{2009}, \emph{131}, 034104\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Closs et~al.(1988)Closs, Piotrowiak, MacInnis, and
-  Fleming]{closs1988determination}
-Closs,~G.~L.; Piotrowiak,~P.; MacInnis,~J.~M.; Fleming,~G.~R. Determination of
-  long-distance intramolecular triplet energy-transfer rates. Quantitative
-  comparison with electron transfer. \emph{J.  Am.  Chem.  Soc.} \textbf{1988}, \emph{110}, 2652--2653\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Closs et~al.(1989)Closs, Johnson, Miller, and
-  Piotrowiak]{closs1989connection}
-Closs,~G.~L.; Johnson,~M.~D.; Miller,~J.~R.; Piotrowiak,~P. A connection
-  between intramolecular long-range electron, hole, and triplet energy
-  transfers. \emph{J.  Am.  Chem.  Soc.} \textbf{1989},
-  \emph{111}, 3751--3753\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Grover and Silbey(1970)Grover, and Silbey]{grover:2099}
-Grover,~M.~K.; Silbey,~R. Exciton--Phonon Interactions in Molecular Crystals.
-  \emph{J. Chem. Phys.} \textbf{1970}, \emph{52},
-  2099--2108\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Rice and Gartstein(1994)Rice, and Gartstein]{rice:2504}
-Rice,~M.~J.; Gartstein,~Y.~N. Excitons and interband excitations in conducting
-  polymers based on phenylene. \emph{Phys. Rev. Lett.} \textbf{1994},
-  \emph{73}, 2504--2507\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Edmiston and Ruedenberg(1963)Edmiston, and
-  Ruedenberg]{RevModPhys.35.457}
-Edmiston,~C.; Ruedenberg,~K. Localized Atomic and Molecular Orbitals.
-  \emph{Rev. Mod. Phys.} \textbf{1963}, \emph{35}, 457--464\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Closs and Miller(1988)Closs, and Miller]{closs1988intramolecular}
-Closs,~G.~L.; Miller,~J.~R. Intramolecular long-distance electron transfer in
-  organic molecules. \emph{Science} \textbf{1988}, \emph{240}, 440--447\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[Silva and Reilly(1996)Silva, and Reilly]{doi:10.1021/jp961282l}
-Silva,~C.~R.; Reilly,~J.~P. Theoretical Calculations on Excited Electronic
-  States of Benzaldehyde and Observation of the $S_2\leftarrow S_0$ Jet-Cooled
-  Spectrum. \emph{J. Phys. Chem.} \textbf{1996}, \emph{100},
-  17111--17123\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-\bibitem[{\AA}gren et~al.(1994){\AA}gren, Minaev, and
-  Knuts]{doi:10.1021/j100066a007}
-{\AA}gren,~H.; Minaev,~B.~F.; Knuts,~S. Response Theory Studies of
-  Triplet-State Spectra and Radiative Lifetimes of Naphthalene, Quinoxaline,
-  and Phthalazine. \emph{J.  Phys.  Chem.} \textbf{1994},
-  \emph{98}, 3943--3949\relax
-\mciteBstWouldAddEndPuncttrue
-\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
-{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
-\EndOfBibitem
-
-% \end{thebibliography}
-\end{mcitethebibliography}
+% \providecommand*\mcitethebibliography{\thebibliography}
+% \csname @ifundefined\endcsname{endmcitethebibliography}
+%   {\let\endmcitethebibliography\endthebibliography}{}
+% \begin{mcitethebibliography}{27}
+% \providecommand*\natexlab[1]{#1}
+% \providecommand*\mciteSetBstSublistMode[1]{}
+% \providecommand*\mciteSetBstMaxWidthForm[2]{}
+% \providecommand*\mciteBstWouldAddEndPuncttrue
+%   {\def\EndOfBibitem{\unskip.}}
+% \providecommand*\mciteBstWouldAddEndPunctfalse
+%   {\let\EndOfBibitem\relax}
+% \providecommand*\mciteSetBstMidEndSepPunct[3]{}
+% \providecommand*\mciteSetBstSublistLabelBeginEnd[3]{}
+% \providecommand*\EndOfBibitem{}
+% \mciteSetBstSublistMode{f}
+% \mciteSetBstMaxWidthForm{subitem}{(\alph{mcitesubitemcount})}
+% \mciteSetBstSublistLabelBeginEnd
+%   {\mcitemaxwidthsubitemform\space}
+%   {\relax}
+%   {\relax}
+
+% % \begin{thebibliography}{27}
+% \bibitem[Marcus(1956)]{marcus1956theory}
+% Marcus,~R.~A. On the Theory of Oxidation-Reduction Reactions Involving Electron
+%   Transfer. I. \emph{Journal Chem. Phys.} \textbf{1956}, \emph{24},
+%   966--978\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Marcus(1965)]{marcus1965theory}
+% Marcus,~R.~A. On the Theory of Electron-Transfer Reactions. VI. Unified
+%   Treatment for Homogeneous and Electrode Reactions. \emph{J. Chem. Phys} \textbf{1965}, \emph{43}, 679\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Marcus(1993)]{marcus1993electron}
+% Marcus,~R.~A. Electron transfer reactions in chemistry. Theory and experiment.
+%   \emph{Rev. Mod.  Phys.} \textbf{1993}, \emph{65}, 599--610\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Dexter(1953)]{dexter1953theory}
+% Dexter,~D.~L. A Theory of Sensitized Luminescence in Solids. \emph{J. Chem. Phys.} \textbf{1953}, \emph{21}, 836--850\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Miller et~al.(1984)Miller, Calcaterra, and
+%   Closs]{miller1984intramolecular}
+% Miller,~J.; Calcaterra,~L.; Closs,~G. Intramolecular long-distance electron
+%   transfer in radical anions. The effects of free energy and solvent on the
+%   reaction rates. \emph{J.  Am.  Chem.  Soc.}
+%   \textbf{1984}, \emph{106}, 3047--3049\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Subotnik et~al.(2008)Subotnik, Yeganeh, Cave, and
+%   Ratner]{subotnik2008constructing}
+% Subotnik,~J.~E.; Yeganeh,~S.; Cave,~R.~J.; Ratner,~M.~A. Constructing diabatic
+%   states from adiabatic states: Extending generalized Mulliken--Hush to
+%   multiple charge centers with Boys localization. \emph{J. Chem. Phys.} \textbf{2008}, \emph{129}, 244101\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Subotnik et~al.(2009)Subotnik, Cave, Steele, and
+%   Shenvi]{subotnik2009initial}
+% Subotnik,~J.~E.; Cave,~R.~J.; Steele,~R.~P.; Shenvi,~N. The initial and final
+%   states of electron and energy transfer processes: Diabatization as motivated
+%   by system-solvent interactions. \emph{J. Chem. Phys.}
+%   \textbf{2009}, \emph{130}, 234102--234102\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Subotnik et~al.(2010)Subotnik, Vura-Weis, Sodt, and
+%   Ratner]{subotnik2010predicting}
+% Subotnik,~J.~E.; Vura-Weis,~J.; Sodt,~A.~J.; Ratner,~M.~A. Predicting accurate
+%   electronic energy transfer rates via Marcus theory and Edminston-Ruedeberg
+%   localized diabatization. \emph{J. Phys. Chem. A} \textbf{2010},
+%   \emph{114}\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Pereverzev and Bittner(2006)Pereverzev, and
+%   Bittner]{pereverzev2006time}
+% Pereverzev,~A.; Bittner,~E.~R. Time-convolutionless master equation for
+%   mesoscopic electron-phonon systems. \emph{J. Chem. Phys.}
+%   \textbf{2006}, \emph{125}, 104906\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Tamura et~al.(2008)Tamura, Ramon, Bittner, and Burghardt]{tamura2008phonon}
+% Tamura,~H.; Ramon,~J. G.~S.; Bittner,~E.~R.; Burghardt,~I. Phonon-Driven
+%   Ultrafast Exciton Dissociation at Donor-Acceptor Polymer Heterojunctions.
+%   \emph{Physical Review Letters} \textbf{2008}, \emph{100}, APS\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Tamura et~al.(2007)Tamura, Bittner, and Burghardt]{tamura2007exciton}
+% Tamura,~H.; Bittner,~E.~R.; Burghardt,~I. Exciton dissociation at
+%   donor-acceptor polymer heterojunctions: Quantum nonadiabatic dynamics and
+%   effective-mode analysis. \emph{J. Chem. Phys.}
+%   \textbf{2007}, \emph{126}, 021103\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Bittner and Silva(2014)Bittner, and Silva]{bittner2014noise}
+% Bittner,~E.~R.; Silva,~C. Noise-induced quantum coherence drives photo-carrier
+%   generation dynamics at polymeric semiconductor heterojunctions. \emph{Nat.   Comm.} \textbf{2014}, \emph{5}, 3119\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Singh et~al.(2009)Singh, Bittner, Beljonne, and
+%   Scholes]{singh2009fluorescence}
+% Singh,~J.; Bittner,~E.~R.; Beljonne,~D.; Scholes,~G.~D. Fluorescence Depolarization in MEH-PPV:
+% Sites vs. Eigenstates Hopping. \emph{J. Chem.
+%   Phys.} \textbf{2009}, \emph{131}, 194905\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Cederbaum et~al.(2005)Cederbaum, Gildensperger, and
+%   Burghardt]{cederbaum2005short}
+% Cederbaum,~L.; Gildensperger,~E.; Burghardt,~I. Short-Time Dynamics Through
+%   Conical Intersections in Macrosystems. \emph{Phys. Rev. Lett.} \textbf{2005},
+%   \emph{94}, 113003\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Gindensperger et~al.(2006)Gindensperger, Burghardt, and
+%   Cederbaum]{gindensperger2006shortI}
+% Gindensperger,~E.; Burghardt,~I.; Cederbaum,~L.~S. Short-time dynamics through
+%   conical intersections in macrosystems. I. Theory: Effective-mode formulation.
+%   \emph{J. Chem. Phys.} \textbf{2006}, \emph{124},
+%   144103\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Gindensperger et~al.(2006)Gindensperger, Burghardt, and
+%   Cederbaum]{gindensperger2006shortII}
+% Gindensperger,~E.; Burghardt,~I.; Cederbaum,~L.~S. Short-time dynamics through
+%   conical intersections in macrosystems. II. Applications. \emph{J. Chem. Phys.} \textbf{2006}, \emph{124}, 144104\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Cederbaum et~al.(2005)Cederbaum, Gindensperger, and
+%   Burghardt]{cederbaum2005short}
+% Cederbaum,~L.~S.; Gindensperger,~E.; Burghardt,~I. Short-Time Dynamics Through
+%   Conical Intersections in Macrosystems. \emph{Phys. Rev. Lett.} \textbf{2005},
+%   \emph{94}, 113003\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Pereverzev et~al.(2009)Pereverzev, Bittner, and  Burghardt]{pereverzev2009energy}
+% Pereverzev,~A.; Bittner,~E.~R.; Burghardt,~I. Energy and charge-transfer
+%   dynamics using projected modes. \emph{J. Chem. Phys.}
+%   \textbf{2009}, \emph{131}, 034104\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Closs et~al.(1988)Closs, Piotrowiak, MacInnis, and
+%   Fleming]{closs1988determination}
+% Closs,~G.~L.; Piotrowiak,~P.; MacInnis,~J.~M.; Fleming,~G.~R. Determination of
+%   long-distance intramolecular triplet energy-transfer rates. Quantitative
+%   comparison with electron transfer. \emph{J.  Am.  Chem.  Soc.} \textbf{1988}, \emph{110}, 2652--2653\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Closs et~al.(1989)Closs, Johnson, Miller, and
+%   Piotrowiak]{closs1989connection}
+% Closs,~G.~L.; Johnson,~M.~D.; Miller,~J.~R.; Piotrowiak,~P. A connection
+%   between intramolecular long-range electron, hole, and triplet energy
+%   transfers. \emph{J.  Am.  Chem.  Soc.} \textbf{1989},
+%   \emph{111}, 3751--3753\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Grover and Silbey(1970)Grover, and Silbey]{grover1970exciton}
+% Grover,~M.~K.; Silbey,~R. Exciton--Phonon Interactions in Molecular Crystals.
+%   \emph{J. Chem. Phys.} \textbf{1970}, \emph{52},
+%   2099--2108\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Rice and Gartstein(1994)Rice, and Gartstein]{rice1994excitons}
+% Rice,~M.~J.; Gartstein,~Y.~N. Excitons and interband excitations in conducting
+%   polymers based on phenylene. \emph{Phys. Rev. Lett.} \textbf{1994},
+%   \emph{73}, 2504--2507\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Edmiston and Ruedenberg(1963)Edmiston, and
+%   Ruedenberg]{edmiston1963localized}
+% Edmiston,~C.; Ruedenberg,~K. Localized Atomic and Molecular Orbitals.
+%   \emph{Rev. Mod. Phys.} \textbf{1963}, \emph{35}, 457--464\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Closs and Miller(1988)Closs, and Miller]{closs1988intramolecular}
+% Closs,~G.~L.; Miller,~J.~R. Intramolecular long-distance electron transfer in
+%   organic molecules. \emph{Science} \textbf{1988}, \emph{240}, 440--447\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[Silva and Reilly(1996)Silva, and Reilly]{silva1996theoretical}
+% Silva,~C.~R.; Reilly,~J.~P. Theoretical Calculations on Excited Electronic
+%   States of Benzaldehyde and Observation of the $S_2\leftarrow S_0$ Jet-Cooled
+%   Spectrum. \emph{J. Phys. Chem.} \textbf{1996}, \emph{100},
+%   17111--17123\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+% \bibitem[{\AA}gren et~al.(1994){\AA}gren, Minaev, and
+%   Knuts]{aagren1994response}
+% {\AA}gren,~H.; Minaev,~B.~F.; Knuts,~S. Response Theory Studies of
+%   Triplet-State Spectra and Radiative Lifetimes of Naphthalene, Quinoxaline,
+%   and Phthalazine. \emph{J.  Phys.  Chem.} \textbf{1994},
+%   \emph{98}, 3943--3949\relax
+% \mciteBstWouldAddEndPuncttrue
+% \mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+% {\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+% \EndOfBibitem
+
+% % \end{thebibliography}
+% \end{mcitethebibliography}
 

### 2016-03-29 Chapters/chap3/Manuscript-FINAL.tex
Change to bib

@@
 state-to-state rate in which the coupling between  states depends upon the
-nuclear coordinates\cite{pereverzev:104906}. This approach incorporates a fully quantum
+nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
 mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
@@
 transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
-\cite{tamura:107402,tamura:021103,singh:194905,Bittner:2014aa}.
+\cite{tamura2008phonon,tamura2007exciton,singh2009fluorescence,bittner2014noise}.
 Central to our work here is the use of a mode-projection scheme
@@
 triplet-triplet excitation energy transfer between a naphthalene donor and a
-benzaldehyde acceptor linked by a variety of bridging units as shown in Fig.~\ref{struct}. \cite{xunmo2014}
+benzaldehyde acceptor linked by a variety of bridging units as shown in Fig.~\ref{struct}. \cite{yang2014intramolecular}
 \begin{figure}
@@
 which verified the existence of the Marcus inverted regime.
-In Ref. \cite{xunmo2014} we showed that both
+In Ref. \cite{yang2014intramolecular} we showed that both
 the autocorrelation function of the electronic coupling operators
@@
 % \subsection{Construction and parameterization}
-Our method was detailed in Ref.\cite{xunmo2014} but to be self-contained, we briefly present it here.
+Our method was detailed in ~Ref. \cite{yang2014intramolecular} but to be self-contained, we briefly present it here.
 
@@
 % and perform a polaron transform
-% using the unitary transformation~\cite{grover:2099,rice:2504,pereverzev:104906}.
+% using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
 % \begin{eqnarray}
@@
 % The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
-% Ref.~\citenum{pereverzev:104906}.
+% Ref.~\citenum{pereverzev2006time}.
 % Using this approach , the golden-rule rates are given by
@@
 % normal modes, as well as the experimental rates,
-% when parameterized using accurate quantum chemical data.\cite{xunmo2014}
+% when parameterized using accurate quantum chemical data.\cite{yang2014intramolecular}
 
@@
 
-Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam} can be expressed in a time-convolutionless mater equation \cite{pereverzev:104906}.
+Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam} can be expressed in a time-convolutionless mater equation \cite{pereverzev2006time}.
 The derivation is lengthy so we present it briefly.
@@
 then perform a polaron transform
-using the unitary transformation~\cite{grover:2099,rice:2504,pereverzev:104906}.
+using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
 \begin{eqnarray}
@@
 % The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
-% Ref.~\citenum{pereverzev:104906}.
+% Ref.~\citenum{pereverzev2006time}.
 Using this approach , the golden-rule rates are given by
@@
 normal modes, as well as the experimental rates,
-when parameterized using accurate quantum chemical data.\cite{xunmo2014}
+when parameterized using accurate quantum chemical data.\cite{yang2014intramolecular}
 
@@
 % open an avenue for developing improved approximations for transition rates.
-% In our previous work \cite{xunmo2014},  we presented a Lanczos-base ranking algorithm that project
+% In our previous work \cite{yang2014intramolecular},  we presented a Lanczos-base ranking algorithm that project
 % out a series of nuclear displacements that are most important for
@@
 open an avenue for developing improved approximations for transition rates.
-In our previous work \cite{xunmo2014},  we presented a Lanczos-base ranking algorithm that project
+In our previous work \cite{yang2014intramolecular},  we presented a Lanczos-base ranking algorithm that project
 out a series of nuclear displacements that are most important for
@@
 
-However, as seen on our previous work \cite{xunmo2014},
+However, as seen on our previous work \cite{yang2014intramolecular},
 the approximate correlation function does not need to give perfect agreement
@@
 
+% \bibliography{Dbib}
+
 % \bibliography{fragmentanalysis}
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{16}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{http://dx.doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\bibitem [{\citenamefont {Marcus}(1956)}]{marcus1956theory}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
-  {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
-  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {24}},\ \bibinfo
-  {pages} {966} (\bibinfo {year} {1956})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Marcus}(1965)}]{marcus1965theory}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
-  {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
-  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {43}},\ \bibinfo
-  {pages} {679} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Marcus}(1993)}]{marcus1993electron}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
-  {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Reviews of Modern Physics}\ }\textbf {\bibinfo {volume} {65}},\ \bibinfo
-  {pages} {599} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Miller}, \citenamefont {Calcaterra},\ and\
-  \citenamefont {Closs}(1984)}]{miller1984intramolecular}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Miller}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Calcaterra}},
-  \ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Closs}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of the
-  American Chemical Society}\ }\textbf {\bibinfo {volume} {106}},\ \bibinfo
-  {pages} {3047} (\bibinfo {year} {1984})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Closs}\ \emph {et~al.}(1988)\citenamefont {Closs},
-  \citenamefont {Piotrowiak}, \citenamefont {MacInnis},\ and\ \citenamefont
-  {Fleming}}]{closs1988determination}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
-  {Closs}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Piotrowiak}},
-  \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont {MacInnis}}, \ and\
-  \bibinfo {author} {\bibfnamefont {G.~R.}\ \bibnamefont {Fleming}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of the
-  American Chemical Society}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo
-  {pages} {2652} (\bibinfo {year} {1988})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Closs}\ \emph {et~al.}(1989)\citenamefont {Closs},
-  \citenamefont {Johnson}, \citenamefont {Miller},\ and\ \citenamefont
-  {Piotrowiak}}]{closs1989connection}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
-  {Closs}}, \bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Johnson}},
-  \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Miller}}, \ and\
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Piotrowiak}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of the
-  American Chemical Society}\ }\textbf {\bibinfo {volume} {111}},\ \bibinfo
-  {pages} {3751} (\bibinfo {year} {1989})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Pereverzev}\ and\ \citenamefont
-  {Bittner}(2006)}]{pereverzev:104906}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Pereverzev}}\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
-  {Bittner}},\ }\href {\doibase 10.1063/1.2348869} {\bibfield  {journal}
-  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
-  {volume} {125}},\ \bibinfo {eid} {104906} (\bibinfo {year}
-  {2006})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Tamura}\ \emph {et~al.}(2008)\citenamefont {Tamura},
-  \citenamefont {Ramon}, \citenamefont {Bittner},\ and\ \citenamefont
-  {Burghardt}}]{tamura:107402}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Tamura}}, \bibinfo {author} {\bibfnamefont {J.~G.~S.}\ \bibnamefont
-  {Ramon}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Bittner}},
-  \ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Burghardt}},\
-  }\href {\doibase 10.1103/PhysRevLett.100.107402} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
-  {100}},\ \bibinfo {eid} {107402} (\bibinfo {year} {2008})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Tamura}, \citenamefont {Bittner},\ and\ \citenamefont
-  {Burghardt}(2007)}]{tamura:021103}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Tamura}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Bittner}},
-  \ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Burghardt}},\
-  }\href {\doibase 10.1063/1.2431358} {\bibfield  {journal} {\bibinfo
-  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
-  {126}},\ \bibinfo {eid} {021103} (\bibinfo {year} {2007})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Singh}\ \emph {et~al.}(2009)\citenamefont {Singh},
-  \citenamefont {Bittner}, \citenamefont {Beljonne},\ and\ \citenamefont
-  {Scholes}}]{singh:194905}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Singh}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Bittner}},
-  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Beljonne}}, \ and\
-  \bibinfo {author} {\bibfnamefont {G.~D.}\ \bibnamefont {Scholes}},\ }\href
-  {\doibase 10.1063/1.3259549} {\bibfield  {journal} {\bibinfo  {journal} {The
-  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {131}},\ \bibinfo
-  {eid} {194905} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bittner}\ and\ \citenamefont
-  {Silva}(2014)}]{Bittner:2014aa}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
-  {Bittner}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Silva}},\ }\href {http://dx.doi.org/10.1038/ncomms4119} {\bibfield
-  {journal} {\bibinfo  {journal} {Nat Commun}\ }\textbf {\bibinfo {volume}
-  {5}},\ \bibinfo {pages} {3119} (\bibinfo {year} {2014})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Yang}\ and\ \citenamefont
-  {Bittner}(2014)}]{xunmo2014}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
-  {Yang}}\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
-  {Bittner}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
-  Journal of Physical Chemistry A}\ }\textbf {\bibinfo {volume} {118}},\
-  \bibinfo {pages} {5196} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Subotnik}\ \emph {et~al.}(2010)\citenamefont
-  {Subotnik}, \citenamefont {Vura-Weis}, \citenamefont {Sodt},\ and\
-  \citenamefont {Ratner}}]{subotnik2010predicting}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
-  {Subotnik}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Vura-Weis}},
-  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Sodt}}, \ and\
-  \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Ratner}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The Journal of
-  Physical Chemistry A}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo {pages}
-  {8665} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Grover}\ and\ \citenamefont
-  {Silbey}(1970)}]{grover:2099}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~K.}\ \bibnamefont
-  {Grover}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Silbey}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
-  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {52}},\ \bibinfo
-  {pages} {2099} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rice}\ and\ \citenamefont
-  {Gartstein}(1994)}]{rice:2504}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Rice}}\ and\ \bibinfo {author} {\bibfnamefont {Y.~N.}\ \bibnamefont
-  {Gartstein}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physical review letters}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo
-  {pages} {2504} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Dexter}(1953)}]{dexter1953theory}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~L.}\ \bibnamefont
-  {Dexter}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
-  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo
-  {pages} {836} (\bibinfo {year} {1953})}\BibitemShut {NoStop}%
-\end{thebibliography}%
+% \begin{thebibliography}{16}%
+% \makeatletter
+% \providecommand \@ifxundefined [1]{%
+%  \@ifx{#1\undefined}
+% }%
+% \providecommand \@ifnum [1]{%
+%  \ifnum #1\expandafter \@firstoftwo
+%  \else \expandafter \@secondoftwo
+%  \fi
+% }%
+% \providecommand \@ifx [1]{%
+%  \ifx #1\expandafter \@firstoftwo
+%  \else \expandafter \@secondoftwo
+%  \fi
+% }%
+% \providecommand \natexlab [1]{#1}%
+% \providecommand \enquote  [1]{``#1''}%
+% \providecommand \bibnamefont  [1]{#1}%
+% \providecommand \bibfnamefont [1]{#1}%
+% \providecommand \citenamefont [1]{#1}%
+% \providecommand \href@noop [0]{\@secondoftwo}%
+% \providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+% \providecommand \@href[1]{\@@startlink{#1}\@@href}%
+% \providecommand \@@href[1]{\endgroup#1\@@endlink}%
+% \providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+%   `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+% \providecommand \@@startlink[1]{}%
+% \providecommand \@@endlink[0]{}%
+% \providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+% \providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+% \providecommand \urlprefix  [0]{URL }%
+% \providecommand \Eprint [0]{\href }%
+% \providecommand \doibase [0]{http://dx.doi.org/}%
+% \providecommand \selectlanguage [0]{\@gobble}%
+% \providecommand \bibinfo  [0]{\@secondoftwo}%
+% \providecommand \bibfield  [0]{\@secondoftwo}%
+% \providecommand \translation [1]{[#1]}%
+% \providecommand \BibitemOpen [0]{}%
+% \providecommand \bibitemStop [0]{}%
+% \providecommand \bibitemNoStop [0]{.\EOS\space}%
+% \providecommand \EOS [0]{\spacefactor3000\relax}%
+% \providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+% \let\auto@bib@innerbib\@empty
+% %</preamble>
+% \bibitem [{\citenamefont {Marcus}(1956)}]{marcus1956theory}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
+%   {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
+%   Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {24}},\ \bibinfo
+%   {pages} {966} (\bibinfo {year} {1956})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Marcus}(1965)}]{marcus1965theory}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
+%   {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
+%   Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {43}},\ \bibinfo
+%   {pages} {679} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Marcus}(1993)}]{marcus1993electron}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
+%   {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+%   {Reviews of Modern Physics}\ }\textbf {\bibinfo {volume} {65}},\ \bibinfo
+%   {pages} {599} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Miller}, \citenamefont {Calcaterra},\ and\
+%   \citenamefont {Closs}(1984)}]{miller1984intramolecular}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+%   {Miller}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Calcaterra}},
+%   \ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Closs}},\
+%   }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of the
+%   American Chemical Society}\ }\textbf {\bibinfo {volume} {106}},\ \bibinfo
+%   {pages} {3047} (\bibinfo {year} {1984})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Closs}\ \emph {et~al.}(1988)\citenamefont {Closs},
+%   \citenamefont {Piotrowiak}, \citenamefont {MacInnis},\ and\ \citenamefont
+%   {Fleming}}]{closs1988determination}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
+%   {Closs}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Piotrowiak}},
+%   \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont {MacInnis}}, \ and\
+%   \bibinfo {author} {\bibfnamefont {G.~R.}\ \bibnamefont {Fleming}},\
+%   }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of the
+%   American Chemical Society}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo
+%   {pages} {2652} (\bibinfo {year} {1988})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Closs}\ \emph {et~al.}(1989)\citenamefont {Closs},
+%   \citenamefont {Johnson}, \citenamefont {Miller},\ and\ \citenamefont
+%   {Piotrowiak}}]{closs1989connection}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
+%   {Closs}}, \bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Johnson}},
+%   \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Miller}}, \ and\
+%   \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Piotrowiak}},\
+%   }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of the
+%   American Chemical Society}\ }\textbf {\bibinfo {volume} {111}},\ \bibinfo
+%   {pages} {3751} (\bibinfo {year} {1989})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Pereverzev}\ and\ \citenamefont
+%   {Bittner}(2006)}]{pereverzev2006time}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%   {Pereverzev}}\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
+%   {Bittner}},\ }\href {\doibase 10.1063/1.2348869} {\bibfield  {journal}
+%   {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+%   {volume} {125}},\ \bibinfo {eid} {104906} (\bibinfo {year}
+%   {2006})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Tamura}\ \emph {et~al.}(2008)\citenamefont {Tamura},
+%   \citenamefont {Ramon}, \citenamefont {Bittner},\ and\ \citenamefont
+%   {Burghardt}}]{tamura2008phonon}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+%   {Tamura}}, \bibinfo {author} {\bibfnamefont {J.~G.~S.}\ \bibnamefont
+%   {Ramon}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Bittner}},
+%   \ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Burghardt}},\
+%   }\href {\doibase 10.1103/PhysRevLett.100.107402} {\bibfield  {journal}
+%   {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
+%   {100}},\ \bibinfo {eid} {107402} (\bibinfo {year} {2008})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Tamura}, \citenamefont {Bittner},\ and\ \citenamefont
+%   {Burghardt}(2007)}]{tamura2007exciton}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+%   {Tamura}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Bittner}},
+%   \ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Burghardt}},\
+%   }\href {\doibase 10.1063/1.2431358} {\bibfield  {journal} {\bibinfo
+%   {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+%   {126}},\ \bibinfo {eid} {021103} (\bibinfo {year} {2007})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Singh}\ \emph {et~al.}(2009)\citenamefont {Singh},
+%   \citenamefont {Bittner}, \citenamefont {Beljonne},\ and\ \citenamefont
+%   {Scholes}}]{singh2009fluorescence}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+%   {Singh}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Bittner}},
+%   \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Beljonne}}, \ and\
+%   \bibinfo {author} {\bibfnamefont {G.~D.}\ \bibnamefont {Scholes}},\ }\href
+%   {\doibase 10.1063/1.3259549} {\bibfield  {journal} {\bibinfo  {journal} {The
+%   Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {131}},\ \bibinfo
+%   {eid} {194905} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Bittner}\ and\ \citenamefont
+%   {Silva}(2014)}]{bittner2014noise}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
+%   {Bittner}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+%   {Silva}},\ }\href {http://dx.doi.org/10.1038/ncomms4119} {\bibfield
+%   {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume}
+%   {5}},\ \bibinfo {pages} {3119} (\bibinfo {year} {2014})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Yang}\ and\ \citenamefont
+%   {Bittner}(2014)}]{yang2014intramolecular}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
+%   {Yang}}\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
+%   {Bittner}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
+%   Journal of Physical Chemistry A}\ }\textbf {\bibinfo {volume} {118}},\
+%   \bibinfo {pages} {5196} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Subotnik}\ \emph {et~al.}(2010)\citenamefont
+%   {Subotnik}, \citenamefont {Vura-Weis}, \citenamefont {Sodt},\ and\
+%   \citenamefont {Ratner}}]{subotnik2010predicting}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
+%   {Subotnik}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Vura-Weis}},
+%   \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Sodt}}, \ and\
+%   \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Ratner}},\
+%   }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The Journal of
+%   Physical Chemistry A}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo {pages}
+%   {8665} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Grover}\ and\ \citenamefont
+%   {Silbey}(1970)}]{grover1970exciton}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~K.}\ \bibnamefont
+%   {Grover}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+%   {Silbey}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
+%   Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {52}},\ \bibinfo
+%   {pages} {2099} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Rice}\ and\ \citenamefont
+%   {Gartstein}(1994)}]{rice1994excitons}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Rice}}\ and\ \bibinfo {author} {\bibfnamefont {Y.~N.}\ \bibnamefont
+%   {Gartstein}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+%   {Physical review letters}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo
+%   {pages} {2504} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Dexter}(1953)}]{dexter1953theory}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~L.}\ \bibnamefont
+%   {Dexter}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
+%   Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo
+%   {pages} {836} (\bibinfo {year} {1953})}\BibitemShut {NoStop}%
+% \end{thebibliography}%
 

### 2016-03-29 Chapters/chap3/Manuscript-FINAL.tex
Solve label conflicts

@@
 \begin{equation}
-k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T}\label{eq:marcus},
+k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T},
 \end{equation}
@@
 -\sin\theta & \cos\theta
-\end{array}\right).\label{eq:boys}
+\end{array}\right).
 \end{equation}
@@
 \end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
-&+& H_{osc}.\label{eq:locaiHam}
+&+& H_{osc}.\label{eq:locaiHam2}
 \end{eqnarray}
@@
 states is small.
-Thus, all parameters in Eq.~\ref{eq:locaiHam}  can be  obtained from
+Thus, all parameters in Eq.~\ref{eq:locaiHam2}  can be  obtained from
 standard  quantum chemical computations.
@@
 
-Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam} can be expressed in a time-convolutionless mater equation \cite{pereverzev2006time}.
+Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam2} can be expressed in a time-convolutionless mater equation \cite{pereverzev2006time}.
 The derivation is lengthy so we present it briefly.
@@
 \nonumber \\
-\label{ham1}
+% \label{ham1}
 \end{eqnarray}
@@
 \sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
-\label{unitary}
+% \label{unitary}
 \end{eqnarray}
@@
 a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
-\label{opm}
+% \label{opm}
 \end{eqnarray}
@@
 k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
-\label{gr-expression}
+% \label{gr-expression}
 \end{eqnarray}
@@
 \subsection{Constructing Primary Lanczos Modes}
-The linear coupling parameter $ {\mathbf g}_{22}$ in Eq.~\ref{eq:locaiHam} defines
+The linear coupling parameter $ {\mathbf g}_{22}$ in Eq.~\ref{eq:locaiHam2} defines
 a force

### 2016-03-29 Chapters/chap2/manuscript.tex
Correct the discussion of irreducible representation

@@
 \caption{Sketch of Marcus parabolas for a model energy or charge transfer system.
-Labeled are the key parameters used to compute the Marcus rate constant (Eq. 1).
+Labeled are the key parameters used to compute the Marcus rate constant (Eq. \ref{eq:marcus}).
 Energies are given in eV and the collective nuclear displacement  is dimensionless.
@@
 vectors of the individual atoms.   In each case, the primary
-coupling mode involves the  $b_{2u}$ in plane C=C stretching motions of the naphthalene donor and the
- in-plane $\nu_{8}$ (in the Mulliken numbering scheme) ring-squeezing motions of the benzaldehyde acceptor\cite{silva1996theoretical}.
-It is interesting to note
-that $^{3}B_{2u}$ is also the symmetry of the first triplet $\pi-\pi^{*}$ excited state in naphthalene \cite{aagren1994response},
-Moreover, if we were to approximate benzaldehyde as a $C_{2v}$ molecule, taking the aldehyde as local site,
-the resulting first triplet $\pi-\pi^{*}$ is the product of a $b_{1}$ HOMO and a $b_{1}$ LUMO giving a state in the
-  $a_{1}$ irreducible representation. This is the same irreducible representation one obtains for the $\nu_{8}$
-  mode, approximating it as a symmetric stretching mode.
-This suggests the existence of underlying symmetry selection or propensity rule in determining the coupling modes.
+coupling mode involves the  $A_{g}$ in plane C=C stretching motions of the naphthalene donor and the
+ in-plane $A_1$ ring-squeezing motions of the benzaldehyde acceptor.
+It is interesting to note that
+% $^{3}B_{2u}$ is also the symmetry of the first triplet $\pi-\pi^{*}$ excited state in naphthalene \cite{aagren1994response}, Moreover,
+if we were to approximate naphthalene as a $D_{2h}$ molecule, and benzaldehyde as a $C_{2v}$ molecule, taking the aldehyde as local site, the primary coupling modes always correspond to the totally symmetric irreducible representations on moieties.
+Further analysis of symmetry reveals interesting details of the reactions, which are discussed in next chapter.
+% the resulting first triplet $\pi-\pi^{*}$ is the product of a $b_{1}$ HOMO and a $b_{1}$ LUMO giving a state in the
+%   $a_{1}$ irreducible representation. This is the same irreducible representation one obtains for the $\nu_{8}$
+%   mode, approximating it as a symmetric stretching mode.
+% This suggests the existence of underlying symmetry selection or propensity rule in determining the coupling modes.
 

### 2016-03-29 Chapters/chap3/Manuscript-FINAL.tex
Correct the discussion of irreducible representation

@@
 \caption{
-Primary Lanczos modes for (a) c14ee and (b) d26ae projected onto the atomic displacement coordinates.  The frequencies
+Primary Lanczos modes for (a) c-1,4ee and (b) d-2,6ae projected onto the atomic displacement coordinates.  The frequencies
 for both these are at 0.185 eV (1490 cm$^{-1}$), a typical $C=C$ stretching frequency for arene systems.
@@
 intramolecular triplet energy transfer within
-two representative donor-bridge-acceptor molecules from our study, termed c14ee and d26ae.
+two representative donor-bridge-acceptor molecules from our study, termed c-1,4ee and d-2,6ae.
 In both cases, triplet energy is transferred from a benzaldehyde (BZ) donor group to a naphthyl- acceptor group.
@@
 Fig.~\ref{fragProj} shows the projection of the PLMs  onto the local vibrational modes of
-D/A moieties in molecules of c14ee and d26ae.
+D/A moieties in molecules of c-1,4ee and d-2,6ae.
 In each case, we label the dominant contributions by the
@@
 \subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2d.pdf}}
-\caption{Projection of PLMs onto (a) benzaldehyde in c14ee (b) symmetrized naphthalene in c14ee, (c) benzaldehyde in d26ae and (d) symmetrized naphthalene in d26ae.
+\caption{Projection of PLMs onto (a) benzaldehyde in c-1,4ee (b) symmetrized naphthalene in c-1,4ee, (c) benzaldehyde in d-2,6ae and (d) symmetrized naphthalene in d-2,6ae.
 The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are color-coded. The assigned IRs for naphthalene are exact
@@
 together with their PLMs and correlation functions for different numbers of projected modes.
-% and d26ae and compute the
+% and d-2,6ae and compute the
 %coupling correlation functions in Eq.~\ref{cor-fun} and displacement vectors of their
@@
 %Moreover, the PLMs in each case are similar to the PLMs in the napthyl-[bridge]-BZ
-Moreover, the PLMs are qualitatively similar to the PLM of unchanged c14ee.
+Moreover, the PLMs are qualitatively similar to the PLM of unchanged c-1,4ee.
 The displacements on the benzaldehyde moiety are almost identical, while on the phenyl and anthracene moieties they belong to totally symmetric irreducible representations as well.
@@
 %\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/D26aeNaphSymmProj.pdf}}
-%\caption{Projection of PLMs onto (a) benzaldehyde in c14ee (b) symmetrized naphthalene in c14ee, (c) benzaldehyde in d26ae and (d) symmetrized naphthalene in d26ae.
+%\caption{Projection of PLMs onto (a) benzaldehyde in c-1,4ee (b) symmetrized naphthalene in c-1,4ee, (c) benzaldehyde in d-2,6ae and (d) symmetrized naphthalene in d-2,6ae.
 %The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are colorcoded. The assigned IRs for naphthalene are exact
@@
 %\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/PrimeModeBenzeneD26ae.pdf}}
-\caption{The correlation functions of projected modes for c14ee with the naphthalene moiety
+\caption{The correlation functions of projected modes for c-1,4ee with the naphthalene moiety
 replaced by (a) phenyl ring and (b) anthracene, with their PLMs shown in (c) and (d). \label{benz}}
-%\caption{The correlation function of PLM compared to the exact one calculated with all normal modes for the (a) c14ee (b) d26ae, with naphthalene replaced by phenyl ring.Their PLMs are in (c) for c14ee and (d) for d26ae.\label{benz}}
+%\caption{The correlation function of PLM compared to the exact one calculated with all normal modes for the (a) c-1,4ee (b) d-2,6ae, with naphthalene replaced by phenyl ring.Their PLMs are in (c) for c-1,4ee and (d) for d-2,6ae.\label{benz}}
 \end{figure*}
@@
 \subfloat[]{\includegraphics[width=0.87\columnwidth]{Chapters/chap3/Figure5b.pdf}}
-\caption{Projections of the PLM onto the normal modes of (a) c14ee and (b) d26ae.\label{LancProj}}
+\caption{Projections of the PLM onto the normal modes of (a) c-1,4ee and (b) d-2,6ae.\label{LancProj}}
 \end{figure*}
@@
 \subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure6b.pdf}}
-\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c14ee and (b) d26ae.
-They are almost same to Fig.~\ref{fragProj}(b) and (d) except for a mode with $B_{2u}$ symmetry in c14ee.
+\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c-1,4ee and (b) d-2,6ae.
+They are almost same to Fig.~\ref{fragProj}(b) and (d) except for a mode with $B_{2u}$ symmetry in c-1,4ee.
 Embedded are the most significant modes, namely, the 33rd modes \label{projNaph}}
@@
 %\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/D26aeNaphProj.pdf}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeNaph1stMode.png}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeNaph1stMode.png}}
-%\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c14ee and (b) d26ae.
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c-1,4eeNaph1stMode.png}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d-2,6aeNaph1stMode.png}}
+%\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c-1,4ee and (b) d-2,6ae.
 They are almost same to Fig.~\ref{fragProj}(b) and (d) except for a mode with $b_{2u}$ symmetry in (c).
-In the second row are the most dominant mode in projections above, namely, the 33rd normal mode of naphthalene in (c) c14ee and (d) d26ae.
+In the second row are the most dominant mode in projections above, namely, the 33rd normal mode of naphthalene in (c) c-1,4ee and (d) d-2,6ae.
 The mode in (d) belongs to  $A_g$ representation quite well while in (c), hydrogens move  in the  $B_{2u}$ way.
@@
 almost same to the ones on the symmetrized geometry, except a new $B_{2u}$ mode is involved
-in c14ee. However, it does not exist in d26ae. The reason is that the most significant
-mode of c14ee and d26ae are slightly different. The corresponding displacement vectors are
-embedded in Fig.~\ref{projNaph}. For c14ee, the dominant mode is not an exact $A_g$ mode, because
+in c-1,4ee. However, it does not exist in d-2,6ae. The reason is that the most significant
+mode of c-1,4ee and d-2,6ae are slightly different. The corresponding displacement vectors are
+embedded in Fig.~\ref{projNaph}. For c-1,4ee, the dominant mode is not an exact $A_g$ mode, because
 carbons move in the way of $A_g$ while
-hydrogens behave like $B_{2u}$. On the contrary, d26ae has
+hydrogens behave like $B_{2u}$. On the contrary, d-2,6ae has
 a mode more similar to $A_g$.
-As the result, in the projection of naphthalene in c14ee, a  $B_{2u}$
+As the result, in the projection of naphthalene in c-1,4ee, a  $B_{2u}$
 mode is needed to correct the hydrogen motions.
@@
 %\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateD26ae.pdf}}
-\caption{Correlation functions for different combinations of normal modes are shown for (a) c14ee and (b) d26ae.  The ``exact'' ones refer are for the PLMs.  ``NfBf"
+\caption{Correlation functions for different combinations of normal modes are shown for (a) c-1,4ee and (b) d-2,6ae.  The ``exact'' ones refer are for the PLMs.  ``NfBf"
 is the mode made up from all normal modes of both the donor and acceptor sites.
@@
  relative error in rate constants calculated for various combinations of normal modes compared to the exact result
- or c14ee (c) and d26ae (d) respectively. \label{backCorr}}
+ or c-1,4ee (c) and d-2,6ae (d) respectively. \label{backCorr}}
 \end{figure*}
@@
 This data is summarized in the form of contour plots in  Fig.~\ref{backCorr}(c,d).
-For the c14ee case, there is an optimal ``valley'' whereby taking 3 modes from benzaldehyde and 4-6 modes from
+For the c-1,4ee case, there is an optimal ``valley'' whereby taking 3 modes from benzaldehyde and 4-6 modes from
 naphthalene produces an agreement with the exact result to within 5\%.
-For the d26ae case,  fewer number of benzaldehyde modes than naphthalene modes are needed to
+For the d-2,6ae case,  fewer number of benzaldehyde modes than naphthalene modes are needed to
 give agreement to within 5\% of the exact rate constant.   This is easily anticipated since
@@
 \subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8d.pdf}}
-\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) benzaldehyde and (b) naphthalene sites in c14ee, and d26ae in (c) and (d).
+\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) benzaldehyde and (b) naphthalene sites in c-1,4ee, and d-2,6ae in (c) and (d).
 Except for some low frequency modes, they are similar to the projections of PLM.
@@
 \subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure9b.pdf}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeDADiffproj.pdf}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeDADiffproj.pdf}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeNM2.png}}
-%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeNM1.png}}
-\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) c14ee and (b) d26ae.
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c-1,4eeDADiffproj.pdf}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d-2,6aeDADiffproj.pdf}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c-1,4eeNM2.png}}
+%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d-2,6aeNM1.png}}
+\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) c-1,4ee and (b) d-2,6ae.
 They are both dominated by single mode, the relaxation mode (RM), which is embedded.\label{geomDiffProj}}
@@
 %     \hline
-%     Rate constants in c14ee/$s^{-1}$   & 3.66E9 & 3.69E9 & 5.28E9 & 4.31E9   \\
-%     Rate constants in d26ae/$s^{-1}$   & 4.66E4 &4.80E4 & 1.30E4 & 5.11E4 \\
+%     Rate constants in c-1,4ee/$s^{-1}$   & 3.66E9 & 3.69E9 & 5.28E9 & 4.31E9   \\
+%     Rate constants in d-2,6ae/$s^{-1}$   & 4.66E4 &4.80E4 & 1.30E4 & 5.11E4 \\
 %     \hline
@@
 It does not look same to the projections of PLM in Fig.~\ref{LancProj}.
-The geometry change of both c14ee and d26ae are dominated by single mode with very low frequency, shown in Fig.~\ref{geomDiffProj}(c) and (d).
+The geometry change of both c-1,4ee and d-2,6ae are dominated by single mode with very low frequency, shown in Fig.~\ref{geomDiffProj}(c) and (d).
 We term them the dominant mode relaxation mode (RM) for the reason below.
@@
 % \subfloat[]{\includegraphics[width=0.53\columnwidth]{Chapters/chap3/Figure10c.pdf}}
-\caption{Correlation functions of relaxation mode (RM), PLM, geometry change (GC), and geometry change with the RM component eliminated for (a) c14ee and (b) d26ae.
+\caption{Correlation functions of relaxation mode (RM), PLM, geometry change (GC), and geometry change with the RM component eliminated for (a) c-1,4ee and (b) d-2,6ae.
 The exact rate is computed using the full set of normal modes.}
@@
 \subfloat[]{\includegraphics[width=0.9\columnwidth]{Chapters/chap3/Figure10c.pdf}}
-\caption{Relative comparison of the rate constants computed using different sets of reduced modes. blue = c14ee, gold =d26ae. }
+\caption{Relative comparison of the rate constants computed using different sets of reduced modes. blue = c-1,4ee, gold =d-2,6ae. }
 \label{RateComp}

### 2016-03-29 Chapters/chap1/introduction.tex
Correct bib for uppercase

@@
 %!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
+\chapter{Chapter 1}
+\section{Introduction}
+
+Energy and electronic transport plays a central role in a
+wide range of  chemical  and biological systems.
+It is the fundamental mechanism for transporting the  energy  of a
+absorbed photon to a reaction center in light harvesting systems
+and for initiating a wide range of photo-induced  chemical processes,
+including vision, DNA mutation, and pigmentation.
+The seminal model for calculating electron transfer rates was developed by
+Marcus in the 1950's\cite{marcus1956theory,marcus1965theory,marcus1993electron}.
+\begin{equation}
+k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta\epsilon)^{2}/4\text{\ensuremath{\lambda}}k_{B}T}.\label{eq:marcus}
+\end{equation}
+where $\lambda$ is  energy required to reorganize the environment
+following the transfer of an electron from donor to acceptor.
+and $\Delta \epsilon$ is the driving force for the reaction.
+
+\begin{figure}[h]
+\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure1}
+\caption{Sketch of Marcus parabolas for a model energy or charge transfer system.
+Labeled are the key parameters used to compute the Marcus rate constant (Eq. \ref{eq:marcus}).
+Energies are given in eV and the collective nuclear displacement  is dimensionless.
+}
+\label{marcus}
+\end{figure}
+
+If we assume that the nuclear motions about the equilibrium configurations of the
+donor and acceptor species is harmonic,  the chemical reactions resulting from
+energy or charge transfer events can be understood in terms of intersecting
+diabatic potentials as sketched in Fig.~\ref{marcus}.    The upper and lower
+curves are the adiabatic potential energy surfaces describing the nuclear dynamics
+resulting from an energy or charge transfer event, taking the geometry of the donor
+state as the origin.
+%For reactions carried out in open systems,  the Marcus parabolas represent
+%free energy surfaces with driving force $\Delta G$.
+As the transfer occurs by crossing an energy barrier,
+the transfer rate can be expected to be in the Arrhenius form
+\begin{eqnarray}
+k\propto e^{-E_{A}/k_{B}T},
+\end{eqnarray}
+with $E_{A}$ as the activation energy.
+ Using $E_{A}={(\lambda+\Delta \epsilon)^{2}}/{4\lambda}$
+ we can relate the activation energy to both the reorganization energy and driving force, $-\Delta \epsilon$.
+One of the most profound predictions of the theory is that  as the driving force increases,
+the transfer rate reaches a maximum and further increases in the driving force
+lead to lower reaction rates, termed the inverted regime.
+
+A number of years ago,  we developed a time-convolutionless  master equation approach for computing
+state-to-state rates in which the coupling between  states depends upon the
+nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
+mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
+well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
+vibrational normal mode frequencies, and the electronic energies and energy derivatives
+at a reference configuration.  The approach has been used by our group to compute state-to-state
+transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
+\cite{tamura2008phonon,tamura2007exciton,bittner2014noise,singh2009fluorescence}.
+This paper represents the first time we have used this approach within the context of a fully {\em ab initio} quantum
+chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
+using state-of-the-art quantum chemical methods
+and results compared to both theoretical and experimental
+rates.
+
+% Central to the work presented here consists of two parts. One is the use of a diabatization scheme for determining
+% donor and acceptor states in a molecular unit.
+The other is a projection scheme which enables us to analyze the contribution of vibrations in reactions.
+Similar decomposition schemes have been presented by Burghardt
+%  \cite{cederbaum2005short,gindensperger2006shortI,gindensperger2006shortII,cederbaum2005short}
+%  and the approach used here builds upon the method given in Ref.~\cite{pereverzev2009energy}. In Chapter \ref{chap:chapt2} we benchmark the approach
+% by computing the  triplet energy transfer rates for a series of donor-bridge-acceptor molecules
+% originally studied by Closs\cite{miller1984intramolecular}.  The triplet energy transfer rates computed using our approach
+% compare well against both the experimental rates and with
+% more recent theoretical rates presented by Subotnik {\em et al.}
+% \cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
+% Then we use the projection operator scheme
+% to parses out specific internal nuclear motions that accompany
+% the electronic transition.
+%  By analyzing the electron-phonon couplings, we can
+% discern a reduced set of motions that are responsible for coupling between the donor and
+% acceptor states.
+
+\section{Theoretical Approach}
+Below we give a detailed description of our methods.
+
+\subsection{Model Hamiltonian}
+We consider a generic model for $n$ electronic states coupled linearly
+to a phonon bath.  Taking the electronic ground state of the system as a reference
+and assuming that the electronic states are coupled linearly to a common set of
+ modes, we arrive a generic form for the Hamiltonian:
+ \begin{eqnarray}
+H=\left(\begin{array}{cc}
+\epsilon_{1} & 0\\
+0 & \epsilon_{2}
+\end{array}\right)+\left(\begin{array}{cc}
+{\mathbf g}_{11}&{\mathbf g}_{12} \\
+{\mathbf g}_{21} &{\mathbf g}_{22}
+\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
+\nonumber \\
+\label{ham1}
+\end{eqnarray}
+Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
+reference geometry--typically that of the donor or acceptor state.   The second term represents the
+linearized coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
+normal coordinates $\mathbf q$.   The diagonal terms
+give the adiabatic displacement forces between the reference geometry and the two states.  If we choose one of the
+states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish.
+The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
+In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.
+
+We now separate Eq.~\ref{ham1} into diagonal and
+off-diagonal terms
+\begin{eqnarray}
+\hat  H = \hat H_{o} + \hat V
+\end{eqnarray}
+and perform a polaron transform
+using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
+\begin{eqnarray}
+U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
+n|(a^{\dagger}_i-a_i)}
+ \nonumber \\
+&=&
+\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
+\label{unitary}
+\end{eqnarray}
+under which the transformed Hamiltonian is written in terms of the
+diagonal elements
+\begin{eqnarray} \tilde H_0=U^{-1}H_0U
+=\sum_n\tilde\epsilon_n |n\rangle \langle
+n|+\sum_i\omega_ia^{\dagger}_ia_i,
+ \end{eqnarray}
+with  the renormalized electronic energies,
+\begin{eqnarray}
+\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
+\end{eqnarray}
+and off-diagonal terms,
+\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
+a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
+\label{opm}
+\end{eqnarray}
+In the transformed (or dressed) picture the electronic transition from state
+$|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
+normal phonon modes.  Transforming to the interaction representation
+and performing a trace over the phonons gives the spectral density in
+terms of the autocorrelation of the electron-phonon coupling
+operators.
+\begin{eqnarray}
+S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{spec-dens}
+\end{eqnarray}
+Here, $\hat V_{nm}(t)$ is the electron-phonon coupling term in the Heisenberg representation and
+$\langle \cdots \rangle$ denotes a thermal average over the
+vibrational degrees of freedom.
+The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
+Ref.~\cite{pereverzev2006time}.
+
+\subsection{Non-Markovian Master Equation and Golden-Rule rates}
+
+In Ref.~\cite{pereverzev2006time}, Pereverzev and Bittner derived
+a non-Markovian, time-convolutionless form of the Pauli master
+equation (TCLME)  for general system described by Eq.~\ref{ham1}.
+\begin{eqnarray}
+\frac{dP_{n}}{dt} = \sum_{m} W_{nm}(t)P_{m}(t) - \left(\sum_{m} W_{mn}(t)\right)P_{n}(t)
+\end{eqnarray}
+where the time-dependent rates are given by
+\begin{eqnarray}
+W_{nm}(\tau)=2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
+\label{rate-expression}
+\end{eqnarray}
+In the limit that $\tau\to\infty$, Eq.~\ref{rate-expression} gives the Fermi's Golden Rule expression for the
+transition rate,
+\begin{eqnarray}
+k_{nm}=2{\rm Re}\int_{0}^{\infty}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
+\label{gr-expression}
+\end{eqnarray}
+
+At this point it is useful to connect the various terms in the phonon-dressed Hamiltonian
+with specific physical parameters.
+First, the reorganization energy is given by
+%The terms involving $$
+%are related to the reorganized energy difference between the two states.
+%$$
+%\lambda_{nm} =\sum_{j}((g_{nnj}-g_{mmj})/\omega_j)^{2} = \sum_{j}\hbar \omega_{j}S_{j}
+%$$
+\[
+\lambda_{nm}=\sum_{j}\frac{\left(g_{nnj}-g_{mmj}\right)^{2}}{\omega_{j}} = \sum_{j}\hbar \omega_{j}S_{j}
+\]
+where  the $\{S_{j}\}$  are  the Huang-Rhys factors for each phonon mode.
+These are related to the Franck-Condon factor
+describing the overlap between the $v_j=1$ vibronic state in one electronic state
+with the $v_j=0$ vibronic state in the other.
+Likewise, the energy difference between the renormalized energy gaps is related to the
+driving force of the state-to-state transition,
+\begin{eqnarray}
+\Delta E_{nm} = \tilde \epsilon_n-\tilde \epsilon_m.
+\end{eqnarray}
+
+The difficulty in using this approach is that
+it requires both diagonal (${\mathbf g}_{nn}$) and off-diagonal  (${\mathbf g}_{nm}$) derivative couplings between
+adiabatic states.    In the following section, we discuss how we have used the Edmiston-Ruedenberg localization scheme
+to estimate the couplings\cite{edmiston1963localized}.   We also
+present how one can construct a reduced set of harmonic modes that
+fully capture the electron/nuclear coupling.
+\subsection{Parameterization From Quantum Chemistry}
+
+ In order to obtain the final form of our target Hamiltonian, we assume the diabatic  potentials
+are a good approximation to the actual adiabatic potentials.
+
+When the adiabatic (and diabatic) energy minima
+are far enough away from the crossing points and the mixing angles between the diabatic  and adiabatic
+states is small, we can
+use the gradients of the adiabatic potentials to approximate the diabatic potentials.
+Thus, if we perform calculations at the
+optimized geometry of the final acceptor state  ({\em i.~e.} about $Q_{2}$  in Fig.~\ref{marcus}),
+we can write the Hamiltonian as
+\begin{eqnarray}
+H_{dia,e}=\left(\begin{array}{cc}
+\epsilon_{1} & V_{12}\\
+V_{21} & \epsilon_{2}
+\end{array}\right)+\left(\begin{array}{cc}
+0 & 0\\
+0 & 1
+\end{array}\right) {\mathbf g}_{22}\cdot{\mathbf q}+H_{osc},
+\end{eqnarray}
+where $H_{osc}$ is the harmonic oscillator Hamiltonian for the vibrational normal modes.
+The linear assumption amounts  to performing a series expansion of the
+full, multi-dimensional coupling term and keeping only the lowest order terms.
+Systematic improvement can be made by including higher-order (e.g.  quadratic) off-diagonal couplings.
+However, this would involve a substantial increase in the complexity of the theory.
+The linear assumption is reasonable so long as  the mixing angle is small,
+as verified by the benchmark calculations presented below.
+
+We obtain the diabatic couplings $V_{12}$
+and the mixing angle $\theta$  via ER localization and transform the electronic Hamiltonian
+from the adiabatic basis to the diabatic basis {\em viz.}
+\begin{equation}
+H_{dia}=\left(\begin{array}{cc}
+\cos\theta & -\sin\theta\\
+\sin\theta & \cos\theta
+\end{array}\right)\left(\begin{array}{cc}
+\epsilon_{1}  & 0 \\
+0  & \epsilon_{2}
+\end{array}\right)\left(\begin{array}{cc}
+\cos\theta & \sin\theta\\
+-\sin\theta & \cos\theta
+\end{array}\right).\label{eq:boys}
+\end{equation}
+The diabatic coupling is then given by
+\begin{eqnarray}
+V_{ab}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
+\end{eqnarray}
+
+We then diagonalize the electronic part and transform the electron/nuclear coupling
+back into the adiabatic basis.  In doing so,  we obtain the Hamiltonian in the
+form given in Eq. \ref{ham1}
+\begin{eqnarray}
+H&=&U^{T}H_{dia}U\nonumber  \\
+&=&\left(\begin{array}{cc}
+E_{1}  & 0 \\
+0 & E_{2}
+\end{array}\right)+\left(\begin{array}{cc}
+\sin^{2}\theta & \frac{1}{2}\sin2\theta\\
+\frac{1}{2}\sin2\theta & \cos^{2}\theta
+\end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
+&+& H_{osc}.\label{eq:locaiHam}
+\end{eqnarray}
+
+\section{Determining the Optimal Electron-Phonon Coupling Components}
+
+While the Marcus expression is elegant in its simplicity in requiring three parameters that
+can be obtained experimentally, it masks a wealth of detail that underlie the quantum transition.
+Central to the theory is that there exists a collective nuclear displacement coordinate
+that connects the initial geometry of the donor to the final geometry of the acceptor.
+
+Generally speaking, this collective coordinate involves all nuclear degrees of freedom.
+However, the form of the electronic Hamiltonian in Eq.~\ref{ham1} suggests that
+there exists a subset of motions that are specific modes  that capture the majority of the
+electronic/nuclear coupling and give the dominant contribution to the collective
+reaction coordinate.  Within the linearized approximation for the electronic/nuclear coupling,
+we can write a force tensor
+\begin{eqnarray}
+{\mathbf F} =
+\left(\begin{array}{cc}
+{\mathbf g}_{11}&{\mathbf g}_{12} \\
+{\mathbf g}_{21} &{\mathbf g}_{22}
+\end{array}\right)
+\end{eqnarray}
+where ${\mathbf F}\cdot \mathbf q$ is the electronic/nuclear coupling term in Eq.~\ref{ham1}.
+If we consider each unique element $\{ \mathbf g_{11}, \mathbf g_{12} , \mathbf g_{22}\}$ to be
+linearly independent, but non-orthogonal force vectors,  one can develop a  projection operator scheme to
+to parse the $N$-dimensional linear vector space spanned by the mass-weighted normal mode vectors into two subspaces:
+one spanned by three vectors describing the coupling between the electronic states
+and the other spanned by the remaining $N-3$ dimensional space spanned by motions that
+do not couple the electronic states.
+This  subspace  can be generated by defining a projection operator
+\begin{eqnarray}
+\mathbf{P}=\sum_{\alpha\beta}'\left(\mathbf{S^{-1}}\right)_{\alpha\beta}\mathbf{g_{\alpha}}\otimes\mathbf{g_{\beta}}
+\end{eqnarray}
+in which the summation is limited to linearly independent vectors.
+   Here $\mathbf{S}_{\alpha\beta}=\mathbf{g_{\alpha}}\cdot\mathbf{g_{\beta}}$,
+$\otimes$ is outer product,  and $\mathbf{I}$ is unitary operator.
+This $N\times N$ matrix projects out all normal modes that are directly coupled to the
+electronic degrees of freedom and
+ its complement $\mathbf{Q}=\mathbf{I}-\mathbf{P}$ projects out all modes not directly coupled.
+By diagonalizing the matrix
+\begin{eqnarray}
+\mathbf{K}=\mathbf{P}\cdot\mathbf\Omega\cdot \mathbf{P}+\mathbf{Q}\cdot\mathbf\Omega\cdot\mathbf{Q}
+\end{eqnarray}
+we obtain a  transformation, ${\mathbf M}$,  between the normal coordinates and a new set of orthogonal
+coordinates.  Both $\mathbf{P}\cdot\mathbf\Omega\cdot \mathbf{P}$ and $\mathbf{Q}\cdot\mathbf\Omega\cdot\mathbf{Q}$ are $N\times N$ matrices.
+However, for a two-state system, the former will have exactly $3$ non-trivial eigenvalues, $\{\alpha_{p}\}$, with corresponding
+eigenvectors, $\{ M_{p}\}$, whereas the latter will have exactly $N_{r} = N-3$ non-trivial eigenvalues, $\{\alpha_{q}\}$,  and corresponding
+eigenvectors, $\{M_q\}$.   This the full $N\times N$ transformation is formed by joining the non-trivial vectors from the
+two respective subspaces ${\mathbf M} = \{M_{p}, M_{q}\}$.
+The transformed electron-phonon coupling constants are given by projecting the  couplings   in the normal mode basis on to the new
+basis.
+\begin{eqnarray}
+\mathbf{g}_{ab}'=\mathbf{M}_{p}\cdot\mathbf{g}_{ab}.
+\end{eqnarray}
+By examining the types of molecular motions that compose the ${\mathbf M_{p}}$ subspace, we can
+gain a deeper understanding of the specific classes of internal motion that are directly involved with the
+electron transfer process.  In addition,  we can gain a computational advantage since presumably this
+ reduced set of modes give the dominant contribution to the electron-phonon coupling and  autocorrelation
+ function given as the kernel in Eq. ~\ref{gr-expression}.
+
+\subsection{Lanczos Method}
+It is crucial to notice that the vectors  given in Eq.~\ref{eq:locaiHam} are {\em not linearly independent}.
+ Consequently, special care
+must be taken to generate the reduced sub-space.  To do so, we use an iterative Lanczos approach
+taking the normalized vector ${\mathbf v}_{1} = {\mathbf g}_{22}$ as a starting point.
+
+As above, we initialize each step indexed by $k$,  by defining a projection operator
+\begin{eqnarray}
+{\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
+\end{eqnarray}
+and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
+%${\mathbf P}_{k}$ is the projection operator for the
+$k$-th mode.
+%We also construct
+%\begin{eqnarray}
+%\mathbf p = \sum_{k} \mathbf P_{k}
+%\end{eqnarray}
+%as  the total projection operator for all ${k} \le N$ modes.
+We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
+\begin{eqnarray}
+\mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
+\end{eqnarray}
+and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
+respectively.
+As above, $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
+The first set will have a single
+non-trivial eigenvalue and the second set
+will have $N-k$ non-trivial eigenvalues.  As above we collect the non-trivial eigenvectors associated with each
+to form the orthogonal transformation matrix
+\begin{eqnarray}
+{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
+\end{eqnarray}
+and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
+ At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
+$k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
+a diagonal submatrix in the lower-right.  For example, after $k=3$ iterations, one has
+a Hessian matrix of the form:
+\begin{eqnarray}
+{\mathbf\Omega}' =
+\begin{pmatrix}
+\alpha_{1}   & b_{1}    & 0                    &               &             &            & 0 \\
+b_{1}     & \alpha_{2}  & b_{2}                         \\
+0            &   b_{2}         & \alpha_{3}    &   c_{k+1}   & c_{k+2}  & \cdots & c_{N}     \\
+               &                     &           c_{k+1}           &     \alpha_{k+ 1} & &             & 0                 \\
+               &                     &           c_{k+2}           &                 & \alpha_{k+2}  \\
+               &                     &          \vdots           &                 &                    &  \ddots \\
+   0           &                     &           c_{N}           &     0   &&& \alpha_{N}\\
+\end{pmatrix}.
+\label{omega-prime}
+\end{eqnarray}
+We note that only the $k$-th mode is coupled the $N-k$ remaining modes.
+Since all of the transformations are orthogonal, diagonalizing $\mathbf\Omega'$ at any point
+returns the original Hessian matrix.
+
+To continue iterating, we  take the $k$-th row of $\mathbf\Omega'$ and zero the first $k$ elements
+$$
+{\mathbf e} = \{0,\cdots 0,c_{k+1},c_{k+2},\cdots ,c_{N}\}.
+$$
+This is the coupling between the upper tridiagonal block and the lower diagonal block.
+We thus obtain a new vector
+$$
+{\mathbf v}_{k+1} = {\mathbf e} \cdot {\mathbf M}
+$$
+which is then reintroduced into the iteration scheme.
+
+At any point along the way, we can terminate the iteration and obtain a reduced set of
+couplings.  Since the  Lanczos approach uses the power method for finding the largest eigenvector of a matrix,
+it converges first upon the vector with the largest electron/nuclear coupling--which
+ we refer to as the ``primary mode''.  Subsequent iterations produce reduced modes with
+ weaker electron/nuclear couplings and the entire  process can be terminated after a few iterations.
+After $k$-steps, the final electron-phonon couplings are then obtained by
+projecting the original set of couplings (in the normal mode basis) into the final vector space.
+
+For the first iteration, ${\mathbf v}_{1}$ is parallel to the bare electron-phonon coupling vector $g_{22}$
+and the associated frequency is ${\mathbf v}_{1}\cdot\Omega\cdot{\mathbf v}_{1}$.   The subsequent iterations introduce
+corrections to this via phonon-phonon coupling.  For example, for the $k=3$ iteration,
+we would determine the active vector space in terms of the upper-left 3$\times 3$ block of the matrix in
+Eq.~\ref{omega-prime}.
+\begin{eqnarray}
+{\mathbf \Omega}_{3}' =
+\begin{pmatrix}
+\alpha_{1}   & b_{1}    & 0      \\
+b_{1}     & \alpha_{2}  & b_{2}                         \\
+0            &   b_{2}         & \alpha_{3}
+\end{pmatrix}
+\end{eqnarray}
+Diagonalizing  ${\mathbf \Omega}_{3}'$ returns a set of frequencies and  associated eigenvectors
+which are then used to compute the electron-phonon couplings in this reduced active space.
+After $N-1$ iterations, $\mathbf\Omega'$ is a fully tridiagonal matrix and diagonalizing this returns the original
+normal mode basis.
+
+\section{Summary}
+
+Central to the work presented here consists of two parts. One is the use of a diabatization scheme for determining
+donor and acceptor states in a molecular unit.
+The other is a projection scheme which enables us to analyze the contribution of vibrations in reactions.
+Similar decomposition schemes have been presented by Burghardt
+ \cite{cederbaum2005short,gindensperger2006shortI,gindensperger2006shortII,cederbaum2005short}
+ and the approach used here builds upon the method given in Ref.~\cite{pereverzev2009energy}.
+
+In Chapter \ref{chap:chapt2} we benchmark the approach
+by computing the  triplet energy transfer rates for a series of donor-bridge-acceptor molecules
+originally studied by Closs\cite{miller1984intramolecular}.  The triplet energy transfer rates computed using our approach
+compare well against both the experimental rates and with
+more recent theoretical rates presented by Subotnik {\em et al.}
+\cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
+Then we use the projection operator scheme
+to parses out specific internal nuclear motions that accompany
+the electronic transition.
+ By analyzing the electron-phonon couplings, we can
+discern a reduced set of motions that are responsible for coupling between the donor and
+acceptor states.
+
+In Chapter \ref{chap:chapt3} we analyze the irreducible
+representations  of the dominant contributions of these reduced modes and find that for the cases considered here, they belong to totally symmetric irreducible representations  of
+the donor and acceptor moieties. Upon investigating the molecular geometry changes following  the transition,   we propose that the electronic transition process can be
+broken into two steps, in the agreement of Born-Oppenheimer approximation:  a fast excitation transfer occurs, facilitated by the ``primary Lanczos mode'' (PLM),
+followed by slow nuclear relaxation on the final electronic diabatic surface.

### 2016-03-29 Chapters/chap2/manuscript.tex
Correct bib for uppercase

@@
 
-\chapter{Chapter 2}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}
+\chapter{Chapter 2}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}\label{chap:chapt2}
 \section{Introduction}
@@
 
-Energy and electronic transport plays a central role in a
-wide range of  chemical  and biological systems.
-It is the fundamental mechanism for transporting the  energy  of a
-absorbed photon to a reaction center in light harvesting systems
-and for initiating a wide range of photo-induced  chemical processes,
-including vision, DNA mutation, and pigmentation.
-The seminal model for calculating electron transfer rates was developed by
-Marcus in the 1950's\cite{marcus1956theory,marcus1965theory,marcus1993electron}.
-\begin{equation}
-k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta\epsilon)^{2}/4\text{\ensuremath{\lambda}}k_{B}T}.\label{eq:marcus}
-\end{equation}
-where $\lambda$ is  energy required to reorganize the environment
-following the transfer of an electron from donor to acceptor.
-and $\Delta \epsilon$ is the driving force for the reaction.
-
-\begin{figure}[h]
-\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure1}
-\caption{Sketch of Marcus parabolas for a model energy or charge transfer system.
-Labeled are the key parameters used to compute the Marcus rate constant (Eq. \ref{eq:marcus}).
-Energies are given in eV and the collective nuclear displacement  is dimensionless.
-}
-\label{marcus}
-\end{figure}
-
-If we assume that the nuclear motions about the equilibrium configurations of the
-donor and acceptor species is harmonic,  the chemical reactions resulting from
-energy or charge transfer events can be understood in terms of intersecting
-diabatic potentials as sketched in Fig.~\ref{marcus}.    The upper and lower
-curves are the adiabatic potential energy surfaces describing the nuclear dynamics
-resulting from an energy or charge transfer event, taking the geometry of the donor
-state as the origin.
-%For reactions carried out in open systems,  the Marcus parabolas represent
-%free energy surfaces with driving force $\Delta G$.
-As the transfer occurs by crossing an energy barrier,
-the transfer rate can be expected to be in the Arrhenius form
-\begin{eqnarray}
-k\propto e^{-E_{A}/k_{B}T},
-\end{eqnarray}
-with $E_{A}$ as the activation energy.
- Using $E_{A}={(\lambda+\Delta \epsilon)^{2}}/{4\lambda}$
- we can relate the activation energy to both the reorganization energy and driving force, $-\Delta \epsilon$.
-One of the most profound predictions of the theory is that  as the driving force increases,
-the transfer rate reaches a maximum and further increases in the driving force
-lead to lower reaction rates, termed the inverted regime.
-
-We focus here on the rates of triplet exchange between a naphthalene donor and a benzaldehyde acceptor linked by a variety of bridging units.
+% Energy and electronic transport plays a central role in a
+% wide range of  chemical  and biological systems.
+% It is the fundamental mechanism for transporting the  energy  of a
+% absorbed photon to a reaction center in light harvesting systems
+% and for initiating a wide range of photo-induced  chemical processes,
+% including vision, DNA mutation, and pigmentation.
+% The seminal model for calculating electron transfer rates was developed by
+% Marcus in the 1950's\cite{marcus1956theory,marcus1965theory,marcus1993electron}.
+% \begin{equation}
+% k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta\epsilon)^{2}/4\text{\ensuremath{\lambda}}k_{B}T}.\label{eq:marcus}
+% \end{equation}
+% where $\lambda$ is  energy required to reorganize the environment
+% following the transfer of an electron from donor to acceptor.
+% and $\Delta \epsilon$ is the driving force for the reaction.
+
+% \begin{figure}[h]
+% \includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure1}
+% \caption{Sketch of Marcus parabolas for a model energy or charge transfer system.
+% Labeled are the key parameters used to compute the Marcus rate constant (Eq. \ref{eq:marcus}).
+% Energies are given in eV and the collective nuclear displacement  is dimensionless.
+% }
+% \label{marcus}
+% \end{figure}
+
+% If we assume that the nuclear motions about the equilibrium configurations of the
+% donor and acceptor species is harmonic,  the chemical reactions resulting from
+% energy or charge transfer events can be understood in terms of intersecting
+% diabatic potentials as sketched in Fig.~\ref{marcus}.    The upper and lower
+% curves are the adiabatic potential energy surfaces describing the nuclear dynamics
+% resulting from an energy or charge transfer event, taking the geometry of the donor
+% state as the origin.
+% %For reactions carried out in open systems,  the Marcus parabolas represent
+% %free energy surfaces with driving force $\Delta G$.
+% As the transfer occurs by crossing an energy barrier,
+% the transfer rate can be expected to be in the Arrhenius form
+% \begin{eqnarray}
+% k\propto e^{-E_{A}/k_{B}T},
+% \end{eqnarray}
+% with $E_{A}$ as the activation energy.
+%  Using $E_{A}={(\lambda+\Delta \epsilon)^{2}}/{4\lambda}$
+%  we can relate the activation energy to both the reorganization energy and driving force, $-\Delta \epsilon$.
+% One of the most profound predictions of the theory is that  as the driving force increases,
+% the transfer rate reaches a maximum and further increases in the driving force
+% lead to lower reaction rates, termed the inverted regime.
+
+In this chapter we focus here on the rates of triplet exchange between a naphthalene donor and a benzaldehyde acceptor linked by a variety of bridging units.
 \begin{center}
@@
 
-A number of years ago,  we developed a time-convolutionless  master equation approach for computing
-state-to-state rates in which the coupling between  states depends upon the
-nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
-mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
-well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
-vibrational normal mode frequencies, and the electronic energies and energy derivatives
-at a reference configuration.  The approach has been used by our group to compute state-to-state
-transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
-\cite{tamura2008phonon,tamura2007exciton,bittner2014noise,singh2009fluorescence}.
-This paper represents the first time we have used this approach within the context of a fully {\em ab initio} quantum
-chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
-using state-of-the-art quantum chemical methods
-and results compared to both theoretical and experimental
-rates.
-
-Central to the work presented here is the use of a diabatization scheme for determining
-donor and acceptor states in a molecular unit.  We benchmark the approach
-by computing the  triplet energy transfer rates for a series of donor-bridge-acceptor molecules
-originally studied by Closs\cite{miller1984intramolecular}.  The triplet energy transfer rates computed using our approach
-compare well against both the experimental rates and with
-more recent theoretical rates presented by Subotnik {\em et al.}
-\cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
-An important component of our analysis is the use of a projection operator scheme
-that parses out specific internal nuclear motions that accompany
-the electronic transition.
-Similar decomposition schemes have been presented by Burghardt
- \cite{cederbaum2005short,gindensperger2006shortI,gindensperger2006shortII,cederbaum2005short}
- and the approach used here builds upon the method given in Ref.~\cite{pereverzev2009energy}.
- By analyzing the electron-phonon couplings, we can
-discern a reduced set of motions that are responsible for coupling between the donor and
-acceptor states.
-
-\section{Theoretical Approach}
-
-\subsection{Model Hamiltonian}
-We consider a generic model for $n$ electronic states coupled linearly
-to a phonon bath.  Taking the electronic ground state of the system as a reference
-and assuming that the electronic states are coupled linearly to a common set of
- modes, we arrive a generic form for the Hamiltonian:
- \begin{eqnarray}
-H=\left(\begin{array}{cc}
-\epsilon_{1} & 0\\
-0 & \epsilon_{2}
-\end{array}\right)+\left(\begin{array}{cc}
-{\mathbf g}_{11}&{\mathbf g}_{12} \\
-{\mathbf g}_{21} &{\mathbf g}_{22}
-\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
-\nonumber \\
-\label{ham1}
-\end{eqnarray}
-Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
-reference geometry--typically that of the donor or acceptor state.   The second term represents the
-linearized coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
-normal coordinates $\mathbf q$.   The diagonal terms
-give the adiabatic displacement forces between the reference geometry and the two states.  If we choose one of the
-states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish.
-The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
-In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.
-
-We now separate Eq.~\ref{ham1} into diagonal and
-off-diagonal terms
-\begin{eqnarray}
-\hat  H = \hat H_{o} + \hat V
-\end{eqnarray}
-and perform a polaron transform
-using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
-\begin{eqnarray}
-U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
-n|(a^{\dagger}_i-a_i)}
- \nonumber \\
-&=&
-\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
-\label{unitary}
-\end{eqnarray}
-under which the transformed Hamiltonian is written in terms of the
-diagonal elements
-\begin{eqnarray} \tilde H_0=U^{-1}H_0U
-=\sum_n\tilde\epsilon_n |n\rangle \langle
-n|+\sum_i\omega_ia^{\dagger}_ia_i,
- \end{eqnarray}
-with  the renormalized electronic energies,
-\begin{eqnarray}
-\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
-\end{eqnarray}
-and off-diagonal terms,
-\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
-a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
-\label{opm}
-\end{eqnarray}
-In the transformed (or dressed) picture the electronic transition from state
-$|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
-normal phonon modes.  Transforming to the interaction representation
-and performing a trace over the phonons gives the spectral density in
-terms of the autocorrelation of the electron-phonon coupling
-operators.
-\begin{eqnarray}
-S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{spec-dens}
-\end{eqnarray}
-Here, $\hat V_{nm}(t)$ is the electron-phonon coupling term in the Heisenberg representation and
-$\langle \cdots \rangle$ denotes a thermal average over the
-vibrational degrees of freedom.
-The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
-Ref.~\cite{pereverzev2006time}.
-
-\subsection{Non-Markovian Master Equation and Golden-Rule rates}
-
-In Ref.~\cite{pereverzev2006time}, Pereverzev and Bittner derived
-a non-Markovian, time-convolutionless form of the Pauli master
-equation (TCLME)  for general system described by Eq.~\ref{ham1}.
-\begin{eqnarray}
-\frac{dP_{n}}{dt} = \sum_{m} W_{nm}(t)P_{m}(t) - \left(\sum_{m} W_{mn}(t)\right)P_{n}(t)
-\end{eqnarray}
-where the time-dependent rates are given by
-\begin{eqnarray}
-W_{nm}(\tau)=2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
-\label{rate-expression}
-\end{eqnarray}
-In the limit that $\tau\to\infty$, Eq.~\ref{rate-expression} gives the Fermi's Golden Rule expression for the
-transition rate,
-\begin{eqnarray}
-k_{nm}=2{\rm Re}\int_{0}^{\infty}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
-\label{gr-expression}
-\end{eqnarray}
-
-At this point it is useful to connect the various terms in the phonon-dressed Hamiltonian
-with specific physical parameters.
-First, the reorganization energy is given by
-%The terms involving $$
-%are related to the reorganized energy difference between the two states.
-%$$
-%\lambda_{nm} =\sum_{j}((g_{nnj}-g_{mmj})/\omega_j)^{2} = \sum_{j}\hbar \omega_{j}S_{j}
-%$$
-\[
-\lambda_{nm}=\sum_{j}\frac{\left(g_{nnj}-g_{mmj}\right)^{2}}{\omega_{j}} = \sum_{j}\hbar \omega_{j}S_{j}
-\]
-where  the $\{S_{j}\}$  are  the Huang-Rhys factors for each phonon mode.
-These are related to the Franck-Condon factor
-describing the overlap between the $v_j=1$ vibronic state in one electronic state
-with the $v_j=0$ vibronic state in the other.
-Likewise, the energy difference between the renormalized energy gaps is related to the
-driving force of the state-to-state transition,
-\begin{eqnarray}
-\Delta E_{nm} = \tilde \epsilon_n-\tilde \epsilon_m.
-\end{eqnarray}
-
-The difficulty in using this approach is that
-it requires both diagonal (${\mathbf g}_{nn}$) and off-diagonal  (${\mathbf g}_{nm}$) derivative couplings between
-adiabatic states.    In the following section, we discuss how we have used the Edmiston-Ruedenberg localization scheme
-to estimate the couplings\cite{edmiston1963localized}.   We also
-present how one can construct a reduced set of harmonic modes that
-fully capture the electron/nuclear coupling.
-\subsection{Parameterization From Quantum Chemistry}
-
- In order to obtain the final form of our target Hamiltonian, we assume the diabatic  potentials
-are a good approximation to the actual adiabatic potentials.
-
-When the adiabatic (and diabatic) energy minima
-are far enough away from the crossing points and the mixing angles between the diabatic  and adiabatic
-states is small, we can
-use the gradients of the adiabatic potentials to approximate the diabatic potentials.
-Thus, if we perform calculations at the
-optimized geometry of the final acceptor state  ({\em i.~e.} about $Q_{2}$  in Fig.~\ref{marcus}),
-we can write the Hamiltonian as
-\begin{eqnarray}
-H_{dia,e}=\left(\begin{array}{cc}
-\epsilon_{1} & V_{12}\\
-V_{21} & \epsilon_{2}
-\end{array}\right)+\left(\begin{array}{cc}
-0 & 0\\
-0 & 1
-\end{array}\right) {\mathbf g}_{22}\cdot{\mathbf q}+H_{osc},
-\end{eqnarray}
-where $H_{osc}$ is the harmonic oscillator Hamiltonian for the vibrational normal modes.
-The linear assumption amounts  to performing a series expansion of the
-full, multi-dimensional coupling term and keeping only the lowest order terms.
-Systematic improvement can be made by including higher-order (e.g.  quadratic) off-diagonal couplings.
-However, this would involve a substantial increase in the complexity of the theory.
-The linear assumption is reasonable so long as  the mixing angle is small,
-as verified by the benchmark calculations presented below.
-
-We obtain the diabatic couplings $V_{12}$
-and the mixing angle $\theta$  via ER localization and transform the electronic Hamiltonian
-from the adiabatic basis to the diabatic basis {\em viz.}
-\begin{equation}
-H_{dia}=\left(\begin{array}{cc}
-\cos\theta & -\sin\theta\\
-\sin\theta & \cos\theta
-\end{array}\right)\left(\begin{array}{cc}
-\epsilon_{1}  & 0 \\
-0  & \epsilon_{2}
-\end{array}\right)\left(\begin{array}{cc}
-\cos\theta & \sin\theta\\
--\sin\theta & \cos\theta
-\end{array}\right).\label{eq:boys}
-\end{equation}
-The diabatic coupling is then given by
-\begin{eqnarray}
-V_{ab}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
-\end{eqnarray}
-
-We then diagonalize the electronic part and transform the electron/nuclear coupling
-back into the adiabatic basis.  In doing so,  we obtain the Hamiltonian in the
-form given in Eq. \ref{ham1}
-\begin{eqnarray}
-H&=&U^{T}H_{dia}U\nonumber  \\
-&=&\left(\begin{array}{cc}
-E_{1}  & 0 \\
-0 & E_{2}
-\end{array}\right)+\left(\begin{array}{cc}
-\sin^{2}\theta & \frac{1}{2}\sin2\theta\\
-\frac{1}{2}\sin2\theta & \cos^{2}\theta
-\end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
-&+& H_{osc}.\label{eq:locaiHam}
-\end{eqnarray}
-
+The chapter is arranged in this way.
+First we examine the validity of the assumptions in our method.
+Then we apply the method to get theoretical transfer rate constants, and compare them to experiments.
+Finally, we use the projection scheme to find the primary modes in the reactions.
+The modes turn out to show certain symmetry.
+
+% A number of years ago,  we developed a time-convolutionless  master equation approach for computing
+% state-to-state rates in which the coupling between  states depends upon the
+% nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
+% mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
+% well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
+% vibrational normal mode frequencies, and the electronic energies and energy derivatives
+% at a reference configuration.  The approach has been used by our group to compute state-to-state
+% transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
+% \cite{tamura2008phonon,tamura2007exciton,bittner2014noise,singh2009fluorescence}.
+% This paper represents the first time we have used this approach within the context of a fully {\em ab initio} quantum
+% chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
+% using state-of-the-art quantum chemical methods
+% and results compared to both theoretical and experimental
+% rates.
+
+% Central to the work presented here is the use of a diabatization scheme for determining
+% donor and acceptor states in a molecular unit.  We benchmark the approach
+% by computing the  triplet energy transfer rates for a series of donor-bridge-acceptor molecules
+% originally studied by Closs\cite{miller1984intramolecular}.  The triplet energy transfer rates computed using our approach
+% compare well against both the experimental rates and with
+% more recent theoretical rates presented by Subotnik {\em et al.}
+% \cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
+% An important component of our analysis is the use of a projection operator scheme
+% that parses out specific internal nuclear motions that accompany
+% the electronic transition.
+% Similar decomposition schemes have been presented by Burghardt
+%  \cite{cederbaum2005short,gindensperger2006shortI,gindensperger2006shortII,cederbaum2005short}
+%  and the approach used here builds upon the method given in Ref.~\cite{pereverzev2009energy}.
+%  By analyzing the electron-phonon couplings, we can
+% discern a reduced set of motions that are responsible for coupling between the donor and
+% acceptor states.
+
+% \section{Theoretical Approach}
+
+% \subsection{Model Hamiltonian}
+% We consider a generic model for $n$ electronic states coupled linearly
+% to a phonon bath.  Taking the electronic ground state of the system as a reference
+% and assuming that the electronic states are coupled linearly to a common set of
+%  modes, we arrive a generic form for the Hamiltonian:
+%  \begin{eqnarray}
+% H=\left(\begin{array}{cc}
+% \epsilon_{1} & 0\\
+% 0 & \epsilon_{2}
+% \end{array}\right)+\left(\begin{array}{cc}
+% {\mathbf g}_{11}&{\mathbf g}_{12} \\
+% {\mathbf g}_{21} &{\mathbf g}_{22}
+% \end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
+% \nonumber \\
+% \label{ham1}
+% \end{eqnarray}
+% Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
+% reference geometry--typically that of the donor or acceptor state.   The second term represents the
+% linearized coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
+% normal coordinates $\mathbf q$.   The diagonal terms
+% give the adiabatic displacement forces between the reference geometry and the two states.  If we choose one of the
+% states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish.
+% The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
+% In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.
+
+% We now separate Eq.~\ref{ham1} into diagonal and
+% off-diagonal terms
+% \begin{eqnarray}
+% \hat  H = \hat H_{o} + \hat V
+% \end{eqnarray}
+% and perform a polaron transform
+% using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
+% \begin{eqnarray}
+% U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
+% n|(a^{\dagger}_i-a_i)}
+%  \nonumber \\
+% &=&
+% \sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
+% \label{unitary}
+% \end{eqnarray}
+% under which the transformed Hamiltonian is written in terms of the
+% diagonal elements
+% \begin{eqnarray} \tilde H_0=U^{-1}H_0U
+% =\sum_n\tilde\epsilon_n |n\rangle \langle
+% n|+\sum_i\omega_ia^{\dagger}_ia_i,
+%  \end{eqnarray}
+% with  the renormalized electronic energies,
+% \begin{eqnarray}
+% \tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
+% \end{eqnarray}
+% and off-diagonal terms,
+% \begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
+% a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
+% \label{opm}
+% \end{eqnarray}
+% In the transformed (or dressed) picture the electronic transition from state
+% $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
+% normal phonon modes.  Transforming to the interaction representation
+% and performing a trace over the phonons gives the spectral density in
+% terms of the autocorrelation of the electron-phonon coupling
+% operators.
+% \begin{eqnarray}
+% S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{spec-dens}
+% \end{eqnarray}
+% Here, $\hat V_{nm}(t)$ is the electron-phonon coupling term in the Heisenberg representation and
+% $\langle \cdots \rangle$ denotes a thermal average over the
+% vibrational degrees of freedom.
+% The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
+% Ref.~\cite{pereverzev2006time}.
+
+% \subsection{Non-Markovian Master Equation and Golden-Rule rates}
+
+% In Ref.~\cite{pereverzev2006time}, Pereverzev and Bittner derived
+% a non-Markovian, time-convolutionless form of the Pauli master
+% equation (TCLME)  for general system described by Eq.~\ref{ham1}.
+% \begin{eqnarray}
+% \frac{dP_{n}}{dt} = \sum_{m} W_{nm}(t)P_{m}(t) - \left(\sum_{m} W_{mn}(t)\right)P_{n}(t)
+% \end{eqnarray}
+% where the time-dependent rates are given by
+% \begin{eqnarray}
+% W_{nm}(\tau)=2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
+% \label{rate-expression}
+% \end{eqnarray}
+% In the limit that $\tau\to\infty$, Eq.~\ref{rate-expression} gives the Fermi's Golden Rule expression for the
+% transition rate,
+% \begin{eqnarray}
+% k_{nm}=2{\rm Re}\int_{0}^{\infty}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
+% \label{gr-expression}
+% \end{eqnarray}
+
+% At this point it is useful to connect the various terms in the phonon-dressed Hamiltonian
+% with specific physical parameters.
+% First, the reorganization energy is given by
+% %The terms involving $$
+% %are related to the reorganized energy difference between the two states.
+% %$$
+% %\lambda_{nm} =\sum_{j}((g_{nnj}-g_{mmj})/\omega_j)^{2} = \sum_{j}\hbar \omega_{j}S_{j}
+% %$$
+% \[
+% \lambda_{nm}=\sum_{j}\frac{\left(g_{nnj}-g_{mmj}\right)^{2}}{\omega_{j}} = \sum_{j}\hbar \omega_{j}S_{j}
+% \]
+% where  the $\{S_{j}\}$  are  the Huang-Rhys factors for each phonon mode.
+% These are related to the Franck-Condon factor
+% describing the overlap between the $v_j=1$ vibronic state in one electronic state
+% with the $v_j=0$ vibronic state in the other.
+% Likewise, the energy difference between the renormalized energy gaps is related to the
+% driving force of the state-to-state transition,
+% \begin{eqnarray}
+% \Delta E_{nm} = \tilde \epsilon_n-\tilde \epsilon_m.
+% \end{eqnarray}
+
+% The difficulty in using this approach is that
+% it requires both diagonal (${\mathbf g}_{nn}$) and off-diagonal  (${\mathbf g}_{nm}$) derivative couplings between
+% adiabatic states.    In the following section, we discuss how we have used the Edmiston-Ruedenberg localization scheme
+% to estimate the couplings\cite{edmiston1963localized}.   We also
+% present how one can construct a reduced set of harmonic modes that
+% fully capture the electron/nuclear coupling.
+% \subsection{Parameterization From Quantum Chemistry}
+
+%  In order to obtain the final form of our target Hamiltonian, we assume the diabatic  potentials
+% are a good approximation to the actual adiabatic potentials.
+
+% When the adiabatic (and diabatic) energy minima
+% are far enough away from the crossing points and the mixing angles between the diabatic  and adiabatic
+% states is small, we can
+% use the gradients of the adiabatic potentials to approximate the diabatic potentials.
+% Thus, if we perform calculations at the
+% optimized geometry of the final acceptor state  ({\em i.~e.} about $Q_{2}$  in Fig.~\ref{marcus}),
+% we can write the Hamiltonian as
+% \begin{eqnarray}
+% H_{dia,e}=\left(\begin{array}{cc}
+% \epsilon_{1} & V_{12}\\
+% V_{21} & \epsilon_{2}
+% \end{array}\right)+\left(\begin{array}{cc}
+% 0 & 0\\
+% 0 & 1
+% \end{array}\right) {\mathbf g}_{22}\cdot{\mathbf q}+H_{osc},
+% \end{eqnarray}
+% where $H_{osc}$ is the harmonic oscillator Hamiltonian for the vibrational normal modes.
+% The linear assumption amounts  to performing a series expansion of the
+% full, multi-dimensional coupling term and keeping only the lowest order terms.
+% Systematic improvement can be made by including higher-order (e.g.  quadratic) off-diagonal couplings.
+% However, this would involve a substantial increase in the complexity of the theory.
+% The linear assumption is reasonable so long as  the mixing angle is small,
+% as verified by the benchmark calculations presented below.
+
+% We obtain the diabatic couplings $V_{12}$
+% and the mixing angle $\theta$  via ER localization and transform the electronic Hamiltonian
+% from the adiabatic basis to the diabatic basis {\em viz.}
+% \begin{equation}
+% H_{dia}=\left(\begin{array}{cc}
+% \cos\theta & -\sin\theta\\
+% \sin\theta & \cos\theta
+% \end{array}\right)\left(\begin{array}{cc}
+% \epsilon_{1}  & 0 \\
+% 0  & \epsilon_{2}
+% \end{array}\right)\left(\begin{array}{cc}
+% \cos\theta & \sin\theta\\
+% -\sin\theta & \cos\theta
+% \end{array}\right).\label{eq:boys}
+% \end{equation}
+% The diabatic coupling is then given by
+% \begin{eqnarray}
+% V_{ab}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
+% \end{eqnarray}
+
+% We then diagonalize the electronic part and transform the electron/nuclear coupling
+% back into the adiabatic basis.  In doing so,  we obtain the Hamiltonian in the
+% form given in Eq. \ref{ham1}
+% \begin{eqnarray}
+% H&=&U^{T}H_{dia}U\nonumber  \\
+% &=&\left(\begin{array}{cc}
+% E_{1}  & 0 \\
+% 0 & E_{2}
+% \end{array}\right)+\left(\begin{array}{cc}
+% \sin^{2}\theta & \frac{1}{2}\sin2\theta\\
+% \frac{1}{2}\sin2\theta & \cos^{2}\theta
+% \end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
+% &+& H_{osc}.\label{eq:locaiHam}
+% \end{eqnarray}
+
+\section{Assumption Validity}
+
+Our method employs two assumptions, parabolic assumption and Condon approximation.
+The former assumes that relevant potential energy surfaces are parabolic.
+The latter means diabatic coupling  is independent of nuclear coordinates in the region where reaction occurs.
 In Fig.~\ref{parabs} we show the adiabatic potential curves and off-diagonal couplings along an interpolation coordinate
@@
 
-\begin{figure}[t]
+\begin{figure}[!ht]
 \subfloat[c-1,4ee]{\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure2a}}
@@
 angles for constructing diabatic states. For all calculations shown here we
-used the qChem 4.0 code and employed the 6-31G(d){*}{*} basis set
+used the Q-Chem 4.0 \cite{QCHEM4} code and employed the 6-31G(d){*}{*} basis set
 in order to compare our results  with  Ref. \cite{subotnik2010predicting}.
@@
 
-\section{Determining the Optimal Electron-Phonon Coupling Components}
-
-While the Marcus expression is elegant in its simplicity in requiring three parameters that
-can be obtained experimentally, it masks a wealth of detail that underlie the quantum transition.
-Central to the theory is that there exists a collective nuclear displacement coordinate
-that connects the initial geometry of the donor to the final geometry of the acceptor.
-
-Generally speaking, this collective coordinate involves all nuclear degrees of freedom.
-However, the form of the electronic Hamiltonian in Eq.~\ref{ham1} suggests that
-there exists a subset of motions that are specific modes  that capture the majority of the
-electronic/nuclear coupling and give the dominant contribution to the collective
-reaction coordinate.  Within the linearized approximation for the electronic/nuclear coupling,
-we can write a force tensor
-\begin{eqnarray}
-{\mathbf F} =
-\left(\begin{array}{cc}
-{\mathbf g}_{11}&{\mathbf g}_{12} \\
-{\mathbf g}_{21} &{\mathbf g}_{22}
-\end{array}\right)
-\end{eqnarray}
-where ${\mathbf F}\cdot \mathbf q$ is the electronic/nuclear coupling term in Eq.~\ref{ham1}.
-If we consider each unique element $\{ \mathbf g_{11}, \mathbf g_{12} , \mathbf g_{22}\}$ to be
-linearly independent, but non-orthogonal force vectors,  one can develop a  projection operator scheme to
-to parse the $N$-dimensional linear vector space spanned by the mass-weighted normal mode vectors into two subspaces:
-one spanned by three vectors describing the coupling between the electronic states
-and the other spanned by the remaining $N-3$ dimensional space spanned by motions that
-do not couple the electronic states.
-This  subspace  can be generated by defining a projection operator
-\begin{eqnarray}
-\mathbf{P}=\sum_{\alpha\beta}'\left(\mathbf{S^{-1}}\right)_{\alpha\beta}\mathbf{g_{\alpha}}\otimes\mathbf{g_{\beta}}
-\end{eqnarray}
-in which the summation is limited to linearly independent vectors.
-   Here $\mathbf{S}_{\alpha\beta}=\mathbf{g_{\alpha}}\cdot\mathbf{g_{\beta}}$,
-$\otimes$ is outer product,  and $\mathbf{I}$ is unitary operator.
-This $N\times N$ matrix projects out all normal modes that are directly coupled to the
-electronic degrees of freedom and
- its complement $\mathbf{Q}=\mathbf{I}-\mathbf{P}$ projects out all modes not directly coupled.
-By diagonalizing the matrix
-\begin{eqnarray}
-\mathbf{K}=\mathbf{P}\cdot\mathbf\Omega\cdot \mathbf{P}+\mathbf{Q}\cdot\mathbf\Omega\cdot\mathbf{Q}
-\end{eqnarray}
-we obtain a  transformation, ${\mathbf M}$,  between the normal coordinates and a new set of orthogonal
-coordinates.  Both $\mathbf{P}\cdot\mathbf\Omega\cdot \mathbf{P}$ and $\mathbf{Q}\cdot\mathbf\Omega\cdot\mathbf{Q}$ are $N\times N$ matrices.
-However, for a two-state system, the former will have exactly $3$ non-trivial eigenvalues, $\{\alpha_{p}\}$, with corresponding
-eigenvectors, $\{ M_{p}\}$, whereas the latter will have exactly $N_{r} = N-3$ non-trivial eigenvalues, $\{\alpha_{q}\}$,  and corresponding
-eigenvectors, $\{M_q\}$.   This the full $N\times N$ transformation is formed by joining the non-trivial vectors from the
-two respective subspaces ${\mathbf M} = \{M_{p}, M_{q}\}$.
-The transformed electron-phonon coupling constants are given by projecting the  couplings   in the normal mode basis on to the new
-basis.
-\begin{eqnarray}
-\mathbf{g}_{ab}'=\mathbf{M}_{p}\cdot\mathbf{g}_{ab}.
-\end{eqnarray}
-By examining the types of molecular motions that compose the ${\mathbf M_{p}}$ subspace, we can
-gain a deeper understanding of the specific classes of internal motion that are directly involved with the
-electron transfer process.  In addition,  we can gain a computational advantage since presumably this
- reduced set of modes give the dominant contribution to the electron-phonon coupling and  autocorrelation
- function given as the kernel in Eq. ~\ref{gr-expression}.
-
-\subsection{Lanczos Method}
-It is crucial to notice that the vectors  given in Eq.~\ref{eq:locaiHam} are {\em not linearly independent}.
- Consequently, special care
-must be taken to generate the reduced sub-space.  To do so, we use an iterative Lanczos approach
-taking the normalized vector ${\mathbf v}_{1} = {\mathbf g}_{22}$ as a starting point.
-
-As above, we initialize each step indexed by $k$,  by defining a projection operator
-\begin{eqnarray}
-{\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
-\end{eqnarray}
-and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
-%${\mathbf P}_{k}$ is the projection operator for the
-$k$-th mode.
-%We also construct
-%\begin{eqnarray}
-%\mathbf p = \sum_{k} \mathbf P_{k}
-%\end{eqnarray}
-%as  the total projection operator for all ${k} \le N$ modes.
-We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
-\begin{eqnarray}
-\mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
-\end{eqnarray}
-and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
-respectively.
-As above, $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
-The first set will have a single
-non-trivial eigenvalue and the second set
-will have $N-k$ non-trivial eigenvalues.  As above we collect the non-trivial eigenvectors associated with each
-to form the orthogonal transformation matrix
-\begin{eqnarray}
-{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
-\end{eqnarray}
-and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
- At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
-$k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
-a diagonal submatrix in the lower-right.  For example, after $k=3$ iterations, one has
-a Hessian matrix of the form:
-\begin{eqnarray}
-{\mathbf\Omega}' =
-\begin{pmatrix}
-\alpha_{1}   & b_{1}    & 0                    &               &             &            & 0 \\
-b_{1}     & \alpha_{2}  & b_{2}                         \\
-0            &   b_{2}         & \alpha_{3}    &   c_{k+1}   & c_{k+2}  & \cdots & c_{N}     \\
-               &                     &           c_{k+1}           &     \alpha_{k+ 1} & &             & 0                 \\
-               &                     &           c_{k+2}           &                 & \alpha_{k+2}  \\
-               &                     &          \vdots           &                 &                    &  \ddots \\
-   0           &                     &           c_{N}           &     0   &&& \alpha_{N}\\
-\end{pmatrix}.
-\label{omega-prime}
-\end{eqnarray}
-We note that only the $k$-th mode is coupled the $N-k$ remaining modes.
-Since all of the transformations are orthogonal, diagonalizing $\mathbf\Omega'$ at any point
-returns the original Hessian matrix.
-
-To continue iterating, we  take the $k$-th row of $\mathbf\Omega'$ and zero the first $k$ elements
-$$
-{\mathbf e} = \{0,\cdots 0,c_{k+1},c_{k+2},\cdots ,c_{N}\}.
-$$
-This is the coupling between the upper tridiagonal block and the lower diagonal block.
-We thus obtain a new vector
-$$
-{\mathbf v}_{k+1} = {\mathbf e} \cdot {\mathbf M}
-$$
-which is then reintroduced into the iteration scheme.
-
-At any point along the way, we can terminate the iteration and obtain a reduced set of
-couplings.  Since the  Lanczos approach uses the power method for finding the largest eigenvector of a matrix,
-it converges first upon the vector with the largest electron/nuclear coupling--which
- we refer to as the ``primary mode''.  Subsequent iterations produce reduced modes with
- weaker electron/nuclear couplings and the entire  process can be terminated after a few iterations.
-After $k$-steps, the final electron-phonon couplings are then obtained by
-projecting the original set of couplings (in the normal mode basis) into the final vector space.
-
-For the first iteration, ${\mathbf v}_{1}$ is parallel to the bare electron-phonon coupling vector $g_{22}$
-and the associated frequency is ${\mathbf v}_{1}\cdot\Omega\cdot{\mathbf v}_{1}$.   The subsequent iterations introduce
-corrections to this via phonon-phonon coupling.  For example, for the $k=3$ iteration,
-we would determine the active vector space in terms of the upper-left 3$\times 3$ block of the matrix in
-Eq.~\ref{omega-prime}.
-\begin{eqnarray}
-{\mathbf \Omega}_{3}' =
-\begin{pmatrix}
-\alpha_{1}   & b_{1}    & 0      \\
-b_{1}     & \alpha_{2}  & b_{2}                         \\
-0            &   b_{2}         & \alpha_{3}
-\end{pmatrix}
-\end{eqnarray}
-Diagonalizing  ${\mathbf \Omega}_{3}'$ returns a set of frequencies and  associated eigenvectors
-which are then used to compute the electron-phonon couplings in this reduced active space.
-After $N-1$ iterations, $\mathbf\Omega'$ is a fully tridiagonal matrix and diagonalizing this returns the original
-normal mode basis.
-
-%{\bf XUNMO---how are frequencies and couplings determined at this point??---  }
+% \section{Determining the Optimal Electron-Phonon Coupling Components}
+
+% While the Marcus expression is elegant in its simplicity in requiring three parameters that
+% can be obtained experimentally, it masks a wealth of detail that underlie the quantum transition.
+% Central to the theory is that there exists a collective nuclear displacement coordinate
+% that connects the initial geometry of the donor to the final geometry of the acceptor.
+
+% Generally speaking, this collective coordinate involves all nuclear degrees of freedom.
+% However, the form of the electronic Hamiltonian in Eq.~\ref{ham1} suggests that
+% there exists a subset of motions that are specific modes  that capture the majority of the
+% electronic/nuclear coupling and give the dominant contribution to the collective
+% reaction coordinate.  Within the linearized approximation for the electronic/nuclear coupling,
+% we can write a force tensor
+% \begin{eqnarray}
+% {\mathbf F} =
+% \left(\begin{array}{cc}
+% {\mathbf g}_{11}&{\mathbf g}_{12} \\
+% {\mathbf g}_{21} &{\mathbf g}_{22}
+% \end{array}\right)
+% \end{eqnarray}
+% where ${\mathbf F}\cdot \mathbf q$ is the electronic/nuclear coupling term in Eq.~\ref{ham1}.
+% If we consider each unique element $\{ \mathbf g_{11}, \mathbf g_{12} , \mathbf g_{22}\}$ to be
+% linearly independent, but non-orthogonal force vectors,  one can develop a  projection operator scheme to
+% to parse the $N$-dimensional linear vector space spanned by the mass-weighted normal mode vectors into two subspaces:
+% one spanned by three vectors describing the coupling between the electronic states
+% and the other spanned by the remaining $N-3$ dimensional space spanned by motions that
+% do not couple the electronic states.
+% This  subspace  can be generated by defining a projection operator
+% \begin{eqnarray}
+% \mathbf{P}=\sum_{\alpha\beta}'\left(\mathbf{S^{-1}}\right)_{\alpha\beta}\mathbf{g_{\alpha}}\otimes\mathbf{g_{\beta}}
+% \end{eqnarray}
+% in which the summation is limited to linearly independent vectors.
+%    Here $\mathbf{S}_{\alpha\beta}=\mathbf{g_{\alpha}}\cdot\mathbf{g_{\beta}}$,
+% $\otimes$ is outer product,  and $\mathbf{I}$ is unitary operator.
+% This $N\times N$ matrix projects out all normal modes that are directly coupled to the
+% electronic degrees of freedom and
+%  its complement $\mathbf{Q}=\mathbf{I}-\mathbf{P}$ projects out all modes not directly coupled.
+% By diagonalizing the matrix
+% \begin{eqnarray}
+% \mathbf{K}=\mathbf{P}\cdot\mathbf\Omega\cdot \mathbf{P}+\mathbf{Q}\cdot\mathbf\Omega\cdot\mathbf{Q}
+% \end{eqnarray}
+% we obtain a  transformation, ${\mathbf M}$,  between the normal coordinates and a new set of orthogonal
+% coordinates.  Both $\mathbf{P}\cdot\mathbf\Omega\cdot \mathbf{P}$ and $\mathbf{Q}\cdot\mathbf\Omega\cdot\mathbf{Q}$ are $N\times N$ matrices.
+% However, for a two-state system, the former will have exactly $3$ non-trivial eigenvalues, $\{\alpha_{p}\}$, with corresponding
+% eigenvectors, $\{ M_{p}\}$, whereas the latter will have exactly $N_{r} = N-3$ non-trivial eigenvalues, $\{\alpha_{q}\}$,  and corresponding
+% eigenvectors, $\{M_q\}$.   This the full $N\times N$ transformation is formed by joining the non-trivial vectors from the
+% two respective subspaces ${\mathbf M} = \{M_{p}, M_{q}\}$.
+% The transformed electron-phonon coupling constants are given by projecting the  couplings   in the normal mode basis on to the new
+% basis.
+% \begin{eqnarray}
+% \mathbf{g}_{ab}'=\mathbf{M}_{p}\cdot\mathbf{g}_{ab}.
+% \end{eqnarray}
+% By examining the types of molecular motions that compose the ${\mathbf M_{p}}$ subspace, we can
+% gain a deeper understanding of the specific classes of internal motion that are directly involved with the
+% electron transfer process.  In addition,  we can gain a computational advantage since presumably this
+%  reduced set of modes give the dominant contribution to the electron-phonon coupling and  autocorrelation
+%  function given as the kernel in Eq. ~\ref{gr-expression}.
+
+% \subsection{Lanczos Method}
+% It is crucial to notice that the vectors  given in Eq.~\ref{eq:locaiHam} are {\em not linearly independent}.
+%  Consequently, special care
+% must be taken to generate the reduced sub-space.  To do so, we use an iterative Lanczos approach
+% taking the normalized vector ${\mathbf v}_{1} = {\mathbf g}_{22}$ as a starting point.
+
+% As above, we initialize each step indexed by $k$,  by defining a projection operator
+% \begin{eqnarray}
+% {\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
+% \end{eqnarray}
+% and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
+% %${\mathbf P}_{k}$ is the projection operator for the
+% $k$-th mode.
+% %We also construct
+% %\begin{eqnarray}
+% %\mathbf p = \sum_{k} \mathbf P_{k}
+% %\end{eqnarray}
+% %as  the total projection operator for all ${k} \le N$ modes.
+% We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
+% \begin{eqnarray}
+% \mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
+% \end{eqnarray}
+% and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
+% respectively.
+% As above, $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
+% The first set will have a single
+% non-trivial eigenvalue and the second set
+% will have $N-k$ non-trivial eigenvalues.  As above we collect the non-trivial eigenvectors associated with each
+% to form the orthogonal transformation matrix
+% \begin{eqnarray}
+% {\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
+% \end{eqnarray}
+% and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
+%  At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
+% $k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
+% a diagonal submatrix in the lower-right.  For example, after $k=3$ iterations, one has
+% a Hessian matrix of the form:
+% \begin{eqnarray}
+% {\mathbf\Omega}' =
+% \begin{pmatrix}
+% \alpha_{1}   & b_{1}    & 0                    &               &             &            & 0 \\
+% b_{1}     & \alpha_{2}  & b_{2}                         \\
+% 0            &   b_{2}         & \alpha_{3}    &   c_{k+1}   & c_{k+2}  & \cdots & c_{N}     \\
+%                &                     &           c_{k+1}           &     \alpha_{k+ 1} & &             & 0                 \\
+%                &                     &           c_{k+2}           &                 & \alpha_{k+2}  \\
+%                &                     &          \vdots           &                 &                    &  \ddots \\
+%    0           &                     &           c_{N}           &     0   &&& \alpha_{N}\\
+% \end{pmatrix}.
+% \label{omega-prime}
+% \end{eqnarray}
+% We note that only the $k$-th mode is coupled the $N-k$ remaining modes.
+% Since all of the transformations are orthogonal, diagonalizing $\mathbf\Omega'$ at any point
+% returns the original Hessian matrix.
+
+% To continue iterating, we  take the $k$-th row of $\mathbf\Omega'$ and zero the first $k$ elements
+% $$
+% {\mathbf e} = \{0,\cdots 0,c_{k+1},c_{k+2},\cdots ,c_{N}\}.
+% $$
+% This is the coupling between the upper tridiagonal block and the lower diagonal block.
+% We thus obtain a new vector
+% $$
+% {\mathbf v}_{k+1} = {\mathbf e} \cdot {\mathbf M}
+% $$
+% which is then reintroduced into the iteration scheme.
+
+% At any point along the way, we can terminate the iteration and obtain a reduced set of
+% couplings.  Since the  Lanczos approach uses the power method for finding the largest eigenvector of a matrix,
+% it converges first upon the vector with the largest electron/nuclear coupling--which
+%  we refer to as the ``primary mode''.  Subsequent iterations produce reduced modes with
+%  weaker electron/nuclear couplings and the entire  process can be terminated after a few iterations.
+% After $k$-steps, the final electron-phonon couplings are then obtained by
+% projecting the original set of couplings (in the normal mode basis) into the final vector space.
+
+% For the first iteration, ${\mathbf v}_{1}$ is parallel to the bare electron-phonon coupling vector $g_{22}$
+% and the associated frequency is ${\mathbf v}_{1}\cdot\Omega\cdot{\mathbf v}_{1}$.   The subsequent iterations introduce
+% corrections to this via phonon-phonon coupling.  For example, for the $k=3$ iteration,
+% we would determine the active vector space in terms of the upper-left 3$\times 3$ block of the matrix in
+% Eq.~\ref{omega-prime}.
+% \begin{eqnarray}
+% {\mathbf \Omega}_{3}' =
+% \begin{pmatrix}
+% \alpha_{1}   & b_{1}    & 0      \\
+% b_{1}     & \alpha_{2}  & b_{2}                         \\
+% 0            &   b_{2}         & \alpha_{3}
+% \end{pmatrix}
+% \end{eqnarray}
+% Diagonalizing  ${\mathbf \Omega}_{3}'$ returns a set of frequencies and  associated eigenvectors
+% which are then used to compute the electron-phonon couplings in this reduced active space.
+% After $N-1$ iterations, $\mathbf\Omega'$ is a fully tridiagonal matrix and diagonalizing this returns the original
+% normal mode basis.
 

### 2016-03-29 Chapters/chap3/Manuscript-FINAL.tex
Correct bib for uppercase

@@
 
-\chapter{Chapter 3}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Chemical Physics \textbf{142}, 244114 (2015)}
+\chapter{Chapter 3}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Chemical Physics \textbf{142}, 244114 (2015)}\label{chap:chapt3}
 
@@
 % \subsection{Construction and parameterization}
-Our method was detailed in ~Ref. \cite{yang2014intramolecular} but to be self-contained, we briefly present it here.
+% Our method was detailed in ~Ref. \cite{yang2014intramolecular} but to be self-contained, we briefly present it here.
 
@@
 
-\section{Localized Property of the Primary Lanzcos Mode}
-
-We have established  that the Primary Lanzcos Mode is more like the normal modes of the isolated
+\section{Localized Property of the Primary Lanczos Mode}
+
+We have established  that the primary Lanczos mode is more like the normal modes of the isolated
 donor and acceptor moieties, rather than of the entire molecule. The relation between the

### 2016-03-29 FrontBackmatter/Abstract.tex
Write Abstract

@@
 \chapter*{Abstract}
-Essential microscopic aspects of activated transport in liquids, which
-precedes the glass transition, have evaded explanation for
-decades. These poorly understood aspects include: the molecular
-underpinning of the excess, configurational entropy; the transition
-state configurations for the activated transport; the chemical origin
-of the fragile vs. strong liquid behavior; and many others. This
-dissertation puts forth a radically novel way to address these open
-questions, in which liquids near their glass transition are viewed as
-structurally degenerate assemblies of strongly interacting, local
-sources of frozen-in stress. The thermodynamics and activated barriers
-for rearrangement of this stress field have been mapped onto a
-Heisenberg model with six-dimensional spins. A meanfield analysis of
-the spin model has shown glasses can be viewed as frozen-in patterns
-of shear stress and/or uniform compression/dilation, the two extremes
-corresponding to the strong and fragile behaviors. A self-consistent
-elasticity theory of aperiodic, metastable solids emerges in the
-present analysis; it supersedes the traditional elasticity theory,
-which fails to self-consistently account for the structural degeneracy
-stemming from the inherent mismatch between cohesive forces and steric
-repulsion.  The observable elastic constants self-consistently emerge
-in the present theory similarly to how the dielectric susceptibility
-is determined by the properties of molecular dipoles. First
-simulations of the spin model have been carried out. In addition to
-direct observations of transition states for the activated transport,
-several key features of the glass transition are yielded by the spin
-model, including a strongly non-exponential, non-Arrhenius character
-of the relaxations and its correlation with the Poisson ratio of the
-substance.
+% Essential microscopic aspects of activated transport in liquids, which
+% precedes the glass transition, have evaded explanation for
+% decades. These poorly understood aspects include: the molecular
+% underpinning of the excess, configurational entropy; the transition
+% state configurations for the activated transport; the chemical origin
+% of the fragile vs. strong liquid behavior; and many others. This
+% dissertation puts forth a radically novel way to address these open
+% questions, in which liquids near their glass transition are viewed as
+% structurally degenerate assemblies of strongly interacting, local
+% sources of frozen-in stress. The thermodynamics and activated barriers
+% for rearrangement of this stress field have been mapped onto a
+% Heisenberg model with six-dimensional spins. A meanfield analysis of
+% the spin model has shown glasses can be viewed as frozen-in patterns
+% of shear stress and/or uniform compression/dilation, the two extremes
+% corresponding to the strong and fragile behaviors. A self-consistent
+% elasticity theory of aperiodic, metastable solids emerges in the
+% present analysis; it supersedes the traditional elasticity theory,
+% which fails to self-consistently account for the structural degeneracy
+% stemming from the inherent mismatch between cohesive forces and steric
+% repulsion.  The observable elastic constants self-consistently emerge
+% in the present theory similarly to how the dielectric susceptibility
+% is determined by the properties of molecular dipoles. First
+% simulations of the spin model have been carried out. In addition to
+% direct observations of transition states for the activated transport,
+% several key features of the glass transition are yielded by the spin
+% model, including a strongly non-exponential, non-Arrhenius character
+% of the relaxations and its correlation with the Poisson ratio of the
+% substance.
+We present a new, fully {\em ab initio} approach for computing intramolecular charge and
+energy transfer rates.  Using a time-convolutionless master equation approach and parameterized
+using couplings obtained using an accurate quantum chemical approach, we  benchmark the approach
+against  experimental results and Marcus theory rates for triplet energy transfer for a
+series of donor-bridge-acceptor systems.
+An important component of our analysis is the use of a projection operator scheme
+that parses out specific internal nuclear motions that accompany
+the electronic transition.
+Using an iterative Lanczos approach, we  concentrate the coupling between the electronic and nuclear
+degrees of freedom into a small number of reduced harmonic modes.
+We find that  using only a single reduced mode--termed the ``primary mode'' or ``Lanczos modes'',
+ one obtains an accurate evaluation of the golden-rule rate constant and
+insight into the nuclear motions responsible for coupling the initial and final electronic states.
+
+In particular, the irreducible representation of the primary mode reveals
+hidden details of the dynamics. For the cases considered here, the primary modes belong to totally symmetric irreducible representations  of
+the donor and acceptor moieties. Upon investigating the molecular geometry changes following  the transition,   we propose that the electronic transition process can be
+broken into two steps, in the agreement of Born-Oppenheimer approximation:  a fast excitation transfer occurs, facilitated by the ``primary Lanczos mode'' (PLM),
+followed by slow nuclear relaxation on the final electronic diabatic surface.
+
+We apply the method to a larger, ``star'' molecule, which has been shown experimentally that its exciton transfer pathway can be dramatically modified by mode-specific infrared excitation of vibrations.
+THe primary mode and rate constants we obtain generally agree with the experiments.
 \endgroup

### 2016-03-29 FrontBackmatter/Acknowledgments.tex
Write Acknowledgments

@@
 \chapter*{Acknowledgments}
-I would like to express my sincere gratitude to Vas Lubchenko, whose
-support often extended well beyond of what is normally required from
-the graduate advisor. I am also thankful to him for very careful,
-critical, and multiple reading of this manuscript which greatly
-contributed to its quality.  This work would not be possible without
-help of my family: my parents, my wife, and my son.  I am
-deeply grateful to Eric R. Bittner who, by being such a wonderful
-graduate advisor to my wife, made an inconspicuous, but very important,
-influence on everything I did. I also would like to thank to Anne Goj,
-Jon Golden, Pyotr Rabochiy, and other members of Bittner and
-Lubchenko's groups who made this place such a nice professional
-home. I am indebted to Elena and Phil Motuzko for helping me in the
-time of need. Last but not least, I thank Sergei Lukyanets without
-whom I would never became a scientist.
+% I would like to express my sincere gratitude to Vas Lubchenko, whose
+% support often extended well beyond of what is normally required from
+% the graduate advisor. I am also thankful to him for very careful,
+% critical, and multiple reading of this manuscript which greatly
+% contributed to its quality.  This work would not be possible without
+% help of my family: my parents, my wife, and my son.  I am
+% deeply grateful to Eric R. Bittner who, by being such a wonderful
+% graduate advisor to my wife, made an inconspicuous, but very important,
+% influence on everything I did. I also would like to thank to Anne Goj,
+% Jon Golden, Pyotr Rabochiy, and other members of Bittner and
+% Lubchenko's groups who made this place such a nice professional
+% home. I am indebted to Elena and Phil Motuzko for helping me in the
+% time of need. Last but not least, I thank Sergei Lukyanets without
+% whom I would never became a scientist.
 
-The numerical part of this work was completed using TLC2 HPC
-facility of the University of Houston and Ares cluster of the Texas
-Southern University. I am especially indebted to C. J. Tymczak for
-providing the access to the latter.
+% The numerical part of this work was completed using TLC2 HPC
+% facility of the University of Houston and Ares cluster of the Texas
+% Southern University. I am especially indebted to C. J. Tymczak for
+% providing the access to the latter.
 
-I also gratefully acknowledge support by the Donors of the ACS Petroleum
-Research Fund, the Arnold and Mabel Beckman Foundation, the Welch
-Foundation Grant E-1765, and the NSF Grant CHE 0956127.
+% I also gratefully acknowledge support by the Donors of the ACS Petroleum
+% Research Fund, the Arnold and Mabel Beckman Foundation, the Welch
+% Foundation Grant E-1765, and the NSF Grant CHE 0956127.
+I would like to offer my sincere gratitude to my thesis comittee, Prof.
+Eric R.
+Bittner, Prof.
+Vassiliy Lubchenko, Prof.
+Shoujun Xu, Prof.
+Don Coltart, and Prof.
+Gila Stein for serving my committee and their help.
+
+I would like to express my deepest gratitude to my advisor Prof.
+Eric Bittner for the continuous guidance and support of my Ph.D study and related research, especially for his patience and tolerance.
+I learn and research in a bit uncommon way.
+Without his tolerance, I could not have finished my Ph.D study.
+
+I would like to thank my fellow labmates: Allen Kelly, Svitlana Zaster, Hao Li, Kush Patel, Vladimir Lankevich, and Robert Paradez.
+They, especially Allen, helped me a lot to adapt to the new life here.
+I would like to thank Dmytro Bavzenko for his pretty thesis template.
+
+I would like to express my gratitude to many great men in human history: Einstein, Darwin, Turing, Feynman, Hayek...
+The list is long.
+They are heroes in my heart.
+Bearing their thoughts and stories in mind, I never feel alone.
+
+Last but not least, I would like to thank my mother, for the nurture and support she give me in so many years.
+I am indebted to her.
+Although she cannot understand my research - even a little bit, this thesis is for her.
 \endgroup

### 2016-03-30 Chapters/chap2/manuscript.tex
Finish first 3 chapts

@@
 
-In this chapter we focus here on the rates of triplet exchange between a naphthalene donor and a benzaldehyde acceptor linked by a variety of bridging units.
+In this chapter we focus on the rates of triplet exchange between a naphthalene donor and a benzaldehyde acceptor linked by a variety of bridging units.
 \begin{center}
@@
 nuclear displacement vectors and gain insight into the coupled electronic/nuclear motions that underlie an electronic
-transition.   Our analysis also suggests that the primary  mode reflects the irreducible representations of the
-donor and acceptor excited states.
+transition.   Our analysis also suggests that the primary  mode resembles certain  irreducible representations of the
+donor and acceptor moieties. This is further explored in next chapter.
 

### 2016-04-02 Chapters/chap1/introduction.tex
Finish first 3 chapts
Write chapter 4

@@
 %!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
-\chapter{Chapter 1}
+\chapter{Chapter 1}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}
 \section{Introduction}
@@
 
-\section{Theoretical Approach}
+\section{Theoretical Approach}\label{section:theory}
 Below we give a detailed description of our methods.
@@
 \begin{eqnarray}
-V_{ab}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
+V_{ab}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).\label{mixingangle}
 \end{eqnarray}

### 2016-04-02 Chapters/chap2/manuscript.tex
Write chapter 4

@@
 \end{center}
-Triplet energy exchange in these systems occurs via the through-space Dexter mechanism\cite{dexter1953theory}.
+Triplet energy exchange in these systems occurs via the through-space Dexter mechanism \cite{dexter1953theory}.
 This is a short-ranged interaction involving the simultaneous exchange of two electrons between the
 donor and acceptor moieties.
-Systems such as these formed the basis of a series of experiments by  Closs and Miller\cite{miller1984intramolecular}
+Systems such as these formed the basis of a series of experiments by  Closs and Miller \cite{miller1984intramolecular}
 in which they verified the existence of the Marcus inverted regime
 and serve as crucial benchmarks for testing new theoretical models for computing
-energy and charge transfer rates\cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
+energy and charge transfer rates \cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
 
@@
 used the Q-Chem 4.0 \cite{QCHEM4} code and employed the 6-31G(d){*}{*} basis set
-in order to compare our results  with  Ref. \cite{subotnik2010predicting}.
+in order to compare our results  with  Ref.~\cite{subotnik2010predicting}.
 
  We  benchmark our approach against a series of donor-bridge-acceptor
-molecules studied by Closs\cite{closs1988determination,closs1988intramolecular,closs1989connection}.
+molecules studied by Closs \cite{closs1988determination,closs1988intramolecular,closs1989connection}.
 These cases are significant in that they provided a crucial verification of the Marcus inverted regime.
@@
 from ~Ref. \cite{subotnik2010predicting}
-and experimental rates from Refs.\cite{closs1988determination,closs1989connection}.   The experimental error is estimated to be 20\% in each
+and experimental rates from Refs. \cite{closs1988determination,closs1989connection}.   The experimental error is estimated to be 20\% in each
 case studied here.
@@
 As a result,  the potential surfaces are no longer parabolic
-and the Condon approximation breaks down.\cite{subotnik2010predicting}
+and the Condon approximation breaks down \cite{subotnik2010predicting}.
 

### 2016-04-02 Chapters/chap3/Manuscript-FINAL.tex
Write chapter 4

@@
 electronic degrees of freedom.  The seminal model for the calculation of the transfer rate for this process
-was developed by Marcus in the 1950's\cite{marcus1956theory,marcus1965theory,marcus1993electron}
+was developed by Marcus in the 1950s \cite{marcus1956theory,marcus1965theory,marcus1993electron}
 \begin{equation}
@@
 and further increases in the energy off-set leads to slower transition rates.
-This ``inverted regime''  was confirmed by Closs and Miller\cite{miller1984intramolecular,closs1988determination,closs1989connection}
+This ``inverted regime''  was confirmed by Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
 nearly 30 yrs later.
@@
 state-to-state rate in which the coupling between  states depends upon the
-nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
+nuclear coordinates \cite{pereverzev2006time}. This approach incorporates a fully quantum
 mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
-the Marcus rate equation in the semiclassical limit.  The model itself is parameterized by the
+the Marcus rate equation in the semi-classical limit.  The model itself is parameterized by the
 vibrational normal mode frequencies, the electronic energies, and energy derivatives
@@
 Such systems were the basis of a  classic series of experiments by
-Closs and Miller\cite{miller1984intramolecular,closs1988determination,closs1989connection}
+Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
 which verified the existence of the Marcus inverted regime.
@@
 constants computed using all normal modes, as well as to the experimental
-and recent theoretical values for the transfer rates.\cite{subotnik2010predicting}
+and recent theoretical values for the transfer rates \cite{subotnik2010predicting}.
 
@@
 To calculate transition rate, we transform to adiabatic representation.
-It is done via Edmiston-Ruendenberg (ER) localization\cite{subotnik2010predicting} implemented in Q-Chem and the electronic Hamiltonians
+It is done via Edmiston-Ruendenberg (ER) localization \cite{subotnik2010predicting} implemented in Q-Chem and the electronic Hamiltonians
 on adiabatic and diabatic basis are related by the mixing angle $\theta$.
@@
 then perform a polaron transform
-using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
+using the unitary transformation \cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
 \begin{eqnarray}
@@
 normal modes, as well as the experimental rates,
-when parameterized using accurate quantum chemical data.\cite{yang2014intramolecular}
+when parameterized using accurate quantum chemical data \cite{yang2014intramolecular}.
 
@@
    \hline
-   Mode used & C14ee-PLM   & C14ee-DNM  & D26ae-PLM  & D26ae-DNM\\
+   Mode used & c-1,4ee-PLM   & c-1,4ee-DNM  & d-2,6ae-PLM  & d-2,6ae-DNM\\
    \hline

### 2016-04-02 Chapters/chap4/chap4.tex
Write chapter 4

%!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
\chapter{Chapter 4}\label{chap:chapt4}
\section{Introduction}

Electron transfer (ET) is one of the most important and fundamental processes in chemistry. Its mechanism
 is highly quantum mechanical in nature. ET is often mediated by nuclear-electronic (vibronic) interactions, especially in donor-bridge-acceptor system \cite{ulstrup1975effect,schrauben2010vibrational,davis2009effect,devault1980quantum,gray1996electron,lewis2002donor,bressler2009femtosecond,shih2008tryptophan,repp2010coherent,halpin2014two}. The importance of vibronic coupling in controlling the light-induced transfer is increasingly recognized. Several theoretical frameworks about the influence of infrared light in ET has been established \cite{soler2014signature,skourtis2004inelastic,xiao2009turning,beratan2009steering,antoniou2015vibrational}. Nevertheless, due to the ultra-fast intramolecular vibrational redistribution, it is challenging to experimentally manipulate photo-induced reactions in the condensed phase. Recently Julia {\em et al.} report a series of molecules, whose ET pathways can be radically changed - even completely closed - by infrared light excitation of intramolecular vibrations \cite{delor2014toward,delor2015mechanism,scattergood2014electron}.

The pioneering model for the computation of ET rate was developed by Marcus in the 1950s \cite{marcus1956theory,marcus1965theory,marcus1993electron}
\begin{equation}
k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T},
\end{equation}
which relates the Fermi golden-rule transition rate, $k_{Marcus}$
to the thermodynamic driving force $\Delta G^{o}$ and the reorganization energy $\lambda$. Our group developed a time-convolutionless  master equation (TCLME) for computing state-to-state rate in which vibronic coupling is explicitly considered \cite{pereverzev2006time}. This approach incorporates a fully quantum
mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
the Marcus rate equation in the semi-classical limit.  All parameters necessary in the model can be obtained from {\em ab initio} quantum  chemistry computations.
The approach has been benchmarked and used for many systems, ranging from organic photovoltaics to the molecules in Closs' classical experiments \cite{tamura2008phonon,tamura2007exciton,singh2009fluorescence,bittner2014noise,yang2014intramolecular,yang2015computing}. Besides the computation of transfer rate constant, our method includes a  mode-projection scheme, which can parse out a hierarchy of nuclear motions primarily coupled to the transition. The most important vibrational motion is termed ``primary mode'' or ``Lanczos mode'' in our previous work, as Lanczos algorithm is employed in the projection \cite{yang2014intramolecular,yang2015computing}.

Here we apply our approach to the molecules studied by Julia {\em et al.}. We first briefly review their experiment results and the theory of our approach. Then we compare  rate constants and mode that significantly affects dynamics.

\section{Experiment Results}

Julia {\em et al.} designed and investigated three donor–bridge–acceptor (DBA) molecular triads \cite{delor2014toward,delor2015mechanism,scattergood2014electron}: PTZ-CH\textsubscript{2}-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP, PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP and OMe-PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP (D = PTZ is phenothiazine and A = NAP is naphthalene-monoimide, see Fig. \ref{JuliaStruct}(a)). From now on, they are further abbreviated as PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP, respectively.

All three molecules undergo similar ET processes, as illustrated in Fig. \ref{JuliaStruct}(b) and Fig. \ref{ETscheme}. After excited by a UV pump, molecules are excited to the triplet charge transfer (CT) manifold stemming from electron transfer from the Pt-acetylide center to the NAP acceptor. The transfered charge can undergo further separation to form the full charge-separated state (CSS), or recombine to form a localized excitation, \textsuperscript{3}NAP, both eventually decay to ground state. Julia {\em et al.} showed that if a judiciously chosen IR pump is applied to excite the C$\equiv$C bond after the initial excitation, the yield of intermediate states can be radically changed. For PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can even be completely switched off.

% \begin{figure}[!ht]
%   \begin{adjustbox}{addcode={\begin{minipage}{\width}}{\caption{\textbf{a}. Molecular structure of PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP, from left to right. \textbf{b}. Energy level diagrams for the ET process, with the free energy driving force of charge separation ($\Delta$G) indicated. Adapted with permission from Ref.~\cite{delor2015mechanism}.}\end{minipage}},rotate=90,center}
%       \includegraphics[width=1.7\columnwidth]{Chapters/chap4/Images/molecules.jpg}%
%   \end{adjustbox}\label{JuliaStruct}
% \end{figure}

\begin{figure*}[!t]
\includegraphics[width=\columnwidth]{Chapters/chap4/Images/molecules.jpg}
\caption{\textbf{a}. Molecular structure of PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP, from left to right. \textbf{b}. Energy level diagrams for the ET process, with the free energy driving force of charge separation ($\Delta$G) indicated. Adapted with permission from Ref.~\cite{delor2015mechanism}.\label{JuliaStruct}}
\end{figure*}

\begin{figure*}[!h]
\includegraphics[width=0.71\columnwidth]{Chapters/chap4/Images/scheme.jpg}
\caption{The sketch of ET pathways. For PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can be fully suppressed by intermediate infrared excitation. Reprinted with permission from Ref.~\cite{delor2015mechanism}.\label{ETscheme}}
\end{figure*}

Three molecules also show differences due to their different donor moieties. Addition of the saturated CH\textsubscript{2} spacer from PTZ-Pt-NAP to PTZ-CH\textsubscript{2}-Pt-NAP slows down both charge separation and recombination by a factor of \textasciitilde 5 (the lifetime of CT increases from 3.3 to 14 ps and CSS from 190 ps to 1 ns), while the yield of the CSS decreases from 32 to 10\%. Furthermore, the CSS can decay to \textsuperscript{3}NAP in PTZ-Pt-NAP, while this path does not exist in PTZ-CH\textsubscript{2}-Pt-NAP. By appending methoxy groups to the PTZ in OMe-PTZ-Pt-NAP, the donor strength is increased, and it further accelerates reaction. The lifetime of CT is reduced to 1 ps.

\section{Theoretical Model} % (fold)
% \label{sec:theoretical_model}
The theoretical model is almost same to that presented in Section \ref{section:theory}. There is only one difference. In previous chapters, the diabatic coupling $V_{ab}$ in Eq. \ref{mixingangle}, which determines the mixing angle $\theta$ in Eq. \ref{eq:boys}, is obtained via ER localization, while in this chapter it is computed via the generalized Mulliken-Hush (GMH) model \cite{cave1996generalization,cave1997calculation}. In principle, any diabatization approach can be used to parametrize Eq. \ref{mixingangle}. This time we turn to GMH for two reasons. First, we do the optimization and frequency calculation in Gaussian 09 \cite{g09}. ER diabatization is not available there. Second, nevertheless, GMH has similar theoretical basis with ER and Boys localization methods \cite{subotnik2008constructing,subotnik2010predicting}, so it is supposed to work similarly. The diabatic coupling given by GMH is
$$V_{ab}=\frac{\left(E_2-E_1\right) \left|\mu _{12}\right|}{\sqrt{\left(\mu _1-\mu _2\right){}^2+4 \mu _{12}^2}},$$
where $\left(E_2-E_1\right)$ is the vertical excitation energy, $\mu _1$ and $\mu _2$ are the dipole moments of corresponding adiabatic states, and $\mu _{12}$ is the transition dipole moment between two states.

The molecules were optimized using DFT for ground state and TD-DFT for excited states, with the B3LYP functional, in Gaussian 09. To save computing resource, the molecules were simplified. The P(Bu)\textsubscript{3} moieties and octyl chain of NAP were simplified to PH\textsubscript{3} and a methyl group, respectively. In all calculations, SDD pseudo potential was used for Pt and 6-31G(d) basis for all other atoms. The solvent was described using the Polarizable Continuum Model (PCM), with the default parameters of CH\textsubscript{2}Cl\textsubscript{2} in Gaussian. All integrals were done ultrafine. The transition dipole moments were calculated using Multiwfn 3.3.8 \cite{lu2012multiwfn}.

% section theoretical_model (end)

\section{Results and Discussion} % (fold)

\subsection{Rate Constant}
The results presented here are for PTZ-Pt-NAP. The computation of other two molecules are in progress. We optimized and got two states of PTZ-Pt-NAP, the \textsuperscript{3}NAP and the lowest CT state. For transitions involving the CT state, we use parameters obtained at CT state geometry, and similar for \textsuperscript{3}NAP involved transitions. Obviously, we get two ways to calculate the CT $\rightarrow$ \textsuperscript{3}NAP transition, either geometry can be used. The comparison between theoretical and experimental rate constants is summarized in Fig. \ref{rateComp}. The rate constants calculated with all normal modes at two different geometries for the CT $\rightarrow$ \textsuperscript{3}NAP transition do not agree to each other. The results based on the CT geometry are in the same magnitude with experimental values, and the corresponding primary mode rates are similar to the exact ones. While the \textsuperscript{3}NAP geometry performs poorly. We suppose the fail of Condon approximation partially contribute to the error, and corresponding correction may improve the results, as discussed later.

\begin{figure*}[!ht]
\includegraphics[width=\columnwidth]{Chapters/chap4/Images/kTCLME-VS-EXPT.pdf}
\caption{Comparisons between theoretical rate constants and the experimental rates. Experimental rates are calculated as yield of product/lifetime of reactant, using values from ~Ref. \cite{delor2015mechanism}.  The ``exact'' rates are calculated using all normal modes, while the ``primary mode rate'' only use the first mode in projection scheme. The ``using mean $V_{12}$'' uses the average diabatic coupling along the interpolation coordinate instead of the diabatic coupling at a certain geometry. The CT geometry gives good ``exact'' results, its primary mode rates also agree well. While for the \textsuperscript{3}NAP geometry, using mean value of diabatic couplings along the reaction coordinate significantly improves the performance.\label{rateComp}}
\end{figure*}

\begin{figure}[!t]
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap4/Images/corrT12.pdf}}
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap4/Images/corrT13.pdf}}\\
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap4/Images/corrT31.pdf}}
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap4/Images/corrT32.pdf}}
\caption{
Correlation functions of various numbers of projected modes, compared to exact correlation, for (a) CSS $\rightarrow$ \textsuperscript{3}NAP at \textsuperscript{3}NAP geometry, (b) CT $\rightarrow$ \textsuperscript{3}NAP at \textsuperscript{3}NAP geometry, (c) CT $\rightarrow$ \textsuperscript{3}NAP at CT geometry, and (d) CT $\rightarrow$ CSS at CT geometry.
}\label{corrT1T3}
\end{figure}
\subsection{Primary Mode}

In Fig. \ref{rateComp} we see that for the CT geometry, using only the primary mode is sufficient to get good rate constants. Fig. \ref{corrT1T3} shows the correlation functions of different numbers of projected modes for all four transitions. Again the CT geometry performs better. Its convergence is satisfactory. The primary mode always resembles the exact initial dynamics, especially for the CT $\rightarrow$ \textsuperscript{3}NAP transition, where the primary mode reproduces the dynamics almost exactly up to 9 fs. Though not perfectly, tens of projected modes are enough to reproduce the shape of exact correlation functions for CT geometry. On the contrary, it takes hundreds of modes to recover the correlation for \textsuperscript{3}NAP (note that the degrees of freedom of PTZ-Pt-NAP is 201). Our previous studies \cite{yang2014intramolecular} shows that perfect matching of correlation function is unnecessary for good rate constant. It is verified again here. The primary mode's correlation function at CT geometry does not match the exact correlation perfectly, but the rate it gives agrees well to the exact value, and experiments. Nevertheless, the better it resembles the shape of exact function, the better the rate constant it gives.

\begin{figure}[!t]
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT13.png}}
% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CSS $\rightarrow$ \textsuperscript{3}NAP, (b) CT $\rightarrow$ \textsuperscript{3}NAP calculated at \textsuperscript{3}NAP geometry onto the normal modes of \textsuperscript{3}NAP. Embedded molecule shows the atomic displacement vectors of primary mode.}\label{projT1}
\end{figure}

\begin{figure}[!h]
% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT13.png}}
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CT $\rightarrow$ \textsuperscript{3}NAP, and (b) CT $\rightarrow$ CSS calculated at CT geometry onto the normal modes of CT. Embedded molecule shows the atomic displacement vectors of primary mode.
}\label{projT3}
\end{figure}

\begin{figure}[!h]
\subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t1_174.jpg}}\\
\subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t1_175.jpg}}\\
\subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t3_174.jpg}}\\
\subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t3_175.jpg}}
\caption{From top to bottom: the 174th, 175th mode of \textsuperscript{3}NAP state, the 174th, 175th mode of CT state. For clarity, bonds are removed.
}\label{NMT1T3}
\end{figure}

As experiments show that the excitation of C$\equiv$C bond radically affected the ET process, we expect the triple bond vibration to dominate the primary modes, at least for the CT state based calculations, since they achieve good agreement. Fig. \ref{projT1} and \ref{projT3} show the projection of primary modes onto the normal modes of corresponding state, i.e., the primary modes calculated at CT geometry are projected onto the normal modes of the CT state, and those at \textsuperscript{3}NAP are projected onto \textsuperscript{3}NAP's normal modes. It turns out that all four primary modes involve obvious C$\equiv$C displacement, and it is verified by the projections. The projections of primary modes are dominated by 1 or 2 normal modes. In Fig. \ref{projT1}(a), it is the 174th normal mode (ordering by increasing frequency); in Fig. \ref{projT1}(b), the 174th and 175th modes dominate. SIilarly, it is 174th and 175th modes dominate in Fig. \ref{projT3}(a) and the 175th mode in Fig. \ref{projT3}(b). All these normal modes are C$\equiv$C stretching modes, as shown in Fig. \ref{NMT1T3}. We suggest that the primary mode of  CT $\rightarrow$ CSS transition (Fig. \ref{projT3}(b)) is the one involves C$\equiv$C vibration most. It has a component which has the largest weight, > 0.25, in all four primary modes. And that component clearly dominates other normal modes. As for PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can be fully switched off by vibronic excitation, the step is supposed to be the one influenced by C$\equiv$C stretching most. Although PTZ-Pt-NAP does not show such radical change, we expect the the CT $\rightarrow$ CSS to be the most C$\equiv$C involved, as two molecules only differ by a -CH\textsubscript{2}-

% section results (end)

\subsection{Condon Approximation}

As mentioned above, the results at the CT state, including rate constant and projected modes, are satisfactory, while those at the \textsuperscript{3}NAP state are poor. The reason is complex. Here we illustrate that the break down of Condon approximation may be one of the causes.

Our model explicitly relies on two assumptions, parabolic assumption and Condon approximation. Parabolic assumption assumes potential energy surface (PES) is parabolic. For this molecule, parabolic assumption is probably true, as the PES has been shown to be parabolic along C$\equiv$C bond \cite{delor2014toward,delor2015mechanism}. Condon approximation states that diabatic coupling is independent of nuclear coordinates, i.e., does not change when geometry changes. In Fig. \ref{interCondon} we show the change of diabatic coupling from the \textsuperscript{3}NAP state to the CT state. It is clear that diabatic couplings do undergo significant changes (note the y axis is logarithmic), especially in the CSS $\rightarrow$ \textsuperscript{3}NAP step, where the coupling can differ by two orders of magnitudes. General speaking, Condon approximation fails more near the \textsuperscript{3}NAP than near the CT state. It may explain why CT geometry gives better results.

To explore the effect of the change of diabatic coupling, we replace the original coupling with the average coupling along interpolation and redo the calculations. The new rate constants are illustrated in Fig. \ref{rateComp}, as ``using mean $V_{12}$''. The most poorly computed rate, that of CSS $\rightarrow$ \textsuperscript{3}NAP, is significantly improved, and the other \textsuperscript{3}NAP based calculation, namely, the rate of CT $\rightarrow$ \textsuperscript{3}NAP, is slightly improved.

\begin{figure*}[!h]
\includegraphics[width=\columnwidth]{Chapters/chap4/Images/interpolation.pdf}
\caption{Diabatic coupling values along interpolation coordination. State 0 and 10 stand for the \textsuperscript{3}NAP and the CT state, respectively.\label{interCondon}}
\end{figure*}

There is another example to illustrate that the average coupling is a better value to use than the coupling at \textsuperscript{3}NAP geometry. As we have both \textsuperscript{3}NAP and CT states optimized, we can compute the energy gap between them. It is 0.81 $eV$, and is considered to be the best theoretical estimate we can get. We can also use the information at certain geometry to estimate the gap, with parabolic assumption assumed. Certainly how good the estimation is affects the computation of rate constant. Calculating at the CT state gives 0.78 $eV$, while at the \textsuperscript{3}NAP geometry gives 0.91 $eV$. If we still calculate at the \textsuperscript{3}NAP geometry, but use the average diabatic coupling, the energy gap computed decreases to 0.85 $eV$, which is much closer to 0.81 $eV$. This explains the improvement we get at \textsuperscript{3}NAP geometry by averaging diabatic coupling.

However, interestingly, the results at CT geometry get worse. For the CT $\rightarrow$  CSS reaction, the average diabatic coupling is so unreasonable that Eq. \ref{mixingangle} does not have any real solution, so it is absent in Fig. \ref{rateComp}. Looking at Fig. \ref{interCondon}, we suspect that the best choice of diabatic coupling is where Condon approximation holds, i.e., where the change of coupling is slow. The proposition can be tested when the calculations of other two molecules, PTZ-CH\textsubscript{2}-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP are complete.

\section{Conclusion} % (fold)
% \label{sec:conclusion}
We present here a modified version of our previous approach \cite{yang2014intramolecular,yang2015computing}. We change the ER diabatization to the GMH approach and apply the model to a much more complex system. Certain success is achieved, which illustrates the robustness of our model.

Julia's experiment demonstrates the promising future of IR-controlled electron transfer, which has huge potential in application. The theoretical study is important to understand and predict such property. The results presented here are a blend of success and failure. The calculations based on the CT state give good agreement to experiments, both in rate constant and primary mode. While \textsuperscript{3}NAP geometry gives much poorer results, but they can be partially corrected by adjusting the diabatic coupling. The cause of failure and success of our method needs more research. The undergoing calculations of other molecules can bring new tests to our method.
% section conclusion (end)

### 2016-04-02 FrontBackmatter/Abstract.tex
Write chapter 4

@@
 
-We apply the method to a larger, ``star'' molecule, which has been shown experimentally that its exciton transfer pathway can be dramatically modified by mode-specific infrared excitation of vibrations.
-THe primary mode and rate constants we obtain generally agree with the experiments.
+We apply the method to a larger, ``star'' molecule, which has been experimentally shown  that its exciton transfer pathway can be radically modified by mode-specific infrared excitation of vibrations.
+The primary mode and rate constants we obtain generally agree with the experiments.
 \endgroup

### 2016-04-10 Chapters/Appendix/codes.tex
Write Appendices

%!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
\chapter{Sample Codes}
The codes below are for the computation of rate constants and projected modes, written in Mathematica.
\\\large{Helper functions}
\begin{lstlisting}
ReadRotM[filename_]: = Module[{stream, RotMat},
stream = OpenRead[filename];
RotMat = Transpose[Partition[ToExpression[Last[Transpose[StringSplit[FindList[filename, "diabatic RotMatrix"]]]]], 2]];
Close[stream];
Return[RotMat]]

ReadEne[filename_]: = Module[{stream, e1, e2},
stream = OpenRead[filename];
e1 = ToExpression[Last[StringSplit[Find[stream, "showmatrix adiabatH(0, 0)"]]]]*27.211396132;
e2 = ToExpression[Last[StringSplit[Find[stream, "showmatrix adiabatH(1, 1)"]]]]*27.211396132(*in eV*);
Close[stream];
Return[{e1, e2}](* in hartree *)]

ReadNormalModes[filename_](* for QChem*):= Module[{stream, NAtom, NMode, NBlock, Freq, ForceConst, RedMass, IRActive, IRIntens, RamanActive, NormalModeCoord, IAn, AtomicMass, tmp},
  Freq = {};
  ForceConst = {};
  RedMass = {};
  IRActive = {};
  IRIntens = {};
  RamanActive = {};
  NormalModeCoord = {};
  IAn = {};
  AtomicMass = {};

  stream = OpenRead[filename];
  NMode = ToExpression[Last[Last[StringSplit[FindList[stream, "Mode"]]]]];
  NBlock = If[IntegerQ[#], #, Ceiling[#]]&[NMode/3];
  NAtom = (NMode + 6)/3;
  Close[stream];

  stream = OpenRead[filename];
  Find[stream, "Raman Active"];
  Read[stream];
  tmp = Table[First[StringSplit[Read[stream, String]]], {NAtom}];
  AtomicMass = QuantityMagnitude[ElementData[#, "AtomicWeight"] & /@ tmp];
  IAn = ElementData[#, "AtomicNumber"] & /@ tmp;
  Close[stream];

  stream = OpenRead[filename];
  Do[
   Find[stream, "Mode"];
   AppendTo[Freq, ToExpression[Drop[StringSplit[Read[stream, String]], 1]]];
   AppendTo[ForceConst, ToExpression[Drop[StringSplit[Read[stream, String]], 2]]];
   AppendTo[RedMass, ToExpression[Drop[StringSplit[Read[stream, String]], 2]]];
   AppendTo[IRActive, Drop[StringSplit[Read[stream, String]], 2]];
   AppendTo[IRIntens, ToExpression[Drop[StringSplit[Read[stream, String]], 2]]];
   AppendTo[RamanActive, Drop[StringSplit[Read[stream, String]], 2]];
   Read[stream];
   NormalModeCoord = Join[NormalModeCoord, ToExpression[Transpose[Table[Partition[Rest[StringSplit[Read[stream, String]]], 3], {NAtom}]]]];
   , {i, 1, NBlock}];
  Close[stream];

  {Freq, ForceConst, RedMass, IRActive, IRIntens, RamanActive} = Flatten /@ {Freq, ForceConst, RedMass, IRActive, IRIntens, RamanActive};
  Return[{NAtom, NMode, AtomicMass, Freq, RedMass, NormalModeCoord}]]

ReadGradient[filename_, NAtom_] := Module[{stream, grad, NMode, NBlock, tmp},
  grad = {};
  NBlock = If[IntegerQ[#], #, Ceiling[#]]&[NAtom/6];

  stream = OpenRead[filename];
  Find[stream, "Gradient of the state energy (including CIS Excitation Energy)"];
   Do[
    Read[stream];
    grad = Join[grad, Transpose[Table[ToExpression[Rest[StringSplit[Read[stream, String]]]], {3}]]];
    , {i, 1, NBlock}];
  Return[grad]]
\end{lstlisting}
\begin{lstlisting}
A_$\otimes$B_:= Outer[Times, A, B]
(* Project1by1 sorts phono modes into a 1 by 1 hierarchical form. Only works for one mode case, for general 3 by 3 case it should be modified. *)
Project1by1[gg_, Hess_]: = Module[
{S, P, Q, PHP, QHQ, L, $\omega$c, $\omega$ck, $\omega$b, Mc, Mck, Mb, np, ns, Sinv, G, p, k, g},
(* g should be 1-D, namely, ns = 1 *)
{ns, np} = Dimensions[gg];
g = gg;
$\omega$c = {};
Mc = {};
p = ConstantArray[0, {np, np}];

Do[{
S = Table[g[[i]].g[[j]], {i, ns}, {j, ns}];
Sinv = Inverse[S] ;
(* define projection operators *)
P = Sum[Sinv[[i, j]]  g[[i]]\[CircleTimes]g[[j]], {i, ns}, {j, ns}] ;
p = p+P; (*$P = P_1 + P_2 + ...$*)
Q = IdentityMatrix[np]-p;
PHP = P.Hess.P ;
QHQ = Q.Hess.Q ;
{$\omega$ck, Mck} = Chop[Transpose[Take[Sort[Transpose[Eigensystem[PHP]]], -ns]], 10^-8];
{$\omega$b, Mb} = Chop[Transpose[Take[Sort[Transpose[Eigensystem[QHQ]]], ns+k-1-np]], 10^-8];
$\omega$c = Chop[Join[$\omega$c, $\omega$ck], 10^-8];
Mc = Chop[Join[Mc, Mck], 10^-8];
$\omega$all= Join[$\omega$c, $\omega$b]//Chop;
M = Join[Mc, Mb]//Chop ;
g = Chop[{Join[ConstantArray[0, k], ( M.Hess.Transpose[M])[[k]][[k+1;;np]]].M}, 10^-8]; (* Define nth mode = (0, 0, 0, ..., $\gamma_{k+1}$, $\gamma_{k+2}$, ..., $\gamma_{k+N}$) *)
Gnew = M.gg[[1]];
}, {k, 1, np-1}];
](* The kth step gives k*k tridiagonal submatrix on lefttop, diagonal N-k on rightbottom and only the kth mode is coupled to the N-k bath modes *)
\end{lstlisting}
\begin{lstlisting}
NMode[n_, hess_, M_, g_]: = Module[{h, gn, Mnm, $\omega$prime, Gn},
h = Take[(M.hess.Transpose[M]), {1, n}, {1, n}];
{$\omega$prime, Mn} = Transpose[Sort[Transpose[Eigensystem[h]]]];
gn = Join[Take[g, n], ConstantArray[0, n-Length[Take[g, n]]]];
Gn = Mn.gn;
Return[{$\sqrt{\omega prime}$, Gn}]]
\end{lstlisting}
\large{Initialization}
\begin{itemize}[leftmargin = *]
\item Load Core routines
\begin{lstlisting}
SetDirectory[NotebookDirectory[]];
Needs["PhysicalConstants`"];  (* this package is outdated...but highly useful! *)
\end{lstlisting}

\item Conversion factors
\begin{lstlisting}
hartree = 27.211396132 ElectronVolt(* eV *);
Bohr = 0.5291772108 Angstrom;
$\hbar$ = hbar = PlanckConstantReduced;
\end{lstlisting}

\item Read in files
\begin{lstlisting}
name = {"c13ea", "c13ee", "c14ea", "c14ee", "d26ae", "d26ea", "d26ee", "d27ae", "d27ea", "d27ee", "mmm"};
path = "qchemout/"<>#<>".rtf"&/@name;
\end{lstlisting}
\begin{lstlisting}
kkk = 4;  (* in this case we are looking at c14ee *)
RotMat = ReadRotM[path[[kkk]]];
Ene = ReadEne[path[[kkk]]];
{NAtom, dof, AtomicMass, AngFreq, RedMass, NormMode} = ReadNormalModes[path[[kkk]]];
Grads = ReadGradient[path[[kkk]], NAtom];
$\omega$ = FreqeV = Table[Convert[2Pi SpeedOfLight AngFreq[[i]]Centimeter^-1 PlanckConstantReduced, ElectronVolt]/ElectronVolt, {i, 1, dof}];
Freq = Table[Convert[2Pi SpeedOfLight AngFreq[[i]]Centimeter^-1 , Second^-1], {i, 1, dof}];
NormModeInMWC = Table[Table[NormMode[[m, i, j]]$\sqrt{AtomicMass[[i]]}/\sqrt{RedMass[[m]]}$//Simplify//Chop, {i, NAtom}, {j, 3}], {m, 1, dof}];
Force = Table[Sum[NormModeInMWC[[m]][[i, j]]*Grads[[i, j]]/$\sqrt{AtomicMass[[i]]}$//Simplify//Chop, {i, 1, NAtom}, {j, 1, 3}], {m, 1, dof}];
GGG = CouplingConstant = Table[Convert[Force[[m]]hartree/Bohr$\sqrt{PlanckConstantReduced/(2 Freq[[m]]AMU)}$, ElectronVolt]/.ElectronVolt->1//Simplify//Chop, {m, 1, dof}];
G = G0 = Table[({
 {RotMat[[1, 2]]^2, RotMat[[2, 2]]RotMat[[1, 2]]},
 {RotMat[[2, 2]]RotMat[[1, 2]], RotMat[[2, 2]]^2}
})*CouplingConstant[[m]]//Simplify//Chop, {m, 1, dof}];
\end{lstlisting}
\large{Mode Analysis Routines}
\item Analyze n projected modes
\begin{lstlisting}
ModeAnalysis[n_]: = Module[{$\omega$prime},
Clear[imax];
imax = n;
{$\omega$prime, g} = NMode[n, hmat, M, Gnew];
Clear[$\omega$, G];
$\omega$ = Take[$\omega$prime, imax];
G = Table[({
 {RotMat[[1, 2]]^2, RotMat[[2, 2]]RotMat[[1, 2]]},
 {RotMat[[2, 2]]RotMat[[1, 2]], RotMat[[2, 2]]^2}
})*g[[m]]//Simplify//Chop, {m, 1, imax}];

v12tab[kkk][imax] = Table[{t, V[1, 2, t]}, {t, 0, nstep*tstep, tstep}];
v21tab[kkk][imax] = Table[{t, V[2, 1, t]}, {t, 0, nstep*tstep, tstep}];
v12[kkk][imax]= Interpolation[v12tab[kkk][imax]];
v21[kkk][imax]= Interpolation[v21tab[kkk][imax]];
b12tab[kkk][imax] = Table[{t, Bd[1, 2, t]}, {t, 0, nstep*tstep, tstep}];
b21tab[kkk][imax] = Table[{t, Bd[2, 1, t]}, {t, 0, nstep*tstep, tstep}];
b12d[kkk][imax]= Interpolation[b12tab[kkk][imax]];
b21d[kkk][imax]= Interpolation[b21tab[kkk][imax]];]
\end{lstlisting}
\item Calculation of Correlation Functions
\begin{lstlisting}
nstep = 3000;
tstep = 0.14;
imin = 1;
imax = dof;
Temperature = 298 Kelvin;

$\hbar$ = hbar= 6.582122*10^(-4)(* eV/ps^-1 =Convert[PlanckConstantReduced /10^-12 /Second, ElectronVolt]*);
$\beta$ = Convert[1/(Temperature BoltzmannConstant), ElectronVolt^-1]/.ElectronVolt->1;
Clear[$\epsilon$];
$\epsilon$[n_]: = Ene[[n]]-Sum[(G[[i, n, n]]^2/$\omega$[[i]]), {i, imin, imax}];
nu[i_]: = 1/(Exp[$\beta$*$\omega$[[i]]]-1);

$\Delta$[n_, m_, i_]: = (G[[i, n, n]]-G[[i, m, m]])/$\omega$[[i]];
$\Omega$[n_, m_, i_]: = (G[[i, n, n]]+G[[i, m, m]])/$\omega$[[i]];
f[n_, m_, $\tau$_]: = Exp[-2*Sum[(nu[i]+0.5)*($\Delta$[n, m, i])^2*(1-Cos[$\omega$[[i]]*$\tau$]), {i, imin, imax}]];
q[n_, m_, $\tau$_]: = Exp[I*Sum[($\Delta$[n, m, i])^2*Sin[$\omega$[[i]]*$\tau$], {i, imin, imax}]];
o[n_, m_, $\tau$_]: = (Sum[G[[i, n, m]]*($\Delta$[n, m, i]*(nu[i]+1)Exp[I*$\omega$[[i]]*$\tau$]-$\Delta$[n, m, i]*nu[i]*Exp[-I*$\omega$[[i]]*$\tau$]+$\Omega$[n, m, i]), {i, imin, imax}])^2+Sum[G[[i, n, m]]*G[[i, m, n]]*((nu[i]+1)Exp[I*$\omega$[[i]]*$\tau$]+nu[i]Exp[-I*$\omega$[[i]]*$\tau$]), {i, imin, imax}];
V[m_, n_, $\tau$_]: = 2*f[n, m, $\tau$]*Re[Exp[-I*($\epsilon$[n]-$\epsilon$[m])*$\tau$]*q[n, m, $\tau$]*o[n, m, $\tau$]];
Bd[m_, n_, $\tau$_]: = f[n, m, $\tau$]*q[n, m, $\tau$]*o[n, m, $\tau$];
\end{lstlisting}
\large{Get G and [Omega]}
\begin{lstlisting}
hess = FreqeV^2;
hmat = DiagonalMatrix[hess];
Project1by1[{CouplingConstant}, hmat]; (*This  gives a fully sorted tridiagonal matrix. You may encouter singular matrix error for certain molecules, c14ee for example, because some couplings are zero. Manually abort it and continue.*)
\end{lstlisting}
\begin{lstlisting}
ModeAnalysis[dof](*Exact calculation*)
\end{lstlisting}
\begin{lstlisting}
ModeAnalysis[1](*Do however many modes you like.*)
ModeAnalysis[4]
ModeAnalysis[7]
Do[ModeAnalysis[i], {i, 5, 20, 5}]
\end{lstlisting}
\large{Rate}
\begin{lstlisting}
$\phi$12 = Table[NIntegrate[v12[kkk][dof][$\tau$], {$\tau$, i*tstep, (i+1)*tstep}], {i, 0, nstep-1}];
$\phi$21 = Table[NIntegrate[v21[kkk][dof][$\tau$], {$\tau$, i*tstep, (i+1)*tstep}], {i, 0, nstep-1}];
Ww12 = {{0, 0}};
Ww21 = {{0, 0}};
$\omega$$\omega$12 = 0;
$\omega$$\omega$21 = 0;
Do[$\omega$$\omega$12p = $\omega$$\omega$12+$\phi$12[[i]];
Ww12 = Append[Ww12, {i*tstep*$\hbar$, $\omega$$\omega$12p}];
$\omega$$\omega$12 = $\omega$$\omega$12p, {i, nstep}];
Do[$\omega$$\omega$21p = $\omega$$\omega$21+$\phi$21[[i]];
Ww21 = Append[Ww21, {i*tstep*$\hbar$, $\omega$$\omega$21p}];
$\omega$$\omega$21 = $\omega$$\omega$21p, {i, nstep}];
W12t= Interpolation[Ww12];
W21t= Interpolation[Ww21];
vm12 = Mean@Take[Table[Ww12[[i]][[2]], {i, 1, nstep}], -30];
vm21 = Mean@Take[Table[Ww21[[i]][[2]], {i, 1, nstep}], -100];
W12 = Function[Piecewise[{{W12t[#], 0< = #< = nstep*tstep}, {vm12 , #>nstep*tstep*$\hbar$}}]];
W21 = Function[Piecewise[{{W21t[#], 0< = #< = nstep*tstep}, {vm21 , #>nstep*tstep*$\hbar$}}]];
Print["Golden rule rate =", vm21/$\hbar$*10^12, "$s^{-1}$"];
\end{lstlisting}
\large{Correlation function}
\begin{lstlisting}
 Plot[{
  Re[b21d[kkk][dof][.001 t/$\hbar$]],
  Re[b21d[kkk][1][.001 t/$\hbar$]], Re[b21d[kkk][4][.001 t/$\hbar$]],
  Re[b21d[kkk][7][.001 t/$\hbar$]]},
 {t, 0, 10},
 PlotRange -> All,
 AspectRatio -> 1,
 PlotStyle -> {{Black, Thick, Dashing[0.01]}, Blue, Green, Red, Purple},
 LabelStyle -> 16,
 AxesLabel -> {"t/fs", "Re($C_{12}(t)$))"},
 PlotLegends -> Placed[{"Exact", "1 Mode", "4 Modes", "7 Modes", "7 Modes"}, Right],
 Epilog -> {Style[Text[name[[kkk]], {9, -2.5*10^-7}], 24]}]
\end{lstlisting}

\end{itemize}

### 2016-04-10 Chapters/chap1/introduction.tex
Write Appendices

@@
 %!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
-\chapter{Chapter 1}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}
+\chapter{Introduction}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}
 \section{Introduction}
@@
 and assuming that the electronic states are coupled linearly to a common set of
- modes, we arrive a generic form for the Hamiltonian:
+ modes, we arrive at a generic form for the Hamiltonian, here written for two coupled electronic states:
  \begin{eqnarray}
@@
 linearized coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
-normal coordinates $\mathbf q$.   The diagonal terms
+normal coordinates $\mathbf q$.
+The equation assumes the potentials for the excited states are parabolic.
+This is usually valid in the reaction region, as we will show in next several chapters.
+The diagonal terms
 give the adiabatic displacement forces between the reference geometry and the two states.  If we choose one of the
@@
 The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
-In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.
+In the normal mode basis, the Hessian matrix, $\mathbf \Omega$,  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.
 
@@
 
-The difficulty in using this approach is that
+We first developed the approach about 10 years ago. However, the difficulty in using this approach is that
 it requires both diagonal (${\mathbf g}_{nn}$) and off-diagonal  (${\mathbf g}_{nm}$) derivative couplings between
@@
 can be obtained experimentally, it masks a wealth of detail that underlie the quantum transition.
+Considerable insight into the state-to-state dynamics can be revealed by examining such motions.
+However, until this work a general systematic approach for determining such motions did not exist.
+Our approach is based on earlier work by our group \cite{pereverzev2009energy} and Burghardt {\em et al.} \cite{gindensperger2006shortI,gindensperger2006shortII,cederbaum2005short}.
  Central to the theory is that there exists a collective nuclear displacement coordinate
@@
 
-Central to the work presented here consists of two parts. One is the use of a diabatization scheme for determining
+The theory presented here consists of two parts. One is the use of a diabatization scheme for determining
 donor and acceptor states in a molecular unit.
-The other is a projection scheme which enables us to analyze the contribution of vibrations in reactions.
+The other is a projection scheme enables us to analyze the contribution of vibrations in reactions.
 Similar decomposition schemes have been presented by Burghardt
- \cite{cederbaum2005short,gindensperger2006shortI,gindensperger2006shortII,cederbaum2005short}
- and the approach used here builds upon the method given in Ref.~\cite{pereverzev2009energy}.
+ \cite{gindensperger2006shortI,gindensperger2006shortII,cederbaum2005short}
+ and the approach used here builds upon the method given in Ref.~\cite{pereverzev2009energy}, but they decomposed normal modes into a 3 by 3 hierarchy, while we are able to get projected modes 1 by 1.
+This facilitates the analysis of dominating nuclear motions in transfer.
 
@@
 Then we use the projection operator scheme
-to parses out specific internal nuclear motions that accompany
+to parse out specific internal nuclear motions that accompany
 the electronic transition.
@@
 followed by slow nuclear relaxation on the final electronic diabatic surface.
+
+In Appendices we provide some sample codes and input files for analysis.

### 2016-04-10 Chapters/chap2/manuscript.tex
Write Appendices

@@
 
-\chapter{Chapter 2}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}\label{chap:chapt2}
+\chapter{Benchmark and Primary Mode}\footnotetext{Part of this chapter has been published in Xunmo Yang and E.
+R.
+Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}\label{chap:chapt2}
 \section{Introduction}
@@
 with respect to the number of reduced modes.  We
-can  this term exactly using all $N$ vibrational modes of the molecule and
+calculate  this term exactly using all $N$ vibrational modes of the molecule and
 compare to the results obtained using a subset of modes.
+Correlation function is used to compute transfer rate.
+Such comparison of correlations is very high standard test of the method.
+If we get good agreement, it means the reduced modes are a good representation of nuclear motions involved in transfer; even we do not get perfect correlation function, the rate constants calculated may also agree well, which is still a success.
 

### 2016-04-10 Chapters/chap3/Manuscript-FINAL.tex
Write Appendices

@@
 
-\chapter{Chapter 3}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Chemical Physics \textbf{142}, 244114 (2015)}\label{chap:chapt3}
+\chapter{Primary Mode and Its Relation to Reaction Dynamics}\footnotetext{Part of this chapter has been published in Xunmo Yang and E.
+R.
+Bittner, The Journal of Chemical Physics \textbf{142}, 244114 (2015)}\label{chap:chapt3}
 
@@
 
-However, this is only one side of the story and we  need try to do this in reverse, {\em i.e.}, can we
+However, this is only one side of the story and we  need try to do this in reverse, {\em i.~e.}, can we
 determine the PLM from simply geometric changes accompanying the transition? To see if this is possible,

### 2016-04-10 Chapters/chap4/chap4.tex
Write Appendices

@@
 %!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
-\chapter{Chapter 4}\label{chap:chapt4}
+\chapter{Application on More Complex Molecules}\label{chap:chapt4}
 \section{Introduction}
@@
 Nevertheless, due to the ultra-fast intramolecular vibrational redistribution, it is challenging to experimentally manipulate photo-induced reactions in the condensed phase.
-Recently Julia {\em et al.} report a series of molecules, whose ET pathways can be radically changed - even completely closed - by infrared light excitation of intramolecular vibrations \cite{delor2014toward,delor2015mechanism,scattergood2014electron}.
+Recently, the Weinstein group reported upon a series of molecules, whose ET pathways can be radically changed - even completely closed - by infrared light excitation of intramolecular vibrations \cite{delor2014toward,delor2015mechanism,scattergood2014electron}.
+The experiment is reviewed in next section.
 
@@
 
-Here we apply our approach to the molecules studied by Julia {\em et al.}.
+Here we apply our approach to the molecules studied by Weinstein {\em et al.}.
 We first briefly review their experiment results and the theory of our approach.
@@
 
-Julia {\em et al.} designed and investigated three donor–bridge–acceptor (DBA) molecular triads \cite{delor2014toward,delor2015mechanism,scattergood2014electron}: PTZ-CH\textsubscript{2}-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP, PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP and OMe-PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP (D = PTZ is phenothiazine and A = NAP is naphthalene-monoimide, see Fig.
+Weinstein {\em et al.} designed and investigated three donor–bridge–acceptor (DBA) molecular triads \cite{delor2014toward,delor2015mechanism,scattergood2014electron}: PTZ-CH\textsubscript{2}-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP, PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP and OMe-PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP (D = PTZ is phenothiazine and A = NAP is naphthalene-monoimide, see Fig.
 \ref{JuliaStruct}(a)).
@@
 The transfered charge can undergo further separation to form the full charge-separated state (CSS), or recombine to form a localized excitation, \textsuperscript{3}NAP, both eventually decay to ground state.
-Julia {\em et al.} showed that if a judiciously chosen IR pump is applied to excite the C$\equiv$C bond after the initial excitation, the yield of intermediate states can be radically changed.
+Weinstein {\em et al.} showed that if a judiciously chosen IR pump is applied to excite the C$\equiv$C bond after the initial excitation, the yield of intermediate states can be radically changed.
 For PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can even be completely switched off.
@@
 In principle, any diabatization approach can be used to parametrize Eq.
-\ref{mixingangle}.
-This time we turn to GMH for two reasons.
-First, we do the optimization and frequency calculation in Gaussian 09 \cite{g09}.
-ER diabatization is not available there.
-Second, nevertheless, GMH has similar theoretical basis with ER and Boys localization methods \cite{subotnik2008constructing,subotnik2010predicting}, so it is supposed to work similarly.
+\ref{mixingangle} There are many diabatization approaches (for a review, see Ref.~\cite{domcke2004conical}), and can be classified into three categories.
+ER localization and GMH approach fall in one category \cite{subotnik2008constructing,subotnik2009initial}.
+They do not seek diabatic states with zero derivative couplings, which are expensive to compute.
+Instead, they rely on physical intuition.
+GMH works well for linear or near-linear systems, but does not generalize to noncollinear system with more than two charge centers very well.
+ER localization can be seen as a extension of GMH which overcomes some drawbacks of GMH \cite{subotnik2009initial}.
+This time we do the optimization and frequency calculation in Gaussian 09 \cite{g09}, which does not support ER diabatization, so we turn to GMH.
+The molecule presented here is quite linear, and its charge centers are in the linear C$\equiv$C axis.
+As the result, GMH and ER localization approaches are supposed to give similar results.
 The diabatic coupling given by GMH is
@@
 The P(Bu)\textsubscript{3} moieties and octyl chain of NAP were simplified to PH\textsubscript{3} and a methyl group, respectively.
-In all calculations, SDD pseudo potential was used for Pt and 6-31G(d) basis for all other atoms.
-The solvent was described using the Polarizable Continuum Model (PCM), with the default parameters of CH\textsubscript{2}Cl\textsubscript{2} in Gaussian.
-All integrals were done ultrafine.
+In all calculations, SDD pseudo potential and solvent model were used (see Appendix.~\ref{sec:T1input} for the details of parameters).
 The transition dipole moments were calculated using Multiwfn 3.3.8 \cite{lu2012multiwfn}.
@@
 The computation of other two molecules are in progress.
+A typical calculation takes several months.
 We optimized and got two states of PTZ-Pt-NAP, the \textsuperscript{3}NAP and the lowest CT state.
@@
 \subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t3_175.jpg}}
-\caption{From top to bottom: the 174th, 175th mode of \textsuperscript{3}NAP state, the 174th, 175th mode of CT state. For clarity, bonds are removed.
+\caption{From top to bottom: the 174th, 175th mode of \textsuperscript{3}NAP state, the 174th, 175th mode of CT state. For clarity, bonds are not shown.
 }\label{NMT1T3}
@@
 Fig.
-\ref{projT1} and \ref{projT3} show the projection of primary modes onto the normal modes of corresponding state, i.e., the primary modes calculated at CT geometry are projected onto the normal modes of the CT state, and those at \textsuperscript{3}NAP are projected onto \textsuperscript{3}NAP's normal modes.
+\ref{projT1} and \ref{projT3} show the projection of primary modes onto the normal modes of corresponding state, {\em i.~e.}, the primary modes calculated at CT geometry are projected onto the normal modes of the CT state, and those at \textsuperscript{3}NAP are projected onto \textsuperscript{3}NAP's normal modes.
 It turns out that all four primary modes involve obvious C$\equiv$C displacement, and it is verified by the projections.
@@
 
-Julia's experiment demonstrates the promising future of IR-controlled electron transfer, which has huge potential in application.
+Weinstein's experiment demonstrates the promising future of IR-controlled electron transfer, which has huge potential in application.
 The theoretical study is important to understand and predict such property.

### 2016-04-10 Chapters/chap4/chap4.tex
Improve fig, revision

@@
 \ref{JuliaStruct}(a)).
-From now on, they are further abbreviated as PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP, respectively.
+From now on, they are further abbreviated as PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-Pt-NAP, respectively.
 
@@
 \caption{\textbf{a}.
-Molecular structure of PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP, from left to right.
+Molecular structure of PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-Pt-NAP, from left to right.
 \textbf{b}.
@@
 
+\begin{figure*}[!h]
+\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/parabola.jpg}
+\caption{Calculated energies of the CT (black), CSS (blue) and 3NAP (red) states along the NAP side C$\equiv$C coordinate in the ground state geometries of the molecules studied, in CH\textsubscript{2}Cl\textsubscript{2}.
+a, PTZ-CH\textsubscript{2}-Pt-NAP.
+b, PTZ-Pt-NAP.
+c, OMe-PTZ-Pt-NAP.
+The first and second vibrational energy levels for the asymmetric C$\equiv$C stretch are shown for the CT state.
+The energy gaps from $\nu_0$ to the intersection between CT and CSS are shown in the insets.
+There is a clear trend concerning the energy gap: PTZ-CH\textsubscript{2}-Pt-NAP < PTZ-Pt-NAP < OMe-PTZ-Pt-NAP, reflecting the trend experimentally observed in the efficiency of the infrared control effect.
+Reprinted with permission from Ref.~\cite{delor2015mechanism}.\label{PTZparabolas}} \end{figure*}
+
 Three molecules also show differences due to their different donor moieties.
@@
 The lifetime of CT is reduced to 1 ps.
+
+Weinstein propose the effect of infrared control relies on the distance between CT energy minimum and the intersection of CT and CSS potential energy surfaces.
+For all three molecules, two PESs intersect where C$\equiv$C bond is slightly longer than the equilibrium length.
+When C$\equiv$C bond gets excited, it elongates and helps molecules to pass the intersection.
+If the energy gap between intersection and equilibrium geometry is much larger than C$\equiv$C vibrational energy, the dynamics is barely affected; if the energy gap is small, the vibrational excitation can radically change the dynamics.
+It agrees to that PTZ-CH\textsubscript{2}-Pt-NAP has the smallest energy gap in theoretical calculations, as illustrated in Fig.
+\ref{PTZparabolas}.
 
@@
 \begin{figure}[!t]
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT13.png}}
-% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
-% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT32.png}}
+\subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
+\subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT13.png}}
+% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
+% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT32.png}}
 \caption{
@@
 \begin{figure}[!h]
-% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
-% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT13.png}}
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
-\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT32.png}}
+% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
+% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.png}}
+\subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
+\subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT32.png}}
 \caption{
@@
 In Fig.
-\ref{projT1}(a), it is the 174th normal mode (ordering by increasing frequency); in Fig.
+\ref{projT1}(a), it is the 174th normal mode (ordered by increasing frequency) that dominates; in Fig.
 \ref{projT1}(b), the 174th and 175th modes dominate.
-SIilarly, it is 174th and 175th modes dominate in Fig.
-\ref{projT3}(a) and the 175th mode in Fig.
+Similarly, 174th and 175th modes dominate in Fig.
+\ref{projT3}(a) and  175th mode in Fig.
 \ref{projT3}(b).
@@
 For the CT $\rightarrow$  CSS reaction, the average diabatic coupling is so unreasonable that Eq.
-\ref{mixingangle} does not have any real solution, so it is absent in Fig.
+\ref{mixingangle} does not have any real solution for $\theta$, so it is absent in Fig.
 \ref{rateComp}.
@@
 \ref{interCondon}, we suspect that the best choice of diabatic coupling is where Condon approximation holds, i.e., where the change of coupling is slow.
-The proposition can be tested when the calculations of other two molecules, PTZ-CH\textsubscript{2}-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP are complete.
+The proposition can be tested when the calculations of other two molecules, PTZ-CH\textsubscript{2}-Pt-NAP and OMe-PTZ-Pt-NAP are complete.
 

### 2016-04-12 Chapters/chap1/introduction.tex
Gonna give it to the committee

@@
 wide range of  chemical  and biological systems.
-It is the fundamental mechanism for transporting the  energy  of a
+It is the fundamental mechanism for transporting the  energy  of an
 absorbed photon to a reaction center in light harvesting systems
@@
 following the transfer of an electron from donor to acceptor.
-and $\Delta \epsilon$ is the driving force for the reaction.
+and $\Delta \epsilon$ is the driving force for the reaction, as illustrated in Fig.~\ref{marcus}. If we assume that the nuclear motions about the equilibrium configurations of the
+donor and acceptor species is harmonic,  the chemical reactions resulting from
+energy or charge transfer events can be understood in terms of intersecting
+diabatic potentials as sketched.    The upper and lower
+curves are the adiabatic potential energy surfaces describing the nuclear dynamics
+resulting from an energy or charge transfer event, taking the geometry of the donor
+state as the origin.
 
@@
 
-If we assume that the nuclear motions about the equilibrium configurations of the
-donor and acceptor species is harmonic,  the chemical reactions resulting from
-energy or charge transfer events can be understood in terms of intersecting
-diabatic potentials as sketched in Fig.~\ref{marcus}.    The upper and lower
-curves are the adiabatic potential energy surfaces describing the nuclear dynamics
-resulting from an energy or charge transfer event, taking the geometry of the donor
-state as the origin.
 %For reactions carried out in open systems,  the Marcus parabolas represent
@@
 
-A number of years ago,  we developed a time-convolutionless  master equation approach for computing
+A number of years ago,  our group developed a time-convolutionless  master equation approach for computing
 state-to-state rates in which the coupling between  states depends upon the
 nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
-mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
+mechanical treatment of both the nuclear and electronic degrees of freedom and recovers the
 well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
@@
 \cite{tamura2008phonon,tamura2007exciton,bittner2014noise,singh2009fluorescence}.
-This paper represents the first time we have used this approach within the context of a fully {\em ab initio} quantum
+Our work here represents the first time this approach has been used within the context of a fully {\em ab initio} quantum
 chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
@@
 $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
-normal phonon modes.  Transforming to the interaction representation
+normal modes. Following the conventional notations in this field, we refer to all harmonic nuclear motions as phonons. Transforming to the interaction representation
 and performing a trace over the phonons gives the spectral density in
@@
 
-\subsection{Non-Markovian Master Equation and Golden-Rule rates}
+\subsection{Non-Markovian Master Equation and Golden-Rule Rates}
 
@@
 %$$
-\[
+\begin{eqnarray}
 \lambda_{nm}=\sum_{j}\frac{\left(g_{nnj}-g_{mmj}\right)^{2}}{\omega_{j}} = \sum_{j}\hbar \omega_{j}S_{j}
-\]
+\end{eqnarray}
 where  the $\{S_{j}\}$  are  the Huang-Rhys factors for each phonon mode.
@@
 it requires both diagonal (${\mathbf g}_{nn}$) and off-diagonal  (${\mathbf g}_{nm}$) derivative couplings between
-adiabatic states.    In the following section, we discuss how we have used the Edmiston-Ruedenberg localization scheme
-to estimate the couplings\cite{edmiston1963localized}.   We also
-present how one can construct a reduced set of harmonic modes that
+adiabatic states.
+In the following section, we discuss how we have used the Edmiston-Ruedenberg (ER) localization scheme \cite{edmiston1963localized} to estimate the couplings.
+We also present how one can construct a reduced set of harmonic modes that
 fully capture the electron/nuclear coupling.
+
+\subsection{Adiabatic and Diabatic Representations}
+There are two common ways to represent the Hamiltonian, adiabatic and diabatic representations, as sketched in Fig.
+\ref{adiaDiab}.
+The way we represent the Hamiltonian in Eq.
+\ref{ham1} is adiabatic representation, where states are the eigenstates of molecule, and hence can be directly calculated in {\em ab initio} quantum chemistry software.
+However, the off-diagonal couplings in adiabatic representations ($g_{ij}$ in Eq.
+\ref{ham1}) are derivative couplings, which are difficult to compute.
+Even worse, the  couplings change radically near avoided crossing.
+A workaround is switching to diabatic representation, where the Hamiltonian is written as
+\begin{eqnarray}
+H_{dia}=U^{T}H_{adia}U=\left(\begin{array}{cc}
+\epsilon_{a}(\mathbf{R})\mathrm{+T'_{n}}(\mathbf{R})_{11} & V_{ab}\\
+V_{ab} & \epsilon_{b}(\mathbf{R})\mathrm{+T'_{n}}(\mathbf{R})_{22}
+\end{array}\right).
+\end{eqnarray}
+
+The diabatic representation has several advantages.
+First, sharp derivative couplings in adiabatic representations are transformed to smoother static diabatic couplings, $V_{ab}$.
+Second, potential energy surfaces are  smoothened and avoided crossing is eliminated.
+
+\begin{figure}[!t]
+\includegraphics[width=0.95\columnwidth]{Chapters/chap2/adia_vs_diabatic.png}
+\caption{Sketch of adiabatic and diabatic representations for two-state system. Compared to adiabatic representation, diabatic representation has smoother energy surfaces and couplings.
+}
+\label{adiaDiab}
+\end{figure}
+
+The problem now is how to obtain the transformation matrix
+\begin{eqnarray}
+U = \left(\begin{array}{cc}
+\cos\theta & \sin\theta\\
+-\sin\theta & \cos\theta
+\end{array}\right).
+\end{eqnarray}
+There are many methods available \cite{domcke2004conical}. Here we introduce the Edmiston-Ruedenberg diabatization approach.
+
+\subsection{Edmiston-Ruedenberg Diabatization}\label{sec:ER}
+A straightforward way to construct diabatic states is to eliminate derivative coupling mathematically, namely, to solve
+\begin{eqnarray}
+\left\langle \phi_{i}(\mathbf{r};\mathbf{R})|\nabla_{\mathbf{R}}|\phi_{j}(\mathbf{r};\mathbf{R})\right\rangle = 0.
+\end{eqnarray}
+However, it is computationally very expensive, and exact solution do not usually exist \cite{mead1982conditions}.
+
+Another category of diabatization methods is based on physical intuition, with ER diabatization being one of them.
+The ER diabatization is based on the idea that good diabatic states are supposed to be localized, so the approach defines the diabatic states by minimizing the total electron repulsion
+\begin{eqnarray}
+f_{ER}=\sum_{k}^{N_{states}}\iint dr_{1}dr_{2}\frac{\left\langle \phi_{k}|\hat{\rho}\left(r_{1}\right)|\phi_{k}\right\rangle \left\langle \phi_{k}|\hat{\rho}\left(r_{2}\right)|\phi_{k}\right\rangle }{\left\Vert r_{1}-r_{2}\right\Vert }.
+\end{eqnarray}
+
 \subsection{Parameterization From Quantum Chemistry}
@@
  Consequently, special care
-must be taken to generate the reduced sub-space.  To do so, we use an iterative Lanczos approach
+must be taken to generate the reduced sub-space.  To facilitate this, we develop an iterative Lanczos approach,
 taking the normalized vector ${\mathbf v}_{1} = {\mathbf g}_{22}$ as a starting point.
@@
 %as  the total projection operator for all ${k} \le N$ modes.
-We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
+We then project the Hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
 \begin{eqnarray}
@@
 \begin{eqnarray}
-{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
+{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\},
 \end{eqnarray}
-and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
- At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
+and again transform the full Hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
+ At each step in the iteration, the transformed Hessian, $\mathbf\Omega'$ is in the form of a
 $k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
-a diagonal submatrix in the lower-right.  For example, after $k=3$ iterations, one has
-a Hessian matrix of the form:
+a diagonal submatrix in the lower-right.  For example, after $k=3$ iterations, the Hessian matrix takes the form:
 \begin{eqnarray}
@@
 it converges first upon the vector with the largest electron/nuclear coupling--which
- we refer to as the ``primary mode''.  Subsequent iterations produce reduced modes with
+ we refer to as the ``primary mode''.  Subsequent iterations produce reduced modes with progressively
  weaker electron/nuclear couplings and the entire  process can be terminated after a few iterations.
@@
 and the associated frequency is ${\mathbf v}_{1}\cdot\Omega\cdot{\mathbf v}_{1}$.   The subsequent iterations introduce
-corrections to this via phonon-phonon coupling.  For example, for the $k=3$ iteration,
+corrections to this via phonon-phonon coupling mediated via the electronic couplings.  For example, for the $k=3$ iteration,
 we would determine the active vector space in terms of the upper-left 3$\times 3$ block of the matrix in

### 2016-04-12 Chapters/chap2/manuscript.tex
Gonna give it to the committee

@@
 R.
-Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}\label{chap:chapt2}
+Bittner, Intramolecular Charge- and Energy-Transfer Rates with Reduced Modes: Comparison to Marcus Theory for Donor–Bridge–Acceptor Systems.
+The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}\label{chap:chapt2}
 \section{Introduction}
@@
 Systems such as these formed the basis of a series of experiments by  Closs and Miller \cite{miller1984intramolecular}
-in which they verified the existence of the Marcus inverted regime
+in which they verified the existence of the Marcus ``inverted regime'' - the very negative $\Delta G$ domain where transfer becomes slower -
 and serve as crucial benchmarks for testing new theoretical models for computing
-energy and charge transfer rates \cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}.
+energy and charge transfer rates \cite{subotnik2008constructing,subotnik2009initial,subotnik2010predicting}. The molecules are sketched in Table. \ref{summarytable}.
 
@@
 First we examine the validity of the assumptions in our method.
-Then we apply the method to get theoretical transfer rate constants, and compare them to experiments.
+Then we apply the method to obtain theoretical transfer rate constants, and compare these to experimental results.
 Finally, we use the projection scheme to find the primary modes in the reactions.
-The modes turn out to show certain symmetry.
+% The modes turn out to show certain symmetry.
 
@@
 
-Our method employs two assumptions, parabolic assumption and Condon approximation.
-The former assumes that relevant potential energy surfaces are parabolic.
-The latter means diabatic coupling  is independent of nuclear coordinates in the region where reaction occurs.
-In Fig.~\ref{parabs} we show the adiabatic potential curves and off-diagonal couplings along an interpolation coordinate
-connecting the equilibrium geometries of the donor and acceptor states for the donor-[d-2,6ae]-acceptor case.
+Our method employs two assumptions.
+First is that the diabatic surfaces are harmonic.
+Second, the Condon approximation is valid, namely, the diabatic couplings are independent of nuclear coordinates in the region where the reaction occurs.
+In Fig.~\ref{parabs} we show the computed adiabatic potential curves and off-diagonal couplings along an interpolation coordinate
+connecting the equilibrium geometries of the donor and acceptor states for the d-2,6ae molecule.
 The dashed curve gives the parabolic approximation to the
@@
 
-Using the ER localization approach, all parameters needed for our model can be  obtained from
+Using the ER localization approach explained in Section \ref{sec:ER}, all parameters needed for our model can be  obtained from
 standard  quantum chemical packages.   The vertical energies, $\epsilon_{a}$
@@
 used the Q-Chem 4.0 \cite{QCHEM4} code and employed the 6-31G(d){*}{*} basis set
-in order to compare our results  with  Ref.~\cite{subotnik2010predicting}.
+in order to compare our results  against other theoretical results in  Ref.~\cite{subotnik2010predicting}.
 
@@
 % %as  the total projection operator for all ${k} \le N$ modes.
-% We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
+% We then project the Hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
 % \begin{eqnarray}
@@
 % \end{eqnarray}
-% and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
-%  At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
+% and again transform the full Hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
+%  At each step in the iteration, the transformed Hessian, $\mathbf\Omega'$ is in the form of a
 % $k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
@@
 test case.  Uniformly, these modes correspond to ring breathing motions on the donor and acceptor as illustrated in Fig.~\ref{LanczosModes_chap2}.
-As seen in this figure, coupling mode does not involve normal modes localized on the bridge species.
+As seen in this figure, the coupling mode does not involve normal modes localized on the bridge species.
 Moreover, the magnitude of the electronic coupling carried by this mode is uniformly around 0.37 eV  and independent of the bridge.
@@
 transition.   Our analysis also suggests that the primary  mode resembles certain  irreducible representations of the
-donor and acceptor moieties. This is further explored in next chapter.
+donor and acceptor moieties. This connection is further explored in next chapter.
 

### 2016-04-12 Chapters/chap3/Manuscript-FINAL.tex
Improve fig, revision
Gonna give it to the committee

@@
 
-\chapter{Primary Mode and Its Relation to Reaction Dynamics}\footnotetext{Part of this chapter has been published in Xunmo Yang and E.
+\chapter{Primary Mode and Its Relation to Transfer Dynamics}\footnotetext{Part of this chapter has been published in Xunmo Yang and E.
 R.
-Bittner, The Journal of Chemical Physics \textbf{142}, 244114 (2015)}\label{chap:chapt3}
+Bittner, Computing Intramolecular Charge and Energy Transfer Rates Using Optimal Modes.
+The Journal of Chemical Physics \textbf{142}, 244114 (2015)}\label{chap:chapt3}
 
@@
 
-One of the most important and fundamental processes in chemical  dynamics is
-that of energy and charge transfer between molecular species.  The mechanism
-itself is highly quantum mechanical in nature and involves strong coupling between nuclear and
-electronic degrees of freedom.  The seminal model for the calculation of the transfer rate for this process
-was developed by Marcus in the 1950s \cite{marcus1956theory,marcus1965theory,marcus1993electron}
-\begin{equation}
-k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T},
-\end{equation}
-which relates the Fermi golden-rule transition rate, $k_{Marcus}$
-to the thermodynamic driving force $\Delta G^{o}$ and the reorganization energy $\lambda$.
-One of the most striking predictions of this theory is that as the free energy difference between the final and initial state increases, the transition rate reaches its maximum,
-and further increases in the energy off-set leads to slower transition rates.
-This ``inverted regime''  was confirmed by Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
-nearly 30 yrs later.
-
-Numerous improvements to the Marcus model have been presented over the years and
-a detailed exploration of each is well beyond the scope of this work.
-Aside from the electronic coupling, $V_{ab}$,  the other terms in the expression of rate constant arise from
-a semi-classical approximation to the overlap between the initial vibrational states of the donor and the
-the final  states of the acceptor state. It suffices to say that most of the
-efforts focus upon incorporating more molecular-level detail into the couplings and vibrational modes
-used in computing these terms.
-
-A number of years ago,  we developed a time-convolutionless  master equation approach (TCLME) for computing
-state-to-state rate in which the coupling between  states depends upon the
-nuclear coordinates \cite{pereverzev2006time}. This approach incorporates a fully quantum
-mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
-the Marcus rate equation in the semi-classical limit.  The model itself is parameterized by the
-vibrational normal mode frequencies, the electronic energies, and energy derivatives
-at a reference configuration obtained from {\em ab initio} quantum  chemistry computations.
-The approach has been intensively used and testified by our group to compute state-to-state
-transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
- \cite{tamura2008phonon,tamura2007exciton,singh2009fluorescence,bittner2014noise}.
-Central to our work here is the use of a mode-projection scheme
- % which is similar to the Page-rank algorithm used by internet search engines such as
- % Google and Netflix\cite{brin1998anatomy, page2004method},
- which parses out a
-reduced set of nuclear motions primarily coupled to the quantum transition.
-We refer to the modes identified early in the iterative process as the ``primary Lanczos modes'' or PLMs.
-
-Using the TCLME approach,  we recently investigated
-triplet-triplet excitation energy transfer between a naphthalene donor and a
-benzaldehyde acceptor linked by a variety of bridging units as shown in Fig.~\ref{struct}. \cite{yang2014intramolecular}
-\begin{figure}
-%\includegraphics[width=\columnwidth]{Chapters/chap3/D-B-A-Numbered.pdf}
-\includegraphics[width=\columnwidth]{Chapters/chap3/molecule1.pdf}
-\caption{Molecular structure of naphthalene donor and a
-benzaldehyde acceptor linked by various bridging units. }\label{struct}
-\end{figure}
-Such systems were the basis of a  classic series of experiments by
-Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
-which verified the existence of the Marcus inverted regime.
-In Ref. \cite{yang2014intramolecular} we showed that both
-the autocorrelation function of the electronic coupling operators
-and the total transfer rate constant calculated using TCLME approach with only PLMs provide an
-excellent approximation to the exact correlation functions and rate
-constants computed using all normal modes, as well as to the experimental
-and recent theoretical values for the transfer rates \cite{subotnik2010predicting}.
-
-In this paper we analyze the symmetry of PLMs in model donor-bridge-acceptor systems as projected onto the local
+% One of the most important and fundamental processes in chemical  dynamics is
+% that of energy and charge transfer between molecular species.  The mechanism
+% itself is highly quantum mechanical in nature and involves strong coupling between nuclear and
+% electronic degrees of freedom.  The seminal model for the calculation of the transfer rate for this process
+% was developed by Marcus in the 1950s \cite{marcus1956theory,marcus1965theory,marcus1993electron}
+% \begin{equation}
+% k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T},
+% \end{equation}
+% which relates the Fermi golden-rule transition rate, $k_{Marcus}$
+% to the thermodynamic driving force $\Delta G^{o}$ and the reorganization energy $\lambda$.
+% One of the most striking predictions of this theory is that as the free energy difference between the final and initial state increases, the transition rate reaches its maximum,
+% and further increases in the energy off-set leads to slower transition rates.
+% This ``inverted regime''  was confirmed by Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
+% nearly 30 yrs later.
+
+% Numerous improvements to the Marcus model have been presented over the years and
+% a detailed exploration of each is well beyond the scope of this work.
+% Aside from the electronic coupling, $V_{ab}$,  the other terms in the expression of rate constant arise from
+% a semi-classical approximation to the overlap between the initial vibrational states of the donor and the
+% the final  states of the acceptor state. It suffices to say that most of the
+% efforts focus upon incorporating more molecular-level detail into the couplings and vibrational modes
+% used in computing these terms.
+
+% A number of years ago,  we developed a time-convolutionless  master equation approach (TCLME) for computing
+% state-to-state rate in which the coupling between  states depends upon the
+% nuclear coordinates \cite{pereverzev2006time}. This approach incorporates a fully quantum
+% mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
+% the Marcus rate equation in the semi-classical limit.  The model itself is parameterized by the
+% vibrational normal mode frequencies, the electronic energies, and energy derivatives
+% at a reference configuration obtained from {\em ab initio} quantum  chemistry computations.
+% The approach has been intensively used and testified by our group to compute state-to-state
+% transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
+%  \cite{tamura2008phonon,tamura2007exciton,singh2009fluorescence,bittner2014noise}.
+% Central to our work here is the use of a mode-projection scheme
+%  % which is similar to the Page-rank algorithm used by internet search engines such as
+%  % Google and Netflix\cite{brin1998anatomy, page2004method},
+%  which parses out a
+% reduced set of nuclear motions primarily coupled to the quantum transition.
+% We refer to the modes identified early in the iterative process as the ``primary Lanczos modes'' or PLMs.
+
+% Using the TCLME approach,  we recently investigated
+% triplet-triplet excitation energy transfer between a naphthalene donor and a
+% benzaldehyde acceptor linked by a variety of bridging units as shown in Fig.~\ref{struct}. \cite{yang2014intramolecular}
+% \begin{figure}
+% %\includegraphics[width=\columnwidth]{Chapters/chap3/D-B-A-Numbered.pdf}
+% \includegraphics[width=\columnwidth]{Chapters/chap3/molecule1.pdf}
+% \caption{Molecular structure of naphthalene donor and a
+% benzaldehyde acceptor linked by various bridging units. }\label{struct}
+% \end{figure}
+% Such systems were the basis of a  classic series of experiments by
+% Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
+% which verified the existence of the Marcus inverted regime.
+% In Ref. \cite{yang2014intramolecular} we showed that both
+% the autocorrelation function of the electronic coupling operators
+% and the total transfer rate constant calculated using TCLME approach with only PLMs provide an
+% excellent approximation to the exact correlation functions and rate
+% constants computed using all normal modes, as well as to the experimental
+% and recent theoretical values for the transfer rates \cite{subotnik2010predicting}.
+
+In this chapter we analyze the symmetry of PLMs (see Fig. \ref{LanczosModes_chap2}) in model donor-bridge-acceptor systems as projected onto the local
  vibrational modes of the  donor (benzaldehyde)    and  acceptor (naphthalene) moieties.    By constructing the local modes
@@
 fragment modes,  and normal modes for the entire molecule.
-The structure of this paper is as follows.
-We begin by reviewing the TCLME approach and how one generates the PLMs.  We then
-discuss the symmetry  of PLMs and their relation to a linear coordinate linking the
-initial/donor geometry to the final/acceptor geometry of the molecule.
+% The structure of this paper is as follows. We begin by reviewing the TCLME approach and how one generates the PLMs.
+% Below we discuss the symmetry  of PLMs and their relation to a linear coordinate linking the initial/donor geometry to the final/acceptor geometry of the molecule.
 %---NEED CONCLUDING STATEMENT----
 
-\section{Theoretical Model}
+% \section{Theoretical Model}
 
@@
 
-\subsection{Hamiltonian and Parameterization}
-
-We start with the  generic form for the diabatic Hamiltonian, describing two electronic states coupled with $N$ normal modes:
-\begin{eqnarray}
-H_{dia}=\left(\begin{array}{cc}
-\epsilon_{1} & V_{12}\\
-V_{21} & \epsilon_{2}
-\end{array}\right)
-+\left(\begin{array}{cc}
-{\mathbf g}_{11}&{\mathbf g}_{12} \\
-{\mathbf g}_{21} &{\mathbf g}_{22}
-\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
-\nonumber \\
-\end{eqnarray}
-Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
-reference geometry--typically that of the donor or acceptor state. $V_{ij}$ is the diabatic coupling between them.  The second term represents the
-linear coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
-normal coordinates $\mathbf q$.   The diagonal terms
-give the diabatic displacement forces between the reference geometry and the two states.
-The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
-In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.
-
-If we choose one of the states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish.
+% \subsection{Hamiltonian and Parameterization}
+
+% We start with the  generic form for the diabatic Hamiltonian, describing two electronic states coupled with $N$ normal modes:
+% \begin{eqnarray}
+% H_{dia}=\left(\begin{array}{cc}
+% \epsilon_{1} & V_{12}\\
+% V_{21} & \epsilon_{2}
+% \end{array}\right)
+% +\left(\begin{array}{cc}
+% {\mathbf g}_{11}&{\mathbf g}_{12} \\
+% {\mathbf g}_{21} &{\mathbf g}_{22}
+% \end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
+% \nonumber \\
+% \end{eqnarray}
+% Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
+% reference geometry--typically that of the donor or acceptor state. $V_{ij}$ is the diabatic coupling between them.  The second term represents the
+% linear coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
+% normal coordinates $\mathbf q$.   The diagonal terms
+% give the diabatic displacement forces between the reference geometry and the two states.
+% The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
+% In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.
+
+% If we choose one of the states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish.
 We further assume Condon approximation to neglect $\mathbf g_{12}$ and $\mathbf g_{21}$.
 Now the Hamiltonian is simplified to
-\begin{eqnarray}
-H_{dia}=\left(\begin{array}{cc}
-\epsilon_{1} & V_{12}\\
-V_{21} & \epsilon_{2}
-\end{array}\right)+\left(\begin{array}{cc}
-0 & 0\\
-0 & 1
-\end{array}\right) {\mathbf g}_{22}\cdot{\mathbf q}+H_{osc},
-\end{eqnarray}
-\label{eq:diaHam}
-where $H_{osc}$ is the harmonic oscillator Hamiltonian for the vibrational normal modes.
-
-To calculate transition rate, we transform to adiabatic representation.
+% \begin{eqnarray}
+% H_{dia}=\left(\begin{array}{cc}
+% \epsilon_{1} & V_{12}\\
+% V_{21} & \epsilon_{2}
+% \end{array}\right)+\left(\begin{array}{cc}
+% 0 & 0\\
+% 0 & 1
+% \end{array}\right) {\mathbf g}_{22}\cdot{\mathbf q}+H_{osc},
+% \end{eqnarray}
+% \label{eq:diaHam}
+% where $H_{osc}$ is the harmonic oscillator Hamiltonian for the vibrational normal modes.
+
+% To calculate transition rate, we transform to adiabatic representation.
 It is done via Edmiston-Ruendenberg (ER) localization \cite{subotnik2010predicting} implemented in Q-Chem and the electronic Hamiltonians
-on adiabatic and diabatic basis are related by the mixing angle $\theta$.
-\begin{equation}
-H_{dia,e}=\left(\begin{array}{cc}
-\cos\theta & -\sin\theta\\
-\sin\theta & \cos\theta
-\end{array}\right)\left(\begin{array}{cc}
-\epsilon_{1}  & 0 \\
-0  & \epsilon_{2}
-\end{array}\right)\left(\begin{array}{cc}
-\cos\theta & \sin\theta\\
--\sin\theta & \cos\theta
-\end{array}\right).
-\end{equation}
-The diabatic coupling is then given by
-\begin{eqnarray}
-V_{12}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
-\end{eqnarray}
-The full adiabatic Hamiltonian reads:
-\begin{eqnarray}
-H&=&U^{T}H_{dia}U\nonumber  \\
-&=&\left(\begin{array}{cc}
-E_{1}  & 0 \\
-0 & E_{2}
-\end{array}\right)+\left(\begin{array}{cc}
-\sin^{2}\theta & \frac{1}{2}\sin2\theta\\
-\frac{1}{2}\sin2\theta & \cos^{2}\theta
-\end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
-&+& H_{osc}.\label{eq:locaiHam2}
-\end{eqnarray}
-where the electronic part is in the adiabatic basis with eigenenergies of $E_1$ and $E_2$ at certain reference geometry.
+% on adiabatic and diabatic basis are related by the mixing angle $\theta$.
+% \begin{equation}
+% H_{dia,e}=\left(\begin{array}{cc}
+% \cos\theta & -\sin\theta\\
+% \sin\theta & \cos\theta
+% \end{array}\right)\left(\begin{array}{cc}
+% \epsilon_{1}  & 0 \\
+% 0  & \epsilon_{2}
+% \end{array}\right)\left(\begin{array}{cc}
+% \cos\theta & \sin\theta\\
+% -\sin\theta & \cos\theta
+% \end{array}\right).
+% \end{equation}
+% The diabatic coupling is then given by
+% \begin{eqnarray}
+% V_{12}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
+% \end{eqnarray}
+% The full adiabatic Hamiltonian reads:
+% \begin{eqnarray}
+% H&=&U^{T}H_{dia}U\nonumber  \\
+% &=&\left(\begin{array}{cc}
+% E_{1}  & 0 \\
+% 0 & E_{2}
+% \end{array}\right)+\left(\begin{array}{cc}
+% \sin^{2}\theta & \frac{1}{2}\sin2\theta\\
+% \frac{1}{2}\sin2\theta & \cos^{2}\theta
+% \end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
+% &+& H_{osc}.\label{eq:locaiHam2}
+% \end{eqnarray}
+% where the electronic part is in the adiabatic basis with eigenenergies of $E_1$ and $E_2$ at certain reference geometry.
 The nuclear normal modes are described by $H_{osc}$ whereas $\theta$ is the mixing angle between two states.
-%to describe the coupling between two electronic states, $|1\rangle$ and $|2\rangle$  by a set of nuclear vibrational motionsdescribed by $H_{osc}$.
+% %to describe the coupling between two electronic states, $|1\rangle$ and $|2\rangle$  by a set of nuclear vibrational motionsdescribed by $H_{osc}$.
 The angle $\theta$ gives the mixing angle between diabatic states and $E_1$ and $E_{2}$ are electronic energies computed at the same reference configuration.
 
-To parametrize our Hamiltonian, we assume the diabatic
-are a good approximation to the actual adiabatic potentials.
-This allows us to
-use the gradients of the adiabatic potentials to approximate the diabatic potentials.
-This approximation is  valid when the adiabatic (and diabatic) energy minima
-are far enough away from the crossing points and the mixing angles between the diabatic  and adiabatic
-states is small.
-Thus, all parameters in Eq.~\ref{eq:locaiHam2}  can be  obtained from
-standard  quantum chemical computations.
-As in our previous work, we use the Q-Chem 4.0 package  to obtain the vertical energies
- from single point CI(S) calculations with 6-31G** basis set at a given
-reference geometry.   We then project the energy gradients onto the vibrational normal
-coordinates
-
-Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam2} can be expressed in a time-convolutionless mater equation \cite{pereverzev2006time}.
+% To parametrize our Hamiltonian, we assume the diabatic
+% are a good approximation to the actual adiabatic potentials.
+% This allows us to
+% use the gradients of the adiabatic potentials to approximate the diabatic potentials.
+% This approximation is  valid when the adiabatic (and diabatic) energy minima
+% are far enough away from the crossing points and the mixing angles between the diabatic  and adiabatic
+% states is small.
+% Thus, all parameters in Eq.~\ref{eq:locaiHam2}  can be  obtained from
+% standard  quantum chemical computations.
+% As in our previous work, we use the Q-Chem 4.0 package  to obtain the vertical energies
+%  from single point CI(S) calculations with 6-31G** basis set at a given
+% reference geometry.   We then project the energy gradients onto the vibrational normal
+% coordinates
+
+% Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam2} can be expressed in a time-convolutionless mater equation \cite{pereverzev2006time}.
 The derivation is lengthy so we present it briefly.
 
-\subsection{Transition Rate and Autocorrelation}
-We start from a more general Hamiltonian:
-\begin{eqnarray}
-H=\left(\begin{array}{cc}
-\epsilon_{1} & 0\\
-0 & \epsilon_{2}
-\end{array}\right)+\left(\begin{array}{cc}
-{\mathbf g}_{11}&{\mathbf g}_{12} \\
-{\mathbf g}_{21} &{\mathbf g}_{22}
-\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}
-\nonumber \\
-% \label{ham1}
-\end{eqnarray}
-then perform a polaron transform
-using the unitary transformation \cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
-\begin{eqnarray}
-U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
-n|(a^{\dagger}_i-a_i)}
- \nonumber \\
-&=&
-\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
-% \label{unitary}
-\end{eqnarray}
-under which the transformed Hamiltonian is written in terms of the
-diagonal elements
-\begin{eqnarray} \tilde H_0=U^{-1}H_0U
-=\sum_n\tilde\epsilon_n |n\rangle \langle
-n|+\sum_i\omega_ia^{\dagger}_ia_i,
- \end{eqnarray}
-with  the renormalized electronic energies,
-\begin{eqnarray}
-\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
-\end{eqnarray}
-and off-diagonal terms,
-\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
-a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
-% \label{opm}
-\end{eqnarray}
-% In the transformed (or dressed) picture the electronic transition from state
-% $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
-% normal phonon modes.  Transforming to the interaction representation
-% and performing a trace over the phonons gives the spectral density in
-% terms of the autocorrelation of the electron/phonon coupling
-% operators.
-% \begin{eqnarray}
-% S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
-% \end{eqnarray}
-% where
+% \subsection{Transition Rate and Autocorrelation}
+% We start from a more general Hamiltonian:
+% \begin{eqnarray}
+% H=\left(\begin{array}{cc}
+% \epsilon_{1} & 0\\
+% 0 & \epsilon_{2}
+% \end{array}\right)+\left(\begin{array}{cc}
+% {\mathbf g}_{11}&{\mathbf g}_{12} \\
+% {\mathbf g}_{21} &{\mathbf g}_{22}
+% \end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}
+% \nonumber \\
+% % \label{ham1}
+% \end{eqnarray}
+% then perform a polaron transform
+% using the unitary transformation \cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
+% \begin{eqnarray}
+% U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
+% n|(a^{\dagger}_i-a_i)}
+%  \nonumber \\
+% &=&
+% \sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
+% % \label{unitary}
+% \end{eqnarray}
+% under which the transformed Hamiltonian is written in terms of the
+% diagonal elements
+% \begin{eqnarray} \tilde H_0=U^{-1}H_0U
+% =\sum_n\tilde\epsilon_n |n\rangle \langle
+% n|+\sum_i\omega_ia^{\dagger}_ia_i,
+%  \end{eqnarray}
+% with  the renormalized electronic energies,
+% \begin{eqnarray}
+% \tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
+% \end{eqnarray}
+% and off-diagonal terms,
+% \begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
+% a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
+% % \label{opm}
+% \end{eqnarray}
+% % In the transformed (or dressed) picture the electronic transition from state
+% % $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
+% % normal phonon modes.  Transforming to the interaction representation
+% % and performing a trace over the phonons gives the spectral density in
+% % terms of the autocorrelation of the electron/phonon coupling
+% % operators.
+% % \begin{eqnarray}
+% % S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
+% % \end{eqnarray}
+% % where
+% % $$
+% %C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
+% After lengthy derivation we get the autocorrelation function in the Heisenberg representation
 % $$
-%C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
-After lengthy derivation we get the autocorrelation function in the Heisenberg representation
-$$
-C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
-$$
-where $\langle \cdots \rangle$ denotes a thermal average over the
-vibrational degrees of freedom.
-% The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
-% Ref.~\citenum{pereverzev2006time}.
-Using this approach , the golden-rule rates are given by
-\begin{eqnarray}
-k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
-% \label{gr-expression}
-\end{eqnarray}
-In a practical sense, we take $\tau$ to be some finite time at which the
-autocorrelation function $C(t)$
-has relaxed to zero.
-
-Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
-the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
-For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
-In our previous work we showed that both $C(t)$
-and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
-excellent agreement with the exact quantities computed using  the full set of
-normal modes, as well as the experimental rates,
-when parameterized using accurate quantum chemical data \cite{yang2014intramolecular}.
-
-% Diagonalizing $H$ at a given nuclear configuration  provides the adiabatic potentials for our system, which can be used to approximate the diabatic potentials.
-
-% The linear coupling parameter $ {\mathbf g}_{22}$ defines
+% C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
+% $$
+% where $\langle \cdots \rangle$ denotes a thermal average over the
+% vibrational degrees of freedom.
+% % The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
+% % Ref.~\citenum{pereverzev2006time}.
+% Using this approach , the golden-rule rates are given by
+% \begin{eqnarray}
+% k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
+% % \label{gr-expression}
+% \end{eqnarray}
+% In a practical sense, we take $\tau$ to be some finite time at which the
+% autocorrelation function $C(t)$
+% has relaxed to zero.
+
+% Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
+% the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
+% For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
+% In our previous work we showed that both $C(t)$
+% and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
+% excellent agreement with the exact quantities computed using  the full set of
+% normal modes, as well as the experimental rates,
+% when parameterized using accurate quantum chemical data \cite{yang2014intramolecular}.
+
+% % Diagonalizing $H$ at a given nuclear configuration  provides the adiabatic potentials for our system, which can be used to approximate the diabatic potentials.
+
+% % The linear coupling parameter $ {\mathbf g}_{22}$ defines
+% % a force
+% % along a vector connecting the
+% % the initial and final equilibrium geometries of the molecule.
+% % This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
+% % using the ER localization
+% % scheme to approximate the donor and acceptor states.
+% % By analyzing this force we can gain the insight into the dynamics of the transition as well as
+% % open an avenue for developing improved approximations for transition rates.
+% % In our previous work \cite{yang2014intramolecular},  we presented a Lanczos-base ranking algorithm that project
+% % out a series of nuclear displacements that are most important for
+% % the transition.   We refer to the highest-ranked mode identified by the algorithm
+% % as the ``primary Lanczos mode'' (PLM).
+
+% % \subsection{Computing spectral densities and transition rates}
+
+% % Once a suitable set of parameters and vibrational modes  have been determined,
+
+% \subsection{Constructing Primary Lanczos Modes}
+% The linear coupling parameter $ {\mathbf g}_{22}$ in Eq.~\ref{eq:locaiHam2} defines
 % a force
-% along a vector connecting the
+% along a vector connecting
 % the initial and final equilibrium geometries of the molecule.
@@
 % as the ``primary Lanczos mode'' (PLM).
-
-% \subsection{Computing spectral densities and transition rates}
-
-% Once a suitable set of parameters and vibrational modes  have been determined,
-
-\subsection{Constructing Primary Lanczos Modes}
-The linear coupling parameter $ {\mathbf g}_{22}$ in Eq.~\ref{eq:locaiHam2} defines
-a force
-along a vector connecting
-the initial and final equilibrium geometries of the molecule.
-This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
-using the ER localization
-scheme to approximate the donor and acceptor states.
-By analyzing this force we can gain the insight into the dynamics of the transition as well as
-open an avenue for developing improved approximations for transition rates.
-In our previous work \cite{yang2014intramolecular},  we presented a Lanczos-base ranking algorithm that project
-out a series of nuclear displacements that are most important for
-the transition.   We refer to the highest-ranked mode identified by the algorithm
-as the ``primary Lanczos mode'' (PLM).
-The process of finding the PLMs is initiated by defining the vector ${\mathbf v}_{1} = {\mathbf g}_{22}$.
-At each step indexed by $k$,  we define a projection operator
-\begin{eqnarray}
-{\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
-\end{eqnarray}
-and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
-We also construct
-\begin{eqnarray}
-\mathbf p = \sum_{k} \mathbf P_{k}
-\end{eqnarray}
-as  the total projection operator for all ${k} \le N$ modes.
-We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
-\begin{eqnarray}
-\mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
-\end{eqnarray}
-and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
-respectively.  $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
-The first set of these  will have a single
-non-trivial eigenvalue and the second set
-will have $N-k$ non-trivial eigenvalues. We then collect the non-trivial eigenvectors associated with each
-to form the orthogonal transformation matrix
-\begin{eqnarray}
-{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
-\end{eqnarray}
-and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
- At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
-$k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
-a diagonal submatrix in the lower-right.
-
-\begin{figure*}[t]
-\subfloat[c-1,4ee]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1a.pdf}}\\
-\subfloat[d-2,6ae]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1b.pdf}}
-\caption{
-Primary Lanczos modes for (a) c-1,4ee and (b) d-2,6ae projected onto the atomic displacement coordinates.  The frequencies
-for both these are at 0.185 eV (1490 cm$^{-1}$), a typical $C=C$ stretching frequency for arene systems.
-}\label{LanczosModes}
-\end{figure*}
-
-In Fig.~\ref{LanczosModes}  we show the PLMs for the
-intramolecular triplet energy transfer within
-two representative donor-bridge-acceptor molecules from our study, termed c-1,4ee and d-2,6ae.
-In both cases, triplet energy is transferred from a benzaldehyde (BZ) donor group to a naphthyl- acceptor group.
-Several observations can be made from Fig.~\ref{LanczosModes} concerning the primary Lanczos modes for these
-donor-bridge-acceptor systems. First, there is negligible contribution from the bridging unit.
-This is not surprising since the transitions involve  electronic energy
- transfer between $\pi$-orbitals localized on the donor and acceptor moieties.
- Since the bridges in these cases
-are not conjugated, there is very weak electronic coupling between the D/A groups and the bridge itself.
-Hence, to a good approximation, the electronic
-contribution from the bridge can be effectively ignored, it simply serves to hold the donor and acceptor in fixed relative positions.
-Secondly, the displacement vectors on donor and acceptor moieties are very much akin to  totally symmetric normal modes
-of the corresponding moieties, and do not correspond any single normal vibrational  mode of the whole molecule.
-
-In the next two Sections, we explore the role of symmetry in detail.
+% The process of finding the PLMs is initiated by defining the vector ${\mathbf v}_{1} = {\mathbf g}_{22}$.
+% At each step indexed by $k$,  we define a projection operator
+% \begin{eqnarray}
+% {\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
+% \end{eqnarray}
+% and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
+% We also construct
+% \begin{eqnarray}
+% \mathbf p = \sum_{k} \mathbf P_{k}
+% \end{eqnarray}
+% as  the total projection operator for all ${k} \le N$ modes.
+% We then project the Hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
+% \begin{eqnarray}
+% \mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
+% \end{eqnarray}
+% and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
+% respectively.  $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
+% The first set of these  will have a single
+% non-trivial eigenvalue and the second set
+% will have $N-k$ non-trivial eigenvalues. We then collect the non-trivial eigenvectors associated with each
+% to form the orthogonal transformation matrix
+% \begin{eqnarray}
+% {\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
+% \end{eqnarray}
+% and again transform the full Hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
+%  At each step in the iteration, the transformed Hessian, $\mathbf\Omega'$ is in the form of a
+% $k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
+% a diagonal submatrix in the lower-right.
+
+% \begin{figure*}[t]
+% \subfloat[c-1,4ee]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1a.pdf}}\\
+% \subfloat[d-2,6ae]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1b.pdf}}
+% \caption{
+% Primary Lanczos modes for (a) c-1,4ee and (b) d-2,6ae projected onto the atomic displacement coordinates.  The frequencies
+% for both these are at 0.185 eV (1490 cm$^{-1}$), a typical $C=C$ stretching frequency for arene systems.
+% }\label{LanczosModes}
+% \end{figure*}
+
+% In Fig.~\ref{LanczosModes_chap2}  we show the PLMs for the
+% intramolecular triplet energy transfer within
+% two representative donor-bridge-acceptor molecules from our study, termed c-1,4ee and d-2,6ae.
+% In both cases, triplet energy is transferred from a benzaldehyde (BZ) donor group to a naphthyl- acceptor group.
+% Several observations can be made from Fig.~\ref{LanczosModes_chap2} concerning the primary Lanczos modes for these
+% donor-bridge-acceptor systems. First, there is negligible contribution from the bridging unit.
+% This is not surprising since the transitions involve  electronic energy
+%  transfer between $\pi$-orbitals localized on the donor and acceptor moieties.
+%  Since the bridges in these cases
+% are not conjugated, there is very weak electronic coupling between the D/A groups and the bridge itself.
+% Hence, to a good approximation, the electronic
+% contribution from the bridge can be effectively ignored, it simply serves to hold the donor and acceptor in fixed relative positions.
+% Secondly, the displacement vectors on donor and acceptor moieties are very much akin to  totally symmetric normal modes
+% of the corresponding moieties, and do not correspond any single normal vibrational  mode of the whole molecule.
+
+In the next two sections, we discuss the symmetry  of PLMs and their relation to a linear coordinate linking the initial/donor geometry to the final/acceptor geometry of the molecule.
 We first project the PLMs onto the normal modes of both the donor or acceptor moieties
@@
 
-Fig.~\ref{fragProj} shows the projection of the PLMs  onto the local vibrational modes of
-D/A moieties in molecules of c-1,4ee and d-2,6ae.
+Fig.~\ref{fragProj} shows the projection of the PLMs  onto the normal modes of
+donor and acceptor moieties in molecules of c-1,4ee and d-2,6ae, respectively.
 In each case, we label the dominant contributions by the
-irreducible representation (IR) of the moiety. The normal mode basis is generated as follows:
-first, we take the geometry of donor or acceptor moiety and add  the necessary hydrogens.
-Then the $D_{2h}$ symmetry is applied to naphthalene using GaussView 5.
-The benzaldehyde moiety is unchanged because it has very low  symmetry:  $C_{s}$ if planar and $C_{1}$  other wise.
+irreducible representations (IR) of the moiety.
+There are 4 sets of normal modes used as basis in projections.
+Two are the normal modes of benzaldehyde and two of naphthalene.
+They are generated as follows: first, we take the  coordinates of benzaldehyde  and naphthalene from the equilibrium geometry of c-1,4ee and d-2,6ae, and add necessary hydrogens.
+In theory, naphthalene has $D_{2h}$ symmetry.
+However, by taking coordinates directly from the D-B-A molecules, the geometry of naphthalene is distorted slightly by the bridge and acceptor moieties, and its point group reduces to $C_{1}$.
+We want the naphthalene to have high symmetry, so we can use the irreducible representations of $D_{2h}$ to classify its normal modes.
+As the result, we use GaussView 5 to enforce $D_{2h}$ symmetry on naphthalene.
+For  benzaldehyde, we leave  the coordinates unchanged, as there is no obvious way to increase the symmetry for benzaldehyde.
+Finally we run frequency computations for all 4 sets of coordinates.
+% The normal mode basis is generated as follows:
+% first, we take the geometry of donor or acceptor moiety and add  the necessary hydrogens.
+% Then the $D_{2h}$ symmetry is applied to naphthalene using GaussView 5.
+% The benzaldehyde moiety is unchanged because it has very low  symmetry:  $C_{s}$ if planar and $C_{1}$  otherwise.
 
@@
 $$
-where $\overrightarrow{M_{i}}$ is the displacement vector of the $i$th normal mode.
-The symmetrization of naphthalene introduces another problem
-in that the projection depends on the orientation of the basis vectors.
-Thus, we orient the original and symmetrized frames by first aligning the center of masses
+where $\overrightarrow{M_{i}}$ is the displacement vector of the $i$th normal mode, and $\overrightarrow{PLM}$ is the displacement vector of the PLM on the corresponding moiety.
+For example, for naphthalene, the $\overrightarrow{PLM}$ are the vectors in Fig.
+\ref{LanczosModes_chap2}, with only the atoms of naphthalene kept.
+The symmetrization of naphthalene introduces a subtle problem.
+The $\overrightarrow{PLM}$  is based on the distorted geometry of naphthalene in the D-B-A molecule, while $\overrightarrow{M_{i}}$ is computed on the geometry of symmetrized naphthalene.
+Two geometries differ slightly, so $\left\langle \overrightarrow{M_{i}}|\overrightarrow{PLM}\right\rangle$ depends on how we orient them.
+We choose to orient the original and symmetrized frames by first aligning the center of masses
 and then minimize the RMS displacement between atoms.
-Analyzing the projections it becomes clear that in all cases, the dominant components
+This is arbitrary.
+Fortunately, two geometries are really similar, so we expect the choice of orientation, as long as it is not ridiculous, is acceptable.
+By analyzing the projections it becomes clear that in all cases, the dominant components
 belong to totally symmetric $A_{g}$ or $A_1$ irreducible representations,  in agreement
-with the intuitive observations from Fig.~\ref{LanczosModes}.
+with the intuitive observations from Fig.~\ref{LanczosModes_chap2}.
 
 This behavior is not unique for the napthyl-bridge-benzaldehyde  system.
-To see this, we repeated the analysis using various acceptor groups as shown in Fig.~\ref{benz}.
-together with their PLMs and correlation functions for different numbers of projected modes.
+To see this, we repeated the analysis by replacing naphthalene with various acceptor groups, as shown in Fig.~\ref{benz}. Fig.~\ref{benz} also shows the corresponding PLMs and correlation functions.
 % and d-2,6ae and compute the
@@
 %PLMs.  Fig.~\ref{benz} shows the correlation functions and PLMs for  two phenyl-[bridge]-BZ
-For both molecules,  with 4 projected modes or more, the excellent agreement with exact (all modes) result out to 10 fs indicates that
+For both molecules,  4 projected modes are enough to reproduce the exact (all modes) correlation function up to 10 fs. It indicates that
 the projection scheme provides an accurate description of the electronic coupling in  these cases as well.
 %Moreover, the PLMs in each case are similar to the PLMs in the napthyl-[bridge]-BZ
-Moreover, the PLMs are qualitatively similar to the PLM of unchanged c-1,4ee.
-The displacements on the benzaldehyde moiety are almost identical, while on the phenyl and anthracene moieties they belong to totally symmetric irreducible representations as well.
+Moreover, the PLMs in Fig.~\ref{benz} are qualitatively similar to those in Fig.~\ref{LanczosModes_chap2}, where the acceptor is naphthalene.
+The displacements vectors on the benzaldehyde moiety in all 4 molecules are almost identical, and  the displacements vectors on the naphthalene, phenyl and anthracene moieties all belong to totally symmetric irreducible representations.
 
@@
 This connection can be understood by analyzing the corresponding  the changes in the electron density that accompany the transition.
-For example, the PLM on the naphthalene part shown in  Fig.~\ref{LanczosModes}
+For example, the PLM on the naphthalene part shown in  Fig.~\ref{LanczosModes_chap2}
 largely corresponds to a symmetric ring-stretching mode,  involving carbons
@@
 \begin{figure*}[!h]
-\subfloat[]{\includegraphics[width=0.87\columnwidth]{Chapters/chap3/Figure5a.pdf}}\\
-\subfloat[]{\includegraphics[width=0.87\columnwidth]{Chapters/chap3/Figure5b.pdf}}
+\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure5a.pdf}}\\
+\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure5b.pdf}}
 \caption{Projections of the PLM onto the normal modes of (a) c-1,4ee and (b) d-2,6ae.\label{LancProj}}
@@
 
-One may argue that bridge is not included in our comparison.
-As showed in Fig.~\ref{LanczosModes}, one can see that very few motions involving the bridge contribute to the PLM.
-Thus, that we anticipate that we can construct the PLM using only local modes on the donor and acceptor units.
+% One may argue that bridge is not included in our comparison.
+We do not include the bridge in the projections, because as showed in Fig.~\ref{LanczosModes_chap2}, very few motions involving the bridge contribute to the PLM.
+Thus, we anticipate that we can construct the PLM using only local modes on the donor and acceptor units.
  In the next section, we  quantitatively verify this by using only
@@
 By breaking down geometry change, we get the insight that the entire process consists of two steps, the fast excitation transfer facilitated by PLM and the relaxation after that.
-%Looking at the symmetry of PLM in Fig.~\ref{LanczosModes}, especially the naphthalene, it is basically the stretch of four bonds being symmetric to each other.
+%Looking at the symmetry of PLM in Fig.~\ref{LanczosModes_chap2}, especially the naphthalene, it is basically the stretch of four bonds being symmetric to each other.
 Comparing the bonding and antibonding in the HOMO/LUMO of naphthalene in Fig.~\ref{naphHOMOLUMO}, we noticed that these four bonds change lengths dramatically in deexcitation, so does PLM correspond to geometry change?

### 2016-04-12 Chapters/chap4/chap4.tex
Gonna give it to the committee

@@
 
-Electron transfer (ET) is one of the most important and fundamental processes in chemistry. Its mechanism
- is highly quantum mechanical in nature.
+% Electron transfer (ET) is one of the most important and fundamental processes in chemistry. Its mechanism
+%  is highly quantum mechanical in nature.
 ET is often mediated by nuclear-electronic (vibronic) interactions, especially in donor-bridge-acceptor system \cite{ulstrup1975effect,schrauben2010vibrational,davis2009effect,devault1980quantum,gray1996electron,lewis2002donor,bressler2009femtosecond,shih2008tryptophan,repp2010coherent,halpin2014two}.
@@
 Nevertheless, due to the ultra-fast intramolecular vibrational redistribution, it is challenging to experimentally manipulate photo-induced reactions in the condensed phase.
-Recently, the Weinstein group reported upon a series of molecules, whose ET pathways can be radically changed - even completely closed - by infrared light excitation of intramolecular vibrations \cite{delor2014toward,delor2015mechanism,scattergood2014electron}.
-The experiment is reviewed in next section.
+In previous chapters, we have benchmarked our approach against  a well-known set of test cases. In this chapter we want to apply the method to an entirely new molecule.
+ Recently, the Weinstein group at University of Sheffield reported upon a series of molecules, whose electron transfer (ET) pathways can be radically changed - even completely closed - by infrared light excitation of intramolecular vibrations \cite{delor2014toward,delor2015mechanism,scattergood2014electron}.
+The molecules are shown in Fig.
+\ref{JuliaStruct}.
+They are much larger than the molecules in previous chapters.
+Also, they contain heavy atoms, Pt, which makes the computation more difficult.
+Nevertheless, there is no difficulty in principle preventing us from applying our method to these molecules.
+They seem to be good candidates to further test our model.
+% Here we apply our approach to the molecules studied by Weinstein {\em et al.}.
 
-The pioneering model for the computation of ET rate was developed by Marcus in the 1950s \cite{marcus1956theory,marcus1965theory,marcus1993electron}
-\begin{equation}
-k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T},
-\end{equation}
-which relates the Fermi golden-rule transition rate, $k_{Marcus}$
-to the thermodynamic driving force $\Delta G^{o}$ and the reorganization energy $\lambda$.
+In this chapter, we first briefly review their experiment results and the theory of our approach. Then we compare  rate constants and mode that significantly affects dynamics.
+
+% The pioneering model for the computation of ET rate was developed by Marcus in the 1950s \cite{marcus1956theory,marcus1965theory,marcus1993electron}
+% \begin{equation}
+% k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T},
+% \end{equation}
+% which relates the Fermi golden-rule transition rate, $k_{Marcus}$
+% to the thermodynamic driving force $\Delta G^{o}$ and the reorganization energy $\lambda$.
 Our group developed a time-convolutionless  master equation (TCLME) for computing state-to-state rate in which vibronic coupling is explicitly considered \cite{pereverzev2006time}.
 This approach incorporates a fully quantum
-mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
-the Marcus rate equation in the semi-classical limit.  All parameters necessary in the model can be obtained from {\em ab initio} quantum  chemistry computations.
-The approach has been benchmarked and used for many systems, ranging from organic photovoltaics to the molecules in Closs' classical experiments \cite{tamura2008phonon,tamura2007exciton,singh2009fluorescence,bittner2014noise,yang2014intramolecular,yang2015computing}.
+% mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
+% the Marcus rate equation in the semi-classical limit.  All parameters necessary in the model can be obtained from {\em ab initio} quantum  chemistry computations.
+% The approach has been benchmarked and used for many systems, ranging from organic photovoltaics to the molecules in Closs' classical experiments \cite{tamura2008phonon,tamura2007exciton,singh2009fluorescence,bittner2014noise,yang2014intramolecular,yang2015computing}.
 Besides the computation of transfer rate constant, our method includes a  mode-projection scheme, which can parse out a hierarchy of nuclear motions primarily coupled to the transition.
 The most important vibrational motion is termed ``primary mode'' or ``Lanczos mode'' in our previous work, as Lanczos algorithm is employed in the projection \cite{yang2014intramolecular,yang2015computing}.
-
-Here we apply our approach to the molecules studied by Weinstein {\em et al.}.
-We first briefly review their experiment results and the theory of our approach.
-Then we compare  rate constants and mode that significantly affects dynamics.
 
@@
 
-All three molecules undergo similar ET processes, as illustrated in Fig.
+All three molecules undergo similar ET processes after excitation, as illustrated in Fig.
 \ref{JuliaStruct}(b) and Fig.
 \ref{ETscheme}.
-After excited by a UV pump, molecules are excited to the triplet charge transfer (CT) manifold stemming from electron transfer from the Pt-acetylide center to the NAP acceptor.
-The transfered charge can undergo further separation to form the full charge-separated state (CSS), or recombine to form a localized excitation, \textsuperscript{3}NAP, both eventually decay to ground state.
-Weinstein {\em et al.} showed that if a judiciously chosen IR pump is applied to excite the C$\equiv$C bond after the initial excitation, the yield of intermediate states can be radically changed.
-For PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can even be completely switched off.
+Following UV excitation, molecules first jump to the triplet charge transfer (CT) manifold stemming from electron transfer from the Pt-acetylide center to the NAP acceptor.
+The transfered charge can undergo either further separation to form the full charge-separated state (CSS), or recombine to form a localized excitation, \textsuperscript{3}NAP.
+Both eventually decay to ground state.
+Weinstein {\em et al.} showed that if a judiciously chosen IR pump is applied to excite the C$\equiv$C bond after the initial UV excitation, the yield of intermediate states can be radically changed.
+Foe example, when a IR pump with frequency = 1,940 $cm^{-1}$ is applied to excite the C$\equiv$C in PTZ-CH\textsubscript{2}-Pt-NAP, 1 ps after the UV pump, the yield of the CSS state decrease from 32\% to 15\%, while that of the \textsuperscript{3}NAP increases from 29\% to 46\%.
+The most striking observation is that when a 1,908 $cm^{-1}$ IR pulse is applied to PTZ-CH\textsubscript{2}-Pt-NAP 2 ps after UV excitation, the CT $\rightarrow$ CSS step is completely switched off, as illustrated in Fig.~\ref{ETscheme}.
 
@@
 \textbf{b}.
-Energy level diagrams for the ET process, with the free energy driving force of charge separation ($\Delta$G) indicated.
+Energy level diagrams for the ET process, with the lifetimes and the driving force ($\Delta$G) of CT $\rightarrow$ CSS transfer  indicated.
 Adapted with permission from Ref.~\cite{delor2015mechanism}.\label{JuliaStruct}}
@@
 
-Three molecules also show differences due to their different donor moieties.
-Addition of the saturated CH\textsubscript{2} spacer from PTZ-Pt-NAP to PTZ-CH\textsubscript{2}-Pt-NAP slows down both charge separation and recombination by a factor of \textasciitilde 5 (the lifetime of CT increases from 3.3 to 14 ps and CSS from 190 ps to 1 ns), while the yield of the CSS decreases from 32 to 10\%.
-Furthermore, the CSS can decay to \textsuperscript{3}NAP in PTZ-Pt-NAP, while this path does not exist in PTZ-CH\textsubscript{2}-Pt-NAP.
-By appending methoxy groups to the PTZ in OMe-PTZ-Pt-NAP, the donor strength is increased, and it further accelerates reaction.
-The lifetime of CT is reduced to 1 ps.
+The molecules show different changes in yield because of the different donors.
+From PTZ-CH\textsubscript{2}-Pt-NAP to PTZ-Pt-NAP, to OMe-PTZ-Pt-NAP, the donor strength increases, which enlarges the energy gap between CT and CSS states, as sketched in Fig.~\ref{JuliaStruct}.
+The driving force ($\Delta$G) of CT $\rightarrow$ CSS transfer increases from 0.2 $eV$ in PTZ-CH\textsubscript{2}-Pt-NAP, to 0.4 $eV$ in PTZ-Pt-NAP, to 0.6 $eV$ in OMe-PTZ-Pt-NAP.
+Large $\Delta$G accelerates the CT decay and hence decreases the lifetime of CT state.
+Comparing  PTZ-Pt-NAP and PTZ-CH\textsubscript{2}-Pt-NAP, CT transfer to both charge separation and recombination slows down by a factor of \textasciitilde 5 (the lifetime of CT increases from 3.3 to 14 ps and CSS from 190 ps to 1 ns).
+By appending methoxy groups to the PTZ, the donor strength is increased, and reaction is accelerated.
+As the result, the lifetime of CT in OMe-PTZ-Pt-NAP is further reduced to 1 ps.
 
-Weinstein propose the effect of infrared control relies on the distance between CT energy minimum and the intersection of CT and CSS potential energy surfaces.
+Weinstein proposes the effect of infrared control is caused by the fact that the distance between CT energy minimum and the intersection of CT and CSS potential energy surfaces is small.
 For all three molecules, two PESs intersect where C$\equiv$C bond is slightly longer than the equilibrium length.
@@
 If the energy gap between intersection and equilibrium geometry is much larger than C$\equiv$C vibrational energy, the dynamics is barely affected; if the energy gap is small, the vibrational excitation can radically change the dynamics.
-It agrees to that PTZ-CH\textsubscript{2}-Pt-NAP has the smallest energy gap in theoretical calculations, as illustrated in Fig.
-\ref{PTZparabolas}.
+% It agrees to that PTZ-CH\textsubscript{2}-Pt-NAP has the smallest energy gap in theoretical calculations, as illustrated in Fig. \ref{PTZparabolas}.
+Fig.
+\ref{PTZparabolas} shows the calculated PESs along the NAP side C$\equiv$C coordinate in the ground state geometries.
+Several observations can be drawn.
+First, they are quite parabolic, which suggest the parabolic assumption in our approach probably holds.
+Second, the geometry at the intersection of CT and CSS potential energy surfaces have  longer C$\equiv$C bond than the equilibrium geometry.
+Third, PTZ-CH\textsubscript{2}-Pt-NAP has the smallest energy difference between the intersection and the equilibrium geometry, agreeing to the explanation above.
 
@@
 % \label{sec:theoretical_model}
-The theoretical model is almost same to that presented in Section \ref{section:theory}.
-There is only one difference.
+% The theoretical model is almost same to that presented in Section \ref{section:theory}. There is only one difference.
 In previous chapters, the diabatic coupling $V_{ab}$ in Eq.
@@
 ER localization can be seen as a extension of GMH which overcomes some drawbacks of GMH \cite{subotnik2009initial}.
-This time we do the optimization and frequency calculation in Gaussian 09 \cite{g09}, which does not support ER diabatization, so we turn to GMH.
-The molecule presented here is quite linear, and its charge centers are in the linear C$\equiv$C axis.
-As the result, GMH and ER localization approaches are supposed to give similar results.
+This time we obtain the  frequency and optimized geometry from Weinstein group.
+They do the computation in Gaussian 09 \cite{g09}, which does not support ER diabatization.
+Considering a typical calculation of such molecule takes months of CPU effort, we do not try to recompute it in Q-Chem.
+Instead, we turn to GMH.
+Fortunately, the molecule presented here is quite linear, and its charge centers are in the linear C$\equiv$C axis.
+As the result, GMH and ER localization approaches are expected to give similar results.
 The diabatic coupling given by GMH is
@@
 
-The molecules were optimized using DFT for ground state and TD-DFT for excited states, with the B3LYP functional, in Gaussian 09.
-To save computing resource, the molecules were simplified.
-The P(Bu)\textsubscript{3} moieties and octyl chain of NAP were simplified to PH\textsubscript{3} and a methyl group, respectively.
-In all calculations, SDD pseudo potential and solvent model were used (see Appendix.~\ref{sec:T1input} for the details of parameters).
-The transition dipole moments were calculated using Multiwfn 3.3.8 \cite{lu2012multiwfn}.
+The molecules were optimized using DFT for ground state and TD-DFT for excited states
+% , with the B3LYP functional,
+in Gaussian 09.
+The molecules are simplified to speed up the  computations.
+The P(Bu)\textsubscript{3} moieties and octyl chain of NAP are simplified to PH\textsubscript{3} and a methyl group, respectively.
+In all calculations, SDD pseudo potential and solvent model are used (see Appendix.~\ref{sec:T1input} for the details of parameters).
+The transition dipole moments and electron/hole distributions surfaces are calculated using Multiwfn 3.3.8 \cite{lu2012multiwfn}.
 
@@
 The computation of other two molecules are in progress.
-A typical calculation takes several months.
-We optimized and got two states of PTZ-Pt-NAP, the \textsuperscript{3}NAP and the lowest CT state.
-For transitions involving the CT state, we use parameters obtained at CT state geometry, and similar for \textsuperscript{3}NAP involved transitions.
-Obviously, we get two ways to calculate the CT $\rightarrow$ \textsuperscript{3}NAP transition, either geometry can be used.
+We optimize and get two states of PTZ-Pt-NAP, the \textsuperscript{3}NAP and the lowest CT state.
+The energy diagram is sketched in Fig.
+\ref{ene_diagram}, together with the electron/hole distribution plots.
+At both \textsuperscript{3}NAP or CT state geometries, the lowest state is the \textsuperscript{3}NAP, and there are two CT states above the CSS state.
+We can use parameters obtained at CT state geometry to compute transitions involving the CT state, and  for \textsuperscript{3}NAP involved transitions, we use  \textsuperscript{3}NAP geometry.
+Obviously, for the CT $\rightarrow$ \textsuperscript{3}NAP transition, we can use either geometry of CT or \textsuperscript{3}NAP.
+
+% \begin{figure}[!ht]
+%   \begin{adjustbox}{addcode={\begin{minipage}{1.5\columnwidth}}{\caption{%
+%      The energy diagram of triplet states at \textsuperscript{3}NAP and CT state geometries.
+The electron/hole distribution are shown as well (green for electron, blue for hole).
+The arrows indicate the transitions we calculate.
+%       }\end{minipage}},rotate=90,center}
+%       \includegraphics[width=2\columnwidth]{Chapters/chap4/Images/energy_diagram.pdf}%
+%   \end{adjustbox}
+% \end{figure}
+
+\begin{figure}[!t]
+\includegraphics[width=\columnwidth]{Chapters/chap4/Images/energy_diagram.pdf}
+\caption{The energy diagram of triplet states at \textsuperscript{3}NAP and CT state geometries.
+The electron/hole distribution are shown as well (green for electron, blue for hole).
+The arrows indicate the transitions we calculate.
+}\label{ene_diagram}
+\end{figure}
+
 The comparison between theoretical and experimental rate constants is summarized in Fig.
 \ref{rateComp}.
-The rate constants calculated with all normal modes at two different geometries for the CT $\rightarrow$ \textsuperscript{3}NAP transition do not agree to each other.
+We calculate several sets of theoretical rates.
+First, we calculate the Marcus theory rates (Eq.
+\ref{eq:marcus}).
+At the CT geometry, we get good agreement.
+However, at the \textsuperscript{3}NAP geometry, the results are very poor.
+Second, we calculate the TCLME rates (Eq.
+\ref{gr-expression}).
+The results are still not satisfactory for the \textsuperscript{3}NAP geometry.
+Nevertheless, TCLME is better than Marcus theory in all cases.
+We also calculate the TCLME rates with only the primary mode used.
+Still, they agree to the exact TCLME rates better at the CT geometry.
+
+The failure of the \textsuperscript{3}NAP geometry is especially obvious when we look at the CT $\rightarrow$ \textsuperscript{3}NAP transition.
+For this transition, we can calculate at either geometry.
+The TCLME rate constants at two geometries do not agree to each other.
 The results based on the CT geometry are in the same magnitude with experimental values, and the corresponding primary mode rates are similar to the exact ones.
 While the \textsuperscript{3}NAP geometry performs poorly.
-We suppose the fail of Condon approximation partially contribute to the error, and corresponding correction may improve the results, as discussed later.
+In Section \ref{sec:condon}, we illustrate that the error is, at least partially, caused by the break down of Condon approximation, and according corrections may improve the results.
 
@@
 \cite{delor2015mechanism}.
-The ``exact'' rates are calculated using all normal modes, while the ``primary mode rate'' only use the first mode in projection scheme.
-The ``using mean $V_{12}$'' uses the average diabatic coupling along the interpolation coordinate instead of the diabatic coupling at a certain geometry.
+The ``Marcus'' rates are calculated using Marcus theory with the diabatic couplings at according geometries.
+The ``Marcus (mean V)'' rates are calculated using mean diabatic couplings along the interpolated coordinate in Fig.
+\ref{interCondon}.
+Similarly, the ``TCLME'' and ``TCLME (mean V)'' rates are calculated using the TCLME approach, with all normal modes used.
+The ``PLM'' rates are calculated using only the primary mode.
+Our approach performs better than Marcus theory.
 The CT geometry gives good ``exact'' results, its primary mode rates also agree well.
@@
 Projection of primary mode of (a) CSS $\rightarrow$ \textsuperscript{3}NAP, (b) CT $\rightarrow$ \textsuperscript{3}NAP calculated at \textsuperscript{3}NAP geometry onto the normal modes of \textsuperscript{3}NAP.
-Embedded molecule shows the atomic displacement vectors of primary mode.}\label{projT1}
+Embedded molecule shows the atomic displacement vectors of primary mode.
+If we focus on the C$\equiv$C bonds, PLMs are like
+PTZ-Ph-C$\equiv$C-Pt-C$\protect\overset{\longleftrightarrow}{\equiv}$C-NAP
+in (a) and
+PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\longrightarrow}{C}\equiv\protect\overset{\longleftarrow}{C}$-NAP
+in (b).}\label{projT1}
 \end{figure}
@@
 Embedded molecule shows the atomic displacement vectors of primary mode.
+If we focus on the C$\equiv$C bonds, PLMs are like
+PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\rightarrow}{C}\equiv\protect\overset{\leftarrow}{C}$-NAP
+in (a) and
+PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\leftarrow}{C}\equiv\protect\overset{\rightarrow}{C}$-NAP
+in (b).
 }\label{projT3}
@@
 \subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t3_175.jpg}}
-\caption{From top to bottom: the 174th, 175th mode of \textsuperscript{3}NAP state, the 174th, 175th mode of CT state. For clarity, bonds are not shown.
+\caption{From top to bottom: the displacement vectors of the 174th, 175th mode of \textsuperscript{3}NAP state, the 174th, 175th mode of CT state.
+For clarity, bonds are not shown.
+They are all the stretching modes of single C$\equiv$C bond, look like
+PTZ-Ph-C$\equiv$C-Pt-C$\protect\overset{\longleftrightarrow}{\equiv}$C-NAP in (a) and (c),
+PTZ-Ph-C$\protect\overset{\longleftrightarrow}{\equiv}$C-Pt-C$\equiv$C-NAP in (b) and (d).
 }\label{NMT1T3}
@@
 
-\subsection{Condon Approximation}
+\subsection{Condon Approximation}\label{sec:condon}
 
@@
 Parabolic assumption assumes potential energy surface (PES) is parabolic.
-For this molecule, parabolic assumption is probably true, as the PES has been shown to be parabolic along C$\equiv$C bond \cite{delor2014toward,delor2015mechanism}.
+For this molecule, parabolic assumption is probably true, as the PES has been shown to be parabolic along C$\equiv$C bond in Fig.
+\ref{PTZparabolas}.
 Condon approximation states that diabatic coupling is independent of nuclear coordinates, i.e., does not change when geometry changes.
@@
 The new rate constants are illustrated in Fig.
-\ref{rateComp}, as ``using mean $V_{12}$''.
-The most poorly computed rate, that of CSS $\rightarrow$ \textsuperscript{3}NAP, is significantly improved, and the other \textsuperscript{3}NAP based calculation, namely, the rate of CT $\rightarrow$ \textsuperscript{3}NAP, is slightly improved.
+\ref{rateComp}, as ``with mean V''.
+The correction brings significant improvements, to both the Marcus and TCLME approaches, at the \textsuperscript{3}NAP geometry, especially for the most poorly computed  CSS $\rightarrow$ \textsuperscript{3}NAP transfer.
 
@@
 \includegraphics[width=\columnwidth]{Chapters/chap4/Images/interpolation.pdf}
-\caption{Diabatic coupling values along interpolation coordination. State 0 and 10 stand for the \textsuperscript{3}NAP and the CT state, respectively.\label{interCondon}}
+\caption{Diabatic coupling values along the interpolation from the \textsuperscript{3}NAP $\rightarrow$ CT geometries.
+State 0 and 10 stand for the \textsuperscript{3}NAP and the CT state, respectively.\label{interCondon}}
 \end{figure*}
@@
 
-However, interestingly, the results at CT geometry get worse.
+However, the results at CT geometry get worse, especially for Marcus theory.
 For the CT $\rightarrow$  CSS reaction, the average diabatic coupling is so unreasonable that Eq.
@@
 We change the ER diabatization to the GMH approach and apply the model to a much more complex system.
-Certain success is achieved, which illustrates the robustness of our model.
+Certain success is achieved.
+Our approach gives reasonable rate constants and always performs better than Marcus theory, which illustrates the robustness of our model.
 

### 2016-04-12 FrontBackmatter/Abstract.tex
Gonna give it to the committee

@@
 We present a new, fully {\em ab initio} approach for computing intramolecular charge and
-energy transfer rates.  Using a time-convolutionless master equation approach and parameterized
-using couplings obtained using an accurate quantum chemical approach, we  benchmark the approach
-against  experimental results and Marcus theory rates for triplet energy transfer for a
+energy transfer rates.  Using a time-convolutionless master equation approach, parameterized
+with couplings obtained from an accurate quantum chemical approach, we  benchmark the approach
+against  experimental results and predictions from Marcus theory for triplet energy transfer for a
 series of donor-bridge-acceptor systems.
@@
 the electronic transition.
-Using an iterative Lanczos approach, we  concentrate the coupling between the electronic and nuclear
+Using an iterative Lanczos method, we  concentrate the coupling between the electronic and nuclear
 degrees of freedom into a small number of reduced harmonic modes.
@@
 
-We apply the method to a larger, ``star'' molecule, which has been experimentally shown  that its exciton transfer pathway can be radically modified by mode-specific infrared excitation of vibrations.
+We apply the method to a larger, ``star'' molecule, that has been experimentally shown  that its exciton transfer pathway can be radically modified by mode-specific infrared excitation of its vibrational mode.
 The primary mode and rate constants we obtain generally agree with the experiments.

### 2016-04-25 Chapters/chap1/introduction.tex
Defense passed!

@@
 lead to lower reaction rates, termed the inverted regime.
+The inverted region is unequivocally substantiated by Miller {\em et al.} \cite{miller1984intramolecular} in a series experiments of intramolecular transfer.
+Part of their work is used as the experimental benchmark of our model in Chapter \ref{chap:chapt2} and \ref{chap:chapt3}.
 
@@
 =\sum_n\tilde\epsilon_n |n\rangle \langle
-n|+\sum_i\omega_ia^{\dagger}_ia_i,
+n|+\sum_i\hbar\omega_ia^{\dagger}_ia_i,
  \end{eqnarray}
@@
 \begin{eqnarray}
-S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{spec-dens}
+S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} \! \mathrm{d}t e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{spec-dens}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\frac{dP_{n}}{dt} = \sum_{m} W_{nm}(t)P_{m}(t) - \left(\sum_{m} W_{mn}(t)\right)P_{n}(t)
+\frac{dP_{n}}{dt} = \sum_{m \ne n} W_{nm}(t)P_{m}(t) - \sum_{m \ne n} W_{mn}(t)P_{n}(t)
 \end{eqnarray}
@@
 \begin{eqnarray}
-W_{nm}(\tau)=2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
+W_{nm}(\tau)=2{\rm Re}\int_{0}^{\tau} \! \mathrm{d}t\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
 \label{rate-expression}
@@
 \begin{eqnarray}
-k_{nm}=2{\rm Re}\int_{0}^{\infty}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
+k_{nm}=2{\rm Re}\int_{0}^{\infty} \! \mathrm{d}t\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
 \label{gr-expression}
@@
 Another category of diabatization methods is based on physical intuition, with ER diabatization being one of them.
-The ER diabatization is based on the idea that good diabatic states are supposed to be localized, so the approach defines the diabatic states by minimizing the total electron repulsion
+The ER diabatization is based on the idea that good diabatic states are supposed to be localized, so the approach defines the diabatic states by maximizing the total electron repulsion
 \begin{eqnarray}

### 2016-04-25 Chapters/chap2/manuscript.tex
Defense passed!

@@
 only the first mode generated by the Lanczos iterations.   In the first case represented by the blue points,
-we approximate the reorganization energy as
+we approximate the renormalized energy as
 $$
@@
 over the entire series of model donor-bridge-acceptor systems considered.
-The red points represent rates computed using the first reduced mode, but use the exact reorganization energy.
+The red points represent rates computed using the first reduced mode, but use the exact renormalized energy.
 Here, the agreement is almost perfect for the two fastest rates corresponding to d-2,6ae and d-2,6ea.   However,  on average
@@
 \caption{Comparison between exact rate constant and its primary mode approximation.  The blue points correspond to rates computed using
-only the primary mode and the reorganization energy for only that mode.  The red points use the primary mode and the exact
+only the primary mode and the renormalized energy for only that mode.  The red points use the primary mode and the exact
 renormalized energies. }\label{fig-1mode}
@@
 \caption{Frequencies and dimensionless electron-phonon couplings for
-the first reduced mode for each model system. The last column gives the
+the primary mode. The last column gives the
 absolute value of the largest coupling constant within the normal mode basis.

### 2016-04-25 Chapters/chap3/Manuscript-FINAL.tex
Defense passed!

@@
 
+\begin{figure*}[]
+\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure5a.pdf}}\\
+\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure5b.pdf}}
+\caption{Projections of the PLM onto the normal modes of (a) c-1,4ee and (b) d-2,6ae.\label{LancProj}}
+\end{figure*}
+
 %{\bf  Comment: this paragraph needs fleshing out since there's a lot going on here.}
@@
 
-\begin{figure*}[!h]
-\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure5a.pdf}}\\
-\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure5b.pdf}}
-\caption{Projections of the PLM onto the normal modes of (a) c-1,4ee and (b) d-2,6ae.\label{LancProj}}
-\end{figure*}
-
 \section{Localized Property of the Primary Lanczos Mode}
@@
 
-\begin{figure*}[!h]
+\begin{figure*}[]
 \subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure6a.pdf}}\\
@@
  relative error in rate constants calculated for various combinations of normal modes compared to the exact result
- or c-1,4ee (c) and d-2,6ae (d) respectively. \label{backCorr}}
+ of c-1,4ee (c) and d-2,6ae (d), respectively. \label{backCorr}}
 \end{figure*}
@@
  is determined  by minimizing the average bond length difference of the four bonds on naphthalene
- which stretch significantly in PLM, between the optimized and approximate geometries. In Table 1 we list the differences between two geometries.
+ which stretch significantly in PLM, between the optimized and approximate geometries. In Table. ~\ref{aprroxGeom} we list the differences between two geometries.
 Comparing the maximum difference of bond
-lengths and angles between the approximated and true final states (Table. ~\ref{aprroxGeom}), the differences are very small,
+lengths and angles between the approximated and true final states, the differences are very small,
 so PLMs seem to give fairly good approximations of geometry changes.
@@
    \hline
-   Mode used & c-1,4ee-PLM   & c-1,4ee-DNM  & d-2,6ae-PLM  & d-2,6ae-DNM\\
+   Mode used & c-1,4ee-PLM   & c-1,4ee-RM  & d-2,6ae-PLM  & d-2,6ae-RM\\
    \hline
@@
 
-The resolution to this inconsistency is to distinguish between the two types of geometric changes.
+The solution to this inconsistency is to distinguish between the two types of geometric changes.
 One is the internal changes within  the moieties.  These are well represented  by the PLM.
@@
 % In short, the PLM is a subvector within the relaxation mode.
+
+\begin{figure*}[]
+\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10a.pdf}}\\
+\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10b.pdf}}\\
+% \subfloat[]{\includegraphics[width=0.53\columnwidth]{Chapters/chap3/Figure10c.pdf}}
+\caption{Correlation functions of relaxation mode (RM), PLM, geometry change (GC), and geometry change with the RM component eliminated for (a) c-1,4ee and (b) d-2,6ae.
+The exact rate is computed using the full set of normal modes.}
+\label{Corr}
+\end{figure*}
 
@@
 
-\begin{figure*}[!h]
-\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10a.pdf}}\\
-\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10b.pdf}}\\
-% \subfloat[]{\includegraphics[width=0.53\columnwidth]{Chapters/chap3/Figure10c.pdf}}
-\caption{Correlation functions of relaxation mode (RM), PLM, geometry change (GC), and geometry change with the RM component eliminated for (a) c-1,4ee and (b) d-2,6ae.
-The exact rate is computed using the full set of normal modes.}
-\label{Corr}
-\end{figure*}
-
-\begin{figure*}[!h]
-\subfloat[]{\includegraphics[width=0.9\columnwidth]{Chapters/chap3/Figure10c.pdf}}
-\caption{Relative comparison of the rate constants computed using different sets of reduced modes. blue = c-1,4ee, gold =d-2,6ae. }
-\label{RateComp}
-\end{figure*}
-
 %The results are consistent with our intuition.  The relaxation mode a gives negligible correlation
@@
 %
+
+\begin{figure*}[!t]
+\subfloat[]{\includegraphics[width=0.9\columnwidth]{Chapters/chap3/Figure10c.pdf}}
+\caption{Relative comparison of the rate constants computed using different sets of reduced modes. blue = c-1,4ee, gold =d-2,6ae. }
+\label{RateComp}
+\end{figure*}
 

### 2016-04-25 Chapters/chap4/chap4.tex
Defense passed!

@@
 
-\begin{figure*}[!h]
+\begin{figure*}[]
 \includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/parabola.jpg}
-\caption{Calculated energies of the CT (black), CSS (blue) and 3NAP (red) states along the NAP side C$\equiv$C coordinate in the ground state geometries of the molecules studied, in CH\textsubscript{2}Cl\textsubscript{2}.
+\caption{Calculated energies of the CT (black), CSS (blue) and \textsuperscript{3}NAP (red) states along the NAP side C$\equiv$C coordinate in the ground state geometries of the molecules studied, in CH\textsubscript{2}Cl\textsubscript{2}.
 a, PTZ-CH\textsubscript{2}-Pt-NAP.
@@
 
-\begin{figure}[!t]
+\begin{figure}[]
 \includegraphics[width=\columnwidth]{Chapters/chap4/Images/energy_diagram.pdf}
@@
 
-\begin{figure*}[!ht]
+\begin{figure*}[]
 \includegraphics[width=\columnwidth]{Chapters/chap4/Images/kTCLME-VS-EXPT.pdf}
@@
 
-\begin{figure}[!t]
+\begin{figure}[]
 \subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap4/Images/corrT12.pdf}}
@@
 \end{figure}
+
 \subsection{Primary Mode}
@@
 
-\begin{figure}[!t]
+\begin{figure}[]
 \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
@@
 
-\begin{figure}[!h]
+\begin{figure}[]
 % \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
@@
 
-\begin{figure}[!h]
-\subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t1_174.jpg}}\\
-\subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t1_175.jpg}}\\
-\subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t3_174.jpg}}\\
-\subfloat{\includegraphics[height=0.8\textheight,keepaspectratio]{Chapters/chap4/Images/t3_175.jpg}}
+\begin{figure}[]
+\subfloat{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/t1_174.png}}\\
+\subfloat{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/t1_175.png}}\\
+\subfloat{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/t3_174.png}}\\
+\subfloat{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/t3_175.png}}
 \caption{From top to bottom: the displacement vectors of the 174th, 175th mode of \textsuperscript{3}NAP state, the 174th, 175th mode of CT state.
@@
 They are all the stretching modes of single C$\equiv$C bond, look like
-PTZ-Ph-C$\equiv$C-Pt-C$\protect\overset{\longleftrightarrow}{\equiv}$C-NAP in (a) and (c),
-PTZ-Ph-C$\protect\overset{\longleftrightarrow}{\equiv}$C-Pt-C$\equiv$C-NAP in (b) and (d).
+PTZ-Ph-C$\equiv$C-Pt-C$\protect\overset{\longleftrightarrow}{\equiv}$C-NAP in (a),
+PTZ-Ph-C$\protect\overset{\longleftrightarrow}{\equiv}$C-Pt-C$\equiv$C-NAP in (b),
+PTZ-Ph-$\protect\overset{\leftarrow}{C}\equiv\protect\overset{\rightarrow}{C}$-Pt-$\protect\overset{\longrightarrow}{C}\equiv\protect\overset{\longleftarrow}{C}$-NAP
+ in (c), and
+PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\leftarrow}{C}\equiv\protect\overset{\rightarrow}{C}$-NAP
+ in (d).
 }\label{NMT1T3}
@@
 \ref{projT3}(b).
+
 All these normal modes are C$\equiv$C stretching modes, as shown in Fig.
@@
 And that component clearly dominates other normal modes.
-As for PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can be fully switched off by vibronic excitation, the step is supposed to be the one influenced by C$\equiv$C stretching most.
+Experimentally, after the IR pump is applied, the CT $\rightarrow$  \textsuperscript{3}NAP transition is relatively accelerated compared to the CT $\rightarrow$ CSS transition.
+By comparing the primary modes of the two transitions at CT geometry, we see that the primary mode of CT $\rightarrow$  \textsuperscript{3}NAP transition  is mainly antisymmetric stretching of two C$\equiv$C bonds, while that of CT $\rightarrow$ CSS transition is symmetric.
+As a result, the primary mode of CT $\rightarrow$  \textsuperscript{3}NAP is more IR active than that of CT $\rightarrow$ CSS transition.
+It may explain why CT $\rightarrow$  \textsuperscript{3}NAP  transition is relatively accelerated with IR pump.
+% As for PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can be fully switched off by vibronic excitation, the step is supposed to be the one influenced by C$\equiv$C stretching most.
 Although PTZ-Pt-NAP does not show such radical change, we expect the the CT $\rightarrow$ CSS to be the most C$\equiv$C involved, as two molecules only differ by a -CH\textsubscript{2}-
@@
 
-\begin{figure*}[!h]
+\begin{figure*}[t]
 \includegraphics[width=\columnwidth]{Chapters/chap4/Images/interpolation.pdf}

### 2016-04-25 presentation.tex
Defense passed!

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[10pt,english]{beamer}
\usepackage[T1]{fontenc}
\usepackage[utf8]{luainputenc}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{esint}
\ifx\hypersetup\undefined
  \AtBeginDocument{%
    \hypersetup{unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=1,
 breaklinks=false,pdfborder={0 0 0},backref=false,colorlinks=true,
 linkcolor=black, citecolor=black}
  }
\else
  \hypersetup{unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=1,
 breaklinks=false,pdfborder={0 0 0},backref=false,colorlinks=true,
 linkcolor=black, citecolor=black}
\fi

\makeatletter
\@addtoreset{subfigure}{framenumber}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
 % this default might be overridden by plain title style
 \newcommand\makebeamertitle{\frame{\maketitle}}%
 \AtBeginDocument{
   \let\origtableofcontents=\tableofcontents
   \def\tableofcontents{\@ifnextchar[{\origtableofcontents}{\gobbletableofcontents}}
   \def\gobbletableofcontents#1{\origtableofcontents}
 }
 \long\def\lyxframe#1{\@lyxframe#1\@lyxframestop}%
 \def\@lyxframe{\@ifnextchar<{\@@lyxframe}{\@@lyxframe<*>}}%
 \def\@@lyxframe<#1>{\@ifnextchar[{\@@@lyxframe<#1>}{\@@@lyxframe<#1>[]}}
 \def\@@@lyxframe<#1>[{\@ifnextchar<{\@@@@@lyxframe<#1>[}{\@@@@lyxframe<#1>[<*>][}}
 \def\@@@@@lyxframe<#1>[#2]{\@ifnextchar[{\@@@@lyxframe<#1>[#2]}{\@@@@lyxframe<#1>[#2][]}}
 \long\def\@@@@lyxframe<#1>[#2][#3]#4\@lyxframestop#5\lyxframeend{%
   \frame<#1>[#2][#3]{\frametitle{#4}#5}}
 \def\lyxframeend{} % In case there is a superfluous frame end
 \newenvironment{topcolumns}{\begin{columns}[t]}{\end{columns}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{cite}
\usepackage{notoccite}

\usepackage{babel}
%\usepackage{xunicode}

\@ifundefined{showcaptionsetup}{}{%
 \PassOptionsToPackage{caption=false}{subfig}}
\usepackage{subfig}
\makeatother

\begin{document}

\title{\emph{Ab initio} Calculations of Intramolecular Exciton Transfer with Reduced Modes in Donor-Bridge-Acceptor Species}

\author{Xunmo Yang}

\makebeamertitle

\lyxframeend{}\lyxframe{Outline}
\begin{itemize}
\item Introduction
\item Benchmark of TCLME with Edmiston-Ruedenberg diabatization
\item Primary Mode
\item Application in IR-controlled electron transfer
\item Conclusions
\end{itemize}

\lyxframeend{}

\lyxframeend{}\lyxframe{Electron Transfer}

\begin{figure}[t]
\includegraphics[width=0.9\columnwidth]{ET_application.png}
\end{figure}

\small{Rudolph A. Marcus - Nobel Lecture: Electron Transfer Reactions in Chemistry: Theory and Experiment".}
\lyxframeend{}

\lyxframeend{}\lyxframe{Marcus Theory}
\begin{topcolumns}%{}

\column{7cm}

Energy and electronic transport is fundamental in chemistry. The seminal model for calculating transfer rates was developed by Marcus.
\[
H_{dia}=\hat{T_{n}}+\left(\begin{array}{cc}
\epsilon_{a}(\mathbf{R}) & V_{ab}\\
V_{ab} & \epsilon_{b}(\mathbf{R})
\end{array}\right)
\]

\[
k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+\Delta E)^{2}/4\text{\ensuremath{\lambda}}k_{B}T}
\]

\begin{itemize}
\item Condon approximation:$V_{ab}(\mathbf{R})=V_{ab}$
\item All vibrations are included in a collective coordinate
\item $k_{B}T \gg \hbar \omega$
\end{itemize}

\column{4cm }

\includegraphics[height=4cm]{Chapters/chap2/Figure1}

\end{topcolumns}%{}

\lyxframeend{}

\lyxframeend{}\lyxframe{Adiabatic vs. Diabatic Representation}

\begin{figure}

\begin{centering}
\includegraphics[width=0.7\textwidth]{Chapters/chap2/adia_vs_diabatic.png}
\par\end{centering}

\end{figure}

Adiabatic representation

Pros:
\begin{itemize}
\item Eigenstate of electronic Hamiltonian, directly available from quantum chemistry software
\end{itemize}
Cons:
\begin{itemize}
\item Potential energy surfaces aren't parabolic (avoided crossing)
\item Sharp derivative coupling near avoided crossing (hard to compute)
\end{itemize}

\lyxframeend{}

\lyxframeend{}\lyxframe{Diabatization: Boys \& Edmiston-Ruedenberg Localization}

\[
H_{adia}=\begin{pmatrix}E_{1}(\mathbf{R})+\mathrm{T_{n}}(\mathbf{R})_{11} & \mathrm{T_{n}}(\mathbf{R})_{12}\\
\mathrm{T_{n}}(\mathbf{R})_{21} & E_{2}(\mathbf{R})+\mathrm{T_{n}}(\mathbf{R})_{22}
\end{pmatrix}
\]

Construct diabatic states to eliminate dynamical coupling,
\begin{itemize}
\item Exact way $\left\langle \phi_{i}(\mathbf{r};\mathbf{R})|\nabla_{\mathbb{\mathbf{R}}}|\phi_{j}(\mathbf{r};\mathbf{R})\right\rangle =0$
(expensive \& rarely exist)
\item Intuitive way. Transform $H_{adia}$
\end{itemize}
\[
H_{dia}=U^{T}H_{adia}U=\left(\begin{array}{cc}
\epsilon_{a}(\mathbf{R})\mathrm{+T'_{n}}(\mathbf{R})_{11} & V_{ab}(\mathbf{R})\\
V_{ab}(\mathbf{R}) & \epsilon_{b}(\mathbf{R})\mathrm{+T'_{n}}(\mathbf{R})_{22}
\end{array}\right)
\]

to maximize/minimize certain physical property

\[
f_{Boys}=\sum_{kl}^{N_{states}}\left(\left\langle \phi_{k}|\vec{r}|\phi_{k}\right\rangle -\left\langle \phi_{l}|\vec{r}|\phi_{l}\right\rangle \right)^{2}
\]

\textrm{
\[
f_{ER}=\sum_{k}^{N_{states}}\iint \! \mathrm{d}r_{1}\mathrm{d}r_{2}\frac{\left\langle \phi_{k}|\hat{\rho}\left(r_{1}\right)|\phi_{k}\right\rangle \left\langle \phi_{k}|\hat{\rho}\left(r_{2}\right)|\phi_{k}\right\rangle }{\left\Vert r_{1}-r_{2}\right\Vert }
\]
}

\lyxframeend{}

\lyxframeend{}\lyxframe{Diabatization: Generalized Mulliken Hush (GMH)}

\[
\begin{pmatrix} |\phi_{a}\rangle\\|\phi_{b}\rangle\end{pmatrix}
= U^{T}\begin{pmatrix} |\psi_{1}\rangle\\|\psi_{2}\rangle\end{pmatrix}
= \left(\begin{array}{cc}
\cos\theta & \sin\theta\\
-\sin\theta & \cos\theta
\end{array}\right)
\begin{pmatrix} |\psi_{1}\rangle\\|\psi_{2}\rangle\end{pmatrix}
\]

Assuming only the direction along $\vec{\mu}_{11} - \vec{\mu}_{22}$ matters, we project all dipole moments onto $\vec{v} = (\vec{\mu}_{11} - \vec{\mu}_{22})/|\vec{\mu}_{11} - \vec{\mu}_{22}|$.
% \[\mu_{ab} = \langle\phi_{a}| \vec{\mu} | \phi_{b}\rangle
% = \cos2\theta \vec{\mu}_{12} - \frac{1}{2}\sin2\theta(\vec{\mu}_{11} - \vec{\mu}_{22})
% \]
\[\mu_{ab}^{v} = \langle\phi_{a}| \vec{\mu} | \phi_{b}\rangle \cdot \vec{v}
= \cos2\theta \vec{\mu}_{12}^{v} - \frac{1}{2}\sin2\theta|\vec{\mu}_{11} - \vec{\mu}_{22}|
\]
Good diabatic states should have $\mu_{ab}^{v} = 0$, this determines $\theta$ and gives
% \[\tan2\theta=\frac{2\mu_{12}^v}{|\vec{\mu}_{11} - \vec{\mu}_{22}|}
% \]
\[|H_{AB}|=|\cos2\theta {H}_{12} - \frac{1}{2}\sin2\theta({H}_{11} - {H}_{22})|
= \frac{|\mu_{12}^{v}||H_{11}-H_{22}|}{\sqrt{|\vec{\mu}_{11} - \vec{\mu}_{22}|^2 + 4|\mu_{12}^{v}|^2}}
\]
For linear systems, we further assume $|\mu_{12}^{v}| = |\mu_{12}|$.

\lyxframeend{}

\lyxframeend{}\lyxframe{Time-convolutionless Master Equation (TCLME)}

Bittner and Pereversev developed TCLME for Hamiltonian
\[
H=\left(\begin{array}{cc}
E_{a}\\
 & E_{b}
\end{array}\right)+\sum_{ijq}g_{ijq}|\phi_{i}\rangle\langle\phi_{j}|q+\sum_{q}\hbar\omega_{q}(n+1/2)
\]

To get this desired form, we assume diabatic potentials are the parabolas
same as adiabatic potentials, then at $Q_{b}$,

\[
H_{dia}=\left(\begin{array}{cc}
\epsilon_{a} & V_{ab}\\
V_{ab} & \epsilon_{b}
\end{array}\right)+\left(\begin{array}{cc}
\\
 & \sum_{i}g_{22i}q_{i}
\end{array}\right)+h.o.
\]

% Use $U=\left(\begin{array}{cc}
% \cos\theta & -\sin\theta\\
% \sin\theta & \cos\theta
% \end{array}\right)$ to
Diagonalize the electronic part
\[
H=U^{T}H_{dia}U=\left(\begin{array}{cc}
E_{a}\\
 & E_{b}
\end{array}\right)+\left(\begin{array}{cc}
\sin^{2}\theta & \frac{1}{2}\sin2\theta\\
\frac{1}{2}\sin2\theta & \cos^{2}\theta
\end{array}\right)\sum_{i=1}^{NMode}g_{22i}q_{i}+h.o.
\]

\lyxframeend{}

\lyxframeend{}\lyxframe{Validity of Assumptions}

\begin{figure}
\subfloat{\includegraphics[width=0.4\columnwidth]{Chapters/chap2/Figure2a}}
\subfloat{\includegraphics[width=0.4\columnwidth]{Chapters/chap2/Figure2b}}
\caption{Adiabatic energy curves and off-diagonal couplings computed along an interpolation coordinate between the
$D^{*}-B-A$ and $D-B-A^{*}$ equilibrium geometries for (a) c-1,4ee and (b) d-2,6ae.}
\end{figure}
\begin{itemize}
\item Condon approximation: diabatic couplings are small \& steady
\item Parabolic assumption holds well
\end{itemize}

\lyxframeend{}

\lyxframeend{}\lyxframe{Benchmark with Closs' Experiments}

\begin{table}
\caption{Transfer rates obtained from experiments, TCLME and Marcus theory.\label{tab:Transfer rates}}

% \noindent \begin{raggedright}
% \begin{tabular}{|c|c|c|c|c|c|}
% \hline
% Symbol & Structure & $k_{e}\left(1/s\right)$ & $k_{T}\left(1/s\right)$ & $k_{M}\left(1/s\right)$ & $V_{ab}\left(meV\right)$\tabularnewline
% \hline
% \hline
% c-1,3ee & \includegraphics[height=0.35cm]{\string"Chapters/chap2/Table1-c13ee\string".pdf} & $7.7\times10^{9}$ & $2.8\times10^{10}$ & $2.1\times10^{10}$ & $1.6$\tabularnewline
% \hline
% c-1,4ee & \includegraphics[height=0.35cm]{\string"Chapters/chap2/Table1-c14ee\string".pdf} & $1.3\times10^{9}$ & $4.0\times10^{9}$ & $3.9\times10^{9}$ & $0.61$\tabularnewline
% \hline
% c-1,3ea & \includegraphics[height=0.7cm]{\string"Chapters/chap2/Table1-c13ea\string".pdf} & $3.3\times10^{9}$ & $5.0\times10^{9}$ & $3.9\times10^{9}$ & $0.7$\tabularnewline
% \hline
% d-2,6ae & \includegraphics[height=0.7cm]{\string"Chapters/chap2/Table1-d26ae\string".pdf} & $1.3\times10^{5}$ & $5.5\times10^{4}$ & $1.0\times10^{4}$ & $0.0023$\tabularnewline
% \hline
% d-2,6ea & \includegraphics[height=0.7cm]{\string"Chapters/chap2/Table1-d26ea\string".pdf} & $7\times10^{5}$ & $0.7$ & $3.9\mathbf{\times}10^{4}$       & $8.2\times10^{-6}$\tabularnewline
% \hline
% d-2,7ea & \includegraphics[height=0.7cm]{\string"Chapters/chap2/Table1-d27ea\string".pdf} & $1.5\times10^{7}$ & $3.0\times10^{7}$ & $1.8\times10^{7}$ & $0.7$\tabularnewline
% \hline
% \end{tabular}
% \par\end{raggedright}

% \includegraphics[height=1.5cm]{\string"fig/chemical structure/bridge\string".pdf}
% \end{table}

\noindent \begin{raggedright}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Symbol & Structure & $k_{expr}\left(1/s\right)$ & $k_{Marcus}\left(1/s\right)$ & $k_{TCLME}\left(1/s\right)$ \tabularnewline
\hline
 c-1,3ea  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-c13ea.pdf}  &                     3.3E9  &                     3.9E9  &          2.2E9   \\
\hline
 c-1,3ee  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-c13ee.pdf}  &                     7.7E9  &                    2.1E10  &         2.8E10   \\
\hline
 c-1,4ea  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-c14ea.pdf}  &                     4.0E7  &                     1.3E7  &          1.8E7  \\
\hline
 c-1,4ee  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-c14ee.pdf}  &                     1.3E9  &                     3.9E9  &          3.6E9   \\
\hline
 d-2,6ae  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-d26ae.pdf}  &                     1.3E5  &                     1.0E4  &          4.7E4 \\
% \hline
% d-2,6ea  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-d26ea.pdf}  &                     7.0E5  &                     3.9E4  &          5.8E4   \\
% \hline
%  d-2,6ee  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-d26ee.pdf}  &                     3.1E6  &                     5.0E6  &          4.8E6  \\
% \hline
%  d-2,7ae  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-d27ae.pdf}  &                     1.1E7  &                     2.8E7  &          3.0E7   \\
% \hline
%  d-2,7ea  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-d27ea.pdf}  &                     1.5E7  &                     1.8E7  &          4.3E7  \\
% \hline
%  d-2,7ee  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-d27ee.pdf}  &                     9.1E7  &                     3.5E8  &          3.4E8  \\
% \hline
%  M        &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-M.pdf}      &                    5.0E10  &                      n.r.  &          1.2E9  \\
\hline
\end{tabular}
\par\end{raggedright}
\includegraphics[height=1.5cm]{Chapters/chap2/Scheme1}
\end{table}

\lyxframeend{}

\lyxframeend{}\lyxframe{Benchmark with Closs' Experiments (Cont'd)}

\begin{table}
% \caption{Transfer rates obtained from experiments, TCLME and Marcus theory.\label{tab:Transfer rates}}
\noindent \begin{raggedright}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Symbol & Structure & $k_{expr}\left(1/s\right)$ & $k_{Marcus}\left(1/s\right)$ & $k_{TCLME}\left(1/s\right)$ \tabularnewline
\hline
%  c-1,3ea  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-c13ea.pdf}  &                     3.3E9  &                     3.9E9  &          2.2E9   \\
% \hline
%  c-1,3ee  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-c13ee.pdf}  &                     7.7E9  &                    2.1E10  &         2.8E10   \\
% \hline
%  c-1,4ea  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-c14ea.pdf}  &                     4.0E7  &                     1.3E7  &          1.8E7  \\
% \hline
%  c-1,4ee  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-c14ee.pdf}  &                     1.3E9  &                     3.9E9  &          3.6E9   \\
% \hline
%  d-2,6ae  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-d26ae.pdf}  &                     1.3E5  &                     1.0E4  &          4.7E4 \\
\hline
d-2,6ea  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-d26ea.pdf}  &                     7.0E5  &                     3.9E4  &          5.8E4   \\
\hline
 d-2,6ee  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-d26ee.pdf}  &                     3.1E6  &                     5.0E6  &          4.8E6  \\
\hline
 d-2,7ae  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-d27ae.pdf}  &                     1.1E7  &                     2.8E7  &          3.0E7   \\
\hline
 d-2,7ea  &  \includegraphics[height=0.7cm]{Chapters/chap2/Table1-d27ea.pdf}  &                     1.5E7  &                     1.8E7  &          4.3E7  \\
\hline
 d-2,7ee  &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-d27ee.pdf}  &                     9.1E7  &                     3.5E8  &          3.4E8  \\
\hline
 M        &  \includegraphics[height=0.35cm]{Chapters/chap2/Table1-M.pdf}      &                    5.0E10  &                      n.r.  &          1.2E9  \\
\hline
\end{tabular}
\par\end{raggedright}
\includegraphics[height=1.5cm]{Chapters/chap2/Scheme1}
\end{table}

\lyxframeend{}

\lyxframeend{}\lyxframe{Benchmark with Closs' Experiments (Cont'd)}

\begin{figure}

\begin{centering}
\includegraphics[width=0.5\textwidth]{Chapters/chap2/Figure3}
\caption{Comparison between predicted (TCLME) rate constants and the experimental rates.  With exception of
the methyl bridged and d-2,6ea cases, the TCLME results are in good agreement with the experimental results.  }\label{compare}
\par\end{centering}

\end{figure}

\lyxframeend{}

\lyxframeend{}\lyxframe{Why TCLME}
\begin{itemize}
\item Marcus theory
\end{itemize}
\[
H=\hat{T}_{n}+\left(\begin{array}{cc}
\epsilon_{a}(\mathbf{R}) & V_{ab}\\
V_{ab} & \epsilon_{b}(\mathbf{R})
\end{array}\right)
\]

\[
k=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+\Delta E)^{2}/4\text{\ensuremath{\lambda}}k_{B}T}
\]

\begin{itemize}
\item TCLME
\end{itemize}
% \[
% H_{dia}=\left(\begin{array}{cc}
% \epsilon_{a} & V_{ab}\\
% V_{ab} & \epsilon_{b}
% \end{array}\right)+\left(\begin{array}{cc}
% \\
%  & \sum_{i}g_{22i}q_{i}
% \end{array}\right)+h.o.
% \]

\[
H=\left(\begin{array}{cc}
E_{a}\\
 & E_{b}
\end{array}\right)+\sum_{ijq}g_{ijq}|\phi_{i}\rangle\langle\phi_{j}|q+\sum_{q}\hbar\omega_{q}(n+1/2)
\]
\[
H=\left(\begin{array}{cc}
E_{a}\\
 & E_{b}
\end{array}\right)+\left(\begin{array}{cc}
\sin^{2}\theta & \frac{1}{2}\sin2\theta\\
\frac{1}{2}\sin2\theta & \cos^{2}\theta
\end{array}\right)\sum_{i=1}^{NMode}g_{22i}q_{i}+h.o.
\]

% Advantages
% \begin{itemize}
% \item Go beyond Condon approximation easily
% \item Treat normal modes explicitly, which makes projection approach applicable
% \end{itemize}
TCLME treats normal modes explicitly, which makes projection approach applicable.
\lyxframeend{}

\lyxframeend{}\lyxframe{Projected Modes}

\[
H=\left(\begin{array}{cc}
E_{a}\\
 & E_{b}
\end{array}\right)+\left(\begin{array}{cc}
\sum_{i}g_{11i}q_{i} & \sum_{i}g_{12i}q_{i}\\
\sum_{i}g_{12i}q_{i} & \sum_{i}g_{22i}q_{i}
\end{array}\right)+\sum_{i}\frac{p_{i}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\Omega\mathbf{q},
\]
where
\[
\mathbf{q}^{T}=\left(q_{1},q_{2},\cdots,q_{n}\right),\Omega=\left(\begin{array}{cccc}
\omega_{1}^{2}\\
 & \omega_{2}^{2}\\
 &  & \ddots\\
 &  &  & \omega_{n}^{2}
\end{array}\right)
\]
can be transformed to
\[
\Omega'=\left(\begin{array}{cccccc}
\omega_{1}'^{2} &  &  & \gamma_{14} & \cdots & \gamma_{1n}\\
 & \omega_{2}'^{2} &  & \gamma_{24} & \cdots & \gamma_{2n}\\
 &  & \omega_{3}'^{2} & \gamma_{34} & \cdots & \gamma_{3n}\\
\gamma_{14} & \gamma_{24} & \gamma_{24} & \omega_{4}'^{2}\\
\vdots & \vdots & \vdots &  & \ddots\\
\gamma_{1n} & \gamma_{2n} & \gamma_{3n} &  &  & \omega_{n}'^{2}
\end{array}\right)
\]

\lyxframeend{}

\lyxframeend{}\lyxframe{TCLME Equation}

\[
\frac{dP_{n}}{dt} = \sum_{m \ne n} W_{nm}(t)P_{m}(t) - \sum_{m \ne n} W_{mn}(t)P_{n}(t)
\]
\[
W_{nm}(t)=2{\rm Re}\int_{0}^{t} \! \mathrm{d}\tau \left\langle \hat V_{nm}(0)\hat V_{mn}\left(\tau\right)\right\rangle e^{-i(\tilde\epsilon_m - \tilde\epsilon_n)\tau}\]
The renormalization energy is
\[
\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i}\]

$\left\langle \hat V_{nm}(0)\hat V_{mn}\left(\tau\right)\right\rangle$ is the correlation function.
\lyxframeend{}

\lyxframeend{}\lyxframe{Projected Modes for c-1,4ee and d-2,6ae}
\begin{figure}[t]
\subfloat{\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure5a}}
\subfloat{\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure5b}}\\
\subfloat{\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure5c}}
\subfloat{\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure5d}}
% \caption{Convergence of the electronic coupling autocorrelation function (Eq. ~\ref{c-of-t})
% with respect to number of reduced modes.\label{firstmodecorr}}
\end{figure}

\lyxframeend{}

\lyxframeend{}\lyxframe{Primary Mode Rate Constant}

\[
\frac{dP_{n}}{dt} = \sum_{m \ne n} W_{nm}(t)P_{m}(t) - \sum_{m \ne n} W_{mn}(t)P_{n}(t)
\]
\[
W_{nm}(t)=2{\rm Re}\int_{0}^{t} \! \mathrm{d}\tau \left\langle \hat V_{nm}(0)\hat V_{mn}\left(\tau\right)\right\rangle e^{-i(\tilde\epsilon_m - \tilde\epsilon_n)\tau}\]
\[
\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i}\]

\begin{itemize}
\item How about using the approximated correlation function and $\Delta\epsilon$ to calculate the rate?
\item How about the approximated correlation function with exact $\Delta\epsilon$?
\end{itemize}

\lyxframeend{}

\lyxframeend{}\lyxframe{Primary Mode Rate Constant (Cont'd)}
\begin{figure}[t]
\includegraphics[width=0.45\columnwidth]{Chapters/chap2/Figure6}
\caption{Comparison between exact rate constant and its primary mode approximation.  The blue dots correspond to rates computed using
only the primary mode and the renormalized energy for only that mode.  The red points use the primary mode and the exact
renormalized energies. }\label{fig-1mode}
\end{figure}

Only one mode? Seems easy. Any other way possible?
\lyxframeend{}

\lyxframeend{}\lyxframe{No Normal Mode Works That Well}
\begin{table}[t]
\centering
\begin{tabular}{lrrr}
 bridge   &  $\omega_1$(eV)  & $|g_{1}|$ (eV)  &  $|g_{max}|$ (eV)  \\
\hline
\hline
 c-1,3ea  &           0.184  &         0.367  &           0.159  \\
 c-1,3ee  &           0.185  &         0.365  &           0.162  \\
 c-1,4ea  &           0.185  &         0.367  &           0.166  \\
 c-1,4ee  &           0.185  &         0.370  &           0.171  \\
 d-2,6ae  &           0.185  &         0.367  &           0.159  \\
 d-2,6ea  &           0.185  &         0.367  &           0.142  \\
 d-2,6ee  &           0.185  &         0.365  &           0.143  \\
 d-2,7ae  &           0.184  &         0.366  &           0.165  \\
 d-2,7ea  &           0.185  &         0.367  &           0.142  \\
 d-2,7ee  &           0.185  &         0.370  &           0.149  \\
 M           &           0.184  &         0.366  &           0.160  \\
 \hline
\end{tabular}
\caption{Frequencies and dimensionless electron-phonon couplings for
the primary mode. The last column gives the
absolute value of the largest coupling constant within the normal mode basis.
}
\end{table}
$|g_1|$ is more than twice of the largest $|g_i|$. No single normal mod is as representative as the primary mode. Actually, the primary mode generates the largest possible coupling constant.
\lyxframeend{}

\lyxframeend{}\lyxframe{Primary Mode}

\begin{figure}
\subfloat[c-1,4ee: $\omega=1492.47cm^{-1},g=0.370eV$]{\includegraphics[width=0.55\columnwidth]{Chapters/chap2/Figure4a}}\\
\subfloat[d-2,6ae $\omega=1491.09cm^{-1},g=0.367eV$]{\includegraphics[width=0.55\columnwidth]{Chapters/chap2/Figure4b}}
\end{figure}
\begin{itemize}
\item Bridge is barely involved
\item Certain local symmetry
\end{itemize}
\lyxframeend{}

\lyxframeend{}\lyxframe{Phenyl and Anthracene as Acceptors}

\begin{figure}[t]
\subfloat{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3a.pdf}}
\subfloat{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3b.pdf}}\\
\subfloat{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3c.pdf}}
\subfloat{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3d.pdf}}
\end{figure}

\lyxframeend{}

\lyxframeend{}\lyxframe{Projection on Moiety}

\begin{figure}[ht]
\subfloat[]{\includegraphics[width=0.38\columnwidth]{Chapters/chap3/Figure2a.pdf}}
\subfloat[]{\includegraphics[width=0.38\columnwidth]{Chapters/chap3/Figure2b.pdf}} \\
\subfloat[]{\includegraphics[width=0.38\columnwidth]{Chapters/chap3/Figure2c.pdf}}
\subfloat[]{\includegraphics[width=0.38\columnwidth]{Chapters/chap3/Figure2d.pdf}}
\caption{Projection on (a) benzaldehyde, (b) symmetrized naphthalene in c-1,4ee, (c) benzaldehyde, (d) symmetrized naphthalene in d-2,6ae. \label{fragProj}}
\end{figure}

\lyxframeend{}

\lyxframeend{}\lyxframe{Bridge Is Not Important}

\begin{figure}[!h]
\subfloat{\includegraphics[width=0.33\columnwidth]{Chapters/chap3/Figure7a.pdf}}
\subfloat{\includegraphics[width=0.33\columnwidth]{Chapters/chap3/Figure7b.pdf}} \\
\subfloat{\includegraphics[width=0.33\columnwidth]{Chapters/chap3/Figure7c.pdf}}
\subfloat{\includegraphics[width=0.33\columnwidth]{Chapters/chap3/Figure7d.pdf}}
\caption{``Exact'' = primary mode.  ``NfBf" = all normal modes of D and A.
``NxBy'' = $x$ most significant normal modes
on naphthalene + $y$ most significant ones on benzaldehyde. (c) and (d):
 relative error in rate constants compared to the exact result
 of c-1,4ee (c) and d-2,6ae (d), respectively. \label{backCorr}}
\end{figure}
\lyxframeend{}

\lyxframeend{}\lyxframe{Primary Mode and Electron Orbital}

\begin{figure}[t]
\subfloat{\includegraphics[width=0.65\columnwidth]{Chapters/chap2/Figure4b}}\\
\subfloat[HOMO]{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure4a.pdf}}
\subfloat[LUMO]{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure4b.pdf}}
\end{figure}

\lyxframeend{}

\lyxframeend{}\lyxframe{Geometry Change On Benzaldehyde}

\begin{figure}[t]
\subfloat[Geometry change]{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure8a.pdf}
\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure8c.pdf}}\\
\subfloat[Primary mode]{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure2a.pdf}
\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure2c.pdf}}
\end{figure}

\lyxframeend{}

\lyxframeend{}\lyxframe{Geometry Change On Naphthalene}

\begin{figure}[t]
\subfloat[Geometry change]{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure8b.pdf}
\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure8d.pdf}}\\
\subfloat[Primary mode]{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure6a.pdf}
\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure6b.pdf}}
\end{figure}

\lyxframeend{}

\lyxframeend{}\lyxframe{Primary Mode and Geometry Change}

\begin{figure}[t]
\subfloat[Primary mode]{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure5a.pdf}
\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure5b.pdf}}\\
\subfloat[Geometry change]{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure9a.pdf}
\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure9b.pdf}}
\end{figure}

\lyxframeend{}

\lyxframeend{}\lyxframe{Relaxation Mode Doesn't Contribute to Rate}

\begin{figure}[t]
\subfloat{\includegraphics[width=0.48\columnwidth]{Chapters/chap3/Figure9a.pdf}}
\subfloat{\includegraphics[width=0.48\columnwidth]{Chapters/chap3/Figure9b.pdf}}\\
\subfloat{\includegraphics[width=0.48\columnwidth]{Chapters/chap3/Figure10a.pdf}}
\subfloat{\includegraphics[width=0.48\columnwidth]{Chapters/chap3/Figure10b.pdf}}
\label{Corr}
\end{figure}

\lyxframeend{}

\lyxframeend{}\lyxframe{Internal and Gross Motions}

\begin{figure}[t]
\subfloat{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure10c.pdf}}
\subfloat{\includegraphics[width=0.4\columnwidth]{Chapters/chap3/Figure4a.pdf}}
\label{Corr}
\end{figure}
\begin{table}
\centering
 \begin{tabular}{lll}
   \hline
              & Max. bond length    & Max. bond angle  \\
   Mode used  & difference (\AA)    & difference (rad) \\
   \hline
   c-1,4ee-PM   & 0.034 & 0.053  \\
   c-1,4ee-RM   & 0.160 & 0.075 \\
   d-2,6ae-PM   & 0.039 & 0.057  \\
   d-2,6ae-RM   & 0.283 & 0.135 \\
   \hline
\end{tabular}
\caption{Approximated geometry using the primary mode (PM) and the relaxation modes (RM) compared to acceptor states
}
\end{table}
\lyxframeend{}

% \lyxframeend{}\lyxframe{Energy Diagram}
% \begin{figure}[!t]
% \includegraphics[width=\columnwidth]{Chapters/chap4/Images/molecules.jpg}
% % \includegraphics[width=0.4\columnwidth]{Chapters/chap4/Images/scheme.jpg}
% \caption{\textbf{a}. Molecular structure of PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-Pt-NAP, from left to right (D = PTZ is phenothiazine and A = NAP is naphthalene-monoimide). \textbf{b}. Energy level diagrams for the ET process, with the lifetimes and the driving force ($\Delta$G) of CT $\rightarrow$ CSS transfer  indicated. Adabtpe from Ref. \footnote{Delor, Milan, et al. ``On the mechanism of vibrational control of light-induced charge transfer in donor–bridge–acceptor assemblies.'' Nature chemistry (2015)}}
% \end{figure}

% \lyxframeend{}

\lyxframeend{}\lyxframe{Molecule Structure and Energy Diagram}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Chapters/chap4/Images/molecules.jpg}
\caption{\textbf{a}. Molecular structure of PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-Pt-NAP, from left to right (D = PTZ is phenothiazine and A = NAP is naphthalene-monoimide). \textbf{b}. Energy level diagrams for the ET process, with the lifetimes and the driving force ($\Delta$G) of CT $\rightarrow$ CSS transfer  indicated.}
\end{figure}
\small{Delor, Milan, et al. ``On the mechanism of vibrational control of light-induced charge transfer in donor–bridge–acceptor assemblies.'' Nature Chemistry (2015)}
\lyxframeend{}

\lyxframeend{}\lyxframe{IR Control Scheme}

\begin{figure}[t]
\includegraphics[width=0.65\columnwidth]{Chapters/chap4/Images/scheme.jpg}
\end{figure}
\small{Delor, Milan, et al. ``On the mechanism of vibrational control of light-induced charge transfer in donor–bridge–acceptor assemblies.'' Nature Chemistry (2015)}
\lyxframeend{}

\lyxframeend{}\lyxframe{Possible Mechanism}

\begin{figure}[t]
\subfloat[PTZ-CH\textsubscript{2}-Pt-NAP]{\includegraphics[width=0.33\columnwidth]{Chapters/chap4/Images/parabolaA.jpg}}
\subfloat[PTZ-Pt-NAP]{\includegraphics[width=0.33\columnwidth]{Chapters/chap4/Images/parabolaB.jpg}}
\subfloat[OMe-PTZ-Pt-NAP]{\includegraphics[width=0.33\columnwidth]{Chapters/chap4/Images/parabolaC.jpg}}
\caption{Calculated energies of the CT (black), CSS (blue) and \textsuperscript{3}NAP (red) states along the NAP side C$\equiv$C coordinate in the ground state geometries, in CH\textsubscript{2}Cl\textsubscript{2}.}
\end{figure}
\small{Delor, Milan, et al. ``On the mechanism of vibrational control of light-induced charge transfer in donor–bridge–acceptor assemblies.'' Nature Chemistry (2015)}
\lyxframeend{}

\lyxframeend{}\lyxframe{PTZ-Pt-NAP}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Chapters/chap4/Images/energy_diagram.pdf}
\caption{The energy diagram of triplet states at \textsuperscript{3}NAP and CT state geometries. The electron/hole distribution are shown as well (green for electron, blue for hole). The arrows indicate the transitions we calculate.
}
\end{figure}
\lyxframeend{}

\lyxframeend{}\lyxframe{Rate Constants}

\begin{figure}[t]
\includegraphics[width=0.9\columnwidth]{Chapters/chap4/Images/kTCLME-VS-EXPT.pdf}
% \caption{The energy diagram of triplet states at \textsuperscript{3}NAP and CT state geometries. The electron/hole distribution are shown as well (green for electron, blue for hole). The arrows indicate the transitions we calculate.
% }
\end{figure}
\lyxframeend{}

\lyxframeend{}\lyxframe{Correlation Functions}

\begin{figure}[]
\subfloat[CSS $\rightarrow$ \textsuperscript{3}NAP at \textsuperscript{3}NAP geom.]{\includegraphics[width=0.4\columnwidth]{Chapters/chap4/Images/corrT12.pdf}}
\subfloat[CT $\rightarrow$ \textsuperscript{3}NAP at \textsuperscript{3}NAP geom.]{\includegraphics[width=0.4\columnwidth]{Chapters/chap4/Images/corrT13.pdf}}\\
\subfloat[CT $\rightarrow$ \textsuperscript{3}NAP at CT geom.]{\includegraphics[width=0.4\columnwidth]{Chapters/chap4/Images/corrT31.pdf}}
\subfloat[CT $\rightarrow$ CSS at CT geom.]{\includegraphics[width=0.4\columnwidth]{Chapters/chap4/Images/corrT32.pdf}}
% \caption{
% Correlation functions of various numbers of projected modes, compared to exact correlation, for (a) CSS $\rightarrow$ \textsuperscript{3}NAP at \textsuperscript{3}NAP geometry, (b) CT $\rightarrow$ \textsuperscript{3}NAP at \textsuperscript{3}NAP geometry, (c) CT $\rightarrow$ \textsuperscript{3}NAP at CT geometry, and (d) CT $\rightarrow$ CSS at CT geometry.
% }\label{corrT1T3}
\end{figure}
\lyxframeend{}

\lyxframeend{}\lyxframe{Primary Mode}

\begin{figure}[]
% \subfloat[CSS $\rightarrow$ \textsuperscript{3}NAP at \textsuperscript{3}NAP geom.]{\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/plmT12.png}}
% \subfloat[CT $\rightarrow$ \textsuperscript{3}NAP at \textsuperscript{3}NAP geom.]{\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/plmT13.png}}\\
\subfloat[CT $\rightarrow$ \textsuperscript{3}NAP at CT geom.]{\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/plmT31.png}}
\subfloat[CT $\rightarrow$ CSS at CT geom.]{\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/plmT32.png}}\\
\subfloat[174th mode of CT]{\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/t3_174.png}}
\subfloat[175th mode of CT]{\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/t3_175.png}}
% \caption{
% Projection of primary mode of (a) CSS $\rightarrow$ \textsuperscript{3}NAP, (b) CT $\rightarrow$ \textsuperscript{3}NAP calculated at \textsuperscript{3}NAP geometry onto the normal modes of \textsuperscript{3}NAP. Embedded molecule shows the atomic displacement vectors of primary mode. If we focus on the C$\equiv$C bonds, PLMs are like
% PTZ-Ph-C$\equiv$C-Pt-C$\protect\overset{\longleftrightarrow}{\equiv}$C-NAP
% in (a) and
% PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\longrightarrow}{C}\equiv\protect\overset{\longleftarrow}{C}$-NAP
% in (b).}
\end{figure}
\lyxframeend{}

% \lyxframeend{}\lyxframe{Dominant Normal Mode}

% \begin{figure}[]
% \subfloat[174th mode of \textsuperscript{3}NAP]{\includegraphics[height=0.28\textheight,keepaspectratio]{Chapters/chap4/Images/t1_174.jpg}}
% \subfloat[175th mode of \textsuperscript{3}NAP]{\includegraphics[height=0.28\textheight,keepaspectratio]{Chapters/chap4/Images/t1_175.jpg}}\\
% \subfloat[174th mode of CT]{\includegraphics[height=0.28\textheight,keepaspectratio]{Chapters/chap4/Images/t3_174.jpg}}
% \subfloat[175th mode of CT]{\includegraphics[height=0.28\textheight,keepaspectratio]{Chapters/chap4/Images/t3_175.jpg}}
% \end{figure}
% \lyxframeend{}

\lyxframeend{}\lyxframe{Condon Approximation}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{Chapters/chap4/Images/interpolation.pdf}
\caption{Diabatic coupling values along the interpolation from the \textsuperscript{3}NAP $\rightarrow$ CT geometries. State 0 and 10 stand for the \textsuperscript{3}NAP and the CT state, respectively.\label{interCondon}}
\end{figure}
\lyxframeend{}

\lyxframeend{}\lyxframe{Rate Constants}

\begin{figure}[t]
\includegraphics[width=0.9\columnwidth]{Chapters/chap4/Images/kTCLME-VS-EXPT.pdf}
% \caption{The energy diagram of triplet states at \textsuperscript{3}NAP and CT state geometries. The electron/hole distribution are shown as well (green for electron, blue for hole). The arrows indicate the transitions we calculate.
% }
\end{figure}
\lyxframeend{}

% Old slides

% \lyxframeend{}\lyxframe{Projected Modes: Destructive Interference}

% \begin{figure}[t]

% \begin{centering}
% \includegraphics[width=0.49\textwidth]{fig/mode/234modes150fs}\includegraphics[width=0.49\textwidth]{fig/mode/567modes150fs}
% \par\end{centering}

% \begin{centering}
% \includegraphics[width=0.49\textwidth]{fig/mode/8to11modes150fs}\includegraphics[width=0.49\textwidth]{fig/mode/14711modes150fs}
% \par\end{centering}

% \end{figure}

% \lyxframeend{}

% \lyxframeend{}\lyxframe{Projected Modes: Random Modes and Others}

% \begin{figure}

% \begin{centering}
% \subfloat[Random modes]{\begin{centering}
% \includegraphics[width=0.4\textwidth]{fig/mode/random40to70}
% \par\end{centering}

% }\subfloat[Stongest coupled modes]{\begin{centering}
% \includegraphics[width=0.4\textwidth]{fig/mode/strongcoup}
% \par\end{centering}

% }
% \par\end{centering}

% \begin{centering}
% \includegraphics[width=0.49\textwidth]{fig/mode/70random4711}\includegraphics[width=0.49\textwidth]{fig/mode/rhl60modes}
% \par\end{centering}

% \end{figure}

% \lyxframeend{}

% \lyxframeend{}\lyxframe{Analysis of 4 Modes: Mode 1 \& 2}

% \begin{center}
% \includegraphics[bb=40bp 40bp 744bp 250bp,clip,width=0.9\textwidth]{\string"fig/4 modes/4\string".jpeg}
% \par\end{center}

% \begin{center}
% $\omega=0.10eV;g=0.14eV$
% \par\end{center}

% \begin{center}
% \includegraphics[bb=20bp 50bp 724bp 260bp,clip,width=0.9\textwidth]{\string"fig/4 modes/3\string".jpg}
% \par\end{center}

% \begin{center}
% $\omega=0.17eV;g=0.29eV$
% \par\end{center}

% \lyxframeend{}

% \lyxframeend{}\lyxframe{Analysis of 4 Modes: Mode 3 \& 4}

% \begin{center}
% \includegraphics[bb=10bp 72bp 720bp 276bp,clip,width=0.9\textwidth]{\string"fig/4 modes/2\string".jpeg}
% \par\end{center}

% \begin{center}
% $\omega=0.23eV;g=-0.13eV$
% \par\end{center}

% \begin{center}
% \includegraphics[bb=85bp 50bp 730bp 320bp,clip,width=0.9\textwidth]{\string"fig/4 modes/1\string".jpeg}
% \par\end{center}

% \begin{center}
% $\omega=0.41eV;g=0.03eV$
% \par\end{center}

% \lyxframeend{}

% \lyxframeend{}\lyxframe{Analysis of 4 Modes:Projection onto Normal Modes}

% \begin{figure}

% \includegraphics[width=0.48\textwidth]{fig/mode/freq}\includegraphics[width=0.48\textwidth]{\string"fig/4 modes/proj1\string".pdf}

% \includegraphics[width=0.33\textwidth]{\string"fig/4 modes/proj2\string".pdf}\includegraphics[width=0.33\textwidth]{\string"fig/4 modes/proj3\string".pdf}\includegraphics[width=0.33\textwidth]{\string"fig/4 modes/proj4\string".pdf}

% \end{figure}

% \lyxframeend{}

\lyxframeend{}\lyxframe{Conclusions \& Future Work}

A general approach for electron
energy transfer is developed. It
\begin{itemize}
\item agrees with experiments and previous theoretical studies
% \item can go beyond Condon approximation easily
\item treats normal modes explicitly, which enables us to analyze them in
detail
\end{itemize}
In the future, we will
\begin{itemize}
\item investigate the regime where Condon approximation fails and how to correct
\item apply it to more complicated system
\item help to design IR-controllable molecules
\end{itemize}

\lyxframeend{}
\end{document}

### 2016-04-25 Chapters/chap4/chap4.tex
Correct the size of images

@@
-%!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
+%!TEX root = /Users/tcya/Dropbox/XunmoYang/PhDthesis/thesis.tex
 \chapter{Application on More Complex Molecules}\label{chap:chapt4}
@@
 \begin{figure*}[]
-\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/parabola.jpg}
+\includegraphics[width=0.44\columnwidth]{Chapters/chap4/Images/parabola.jpg}
 \caption{Calculated energies of the CT (black), CSS (blue) and \textsuperscript{3}NAP (red) states along the NAP side C$\equiv$C coordinate in the ground state geometries of the molecules studied, in CH\textsubscript{2}Cl\textsubscript{2}.
@@
 \begin{figure}[]
-\subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
-\subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT13.png}}
+\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
+\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT13.png}}
 % \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
@@
 % \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.png}}
-\subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
-\subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT32.png}}
+\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
+\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT32.png}}
 \caption{

### 2016-04-27 Chapters/chap1/introduction.tex
Revision
Revision according to college readers

@@
-%!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
-\chapter{Introduction}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}
+%!TEX root = /Users/tcya/Dropbox/XunmoYang/PhDthesis/thesis.tex
+\chapter{Introduction}\footnotetext{Part of this chapter has been published in Xunmo Yang and E.
+R.
+Bittner, Intramolecular Charge- and Energy-Transfer Rates with Reduced Modes: Comparison to Marcus Theory for Donor–Bridge–Acceptor Systems.
+The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}
 \section{Introduction}
@@
 state-to-state rates in which the coupling between  states depends upon the
-nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
-mechanical treatment of both the nuclear and electronic degrees of freedom and recovers the
+nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum-mechanical treatment of both the nuclear and electronic degrees of freedom and recovers the
 well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
@@
 \cite{tamura2008phonon,tamura2007exciton,bittner2014noise,singh2009fluorescence}.
-Our work here represents the first time this approach has been used within the context of a fully {\em ab initio} quantum
-chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
-using state-of-the-art quantum chemical methods
+Our work here represents the first time this approach has been used within the context of a fully {\em ab initio} quantum-chemical model.
+As such, this present work provides an important benchmark of the approach since all parameters will be determined
+using state-of-the-art quantum-chemical methods
 and results compared to both theoretical and experimental
@@
 \begin{figure}[!t]
-\includegraphics[width=0.95\columnwidth]{Chapters/chap2/adia_vs_diabatic.png}
-\caption{Sketch of adiabatic and diabatic representations for two-state system. Compared to adiabatic representation, diabatic representation has smoother energy surfaces and couplings.
+\includegraphics[width=0.95\columnwidth]{Chapters/chap2/adia_vs_diabatic.pdf}
+\caption{Sketch of adiabatic and diabatic representations for two-state system. Compared to adiabatic representations, diabatic representation has smoother energy surfaces and couplings.
 }

### 2016-04-27 Chapters/chap4/chap4.tex
Revision according to college readers

@@
 For PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can be fully suppressed by intermediate infrared excitation.
-Reprinted with permission from Ref.~\cite{delor2015mechanism}.\label{ETscheme}}
+Adapted with permission from Ref.~\cite{delor2015mechanism}.\label{ETscheme}}
 \end{figure*}
@@
 \begin{figure}[]
-\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
-\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT13.png}}
-% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
-% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT32.png}}
+\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT12.pdf}}\\
+\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT13.pdf}}
+% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.pdf}}\\
+% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT32.pdf}}
 \caption{
@@
 \begin{figure}[]
-% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
-% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.png}}
-\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
-\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT32.png}}
+% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.pdf}}\\
+% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.pdf}}
+\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT31.pdf}}\\
+\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT32.pdf}}
 \caption{

### 2016-04-27 FrontBackmatter/Abstract.tex
Revision according to college readers

@@
 We present a new, fully {\em ab initio} approach for computing intramolecular charge and
-energy transfer rates.  Using a time-convolutionless master equation approach, parameterized
-with couplings obtained from an accurate quantum chemical approach, we  benchmark the approach
+energy transfer rates.  Using a time-convolutionless master-equation approach, parameterized
+with couplings obtained from an accurate quantum-chemical approach, we  benchmark the approach
 against  experimental results and predictions from Marcus theory for triplet energy transfer for a

### 2016-05-11 Chapters/chap4/chap4.tex
Fix too large figs

@@
 \begin{figure}[]
-\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT12.pdf}}\\
-\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT13.pdf}}
-% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.pdf}}\\
-% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT32.pdf}}
+\subfloat[]{\includegraphics[width=0.75\columnwidth]{Chapters/chap4/Images/plmT12.pdf}}\\
+\subfloat[]{\includegraphics[width=0.75\columnwidth]{Chapters/chap4/Images/plmT13.pdf}}
+% \subfloat[]{\includegraphics[width=0.758\columnwidth]{Chapters/chap4/Images/plmT31.pdf}}\\
+% \subfloat[]{\includegraphics[width=0.758\columnwidth]{Chapters/chap4/Images/plmT32.pdf}}
 \caption{
@@
 \begin{figure}[]
-% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.pdf}}\\
-% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.pdf}}
-\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT31.pdf}}\\
-\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT32.pdf}}
+% \subfloat[]{\includegraphics[width=0.759\columnwidth]{Chapters/chap4/Images/plmT12.pdf}}\\
+% \subfloat[]{\includegraphics[width=0.759\columnwidth]{Chapters/chap4/Images/plmT13.pdf}}
+\subfloat[]{\includegraphics[width=0.75\columnwidth]{Chapters/chap4/Images/plmT31.pdf}}\\
+\subfloat[]{\includegraphics[width=0.75\columnwidth]{Chapters/chap4/Images/plmT32.pdf}}
 \caption{
